### 2019-09-16 analyses/analyses.Rmd
- setting up of novel git-hub repository in order to not include person-related data of prior repository

---
title: "A Longitudinal Analysis of the Privacy Paradox"
author: "Tobias Dienlin, Philipp K. Masur, Sabine Trepte"
output: 
  # pdf_document: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
editor_options: 
  chunk_output_type: inline
---

```{r, echo = FALSE, include = FALSE}
# defaults
set.seed(170819)
options(digits = 3, width = 120, max.print = 100000)
knitr::opts_chunk$set(echo = T, error = F, message = F, tidy = T, warning = F, cache = T)
```

```{r Packages, include = FALSE, cache=F}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", "papaja", "psych", "pwr", "RVAideMemoire", "semTools", 
              "sjstats", "tidyverse", "td")

# load required libraries
lapply(required, function(x) library(x, character.only = T))

# export bib library
r_refs("../bibliography/r-references.bib")
```

```{r datawrangling, include=F}
# first run "data_wranling.R", in order to create these objects
d_wide <- read_csv("../data/data_wide.csv")
d_wide_all <- read_csv("../data/data_wide_all.csv")
d_long <- read_csv("../data/data_long.csv")
```

```{r include=FALSE}
# Extract descriptives to report in paper
desc <- d_wide %>% 
  summarize_at(vars(ends_with("_m")), funs(mean(., na.rm = TRUE), sd(., na.rm = TRUE)))
```

# Items
## Privacy Concern

The following deals with things that can happen on the Internet.

1. In general, how concerned are you about your privacy while using the Internet?
2. Are you concerned about online organizations not being who they claim they are?
3. Are you concerned about online identity theft?
4. Are you concerned about people you do not know obtaining personal information about you from your online activities?
5. Are you concerned that if you use your credit card to buy something on the Internet your credit card number will be obtained/intercepted by someone else?
6. Are you concerned that an email you sent may be read by someone else besides the person you sent it to?
7. Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing on the Internet?
8. Are you concerned that website providers are tracking your online activities?
9. Are you concerned that you don’t know what other organizations or website providers are doing with you data?

(NA = "no Internet user / no reply", 1 = "Not concerned at all" : 5 = "very concerned")

## Attitude Toward Online Sharing of Personal Information

Now we will deal with information sharing on the Internet. Do you think that it is sensible to disclose the following pieces of information online, i.e., via the Internet?

1. Financial information (bank data, account balances…)
2. Medical information (health, medical records…)
3. Second name
4. First name
5. Residence
6. Street and house number
7. Email address
8. Phone number
9. Photos (of you)
10. Job (past and present)
11. Education

(NA = “no Internet user / no reply”, 1 = "not sensible at all", 2 = "somewhat not sensible", 3 = "in part", 4 = "somewhat sensible", 5 = "very sensible")

## Online Sharing of Personal Information

In the following, please indicate how often you disclose the following information on the Internet. How often do you disclose the following pieces of information online, i.e., on the Internet?

1. Financial information (bank data, account balances…)
2. Medical information (health, medical records…)
3. Second name
4. First name
5. Residence
6. Street and house number
7. Email address
8. Phone number
9. Photos (of you)
10. Job (past and present)
11. Education

(NA = “no Internet user / no reply”, 1 = "every day", 2 = "weekly", 3 = "monthly", 4 = "less than that", 5 = "never")

# Power Analyses

```{r power}
n_complete <- nrow(d_wide)
alpha <- .05
power <- .95
sesoi <- .1
n <- n_complete
n_apriori <- pwr.r.test(r = sesoi, sig.level = alpha, power = power)$n
power_achieved_h <- pwr.r.test(r = sesoi, sig.level = alpha, n = n, alternative = "greater")$power
alpha_balanced_h <- balance_errors(sesoi, n, one_tailed = TRUE)
power_balanced_h <- 1 - alpha_balanced_h
power_achieved_rq <- pwr.r.test(r = sesoi, sig.level = alpha, n = n)$power
alpha_balanced_rq <- balance_errors(sesoi, n, one_tailed = FALSE)
power_balanced_rq <- 1 - alpha_balanced_rq
```

A-priori power analyses revealed that N = `r n_apriori` people would be needed to find effects with a size of _r_ = `r sesoi` with a power of `r power`.

Overall, the data of `r n` respondents could be used for our analyses. As a result, alpha and beta errors were balanced when using an alpha of `r alpha_balanced_h %>% round(3)`, resulting in an achieved power of `r power_balanced_h %>% round(3)`.

# Sociodemographics

```{r}
age_m <- mean(d_wide$age)
age_sd <- sd(d_wide$age)
male_per <- mean(d_wide$male)
edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100
```

# Analysis of Missing Values

```{r}
d_tmp <- select(d_wide, -contains("_m"), -contains("tim"), -contains("T4"), -contains("T5"), -contains("per"), -contains("use"), -c(id, age, edu, edu_num, male))
(test_mar <- TestMCARNormality(d_tmp))
test_mar_p <- test_mar$pnormality

# calculate percentage of missing data
na_per <- mean(c(d_wide$t1_na_per, d_wide$t2_na_per, d_wide$t3_na_per)) * 100
```

Visual inspection of the missing value patterns as well as the non-parametric test suggested that all missing values could be considered to be missing at random (_p_ `r test_mar$pnormality %>% td::my_round("p_txt")`).

# Factor Analyses
## Concerns about online privacy
### EFA

```{r}
# set-up
no <- 0
name <- "pri_con"
d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
print(factan, sort = TRUE, cut = .3)
```

### CFA
#### First-Order Model Unconstrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_01 + t1_pri_con_02 + t1_pri_con_03 + t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06 + t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
t2_pri_con_f =~ 1*t2_pri_con_01 + t2_pri_con_02 + t2_pri_con_03 + t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06 + t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
t3_pri_con_f =~ 1*t3_pri_con_01 + t3_pri_con_02 + t3_pri_con_03 + t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06 + t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09

# error covariances
t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_01 ~~ t1_pri_con_01
t2_pri_con_02 ~~ t1_pri_con_02 
t2_pri_con_03 ~~ t1_pri_con_03
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### First-Order Model Constrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_01 + b2*t1_pri_con_02 + b3*t1_pri_con_03 + b4*t1_pri_con_04 + b5*t1_pri_con_05 + b6*t1_pri_con_06 + b7*t1_pri_con_07 + b8*t1_pri_con_08 + b9*t1_pri_con_09
t2_pri_con_f =~ 1*t2_pri_con_01 + b2*t2_pri_con_02 + b3*t2_pri_con_03 + b4*t2_pri_con_04 + b5*t2_pri_con_05 + b6*t2_pri_con_06 + b7*t2_pri_con_07 + b8*t2_pri_con_08 + b9*t2_pri_con_09
t3_pri_con_f =~ 1*t3_pri_con_01 + b2*t3_pri_con_02 + b3*t3_pri_con_03 + b4*t3_pri_con_04 + b5*t3_pri_con_05 + b6*t3_pri_con_06 + b7*t3_pri_con_07 + b8*t3_pri_con_08 + b9*t3_pri_con_09

# error covariances
t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_01 ~~ t1_pri_con_01
t2_pri_con_02 ~~ t1_pri_con_02 
t2_pri_con_03 ~~ t1_pri_con_03
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### Longitudinal Invariance

```{r}
anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_")))
```

#### Second-Order Model Unconstrained

In what follows, we analyze a second-order solution of privacy concerns. Here, we distinguish between horizontal privacy concerns (items 4, 5, 6) and vertical privacy concerns (items 7, 8, 9). The resulting model fits the data better than the unidimensional one.

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_f1 + t1_pri_con_f2
t2_pri_con_f =~ 1*t2_pri_con_f1 + t2_pri_con_f2
t3_pri_con_f =~ 1*t3_pri_con_f1 + t3_pri_con_f2
t1_pri_con_f1 =~ 1*t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06
t1_pri_con_f2 =~ 1*t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
t2_pri_con_f1 =~ 1*t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06
t2_pri_con_f2 =~ 1*t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
t3_pri_con_f1 =~ 1*t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06
t3_pri_con_f2 =~ 1*t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09

# error covariances
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### Second-Order Model Constrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
t2_pri_con_f =~ 1*t2_pri_con_f1 + a2*t2_pri_con_f2
t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
t2_pri_con_f1 =~ 1*t2_pri_con_04 + b2*t2_pri_con_05 + b3*t2_pri_con_06
t2_pri_con_f2 =~ 1*t2_pri_con_07 + c2*t2_pri_con_08 + c3*t2_pri_con_09
t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09

# error covariances
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### Longitudinal Invariance

```{r}
anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_")))
```

## Attitude Toward Online Sharing of Personal Information
### EFA

```{r}
no <- 0
name <- "inf_sha_att"
d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
print(factan, sort = TRUE, cut = .3)
```

### CFA
#### First-Order Model Unconstrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_01 + t1_pri_con_02 + t1_pri_con_03 + t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06 + t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
t2_pri_con_f =~ 1*t2_pri_con_01 + t2_pri_con_02 + t2_pri_con_03 + t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06 + t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
t3_pri_con_f =~ 1*t3_pri_con_01 + t3_pri_con_02 + t3_pri_con_03 + t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06 + t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09

# error covariances
t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_01 ~~ t1_pri_con_01
t2_pri_con_02 ~~ t1_pri_con_02 
t2_pri_con_03 ~~ t1_pri_con_03
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### First-Order Model Constrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_01 + a2*t1_pri_con_02 + a3*t1_pri_con_03 + a4*t1_pri_con_04 + a5*t1_pri_con_05 + a6*t1_pri_con_06 + a7*t1_pri_con_07 + a8*t1_pri_con_08 + a9*t1_pri_con_09
t2_pri_con_f =~ 1*t2_pri_con_01 + a2*t2_pri_con_02 + a3*t2_pri_con_03 + a4*t2_pri_con_04 + a5*t2_pri_con_05 + a6*t2_pri_con_06 + a7*t2_pri_con_07 + a8*t2_pri_con_08 + a9*t2_pri_con_09
t3_pri_con_f =~ 1*t3_pri_con_01 + a2*t3_pri_con_02 + a3*t3_pri_con_03 + a4*t3_pri_con_04 + a5*t3_pri_con_05 + a6*t3_pri_con_06 + a7*t3_pri_con_07 + a8*t3_pri_con_08 + a9*t3_pri_con_09

# error covariances
t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_01 ~~ t1_pri_con_01
t2_pri_con_02 ~~ t1_pri_con_02 
t2_pri_con_03 ~~ t1_pri_con_03
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### Longitudinal Invariance

```{r}
anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_")))
```

#### Second-Order Model Unconstrained

We again run models in which we build sub-dimensions referring to the empirical EFA results and theoretical considerations. Resulting model fits the data better than unidimensional one.

```{r}
model <- '
# create factors
t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + t1_inf_sha_att_f2 + t1_inf_sha_att_f3 + t1_inf_sha_att_f4 + t1_inf_sha_att_f5
t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + t2_inf_sha_att_f2 + t2_inf_sha_att_f3 + t2_inf_sha_att_f4 + t2_inf_sha_att_f5
t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + t3_inf_sha_att_f2 + t3_inf_sha_att_f3 + t3_inf_sha_att_f4 + t3_inf_sha_att_f5
t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + t1_inf_sha_att_02
t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + t1_inf_sha_att_04
t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + t1_inf_sha_att_06
t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + t1_inf_sha_att_08
t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + t1_inf_sha_att_11
t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + t2_inf_sha_att_02
t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + t2_inf_sha_att_04
t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + t2_inf_sha_att_06
t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + t2_inf_sha_att_08
t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + t2_inf_sha_att_11
t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + t3_inf_sha_att_02
t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + t3_inf_sha_att_04
t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + t3_inf_sha_att_06
t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + t3_inf_sha_att_08
t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + t3_inf_sha_att_11

# factor covariance
t1_inf_sha_att_f ~~ t2_inf_sha_att_f + t3_inf_sha_att_f
t2_inf_sha_att_f ~~ t3_inf_sha_att_f

# item error covariance
t1_inf_sha_att_01 ~~ t2_inf_sha_att_01 + t3_inf_sha_att_01
t2_inf_sha_att_01 ~~ t3_inf_sha_att_01
t1_inf_sha_att_02 ~~ t2_inf_sha_att_02 + t3_inf_sha_att_02
t2_inf_sha_att_02 ~~ t3_inf_sha_att_02
t1_inf_sha_att_03 ~~ t2_inf_sha_att_03 + t3_inf_sha_att_03
t2_inf_sha_att_03 ~~ t3_inf_sha_att_03
t1_inf_sha_att_04 ~~ t2_inf_sha_att_04 + t3_inf_sha_att_04
t2_inf_sha_att_04 ~~ t3_inf_sha_att_04
t1_inf_sha_att_05 ~~ t2_inf_sha_att_05 + t3_inf_sha_att_05
t2_inf_sha_att_05 ~~ t3_inf_sha_att_05
t1_inf_sha_att_06 ~~ t2_inf_sha_att_06 + t3_inf_sha_att_06
t2_inf_sha_att_06 ~~ t3_inf_sha_att_06
t1_inf_sha_att_07 ~~ t2_inf_sha_att_07 + t3_inf_sha_att_07
t2_inf_sha_att_07 ~~ t3_inf_sha_att_07
t1_inf_sha_att_08 ~~ t2_inf_sha_att_08 + t3_inf_sha_att_08
t2_inf_sha_att_08 ~~ t3_inf_sha_att_08
t1_inf_sha_att_10 ~~ t2_inf_sha_att_10 + t3_inf_sha_att_10
t2_inf_sha_att_10 ~~ t3_inf_sha_att_10
t1_inf_sha_att_11 ~~ t2_inf_sha_att_11 + t3_inf_sha_att_11
t2_inf_sha_att_11 ~~ t3_inf_sha_att_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### Second-Order Model at All Waves Constrained

```{r}
model <- '
# create factors
t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + o2*t1_inf_sha_att_f2 + o3*t1_inf_sha_att_f3 + o4*t1_inf_sha_att_f4 + o5*t1_inf_sha_att_f5
t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + o2*t2_inf_sha_att_f2 + o3*t2_inf_sha_att_f3 + o4*t2_inf_sha_att_f4 + o5*t2_inf_sha_att_f5
t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + o2*t3_inf_sha_att_f2 + o3*t3_inf_sha_att_f3 + o4*t3_inf_sha_att_f4 + o5*t3_inf_sha_att_f5
t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + j2*t1_inf_sha_att_02
t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + k2*t1_inf_sha_att_04
t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + l2*t1_inf_sha_att_06
t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + m2*t1_inf_sha_att_08
t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + n2*t1_inf_sha_att_11
t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + j2*t2_inf_sha_att_02
t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + k2*t2_inf_sha_att_04
t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + l2*t2_inf_sha_att_06
t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + m2*t2_inf_sha_att_08
t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + n2*t2_inf_sha_att_11
t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + j2*t3_inf_sha_att_02
t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + k2*t3_inf_sha_att_04
t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + l2*t3_inf_sha_att_06
t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + m2*t3_inf_sha_att_08
t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + n2*t3_inf_sha_att_11

# factor covariance
t1_inf_sha_att_f ~~ t2_inf_sha_att_f + t3_inf_sha_att_f
t2_inf_sha_att_f ~~ t3_inf_sha_att_f

# item error covariance
t1_inf_sha_att_01 ~~ t2_inf_sha_att_01 + t3_inf_sha_att_01
t2_inf_sha_att_01 ~~ t3_inf_sha_att_01
t1_inf_sha_att_02 ~~ t2_inf_sha_att_02 + t3_inf_sha_att_02
t2_inf_sha_att_02 ~~ t3_inf_sha_att_02
t1_inf_sha_att_03 ~~ t2_inf_sha_att_03 + t3_inf_sha_att_03
t2_inf_sha_att_03 ~~ t3_inf_sha_att_03
t1_inf_sha_att_04 ~~ t2_inf_sha_att_04 + t3_inf_sha_att_04
t2_inf_sha_att_04 ~~ t3_inf_sha_att_04
t1_inf_sha_att_05 ~~ t2_inf_sha_att_05 + t3_inf_sha_att_05
t2_inf_sha_att_05 ~~ t3_inf_sha_att_05
t1_inf_sha_att_06 ~~ t2_inf_sha_att_06 + t3_inf_sha_att_06
t2_inf_sha_att_06 ~~ t3_inf_sha_att_06
t1_inf_sha_att_07 ~~ t2_inf_sha_att_07 + t3_inf_sha_att_07
t2_inf_sha_att_07 ~~ t3_inf_sha_att_07
t1_inf_sha_att_08 ~~ t2_inf_sha_att_08 + t3_inf_sha_att_08
t2_inf_sha_att_08 ~~ t3_inf_sha_att_08
t1_inf_sha_att_10 ~~ t2_inf_sha_att_10 + t3_inf_sha_att_10
t2_inf_sha_att_10 ~~ t3_inf_sha_att_10
t1_inf_sha_att_11 ~~ t2_inf_sha_att_11 + t3_inf_sha_att_11
t2_inf_sha_att_11 ~~ t3_inf_sha_att_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### Longitudinal Invariance

```{r}
anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_")))
```

## Online Sharing of Personal Information
### EFA

```{r}
no <- 0
name <- "inf_sha_beh"
d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
print(factan, sort = TRUE, cut = .3)
```
### CFA
#### First-Order Model Unconstrained

First-order model shows poor fit. Needs to be adapted (see second order model).

```{r}
model <- '
# create factors
t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_01 + t1_inf_sha_beh_02 + t1_inf_sha_beh_03 + t1_inf_sha_beh_04 + t1_inf_sha_beh_05 + t1_inf_sha_beh_06 + t1_inf_sha_beh_07 + t1_inf_sha_beh_08 + t1_inf_sha_beh_09 + t1_inf_sha_beh_10 + t1_inf_sha_beh_11
t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_01 + t2_inf_sha_beh_02 + t2_inf_sha_beh_03 + t2_inf_sha_beh_04 + t2_inf_sha_beh_05 + t2_inf_sha_beh_06 + t2_inf_sha_beh_07 + t2_inf_sha_beh_08 + t2_inf_sha_beh_09 + t2_inf_sha_beh_10 + t2_inf_sha_beh_11
t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_01 + t3_inf_sha_beh_02 + t3_inf_sha_beh_03 + t3_inf_sha_beh_04 + t3_inf_sha_beh_05 + t3_inf_sha_beh_06 + t3_inf_sha_beh_07 + t3_inf_sha_beh_08 + t3_inf_sha_beh_09 + t3_inf_sha_beh_10 + t3_inf_sha_beh_11

# factor covariance
t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f

# item error covariance
t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
t1_inf_sha_beh_09 ~~ t2_inf_sha_beh_09 + t3_inf_sha_beh_09
t2_inf_sha_beh_09 ~~ t3_inf_sha_beh_09
t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### First-Order Model Constrained

```{r}
model <- '
# create factors
t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_01 + c2*t1_inf_sha_beh_02 + c3*t1_inf_sha_beh_03 + c4*t1_inf_sha_beh_04 + c5*t1_inf_sha_beh_05 + c6*t1_inf_sha_beh_06 + c7*t1_inf_sha_beh_07 + c8*t1_inf_sha_beh_08 + c9*t1_inf_sha_beh_09 + c10*t1_inf_sha_beh_10 + c11*t1_inf_sha_beh_11
t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_01 + c2*t2_inf_sha_beh_02 + c3*t2_inf_sha_beh_03 + c4*t2_inf_sha_beh_04 + c5*t2_inf_sha_beh_05 + c6*t2_inf_sha_beh_06 + c7*t2_inf_sha_beh_07 + c8*t2_inf_sha_beh_08 + c9*t2_inf_sha_beh_09 + c10*t2_inf_sha_beh_10 + c11*t2_inf_sha_beh_11
t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_01 + c2*t3_inf_sha_beh_02 + c3*t3_inf_sha_beh_03 + c4*t3_inf_sha_beh_04 + c5*t3_inf_sha_beh_05 + c6*t3_inf_sha_beh_06 + c7*t3_inf_sha_beh_07 + c8*t3_inf_sha_beh_08 + c9*t3_inf_sha_beh_09 + c10*t3_inf_sha_beh_10 + c11*t3_inf_sha_beh_11

# factor covariance
t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f

# item error covariance
t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
t1_inf_sha_beh_09 ~~ t2_inf_sha_beh_09 + t3_inf_sha_beh_09
t2_inf_sha_beh_09 ~~ t3_inf_sha_beh_09
t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### Longitudinal Invariance

```{r}
anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_")))
```

#### Second-Order Model Unconstrained

Second-order model shows much improved fit.

```{r}
model <- '
# create factors
t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + t1_inf_sha_beh_f2 + t1_inf_sha_beh_f3 + t1_inf_sha_beh_f4 + t1_inf_sha_beh_f5
t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_f1 + t2_inf_sha_beh_f2 + t2_inf_sha_beh_f3 + t2_inf_sha_beh_f4 + t2_inf_sha_beh_f5
t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + t3_inf_sha_beh_f2 + t3_inf_sha_beh_f3 + t3_inf_sha_beh_f4 + t3_inf_sha_beh_f5
t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + t1_inf_sha_beh_02
t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + t1_inf_sha_beh_04
t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + t1_inf_sha_beh_06
t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + t1_inf_sha_beh_08
t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + t1_inf_sha_beh_11
t2_inf_sha_beh_f1 =~ 1*t2_inf_sha_beh_01 + t2_inf_sha_beh_02
t2_inf_sha_beh_f2 =~ 1*t2_inf_sha_beh_03 + t2_inf_sha_beh_04
t2_inf_sha_beh_f3 =~ 1*t2_inf_sha_beh_05 + t2_inf_sha_beh_06
t2_inf_sha_beh_f4 =~ 1*t2_inf_sha_beh_07 + t2_inf_sha_beh_08
t2_inf_sha_beh_f5 =~ 1*t2_inf_sha_beh_10 + t2_inf_sha_beh_11
t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + t3_inf_sha_beh_02
t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + t3_inf_sha_beh_04
t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + t3_inf_sha_beh_06
t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + t3_inf_sha_beh_08
t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + t3_inf_sha_beh_11

# factor covariance
t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f

# item error covariance
t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### Second-Order Model Constrained

```{r}
model <- '
# create factors
t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + o2*t1_inf_sha_beh_f2 + o3*t1_inf_sha_beh_f3 + o4*t1_inf_sha_beh_f4 + o5*t1_inf_sha_beh_f5
t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_f1 + o2*t2_inf_sha_beh_f2 + o3*t2_inf_sha_beh_f3 + o4*t2_inf_sha_beh_f4 + o5*t2_inf_sha_beh_f5
t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + o2*t3_inf_sha_beh_f2 + o3*t3_inf_sha_beh_f3 + o4*t3_inf_sha_beh_f4 + o5*t3_inf_sha_beh_f5
t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + j2*t1_inf_sha_beh_02
t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + k2*t1_inf_sha_beh_04
t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + l2*t1_inf_sha_beh_06
t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + m2*t1_inf_sha_beh_08
t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + n2*t1_inf_sha_beh_11
t2_inf_sha_beh_f1 =~ 1*t2_inf_sha_beh_01 + j2*t2_inf_sha_beh_02
t2_inf_sha_beh_f2 =~ 1*t2_inf_sha_beh_03 + k2*t2_inf_sha_beh_04
t2_inf_sha_beh_f3 =~ 1*t2_inf_sha_beh_05 + l2*t2_inf_sha_beh_06
t2_inf_sha_beh_f4 =~ 1*t2_inf_sha_beh_07 + m2*t2_inf_sha_beh_08
t2_inf_sha_beh_f5 =~ 1*t2_inf_sha_beh_10 + n2*t2_inf_sha_beh_11
t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + j2*t3_inf_sha_beh_02
t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + k2*t3_inf_sha_beh_04
t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + l2*t3_inf_sha_beh_06
t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + m2*t3_inf_sha_beh_08
t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + n2*t3_inf_sha_beh_11

# factor covariance
t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f

# item error covariance
t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### Longitudinal Invariance

```{r}
anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_")))
```

## All Measures in one Model 
### Second Order

```{r CFA_All}
name <- "all_vars"
no <- 0
model <- '
# Privacy Concerns
# create factors
t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
t2_pri_con_f =~ 1*t2_pri_con_f1 + a2*t2_pri_con_f2
t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
t2_pri_con_f1 =~ 1*t2_pri_con_04 + b2*t2_pri_con_05 + b3*t2_pri_con_06
t2_pri_con_f2 =~ 1*t2_pri_con_07 + c2*t2_pri_con_08 + c3*t2_pri_con_09
t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09

# error covariances
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f

# Information Sharing Attitude
# create factors
t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + d2*t1_inf_sha_att_f2 + d3*t1_inf_sha_att_f3 + d4*t1_inf_sha_att_f4 + d5*t1_inf_sha_att_f5
t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + d2*t2_inf_sha_att_f2 + d3*t2_inf_sha_att_f3 + d4*t2_inf_sha_att_f4 + d5*t2_inf_sha_att_f5
t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + d2*t3_inf_sha_att_f2 + d3*t3_inf_sha_att_f3 + d4*t3_inf_sha_att_f4 + d5*t3_inf_sha_att_f5
t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + e*t1_inf_sha_att_02
t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + f*t1_inf_sha_att_04
t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + g*t1_inf_sha_att_06
t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + h*t1_inf_sha_att_08
t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + i*t1_inf_sha_att_11
t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + e*t2_inf_sha_att_02
t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + f*t2_inf_sha_att_04
t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + g*t2_inf_sha_att_06
t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + h*t2_inf_sha_att_08
t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + i*t2_inf_sha_att_11
t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + e*t3_inf_sha_att_02
t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + f*t3_inf_sha_att_04
t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + g*t3_inf_sha_att_06
t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + h*t3_inf_sha_att_08
t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + i*t3_inf_sha_att_11

# factor covariance
t1_inf_sha_att_f ~~ t2_inf_sha_att_f + t3_inf_sha_att_f
t2_inf_sha_att_f ~~ t3_inf_sha_att_f

# item error covariance
t1_inf_sha_att_01 ~~ t2_inf_sha_att_01 + t3_inf_sha_att_01
t2_inf_sha_att_01 ~~ t3_inf_sha_att_01
t1_inf_sha_att_02 ~~ t2_inf_sha_att_02 + t3_inf_sha_att_02
t2_inf_sha_att_02 ~~ t3_inf_sha_att_02
t1_inf_sha_att_03 ~~ t2_inf_sha_att_03 + t3_inf_sha_att_03
t2_inf_sha_att_03 ~~ t3_inf_sha_att_03
t1_inf_sha_att_04 ~~ t2_inf_sha_att_04 + t3_inf_sha_att_04
t2_inf_sha_att_04 ~~ t3_inf_sha_att_04
t1_inf_sha_att_05 ~~ t2_inf_sha_att_05 + t3_inf_sha_att_05
t2_inf_sha_att_05 ~~ t3_inf_sha_att_05
t1_inf_sha_att_06 ~~ t2_inf_sha_att_06 + t3_inf_sha_att_06
t2_inf_sha_att_06 ~~ t3_inf_sha_att_06
t1_inf_sha_att_07 ~~ t2_inf_sha_att_07 + t3_inf_sha_att_07
t2_inf_sha_att_07 ~~ t3_inf_sha_att_07
t1_inf_sha_att_08 ~~ t2_inf_sha_att_08 + t3_inf_sha_att_08
t2_inf_sha_att_08 ~~ t3_inf_sha_att_08
t1_inf_sha_att_10 ~~ t2_inf_sha_att_10 + t3_inf_sha_att_10
t2_inf_sha_att_10 ~~ t3_inf_sha_att_10
t1_inf_sha_att_11 ~~ t2_inf_sha_att_11 + t3_inf_sha_att_11
t2_inf_sha_att_11 ~~ t3_inf_sha_att_11

# information sharing behavior
# create factors
t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + o2*t1_inf_sha_beh_f2 + o3*t1_inf_sha_beh_f3 + o4*t1_inf_sha_beh_f4 + o5*t1_inf_sha_beh_f5
t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_f1 + o2*t2_inf_sha_beh_f2 + o3*t2_inf_sha_beh_f3 + o4*t2_inf_sha_beh_f4 + o5*t2_inf_sha_beh_f5
t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + o2*t3_inf_sha_beh_f2 + o3*t3_inf_sha_beh_f3 + o4*t3_inf_sha_beh_f4 + o5*t3_inf_sha_beh_f5
t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + j2*t1_inf_sha_beh_02
t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + k2*t1_inf_sha_beh_04
t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + l2*t1_inf_sha_beh_06
t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + m2*t1_inf_sha_beh_08
t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + n2*t1_inf_sha_beh_11
t2_inf_sha_beh_f1 =~ 1*t2_inf_sha_beh_01 + j2*t2_inf_sha_beh_02
t2_inf_sha_beh_f2 =~ 1*t2_inf_sha_beh_03 + k2*t2_inf_sha_beh_04
t2_inf_sha_beh_f3 =~ 1*t2_inf_sha_beh_05 + l2*t2_inf_sha_beh_06
t2_inf_sha_beh_f4 =~ 1*t2_inf_sha_beh_07 + m2*t2_inf_sha_beh_08
t2_inf_sha_beh_f5 =~ 1*t2_inf_sha_beh_10 + n2*t2_inf_sha_beh_11
t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + j2*t3_inf_sha_beh_02
t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + k2*t3_inf_sha_beh_04
t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + l2*t3_inf_sha_beh_06
t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + m2*t3_inf_sha_beh_08
t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + n2*t3_inf_sha_beh_11

# factor covariance
t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f

# item error covariance
t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11

## Correlations Attitude and Behavior-Items
t1_inf_sha_beh_01 ~~ t1_inf_sha_att_01
t1_inf_sha_beh_02 ~~ t1_inf_sha_att_02
t1_inf_sha_beh_03 ~~ t1_inf_sha_att_03
t1_inf_sha_beh_04 ~~ t1_inf_sha_att_04
t1_inf_sha_beh_05 ~~ t1_inf_sha_att_05
t1_inf_sha_beh_06 ~~ t1_inf_sha_att_06
t1_inf_sha_beh_07 ~~ t1_inf_sha_att_07
t1_inf_sha_beh_08 ~~ t1_inf_sha_att_08
t1_inf_sha_beh_10 ~~ t1_inf_sha_att_10
t1_inf_sha_beh_11 ~~ t1_inf_sha_att_11
t2_inf_sha_beh_01 ~~ t2_inf_sha_att_01
t2_inf_sha_beh_02 ~~ t2_inf_sha_att_02
t2_inf_sha_beh_03 ~~ t2_inf_sha_att_03
t2_inf_sha_beh_04 ~~ t2_inf_sha_att_04
t2_inf_sha_beh_05 ~~ t2_inf_sha_att_05
t2_inf_sha_beh_06 ~~ t2_inf_sha_att_06
t2_inf_sha_beh_07 ~~ t2_inf_sha_att_07
t2_inf_sha_beh_08 ~~ t2_inf_sha_att_08
t2_inf_sha_beh_10 ~~ t2_inf_sha_att_10
t2_inf_sha_beh_11 ~~ t2_inf_sha_att_11
t3_inf_sha_beh_01 ~~ t3_inf_sha_att_01
t3_inf_sha_beh_02 ~~ t3_inf_sha_att_02
t3_inf_sha_beh_03 ~~ t3_inf_sha_att_03
t3_inf_sha_beh_04 ~~ t3_inf_sha_att_04
t3_inf_sha_beh_05 ~~ t3_inf_sha_att_05
t3_inf_sha_beh_06 ~~ t3_inf_sha_att_06
t3_inf_sha_beh_07 ~~ t3_inf_sha_att_07
t3_inf_sha_beh_08 ~~ t3_inf_sha_att_08
t3_inf_sha_beh_10 ~~ t3_inf_sha_att_10
t3_inf_sha_beh_11 ~~ t3_inf_sha_att_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

### Extract Factor Scores

```{r}
d_fs <- lavPredict(get(paste("fit", name, no, sep = "_")), type = "ov") %>% 
  as.data.frame() %>% 
  mutate(t1_pri_con_fs = rowMeans(select(., starts_with("t1_pri"))),
         t2_pri_con_fs = rowMeans(select(., starts_with("t2_pri"))),
         t3_pri_con_fs = rowMeans(select(., starts_with("t3_pri"))),
         t1_inf_sha_att_fs = rowMeans(select(., starts_with("t1_inf_sha_att"))),
         t2_inf_sha_att_fs = rowMeans(select(., starts_with("t2_inf_sha_att"))),
         t3_inf_sha_att_fs = rowMeans(select(., starts_with("t3_inf_sha_att"))),
         t1_inf_sha_beh_fs = rowMeans(select(., starts_with("t1_inf_sha_beh"))),
         t2_inf_sha_beh_fs = rowMeans(select(., starts_with("t2_inf_sha_beh"))),
         t3_inf_sha_beh_fs = rowMeans(select(., starts_with("t3_inf_sha_beh")))
         ) %>% 
  select(contains("_fs"))
d_wide <- cbind(d_fs, d_wide)
```

### Latent correlation matrix with plots

```{r Corrplot, fig.height = 8, fig.width = 8, size=5}
colnames(d_fs) <- c("Concerns\nT1", "Concerns\nT2" , "Concerns\nT3",
                    "Pos. Attitude\nT1", "Pos. Attitude\nT2" , "Pos. Attitude\nT3",
                    "Inf. Sharing\nT1", "Inf. Sharing\nT2" , "Inf. Sharing\nT3")

corr_plot <- ggpairs(d_fs,
                     # upper = list(continuous = wrap(td::cor_matrix, data = d_fs)),
                     lower = list(continuous = wrap(td::scat_plot, coords = c(1, 5, 1, 5)))) + 
  theme_bw()
print(corr_plot)
```

# ICCs

Next, we determine the Intraclass Correlation Coefficients (ICC), to determine how much variance in the measures is due to between-person differences versus within-person changes.

```{r}
fit <- lmer(pri_con_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
icc_pri_con <- icc(fit)

fit <- lmer(inf_sha_att_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
icc_inf_sha_att <- icc(fit)

fit <- lmer(inf_sha_beh_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
icc_inf_sha_beh <- icc(fit)
```

# Results

In what follows, please find all information about our final model we present in the paper.

# Additional Analyses
## RI-CLPM
### Assumptions
#### Multivariate Normal Distribution

```{r multivardis}
mult_norm_test <- mshapiro.test(d_fs)
print(mult_norm_test)
```

Results show that the assumption of multivariate normal distribution was violated. Hence, it'd be preferrable to conduct robust Maximum Likelihood Estimation. However, using robust estimation it's not possible to run SEM on all data using Full Information Maximum Likehoood (FIML). Given that we consider it more important to include as much information as possible and that estimators often produce similar results, we decided to estimate the following models using regular maximum likehood.

### Two Variables

Here, we look at the bivariate relations of privacy concerns and information sharing. This is interesting, because in the paper we also address privacy attitudes, thereby potentially attentuating the effect of privacy concerns. However, when analyzing only these two variables we do not find larger effects sizes.

#### Model 1

Here, we use regular observed means.

```{r }
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m

# intercepts
t1_pri_con_m ~ mu1*1
t2_pri_con_m ~ mu2*1
t3_pri_con_m ~ mu3*1
t1_inf_sha_beh_m ~ pi1*1
t2_inf_sha_beh_m ~ pi2*1
t3_inf_sha_beh_m ~ pi3*1

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_m
t2_pri_con_w =~ 1*t2_pri_con_m
t3_pri_con_w =~ 1*t3_pri_con_m
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m

# estimate variances
pri_con_b ~~ pri_con_b
inf_sha_beh_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_pri_con_w
t2_pri_con_w ~~ t2_pri_con_w
t3_pri_con_w ~~ t3_pri_con_w
t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w

# within person effects
t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w

# covariances
pri_con_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_beh_w
'

fit <- lavaan(model, data = d_wide, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE)
```

#### Model 2

Model with a (broad) single item measure of privacy concerns ("In general, how concerned are you about your privacy while using the Internet?").

```{r }
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_01 + 1*t2_pri_con_01 + 1*t3_pri_con_01
inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m

# intercepts
t1_pri_con_01 ~ mu1*1
t2_pri_con_01 ~ mu2*1
t3_pri_con_01 ~ mu3*1
t1_inf_sha_beh_m ~ pi1*1
t2_inf_sha_beh_m ~ pi2*1
t3_inf_sha_beh_m ~ pi3*1

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_01
t2_pri_con_w =~ 1*t2_pri_con_01
t3_pri_con_w =~ 1*t3_pri_con_01
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m

# estimate variances
pri_con_b ~~ pri_con_b
inf_sha_beh_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_pri_con_w
t2_pri_con_w ~~ t2_pri_con_w
t3_pri_con_w ~~ t3_pri_con_w
t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w

# within person effects
t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w

# covariances
pri_con_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_beh_w
'

fit <- lavaan(model, data = d_wide, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE)
```

#### Model 3

With Factor Scores.

```{r}
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs

# intercepts
t1_pri_con_fs ~ 1
t2_pri_con_fs ~ 1
t3_pri_con_fs ~ 1
t1_inf_sha_beh_fs ~ 1
t2_inf_sha_beh_fs ~ 1
t3_inf_sha_beh_fs ~ 1

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_fs
t2_pri_con_w =~ 1*t2_pri_con_fs
t3_pri_con_w =~ 1*t3_pri_con_fs
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs

# estimate variances
pri_con_b ~~ pri_con_b
inf_sha_beh_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_pri_con_w
t2_pri_con_w ~~ t2_pri_con_w
t3_pri_con_w ~~ t3_pri_con_w
t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w

# within person effects
t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w

# covariances
pri_con_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_beh_w
'
fit <- lavaan(model, data = d_wide)
summary(fit, standardized = TRUE, fit.measures = TRUE)
```

#### Model 4

With Factor Scores and Control Variables.

```{r}
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs

# intercepts
t1_pri_con_fs ~ 1
t2_pri_con_fs ~ 1
t3_pri_con_fs ~ 1
t1_inf_sha_beh_fs ~ 1
t2_inf_sha_beh_fs ~ 1
t3_inf_sha_beh_fs ~ 1

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_fs
t2_pri_con_w =~ 1*t2_pri_con_fs
t3_pri_con_w =~ 1*t3_pri_con_fs
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs

# estimate variances
pri_con_b ~~ pri_con_b
inf_sha_beh_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_pri_con_w
t2_pri_con_w ~~ t2_pri_con_w
t3_pri_con_w ~~ t3_pri_con_w
t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w

# within person effects
t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w

# covariances
pri_con_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_beh_w

# control variables
t1_pri_con_fs ~ age + edu_num + male
t2_pri_con_fs ~ age + edu_num + male
t3_pri_con_fs ~ age + edu_num + male
t1_inf_sha_beh_fs ~ age + edu_num + male
t2_inf_sha_beh_fs ~ age + edu_num + male
t3_inf_sha_beh_fs ~ age + edu_num + male
'

fit <- lavaan(model, data = d_wide, missing = "ml")
summary(fit, standardized = TRUE, fit.measures = TRUE)
```

#### Model 5

In this model, we omit all longitudinal paths in order to better estimate the concurrent relations of the variables for _all_ waves (in the regular RI-CLPM, only the relations at wave 1 can be interpreted meaningfully).

```{r }
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m

# intercepts
t1_pri_con_m ~ mu1*1
t2_pri_con_m ~ mu2*1
t3_pri_con_m ~ mu3*1
t1_inf_sha_beh_m ~ pi1*1
t2_inf_sha_beh_m ~ pi2*1
t3_inf_sha_beh_m ~ pi3*1

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_m
t2_pri_con_w =~ 1*t2_pri_con_m
t3_pri_con_w =~ 1*t3_pri_con_m
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m

# estimate variances
pri_con_b ~~ pri_con_b
inf_sha_beh_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_pri_con_w
t2_pri_con_w ~~ t2_pri_con_w
t3_pri_con_w ~~ t3_pri_con_w
t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w

# covariances
pri_con_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ a*t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_beh_w
'

fit <- lavaan(model, data = d_wide, missing = "ml")
summary(fit, standardized = TRUE, fit.measures = TRUE)
```

#### Model 6

The same like above, using Factor Scores and control variables.

```{r}
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs

# intercepts
t1_pri_con_fs ~ 1
t2_pri_con_fs ~ 1
t3_pri_con_fs ~ 1
t1_inf_sha_beh_fs ~ 1
t2_inf_sha_beh_fs ~ 1
t3_inf_sha_beh_fs ~ 1

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_fs
t2_pri_con_w =~ 1*t2_pri_con_fs
t3_pri_con_w =~ 1*t3_pri_con_fs
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs

# estimate variances
pri_con_b ~~ pri_con_b
inf_sha_beh_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_pri_con_w
t2_pri_con_w ~~ t2_pri_con_w
t3_pri_con_w ~~ t3_pri_con_w
t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w

# covariances
pri_con_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ a*t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_beh_w

# control variables
t1_pri_con_fs ~ age + edu_num + male
t2_pri_con_fs ~ age + edu_num + male
t3_pri_con_fs ~ age + edu_num + male
t1_inf_sha_beh_fs ~ age + edu_num + male
t2_inf_sha_beh_fs ~ age + edu_num + male
t3_inf_sha_beh_fs ~ age + edu_num + male
'

fit <- lavaan(model, data = d_wide, missing = "ml")
summary(fit, standardized = TRUE, fit.measures = TRUE)
```

### Three Variables
#### Model 1

With observed means.

```{r }
model <- '
# random intercepts (between person)
pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
inf_sha_att_b =~ 1*t1_inf_sha_att_m + 1*t2_inf_sha_att_m + 1*t3_inf_sha_att_m
inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_m
t2_pri_con_w =~ 1*t2_pri_con_m
t3_pri_con_w =~ 1*t3_pri_con_m
t1_inf_sha_att_w =~ 1*t1_inf_sha_att_m
t2_inf_sha_att_w =~ 1*t2_inf_sha_att_m
t3_inf_sha_att_w =~ 1*t3_inf_sha_att_m
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m

# within person effects
t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w

# setting variances of observed variables to zero
t1_pri_con_m ~~ 0*t1_pri_con_m
t2_pri_con_m ~~ 0*t2_pri_con_m
t3_pri_con_m ~~ 0*t3_pri_con_m
t1_inf_sha_att_m ~~ 0*t1_inf_sha_att_m
t2_inf_sha_att_m ~~ 0*t2_inf_sha_att_m
t3_inf_sha_att_m ~~ 0*t3_inf_sha_att_m
t1_inf_sha_beh_m ~~ 0*t1_inf_sha_beh_m
t2_inf_sha_beh_m ~~ 0*t2_inf_sha_beh_m
t3_inf_sha_beh_m ~~ 0*t3_inf_sha_beh_m

# allow covariances RIs & variables measured at the same time
pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
inf_sha_att_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
'
fit <- sem(model, estimator = "ML", data = d_wide, orthogonal = TRUE, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
```

#### Model 2

With observed means and control variables.

```{r }
model <- '
# random intercepts (between person)
pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
inf_sha_att_b =~ 1*t1_inf_sha_att_m + 1*t2_inf_sha_att_m + 1*t3_inf_sha_att_m
inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_m
t2_pri_con_w =~ 1*t2_pri_con_m
t3_pri_con_w =~ 1*t3_pri_con_m
t1_inf_sha_att_w =~ 1*t1_inf_sha_att_m
t2_inf_sha_att_w =~ 1*t2_inf_sha_att_m
t3_inf_sha_att_w =~ 1*t3_inf_sha_att_m
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m

# within person effects
t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w

# setting variances of observed variables to zero
t1_pri_con_m ~~ 0*t1_pri_con_m
t2_pri_con_m ~~ 0*t2_pri_con_m
t3_pri_con_m ~~ 0*t3_pri_con_m
t1_inf_sha_att_m ~~ 0*t1_inf_sha_att_m
t2_inf_sha_att_m ~~ 0*t2_inf_sha_att_m
t3_inf_sha_att_m ~~ 0*t3_inf_sha_att_m
t1_inf_sha_beh_m ~~ 0*t1_inf_sha_beh_m
t2_inf_sha_beh_m ~~ 0*t2_inf_sha_beh_m
t3_inf_sha_beh_m ~~ 0*t3_inf_sha_beh_m

# allow covariances RIs & variables measured at the same time
pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
inf_sha_att_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w

# control variables
t1_pri_con_m ~ age + edu_num + male
t2_pri_con_m ~ age + edu_num + male
t3_pri_con_m ~ age + edu_num + male
t1_inf_sha_beh_m ~ age + edu_num + male
t2_inf_sha_beh_m ~ age + edu_num + male
t3_inf_sha_beh_m ~ age + edu_num + male
t1_inf_sha_att_m ~ age + edu_num + male
t2_inf_sha_att_m ~ age + edu_num + male
t3_inf_sha_att_m ~ age + edu_num + male
'
fit <- sem(model, estimator = "ML", data = d_wide, orthogonal = TRUE, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
```

#### Model 3

With Factor Scores.

```{r}
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t2_inf_sha_att_fs + 1*t3_inf_sha_att_fs

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_fs
t2_pri_con_w =~ 1*t2_pri_con_fs
t3_pri_con_w =~ 1*t3_pri_con_fs
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
t2_inf_sha_att_w =~ 1*t2_inf_sha_att_fs
t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs

# within person effects
t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w

# covariances
pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
inf_sha_att_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w

# setting variances of observed variables to zero
t1_pri_con_fs ~~ 0*t1_pri_con_fs
t2_pri_con_fs ~~ 0*t2_pri_con_fs
t3_pri_con_fs ~~ 0*t3_pri_con_fs
t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
t2_inf_sha_att_fs ~~ 0*t2_inf_sha_att_fs
t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
t2_inf_sha_beh_fs ~~ 0*t2_inf_sha_beh_fs
t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs
'
fit <- sem(model, data = d_wide, orthogonal = TRUE, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
```

#### Model 4 (final)

With Factor Scores and control variables. This is the final model we report in the paper.

```{r}
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t2_inf_sha_att_fs + 1*t3_inf_sha_att_fs

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_fs
t2_pri_con_w =~ 1*t2_pri_con_fs
t3_pri_con_w =~ 1*t3_pri_con_fs
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
t2_inf_sha_att_w =~ 1*t2_inf_sha_att_fs
t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs

# within person effects
t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w

# covariances
pri_con_b ~~ cor_b_1*inf_sha_att_b + cor_b_2*inf_sha_beh_b
inf_sha_att_b ~~ cor_b_3*inf_sha_beh_b
t1_pri_con_w ~~ cor_w_1*t1_inf_sha_att_w + cor_w_2*t1_inf_sha_beh_w
t1_inf_sha_att_w ~~ cor_w_3*t1_inf_sha_beh_w
t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w

# setting variances of observed variables to zero
t1_pri_con_fs ~~ 0*t1_pri_con_fs
t2_pri_con_fs ~~ 0*t2_pri_con_fs
t3_pri_con_fs ~~ 0*t3_pri_con_fs
t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
t2_inf_sha_att_fs ~~ 0*t2_inf_sha_att_fs
t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
t2_inf_sha_beh_fs ~~ 0*t2_inf_sha_beh_fs
t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs

# control variables
t1_pri_con_fs ~ age + edu_num + male
t2_pri_con_fs ~ age + edu_num + male
t3_pri_con_fs ~ age + edu_num + male
t1_inf_sha_beh_fs ~ age + edu_num + male
t2_inf_sha_beh_fs ~ age + edu_num + male
t3_inf_sha_beh_fs ~ age + edu_num + male
t1_inf_sha_att_fs ~ age + edu_num + male
t2_inf_sha_att_fs ~ age + edu_num + male
t3_inf_sha_att_fs ~ age + edu_num + male
'
fit <- sem(model, data = d_wide, orthogonal = TRUE, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
fit_riclpm <- fit
effect_std_ci <- standardizedsolution(fit) %>% 
  filter(lhs == "pri_con_b", rhs == "inf_sha_beh_b")
```

#### Model 5

With Factor Scores, control variables, and 4 waves / 1 year intervals

```{r}
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_m + 1*t3_pri_con_m + 1*t4_pri_con_m + 1*t5_pri_con_m
inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t3_inf_sha_beh_m + 1*t4_inf_sha_beh_m + 1*t5_inf_sha_beh_m
inf_sha_att_b =~ 1*t1_inf_sha_att_m + 1*t3_inf_sha_att_m + 1*t4_inf_sha_att_m + 1*t5_inf_sha_att_m

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_m
t3_pri_con_w =~ 1*t3_pri_con_m
t4_pri_con_w =~ 1*t4_pri_con_m
t5_pri_con_w =~ 1*t5_pri_con_m
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
t4_inf_sha_beh_w =~ 1*t4_inf_sha_beh_m
t5_inf_sha_beh_w =~ 1*t5_inf_sha_beh_m
t1_inf_sha_att_w =~ 1*t1_inf_sha_att_m
t3_inf_sha_att_w =~ 1*t3_inf_sha_att_m
t4_inf_sha_att_w =~ 1*t4_inf_sha_att_m
t5_inf_sha_att_w =~ 1*t5_inf_sha_att_m

# within person effects
t3_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
t3_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
t3_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
t4_pri_con_w ~ a1*t3_pri_con_w + a2*t3_inf_sha_att_w + a3*t3_inf_sha_beh_w
t4_inf_sha_att_w ~ b1*t3_pri_con_w + b2*t3_inf_sha_att_w + b3*t3_inf_sha_beh_w
t4_inf_sha_beh_w ~ c1*t3_pri_con_w + c2*t3_inf_sha_att_w + c3*t3_inf_sha_beh_w
t5_pri_con_w ~ a1*t4_pri_con_w + a2*t4_inf_sha_att_w + a3*t4_inf_sha_beh_w
t5_inf_sha_att_w ~ b1*t4_pri_con_w + b2*t4_inf_sha_att_w + b3*t4_inf_sha_beh_w
t5_inf_sha_beh_w ~ c1*t4_pri_con_w + c2*t4_inf_sha_att_w + c3*t4_inf_sha_beh_w

# covariances
pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
inf_sha_att_b ~~ inf_sha_beh_b
t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
t4_pri_con_w ~~ a*t4_inf_sha_att_w + b*t4_inf_sha_beh_w
t4_inf_sha_att_w ~~ c*t4_inf_sha_beh_w
t5_pri_con_w ~~ a*t5_inf_sha_att_w + b*t5_inf_sha_beh_w
t5_inf_sha_att_w ~~ c*t5_inf_sha_beh_w

# setting variances of observed variables to zero
t1_pri_con_m ~~ 0*t1_pri_con_m
t3_pri_con_m ~~ 0*t3_pri_con_m
t4_pri_con_m ~~ 0*t4_pri_con_m
t5_pri_con_m ~~ 0*t5_pri_con_m
t1_inf_sha_att_m ~~ 0*t1_inf_sha_att_m
t3_inf_sha_att_m ~~ 0*t3_inf_sha_att_m
t4_inf_sha_att_m ~~ 0*t4_inf_sha_att_m
t5_inf_sha_att_m ~~ 0*t5_inf_sha_att_m
t1_inf_sha_beh_m ~~ 0*t1_inf_sha_beh_m
t3_inf_sha_beh_m ~~ 0*t3_inf_sha_beh_m
t4_inf_sha_beh_m ~~ 0*t4_inf_sha_beh_m
t5_inf_sha_beh_m ~~ 0*t5_inf_sha_beh_m

# control variables
t1_pri_con_m ~ age + edu_num + male
t3_pri_con_m ~ age + edu_num + male
t4_pri_con_m ~ age + edu_num + male
t5_pri_con_m ~ age + edu_num + male
t1_inf_sha_beh_m ~ age + edu_num + male
t3_inf_sha_beh_m ~ age + edu_num + male
t4_inf_sha_beh_m ~ age + edu_num + male
t5_inf_sha_beh_m ~ age + edu_num + male
t1_inf_sha_att_m ~ age + edu_num + male
t3_inf_sha_att_m ~ age + edu_num + male
t4_inf_sha_att_m ~ age + edu_num + male
t5_inf_sha_att_m ~ age + edu_num + male
'
fit <- sem(model, data = d_wide_all, orthogonal = TRUE, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
```

## Mixed Models

In what follows, we also present the results of several mixed models. Using mixed models, we can include more data. However, one downside is that not all research questions can be answered in one single model.

### Two Variables
#### Model 1

Measures overall correlation between privacy concerns and information sharing.

```{r}
fit <- lmer(pri_con_m ~ 1 + inf_sha_beh_m + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

#### Model 2

Measures how current levels of information sharing are affected by generel levels of privacy concern und current levels of privacy concern.

```{r}
fit <- lmer(inf_sha_beh_m ~ pri_con_m_b + pri_con_m_w + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

Measures how current levels of privacy concern are affected by generel levels of information sharing und current levels of information sharing.

```{r}
fit <- lmer(pri_con_m ~ inf_sha_beh_m_b + inf_sha_beh_m_w + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

#### Model 3

Includes control variables.

```{r}
fit <- lmer(inf_sha_beh_m ~ 1 + pri_con_m_b + pri_con_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

```{r}
fit <- lmer(pri_con_m ~ 1 + inf_sha_beh_m_b + inf_sha_beh_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

### Three Variables
#### Model 1

Measures how current levels of information sharing are affected by generel levels of privacy concern and current levels of privacy concern, as well as general levels of positive attitude toward information sharing and current levels of positive attitude toward information sharing.

```{r}
fit <- lmer(inf_sha_beh_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_att_m_b + inf_sha_att_m_w + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

Measures how current levels of positive attitude toward information sharing are affected by generel levels of privacy concern and current levels of privacy concern, as well as general levels of information sharing and current levels of information sharing.

```{r}
fit <- lmer(inf_sha_att_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_beh_m_b + inf_sha_beh_m_w + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

Measures how current levels of privacy concern are affected by generel levels of positive attitude toward information sharing and current levels of positive attitude toward information sharing, as well as general levels of information sharing and current levels of information sharing.

```{r}
fit <- lmer(pri_con_m ~ 1 + inf_sha_beh_m_b + inf_sha_beh_m_w + inf_sha_att_m_b + inf_sha_att_m_w + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

#### Model 2

Includes control variables

```{r}
fit <- lmer(pri_con_m ~ 1 + inf_sha_att_m_b + inf_sha_att_m_w + inf_sha_beh_m_b + inf_sha_beh_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

```{r}
fit <- lmer(inf_sha_att_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_beh_m_b + inf_sha_beh_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

```{r}
fit <- lmer(inf_sha_beh_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_att_m_b + inf_sha_att_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
summary(fit)
std_beta(fit)
```

```{r cache=F}
save.image("../data/workspace.RData")
```

### 2019-09-16 manuscript/manuscript.RmD
- setting up of novel git-hub repository in order to not include person-related data of prior repository

---
title             : "A Longitudinal Analysis of the Privacy Paradox" 
shorttitle        : "Longitudinal Analysis of the Privacy Paradox"
author:            
  - name          : "Tobias Dienlin"
    email         : "tobias.dienlin@uni-hohenheim.de"
    affiliation   : "1"
    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
    corresponding : yes
  - name          : "Philipp K. Masur"
    affiliation   : "1"
  - name          : "Sabine Trepte"
    affiliation   : "1"
affiliation:

  - id            : "1"
    institution   : "University of Hohenheim"
author_note: |
  All authors contributed extensively to the work presented in this paper. TD, PM, & ST designed the study; PM supervised the data collection; PM administered the data importation; TD & PM wrote the code, ran the models, and analyzed the output data; TD wrote major parts of manuscript, and PM & ST contributed individual sections and comments; ST supervised the project and wrote the grant application (in 2012). 
  The authors declare no competing interests.
  This research was funded by the German Federal Ministry of Education and Research (BMBF) Grant 16KIS0094, awarded to Sabine Trepte.

  This manuscript features online supplementary material that includes the code, additional analyses, and a reproducible version of the manuscript (https://osf.io/4wabh). The data can be downloaded from http://dx.doi.org/10.7802/1937.

abstract: |
  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information.
  Using a representative sample of the German population, featuring `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves that were separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects. 
  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward the online  sharing of personal information than others (between-person level). 
  Next, people who were more concerned than usual also shared slightly less information than usual (within-person level). 
  At the same time, we found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
  Together, the results provide further evidence against the privacy paradox.

keywords          : "privacy paradox, privacy concerns, information disclosure, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
bibliography      : 
  - [../bibliography/references.bib]
  - [../bibliography/r-references.bib]
lang              : "english"
class             : "man"
mask              : no
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
editor_options: 
  chunk_output_type: inline
---
```{r knitr-set-up}
knitr::opts_chunk$set(echo=F, error=F, message=F, tidy=T, warning=F)
```

```{r load-packs, include = F}
# Load and install packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
devtools::install_github("crsh/papaja")
packages <- c("broman", "kableExtra", "knitr", "lavaan", "magrittr", "papaja"
             , "psych", "pwr", "td", "tidyverse", "semTools", "scales")
invisible(lapply(packages, library, character.only = T))

# load r-bib
r_citations <- cite_r("../bibliography/r-references.bib", 
                      footnote = FALSE, 
                      pkgs = c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
                               "MissMech", "papaja", "psych", "pwr", "RVAideMemoire", 
                               "semTools", "sjstats", "tidyverse", "td"), 
                      withhold = FALSE)
```

```{r load-data, include=F, cache=T}
# Load Workspace
load("../data/workspace.RData")
```

The privacy paradox states that the information disclosure practices of Internet users are problematic: 
Although many people are concerned about their online privacy, they still tend to disclose plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
This is problematic, because sharing information online allows to accurately predict a person's future behavior [@bagrowInformationFlowReveals2019].
The privacy paradox and its underlying theoretical conundrum is hence of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
If the privacy paradox really exists, it should inspire worry: 
It would suggest that online behavior is irrational and that people are revealing too much of their personal lives to unknown third parties, fostering potentially unintended consequences such as commodification, exploitation or inappropriate recontextualization [@boydTakenOutContext2008; @sevignaniPrivacyCapitalismAge2016].
In conclusion, understanding why people disclose information online and whether this is paradoxical or not represents an important challenge for communication scholars.

However, current research on the privacy paradox has one major limitation: 
To the best of our knowledge, all empirical studies conducted so far have investigated the privacy paradox from a between-person (i.e., interpersonal) perspective.
By employing empirical tests of between-person variance (e.g., cross-sectional questionnaires analyzed with multiple regression or Pearson correlations), studies have analyzed whether people who are more concerned than _others_ also share less personal information than _others_.
Granted, such a between-person perspective is interesting and represents a viable first step in analyzing the relation between these variables.
At the same time, it is important to emphasize that the privacy paradox actually implies that the research question that should be asked is a within-person (i.e., intrapersonal) relation:
Does a person, if _he or she_ becomes more concerned about online privacy, then also share less personal information?
This mismatch is problematic because although between-person variance is, except some specific cases, a _necessary_ condition for within-person effects, it is by no means a _sufficient_ condition.
For example, it could be that the between-person relation is determined by another stable third variable. 
Hence, as the next step in investigating the privacy paradox and to better understand the intrapersonal relation between privacy concerns and information sharing, we now need studies with within-person designs.

As a result, with this study we aim to answer four major questions. 
First, on a between-person level, how are concerns about online privacy related to the online sharing of personal information? 
Second, on a within-person level, does information sharing decrease when concerns increase?
Third, what are the potential long-term effects, are changes in concerns related to changes in information sharing 6 months later and/or vice versa? 
Fourth, what is the role of privacy attitudes, do they mediate the relation between privacy concerns and information sharing?
To best answer and contextualize these questions, we first provide an in-depth theoretical analysis of the privacy paradox, after which we present the empirical results of a longitudinal panel study.

## A Brief History of the Privacy Paradox

@acquistiLossesGainsHyperbolic2003 were among the first to argue that the online disclosure of personal information is paradoxical. 
"Experiments reveal that very few individuals actually take any action to protect their personal information, even when doing so involves limited costs" (p.1). 
Three years later, @barnesPrivacyParadoxSocial2006 discussed the behavior of young people using SNSs and coined the expression the "privacy paradox." 
Barnes listed six notions that she considered to be particularly paradoxical: (a) illusion of privacy, (b) high quantity of information sharing, (c) attitude behavior discrepancy, (d) lack of privacy concerns, (e) lack of privacy literacy, and (f) fabrication of false information.

Subsequent research analyzed the privacy paradox more explicitly, focusing on Barnes's third tenet, the attitude-behavior discrepancy. 
On the one hand, some studies reported that privacy concerns were not significantly related to the disclosure of personal information [e.g., @grossInformationRevelationPrivacy2005; @taddickenPrivacyParadoxSocial2014; @tufekciCanYouSee2008], lending credence to the privacy paradox. 
On the other hand, a different set of studies showed relations that were statistically significant [@heirmanPredictingAdolescentsDisclosure2013; @walraveConnectingProtectingComparing2012; e.g., @dienlinPrivacyParadoxRelic2015], thereby refuting the privacy paradox.

It is interesting that in a parallel line of research, other studies have also analyzed the relation between privacy concerns and subsequent information sharing; however, the term privacy paradox has often not been mentioned explicitly. 
Instead, studies have referred to the so-called _privacy calculus_. 
The privacy calculus states that sharing personal information is affected by both the respective costs and the anticipated benefits [@culnanInformationPrivacyConcerns1999] and by now, several studies have found empirical support in various online contexts [e.g., @bolUnderstandingEffectsPersonalization2018; @dienlinExtendedPrivacyCalculus2016; @krasnovaOnlineSocialNetworks2010].

@baruhOnlinePrivacyConcerns2017 published the first empirical meta-analysis on the relations between privacy concerns and various forms of social media use (e.g., information sharing or SNS usage). 
On the basis of 37 studies, @baruhOnlinePrivacyConcerns2017 found a small and significant statistical relation between concerns about online privacy and online information sharing (_r_ = -.13). 
For other systematic literature reviews, see @barthPrivacyParadoxInvestigating2017, @gerberExplainingPrivacyParadox2018, and @kokolakisPrivacyAttitudesPrivacy2017.
In conclusion, the current literature suggests that a significant relation between concerns about online privacy and the online sharing of personal information exists and that it is small---which speaks against the privacy paradox.

## Defining Privacy Concerns and Information Sharing

Privacy is defined as the "[...] voluntary and temporary withdrawal of a person from the general society through physical or psychological means [...]" [@westinPrivacyFreedom1967, 7]. 
Hence, privacy captures aspects of both volitional _control_ and social _separateness_.
Several dimensions of privacy have been proposed:
For example, it is possible to distinguish a vertical and a horizontal level;
whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people [@masurSituationalPrivacySelfdisclosure2018].
When it comes to concern, it is interesting that they do not seem to be established as a stand-alone theoretical concept in psychology; 
for example, the Oxford Dictionary of Psychology does not feature a designated entry [@colmanDictionaryPsychology2015].
In general, however, concern is defined as a "marked interest or regard usually arising through a personal tie or relationship" that also reflects an "uneasy state of blended interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
A concern therefore partially represents a latent _motivation_ (or increased attention) to invest oneself in a specific entity and a negatively valenced _emotion_ (or affective cognition).
As such, a concern is not predominantly the result of a deliberate explicit cognition; instead, it primarily reflects an automatic implicit perception.
Taken together, concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened.
As a theoretical construct, privacy concerns can hence be categorized as an affective motivational disposition.
As such, they have similarities with many other concepts such as emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (approval, dissent), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).

The online sharing of personal information, on the other hand, captures how much person-related information people share when they use the Internet, including, for example, information about their age, sex, name, address, health, or finances.
Information sharing can be differentiated from communication and self-disclosure:
Whereas communication is broad because it includes all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011], self-disclosure is narrow because it focuses on deliberate revelations about the true self to others [e.g., @jourardTransparentSelf1964]

## The Relation Between Privacy Concerns and Information Sharing

It is somewhat surprising that the literature seems to lack explicit theoretical treatises on why and how human behavior should be specifically affected by concerns.
More fortunately, however, there are several theoretical insights regarding how the affective motivational concepts presented above can pertain to behavior.
The results are unanimous: They can all affect behavior profoundly.
For example, let us consider the concept that is perhaps closest to concerns, emotions.
By causing fight or flight reactions, emotions are potentially the most primordial trigger of behavior as they are considered an adaptive mechanism that fosters the evolution of a species [@dolanEmotionCognitionBehavior2002].
With their direct link to the amygdala, emotions can already trigger reactions subcortically [i.e., without activation of the more recently evolved cortical structures; @dolanEmotionCognitionBehavior2002].
It hence seems plausible to suggest that privacy concerns, with their emotional dependency, also share this function at least partially.
Moreover, changes in concerns might be correlated with changes in behavior because people usually aim to reduce discrepancies between cognitions and behavior [@festingerTheoryCognitiveDissonance1957].
There are also several empirical accounts of how concerns affect behavior:
People who are more concerned about the environment show more environment-related behaviors [@bambergHowDoesEnvironmental2003], 
people who are more concerned about their appearance consume fewer calories [@hayesConcernAppearanceHealth1987], 
and people who are more concerned about their bodies engage in more physical exercise [@reelRelationsBodyConcerns2007].
Hence, it seems reasonable to also expect that if a person's concerns about online privacy change, this change should be reflected in a change in the extent to which this person will share personal information online.

At the same time, there are several variables that are likely to diminish the relation.
Most prominently, there is the so-called "attitude behavior gap", which pertains to the idea that people often act against their own attitudes [e.g., @fishbeinPredictingChangingBehavior2010]. 
For example, despite endorsing the importance of physical health, a large part of the population does not exercise regularly.
Transferred to the privacy paradox, it should not be surprising to encounter this general discrepancy also in the specific context of privacy concerns and information sharing. 
The explanation is simple: Other factors such as subjective norms and perceived behavioral control can also determine behavior [@ajzenIntentionsActionsTheory1985], and this automatically limits the predictive capacity of attitudes or concerns. 
Specifically, two of the most influential factors that affect online information sharing are (a) the strong subjective norms to participate online [@heirmanPredictingAdolescentsDisclosure2013] and (b) the manifold benefits that accrue from participation [@krasnovaOnlineSocialNetworks2010]. 
In other words, instead of considering privacy concerns it is often more important to attain social support, special offers, or tailored services.
@trepteRiskyBehaviorsHow2014 listed several factors that can additionally attenuate the relation:
if the concerns miss any actual strength,
a lack of negative personal experiences, 
or distortions due to situational constraints such as social desirability.

Finally, there are also some methodological reasons that can explain why some studies did not find statistically significant relations even though they probably exist empirically.
In general, researchers are always confronted with the so-called Duhem-Quine problem, which holds that it is impossible to test theories in isolation, because empirical tests always rely on auxiliary assumptions [e.g., @dienesUnderstandingPsychologyScience2008]. 
In other words, if a psychological experiment fails, we do not know whether the theory is wrong or the questionnaire subpar. 
This tenet is particularly relevant for the privacy paradox: 
Detecting statistical significance for small effects---and in this case, we should expect to find effects that are small---is more challenging because it means that large samples are necessary to guarantee sufficient statistical power.[^power]
Precisely, in order to be capable of detecting a correlation between privacy concerns and information sharing in 95% of all cases, which @baruhOnlinePrivacyConcerns2017 estimated to be _r_ = -.13, we need a sample of _N_ = `r pwr.r.test(r = -.13, sig.level = .05, power = .95)$n %>%  round(0)` people. 
The reality, however, looks different: 
In their meta-analysis, Baruh et al. reported a median sample size of _N_ = 300.

[^power]: Statistical power describes the probability statistically detecting an effect that exists empirically. 
Only with high statistical power is it possible to make valid claims about an effect's existence @cohenPowerPrimer1992.

To conclude, in line with prior research [@baruhOnlinePrivacyConcerns2017] and the within-person rationales that we have presented above, we first expected to find a significant relation between privacy concerns and information sharing both on the between-person level and the within-person level. 
Second, given the strong premise that concerns should be reflected in contiguous behaviors, alongside the existence of several diminishing factors, we expected to find a small relation between concerns about online privacy and the online sharing of personal information also on the within-person level.

Hypothesis 1: People who are more concerned about their online privacy than others will also be less likely to share personal information online than others.

Hypothesis 2: People who are more concerned about their online privacy than they usually are will also share less personal information online than they usually do.

## Long-Term Perspective

Although we hypothesized that changes in people's concerns about online privacy will be directly reflected by their behavior, we were not sure about whether there would also be some long-term effects.
First, when analyzing potential long-term effects, it is important to choose an interval that is both plausible and relevant.
For example, it makes a difference whether the effects of alcohol consumption on driving performance are tested 1 min, 1 h, or 1 day after consumption. 
The main factor that determines an interval's optimal length is stability [@dormannOptimalTimeLags2015].
Privacy concerns and privacy attitudes are predominantly trait-like constructs with high stabilities, therefore necessitating longer intervals.
Other studies with comparable research questions have used an interval of 6 months [e.g., @valkenburgEffectsInstantMessaging2009], which we consider to be plausible also in this case.

In general, we believe that it should be possible to find long-term effects. 
It has been argued that privacy concerns affect privacy behavior [e.g., @heirmanPredictingAdolescentsDisclosure2013]. 
The underlying theoretical mechanism could be that the emotional part of privacy concerns causes (a) motivated information selection and (b) motivated information processing, which is likely to change actual behavior [@nabiCognitivefunctionalModelEffects1999]. 
Specifically, when privacy concerns increase (e.g., because of experienced or witnessed privacy infringements), people might begin reading more media articles on privacy issues and might also consume these articles more carefully, which could prompt information sharing practices that are more cautious.
Also empirically, a study with 290 participants found small negative longitudinal (between-person) relations between privacy concerns and self-disclosure [@koohikamaliInvestigationDynamicModel2019].

At the same time, the adverse effect of information sharing on privacy concerns seems also plausible, with two potential outcomes. 
On the one hand, the long-term relation could be negative: 
If people start to share more information online, they might become increasingly aware that their privacy is at risk, which might stir concern.
On the other hand, the long-term relation might also be positive, because when people share more personal information online, they might become accustomed to doing so, which might reduce concern [for example, due to the mere exposure effect; @zajoncAttitudinalEffectsMere1968].
Finally, there could also be no long-term relation after all. 
For example, people might have already become used to sharing information online and this might stifle any further cognitive or emotional processing, a rationale central to the observation of so-called _privacy cynicism_ [e.g., @hoffmannPrivacyCynicismNew2016].

Research Question 1.1: Do changes in concerns about online privacy affect the online sharing of personal information 6 months later?

Research Question 1.2: Do changes in the online sharing of personal information affect concerns about online privacy 6 months later?

## The Role of Attitudes

It has been argued that privacy attitudes could "bridge the gap" between concerns and information sharing [e.g., @dienlinPrivacyParadoxRelic2015]. 
In contrast to privacy concerns, privacy attitudes capture a more explicit, fluctuating cognitive appraisal. 
Although both variables are related to information disclosure, attitudes are likely to be the better predictor. 
This reasoning thus follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always, at least in part, influenced by convictions, attitudes, and cost-benefit analyses. 
Likewise, evolutionary psychology also suggests that although emotions guide behavior in the long run, it is more adaptive if behavior instead reflects a cognitive appraisal; 
a tenet arguably reflected best by the phylogenetic development of the neocortex or the general dominion of the human race.
These rationales have also found some empirical support. 
For example, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure was moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].

Hypothesis 3.1: People who are more concerned about their online privacy than others will also hold a less positive attitude toward the online sharing of personal information than others.

Hypothesis 3.2: People with a more positive attitude toward the online sharing of personal information than others will also share more information online than others.

Hypothesis 4.1: People who are more concerned about their online privacy than they usually are will also hold a less positive attitude toward the online sharing of personal information than they usually do.

Hypothesis 4.2: People with a more positive attitude toward the online sharing of personal information than they usually have will also share more information online than they usually do.

Concerning the potential long-term relations of privacy attitudes, the same situation exists here as mentioned above:
Given that no prior research exists on long-term relations, several scenarios seem plausible.
For example, attitudes could either have long-term relations or not, and information sharing could either foster or diminish privacy attitudes.

Research Question 2.1: Do changes in concerns about online privacy affect attitudes toward the online sharing of personal information 6 months later?

Research Question 2.2: Do changes in attitudes toward the online sharing of personal information affect concerns about online privacy 6 months later?

Research Question 3.1: Do changes in attitudes toward the online sharing of personal information affect the online sharing of personal information 6 months later?

Research Question 3.2: Do changes in the online sharing of personal information affect attitudes toward the online sharing of personal information 6 months later?

# Method
## Statistics

We follow the recommendation by @lakensJustifyYourAlpha2017 and first justify the choice of our alpha level. 
We determined adequate error margins by considering the potential implications of both false positive and false negative findings (i.e., alpha and beta errors): 
On the one hand, if we committed an alpha error, we would wrongfully conclude that people's concerns and behaviors are consistent. 
Communicating such a false result to the public would unjustly reassure and placate people when they should instead be more alert.
On the other hand, if we committed a beta error, we would wrongfully conclude that individuals behave paradoxically.
Communicating such a false result would unjustly accuse people of implausible behavior, potentially causing unnecessary distress or reactance.
We consider both errors to be equally detrimental. 
Hence, we chose to use error rates that are balanced.
Next, we set a maximum error rate of 5% for both alpha and beta. 
As the smallest effect size of interest [SESOI; @lakensPerformingHighpoweredStudies2014], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses; significantly smaller effects were not considered able to offer support.
The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi`, we calculated that we needed a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents. 
Given the final sample size of `r dollar_format(prefix = "")(n)` respondents (see below), alpha and beta errors were balanced for our hypotheses (research questions) when we used a critical alpha of `r alpha_balanced_h  %>% round(3) * 100`% (`r alpha_balanced_rq  %>% round(3) * 100`%), resulting in a power of `r power_balanced_h %>% round(3) * 100`%  (`r power_balanced_rq %>% round(3) * 100`%) to detect small effects.

The data were analyzed by means of a random-intercepts cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015], a method that already has been used for similar research questions [@dietvorstAdolescentPerceptionsParental2018].
Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs allows to separate between-person variance from within-person variance. 
We used factor scores as observed variables to represent the variables' latent structure more closely.
We tested H1, H3.1, and H3.2 by correlating the random intercepts, which represent the respondents' individual mean scores across all three waves.
We tested H2, H4.1, and H4.2 by correlating the respondents' within-person variance at T1, which captures their specific deviation at T1 from their overall score.
We tested all research questions by regressing variables on all other measures obtained 6 months earlier.
Given that we had three points of measurement, this resulted in two estimates for each Research Question.
As we did not expect longitudinal effects to differ across time, they were constrained to be equal across all waves, thereby producing one single general measure of each effect instead of two time-specific ones.
Fit was assessed according to the common criteria as described by @klinePrinciplesPracticeStructural2016. 
The final model fit the data well, `r fit_txt(fit_riclpm)`.

For the analyses, coding, and typesetting, we used `r r_citations`.
The code, additional analyses, and a reproducible version of the manuscript can be accessed in the Online Supplementary Material (OSM) at https://osf.io/4wabh.

## Procedure and Respondents

This study is part of a large-scale project which investigates the development of privacy and self-disclosure, including several other variables. 
Other publications linked to the project can be accessed at https://osf.io/y35as/.
The data come from a longitudinal, paper-and-pencil questionnaire study, in which a representative sample of the German population (16 years and older) was surveyed on overall five occasions.
The data can be downloaded from http://dx.doi.org/10.7802/1937.

The first three waves were collected from May 2014 to May 2015, with intervals of 6 months each.
The last two waves, collected on May 2016 and May 2017, had an interval of one year.
Because we hypothesized the effects to take place across half a year, the last two waves were not included in the analyses presented here.
First, a sample of 14,714 potential respondents was drawn from a representative omnibus survey in Germany (ADM master sample), employing a random last-two-digit dialing procedure. 
In this CATI screening, 5,286 respondents agreed to participate in all following waves.

Wave 1 was completed by 3,278 respondents (response rate: `r round((1 - (3278 / 5286)) * 100, 0)`%), Wave 2 by 2,448 respondents (attrition rate: `r round((1 - (2448 / 3278)) * 100, 0)`%), and Wave 3 by 2,021 respondents (attrition rate: `r round((1 - (2021 / 2448)) * 100, 0)`%). 
We filtered respondents who never used the Internet at all waves, answered fewer than 50% of the items for at least one wave, provided inconsistent birth-dates across measurements, or who did not report sociodemographic variables.
The final sample consisted of *n* = `r dollar_format(prefix = "")(n_complete)` respondents.

In the final sample, the rate of missing data was `r na_per %>% round(2)`%. 
Visual inspection of the missing value patterns as well as the non-parametric test by @R-MissMech suggested that all missing values could be considered missing at random (*p* `r test_mar_p %>% my_round("p_txt")`). 
Therefore, Full Information Maximum Likelihood (FIML) estimation was conducted using all available data.

In the final sample, the average age was `r round(age_m, 0)` years (*SD* = `r round(age_sd, 0)` years), and `r (round(male_per, 2) - 1) * 100`% were male. 
About `r round(edu_col_per, 0)`% reported that they had graduated from college.

## Measures

We tested the factorial validity of all measures using confirmatory factor analysis (CFA). 
Each CFA included the items from all three waves. 
For each item, factor loadings were constrained to be equal across waves.
Constrained and unconstrained models were compared using $\chi^2$ differences tests; all results were nonsignificant, suggesting longitudinal factorial invariance.
The measures showed good composite reliability in all three waves. 
Graphical displays of the variables' distributions showed that privacy concerns were skewed to the left, privacy attitudes were normally distributed, and information sharing was skewed to the right (Figure \@ref(fig:Distributions), diagonal).
Finally, we also calculated the intra-class correlation coefficient, quantifying how much variance in the variables' factor scores could be attributed to between-person differences.
An English translation of the original German items can be found in the OSM.

### Concerns about online privacy

Privacy concerns were measured as a second-order factor: 
Three items captured the vertical dimension (e.g., "How concerned are you that institutions or intelligence services collect and analyze data that you disclosed on the Internet?"), and three items captured the horizontal dimension (e.g., "How concerned are you that people that you do not know might obtain information about you because of you online activities?"). 
Respondents rated all items on a 5-point scale ranging from 1 (*not at all concerned*) to 5 (*very concerned*). 
The means were _M_~t1~ = `r desc[["t1_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_pri_con_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_pri_con_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_pri_con_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_pri_con_m_sd"]] %>% my_round(2)`.
The two-dimensional model fit the data well, 
`r fit_txt(fit_pri_con_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_pri_con_4, "t1_pri_con_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_pri_con_4, "t2_pri_con_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_pri_con_4, "t3_pri_con_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_pri_con$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

### The online sharing of personal information

To measure respondent's level of information disclosure, they were asked to indicate how often they disclosed 10 different pieces of information on the Internet. 
The exact question was: "How often do you disclose the following pieces of information online (i.e., on the Internet)?" 
Each item was answered on a 5-point scale ranging from 1 (*never*) to 5 (*daily*). 
Factor analyses suggested a second-order factor structure with five first-order factors. 
The first first-order factor subsumed financial and medical information, the second covered first and last name, the third included place of residence and street (including house number), the fourth email address and phone number, and the fifth contained information about education and current job. 
The means were _M_~t1~ = `r desc[["t1_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_inf_sha_beh_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_inf_sha_beh_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_inf_sha_beh_m_sd"]] %>% my_round(2)`.
The model fit the data adequately,
`r fit_txt(fit_inf_sha_beh_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_inf_sha_beh_4, "t1_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_inf_sha_beh_4, "t2_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_inf_sha_beh_4, "t3_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_inf_sha_beh$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

### Attitudes toward the online sharing of personal information

Respondents' attitudes toward disclosing personal information online were similarly captured with 10 items that measured the general appraisal of disclosing the same 10 pieces of information. 
Adhering to the principle of compatibility [@fishbeinPredictingChangingBehavior2010], the items were parallel to those of the actual disclosure scale. 
Specifically, we asked: 
"Do you think that it is sensible to disclose the following pieces of information online (i.e., on the Internet)?" 
The scale ranged from 1 (*not at all sensible*) to 5 (*very sensible*). 
The means were _M_~t1~ = `r desc[["t1_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_pri_con_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_pri_con_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_pri_con_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_pri_con_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_pri_con_m_sd"]] %>% my_round(2)`.
The second-order model with five first-order factors showed an adequate model fit,
`r fit_txt(fit_inf_sha_att_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_inf_sha_att_4, "t1_inf_sha_att_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_inf_sha_att_4, "t2_inf_sha_att_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_inf_sha_att_4, "t3_inf_sha_att_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_inf_sha_att$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

# Results

In a first descriptive step, we analyzed the variables' bivariate relations. All variables associated with the hypotheses showed correlations that were in line with our theoretical rationales (Figure \@ref(fig:Distributions), above the diagonal).

```{r Distributions, fig.cap="Results of the bivariate relations. above the diagonal: zero-order correlation matrix; diagonal: density plots for each variable; below the diagonal: bivariate scatter plots for zero-order correlations. Solid regression lines represent linear regressions, dashed regression lines represent quadratic regressions. Calculated with the variables’ latent factor scores.", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!ht", warning=F}
suppressWarnings(print(corr_plot))
```

Hypothesis 1 predicted that people reporting higher concerns about online privacy than others would also be less likely to share personal information online than others.
Results revealed that the random intercepts of the two variables were significantly correlated (`r coeffs_txt(fit_riclpm, "cor_b_2", one_sided = TRUE)`). 
Respondents who---on average across all three waves---were more concerned about their privacy than others also shared slightly less personal information online.
The effect was small.
However, when looking at the standardized effect's confidence interval ($\beta$ = `r effect_std_ci[["est.std"]] %>% my_round("std")`, 95% CI [`r effect_std_ci[["ci.lower"]] %>% my_round("std")`, `r  effect_std_ci[["ci.upper"]] %>% my_round("std")`]), it was not significantly smaller than our SESOI of $beta$ = .10.
Thus, Hypothesis 1 was supported.

Hypothesis 2 proposed that if people perceived more concerns about their online privacy than they usually do, they would also share less personal information online than they usually do.
Results revealed a small significant correlation (`r coeffs_txt(fit_riclpm, "cor_w_2", one_sided = TRUE)`), suggesting that if respondents were more concerned about their online privacy at T1 than usual, they also shared less personal information online at T1.
In conclusion, the results supported Hypothesis 2.

With Research Question 1.1, we analyzed the longitudinal relation of concerns about online privacy and the online sharing of personal information 6 months later. 
No significant lagged effect across 6 months was found (`r coeffs_txt(fit_riclpm, "c1")`).
With Research Question 1.2, we investigated the longitudinal relation of the online sharing of personal information and concerns about online privacy 6 months later, again revealing no significant effect (`r coeffs_txt(fit_riclpm, "a3")`).

Hypothesis 3.1 predicted that people who perceived more privacy concerns than others would also hold more negative attitudes toward the online sharing of personal information than others. 
The results revealed a medium-sized negative correlation between the two variables on the between-person level (`r coeffs_txt(fit_riclpm, "cor_b_1", one_sided = TRUE)`). 
Thus, people who---on average across all three waves---reported being more concerned about their online privacy relative to the rest of the sample, were also moderately more likely to hold a more negative attitude toward the online sharing of personal information, thereby supporting Hypothesis 3.1.
Hypothesis 3.2 posited that people who held more positive attitudes toward the online sharing of personal information than others would also share more personal information online than others. 
Results showed a very strong between-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_b_3", one_sided = TRUE)`): 
When averaged across all three waves, if people had more positive attitudes toward the online sharing of personal information than others, they were much more likely to actually share personal information online.
In conclusion, the results supported Hypothesis 3.2.

Hypothesis 4.1 proposed that people who perceived more privacy concerns than usual would also hold more negative attitudes toward the online sharing of personal information than usual. 
The results did not reveal a significant effect (`r coeffs_txt(fit_riclpm, "cor_w_1", one_sided = TRUE)`). 
Hypothesis 4.2 proposed that people who held more positive attitudes toward the online sharing of personal information than usual would also share more personal information online than usual. 
Results showed a moderate within-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_w_3", one_sided = TRUE)`), indicating that when respondents had more positive attitudes toward the online sharing of personal information at T1 than usual, they also shared more personal information online.
In conclusion, the results supported Hypothesis 4.2.

With Research Question 2.1, we analyzed the longitudinal relations of concerns about online privacy and positive attitudes toward the online sharing of personal information. 
No significant effect was found, `r coeffs_txt(fit_riclpm, "b1")`.
Regarding Research Question 2.2, again no significant longitudinal relations emerged between privacy attitudes and privacy concerns 6 months later `r coeffs_txt(fit_riclpm, "a2")`.

Research Question 3.1 asked whether changes in attitudes toward the online sharing of personal information would affect changes in personal information sharing 6 months later.
No significant effect was found (`r coeffs_txt(fit_riclpm, "c2")`).
Next, Research Question 3.2 asked whether changes in the online sharing of personal information would affect attitudes toward the online sharing of personal information 6 months later. 
Again, no significant effect was found (`r coeffs_txt(fit_riclpm, "b3")`).

Table \@ref(tab:Results1) presents an overview of all results and the OSM presents additional information and supplementary analyses (e.g., results of the RI-CLPM without socio-demographic control variables or results of alternative multilevel regression models).

```{r Results1, results = "asis"}
tab_results <- rbind(
  td::coeffs_tab(fit_riclpm, 
                 label_effect = c("c1", "a3", "b1", "a2", "c2", "b3"),
                 as_text = TRUE),
  td::coeffs_tab(fit_riclpm, 
                 label_effect = c("cor_b_1", "cor_b_2", "cor_b_3",
                                  "cor_w_1", "cor_w_2", "cor_w_3"), 
                 as_text = TRUE,
                 one_sided = TRUE)
  ) %>%
  .[-c(7:12), ] %>% # filter effects for first wave
  mutate(Effect = c("Positive attitude -> privacy concern",
                    "Information sharing -> privacy concern",
                    "Privacy concern -> positive attitude",
                    "Information sharing -> positive attitude",
                    "Privacy concern -> information sharing",
                    "Positive attitude -> information sharing",
                    "Privacy concern <-> positive attitude",
                    "Privacy concern <-> information sharing",
                    "Positive attitude <-> information sharing",
                    "Privacy concern <-> positive attitude ",
                    "Privacy concern <-> information sharing ",
                    "Positive attitude <-> information sharing ")) %>% 
  mutate(Effect = ordered(Effect, levels = c(
    "Privacy concern <-> information sharing",
    "Privacy concern <-> positive attitude",
    "Positive attitude <-> information sharing",
    "Privacy concern <-> information sharing ",
    "Privacy concern <-> positive attitude ",
    "Positive attitude <-> information sharing ",
    "Privacy concern -> information sharing",
    "Information sharing -> privacy concern",
    "Privacy concern -> positive attitude",
    "Positive attitude -> privacy concern",
    "Positive attitude -> information sharing",
    "Information sharing -> positive attitude"
  ))) %>% 
  arrange(Effect) %>% 
  select(Effect, b, ll, ul, beta, p)

apa_table(
  tab_results
  , caption = "Parameter Estimates Obtained in the Random Intercept Cross-Lagged Panel Model"
  , note = paste0("The between-person correlations represent interpersonal relations. For example, results showed that people who were more concerned than others, averaged across all 3 waves, also shared less information than others. The within-person parameters reflect how intrapersonal changes in one variable are related to intra-personal changes in another. For example, results showed that if a person was more concerned at T1 than he or she usually is, he or she also shared less information than usual.")
  , font_size = "small"
  , stub_indents = list("Between-person correlations across all waves" = c(1:3),
                        "Within-person correlations at T1" = c(4:6),
                        "Within-person effects across 6 months" = c(7:12))
  , align = c("l", rep("r", 6))
  , escape = FALSE
  , col_spanners = list(`95\\% CI` = c(3, 4))
#  , placement = "h"
)
```

# Discussion

Current research on the privacy paradox revealed that a significant relation between concerns about online privacy and the online sharing of personal information exists and that it is small [e.g., @baruhOnlinePrivacyConcerns2017]. 
However, whereas the theoretical premise of the privacy paradox actually addresses a within-person effect,
empirical studies have analyzed between-person relations.
On the basis of a representative sample of the German population, from which three waves of data separated by 6 months were collected, we have hence analyzed the privacy paradox by differentiating general between-person relations, short-term within-person relations, as well as long-term within-person effects.

The results of the between-person analyses showed that people who were more concerned about their privacy than others also shared personal information slightly less frequently.
In addition, people who were more concerned about their privacy than others also held substantially more negative attitudes toward disclosing personal information online.
Notably, we found a very strong between-person correlation between attitudes toward information sharing and actual information sharing, implying that typical online disclosure can be precisely predicted by a person's attitude.
Taken together, the cross-sectional results are in line with the extant literature: 
Specifically, the between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fell within the 95% confidence interval of the effect reported by Baruh et al [i.e., _r_ = -.13, 95% CI [-.07, -.18]; -@baruhOnlinePrivacyConcerns2017]. 
Note that the between-person correlations reported here represent averaged measurements across three waves, thereby rendering the findings comparatively robust. 
In conclusion, this study replicates the finding that the privacy paradox does not seem to exist on a between-person level:
The differences between people with regard to their online information sharing behavior can be explained by differences in privacy concerns to a small extent, and by differences in privacy attitudes to a large extent.

The within-person results showed that when a person's privacy concerns increased, the same person also shared slightly less information online than he or she usually did.
Moreover, we found that people who developed more positive attitudes toward sharing personal information online than usual also shared substantially more personal information online.
In conclusion, the results suggest that changes in concerns and attitudes are both partially related to changes in behavior, implying that the privacy paradox does not seem to exist also on a within-person level.

Turning to the potential long-term effects of privacy concerns, the effects that we found were both theoretically negligible and statistically nonsignificant.  
Changes in both privacy concerns and attitudes toward the online sharing of personal information were not related to any meaningful changes in the online sharing of personal information 6 months later.
As an explanation, it might be the case that changes in privacy concern affect information sharing more immediately. 
To test this assumption, we would need study designs with shorter intervals [cf., @keijsersParentalMonitoringAdolescent2016].
Moreover, given that the directions of most longitudinal relations were in line with the between-person and within-person relations, 
it might be the case that longitudinal effects do indeed take place, 
but only that they are very small.
Finally, it could also be that longterm longitudinal effects simply do not exist.

## Limitations

As a major point of criticism, one can argue that some of the effect sizes reported in this study are only small, too small to refute the privacy paradox.
On the one had, they could simply be a manifestation of the so-called "crud factor" [@meehlWhySummariesResearch1990, p. 204], which states that all psychosocial measures are related to one another to some extent.
On the other hand, other factors such as expected benefits might play a more important role [@dienlinExtendedPrivacyCalculus2016].
In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with  information sharing, one should indeed not overestimate the importance of privacy concerns; the impact on the online sharing of personal information could be larger, and other variables also play a role.

The study relied on estimations of information sharing that were based on self-reports. 
As has been shown before, people are not particularly good at estimating the frequency of behaviors that are part of their daily routines [@scharkowAccuracySelfreportedInternet2016].
Whenever possible, future studies should aim to combine self-reports of cognitions with objective observations of behavior.

Finally, please note that the hypotheses presented in this study were not formally preregistered.
At the time when the study was conceived in 2014, we unfortunately were not yet aware of the importance of this practice.

## Future Research

Although this is arguably the first study to demonstrate a within-person relation between concerns about online privacy and the online sharing of personal information, what is still missing is evidence of within-person longitudinal effects. 
The fact that we found significant within-person correlations at T1 but not across the 6-month intervals suggests that longitudinal effects do take place, but that a different time interval might be needed to uncover them.
For theoretical reasons (e.g., due to availability heuristics), it would be plausible to use intervals that are shorter;
for statistical reasons (e.g., because of the high stability of privacy concerns), however, it would even make sense to probe intervals that are longer [@dormannOptimalTimeLags2015].

Linking general personality traits with typical behavior, recent studies have analyzed the privacy paradox by taking an aggregate perspective.
However, it seems important to analyze privacy behaviors from a situational perspective as well, one that accounts for temporal needs, contexts, or communication channels [@masurSituationalPrivacySelfdisclosure2018].
For example, it might be the case that whereas general levels of information sharing are best explained by using privacy _concerns_, situational information sharing might be best explained using privacy _heuristics_, which are less energy consuming and more situational [cf., @sundarUnlockingPrivacyParadox2013].

As a final note, the privacy paradox argues that privacy concerns do not reflect whatsoever on the sharing of personal information online, 
which we view as a strong claim.
However, when a single study does not yield a significant result, it does not necessarily imply a theoretical problem; 
instead, it could also be a statistical miss.
Because when analyzing the privacy paradox we are likely dealing with small effects [@baruhOnlinePrivacyConcerns2017],
and to be able to reliably detect these effect we need large samples. 
In conclusion, we encourage researchers to use statistical designs that allow for sufficient statistical power.

## Conclusion

Taken together, one might ask: What's the big deal? 
Researchers have now come closer to solving the privacy paradox, which is a problem that by producing studies with non-significant results they have created themselves.
Admittedly, there is some truth to this statement. 
At the same time, it is not only researchers who have thought that the online sharing of personal information is paradoxical---the public media have also often suggested that people tend to use the Internet in a somewhat nonsensical or overtly risky way [e.g., @naughtonPrivacyParadoxWhy2019]. 
Hence, given the common interest and involvement in the privacy paradox, providing the public with a scientific answer seems relevant.

Second, being able to show that online behaviors are not paradoxical has another benefit: 
It suggests that online and offline behaviors are not ontologically different. 
In offline contexts, as well, we find that concerns are not closely aligned with behaviors.
For example, although most people are concerned about their health, a considerable number of people are  nonetheless smokers.
However, despite this discrepancy public agencies are aware that they still need to foster concern about health.
For example, in May 2016, the European Union mandated that cigarette packages must display graphic warning labels;
while stable in the years before, sales of cigarettes in Germany in 2016 dropped by 6.3 billion units, equaling 7.7% [@statistischesbundesamt201675Billion2017]. 
Although this result is only a correlation, it suggests that addressing concerns can have societal benefits.
Therefore, proclaiming that the online sharing of personal information is not paradoxical and that concerns about online privacy matter might leverage both people's responsibility and their agency [see also @adjeridPrivacyParadoxObjective2018].

In sum, this study showed that when people were more concerned about their privacy, they also shared a little less personal information about themselves online, 
and if respondents considered sharing personal information not to be a sensible idea, they disclosed even less.
Both this study and the majority of the extant literature do not support a 'privacy paradox'; 
instead, if anything, they suggest a 'privacy orthodox'.

\newpage
# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs"></div>

### 2019-09-16 presentations/2018-05-25_ica/presentation.Rmd
- setting up of novel git-hub repository in order to not include person-related data of prior repository

---
title: "Longitudinal Analysis of the Privacy Paradox"
author: "Tobias Dienlin (@tdienlin), Philipp Masur (@masurphil), Sabine Trepte <br /> <br /> University of Hohenheim"
date: "2018-05-25"
output:
  xaringan::moon_reader:
    css: "theme.css"
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
    self_contained: false
---

layout: true

<div class="my-footer"></div>

```{r load_libraries, echo=FALSE, cache=FALSE, include=FALSE}
pks <- c("RefManageR", "tidyverse")
invisible(lapply(pks, library, character.only = TRUE))
load("../../.RData")
```

```{r load_refs, echo=FALSE, cache=FALSE}
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear", 
           cite.style = "year", 
           style = "markdown",
           hyperlink = FALSE, 
           dashed = FALSE)
my_bib <- ReadBib("../../bibliography/references.bib", check = FALSE)
```

---

# Brief history of privacy paradox

- Privacy concerns **inconsistent with** SNS behavior `r Cite(my_bib, "Acquisti.2003")`

--

- Description of SNS privacy behavior as **paradoxical** `r Cite(my_bib, "Barnes.2006")`

--

- Afterward, explicit studies on privacy paradox

   - Some show **no relation** between privacy concerns and information sharing  `r Cite(my_bib, "Taddicken.2014")`

   - Some show **significant relation** between privacy concerns and information sharing `r Cite(my_bib, "Dienlin.2016a")`

--

- Meta-Analysis: Privacy concerns and information sharing on SNSs are **significantly related, _r_ = -.13** `r Cite(my_bib, "Baruh.2017")`

---

# Aims of current study

- **Longitudinal analysis** of privacy concerns and information sharing

--

- Separation of **between and within-person** variance

--

    - General differences between people?

--

    - Short term relations within a person?

--

    - Long term relations within a person?

--

- Longitudinal analysis of **privacy attitudes**

---

background-image: url(../../figures/model_1.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/model_2.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/model_3.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/model_4.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/model_5.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/model_7.png)
background-size: 850px
background-position: 50% 10%

---

class: center, middle, inverse

# Method

---

# Procedure & participants

- Paper-pencil questionnaire

    - **3 waves**: May 2014, November 2014, May 2015

- **Representative sample** of the German population

    - _N_ = 1,419

    - Age = 54 years, _SD_ = 15 years

    - Female = 49%

---

# Measures

.smaller[
**Privacy concerns** (6 items; CFI = .97, RMSEA = .06, $\omega$ = .90)

- “Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing in the Internet?”
- “Are you concerned about people you do not know obtaining personal information about you from your online activities?”

**Attitudes information sharing** (10 items; CFI = .96, RMSEA = .11, $\omega$ = .94)

- „Do you think that it is sensible to share the following pieces of information online?”
- 1. Second name, 2. First name, 3. Residence (town), 4. Street + no., 5. Financial information, 6. Medical information, 7. e-mail address, 8. Phone number, 9. Job, 10. Education

**Information sharing** (10 items; CFI = .97, RMSEA = .10, $\omega$ = .95)

- How often do you share the following pieces of information online?
- 1. Second name, 2. First name, 3. Residence (town), 4. Street + no., 5. Financial information, 6. Medical information, 7. e-mail address, 8. Phone number, 9. Job, 10. Education
]

---

# Statistics

- Hypotheses tested with **one-tailed** approach, Research Questions with **two-tailed** approach (Holm-Bonferroni-corrected)

--

- Smallest effect size of interest `r Cite(my_bib, "Lakens.2014")`: $\beta$ = **.10**

--

- Alpha and beta-errors **balanced** `r Cite(my_bib, "Rouder.2016")`

--

   - $\alpha$ = `r alpha_balanced %>% round(3)`
   - $\beta$ = `r alpha_balanced %>% round(3)`
   - Power = `r (1 - alpha_balanced) * 100 %>% round(3)`%

--

- Data analysed with Random Intercept-Cross Lagged Panel Model (RI-CLPM) `r Cite(my_bib, "Hamaker.2015")`

---

class: center, middle, inverse

# Results

---

background-image: url(../../figures/results_1.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/results_2.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/results_3.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/results_4.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/results_6.png)
background-size: 850px
background-position: 50% 10%

---

background-image: url(../../figures/results_7.png)
background-size: 850px
background-position: 50% 10%

---

class: center, middle, inverse

# Discussion

---

# Implications

- Important to conduct longitudinal studies to separate between- and within relations

--

- Between people

    - Concerns and sharing **related weakly**
    - Attitudes and sharing **related strongly**

--

- Within people

    - Concerns and sharing **related weakly**
    - Attitudes and sharing **related substantially**
    - **No long-term effects** for concerns and sharing

--

- Future research: Shorter invervals with actual observations of behavior

--

- Information sharing online **not paradoxical**

    - Instead of privacy paradox, rather **privacy orthodox**

---

# References

.small[
```{r, 'refs', results='asis', echo=FALSE}
PrintBibliography(my_bib)
```
]

---

class: center, middle
background-image: url(../../figures/bmbf.png)
background-position: center bottom 50px
background-size: 30%

# Thank you for your attention

This research was funded by the German Federal Ministry of Education and Research (BMBF) Grant 16KIS0094

### 2019-09-16 data/data_wrangling.R

@@ -1,0 +1,199 @@
+# load library
+library(DataCombine); library(magrittr); library(tidyverse)
+
+# load data
+# note: the actual data can be obtained from http://dx.doi.org/10.7802/1937
+# please download the file "privacy-longitudinal-study_data_2019-08-27.csv" and paste into folder "data"
+d_raw <- read_csv("data/privacy-longitudinal-study_data_2019-08-27.csv")
+
+# select variables
+d_wide <- d_raw %>%
+  # first, we need to adapt variable measuring education
+  # currently, each option exists as specific variable
+  # needs to be combined into one single measure
+  mutate(edu = ifelse(T1_SOZ_BIL_08 == 1, "Promotion", ifelse(
+    T1_SOZ_BIL_07 == 1, "Master/Diplom/Magister", ifelse(
+      T1_SOZ_BIL_06 == 1, "Bachelor", ifelse(
+        T1_SOZ_BIL_05 == 1, "Berufausbildung", ifelse(
+          T1_SOZ_BIL_04 == 1, "Abitur", ifelse( 
+            T1_SOZ_BIL_03 == 1, "Realschule", ifelse(
+              T1_SOZ_BIL_02 == 1, "Hauptschule", ifelse(
+                T1_SOZ_BIL_01 == 1, "No Degree", NA
+              ))))))))) %>% 
+  mutate(edu = factor(edu, levels = c("No Degree", "Hauptschule", "Realschule",
+                                        "Berufausbildung", "Abitur", "Bachelor",
+                                        "Master/Diplom/Magister", "Promotion"))) %>%
+  mutate(edu_num = as.integer(edu)) %>% 
+  select(id = T1_paginiernummer, 
+         contains("PBE_ONL"), 
+         contains("PVE"), 
+         contains("PEI"),
+         sex_t = contains("_SOZ_GES_01"), 
+         year_birth_t = contains("_SOZ_ALT_01"),
+         contains("edu"),
+         -contains("_neu"),
+         contains("_TIM_INT"),
+         )
+
+# rename variables
+names <- names(d_wide)
[…]

### 2019-09-17 analyses/analyses.Rmd
- Substituted "RVAideMemoire" with "MVN" due to the former's incompatibility with newer R versions. - Added visual representation of the final model

@@
 required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
-              "MissMech", "papaja", "psych", "pwr", "RVAideMemoire", "semTools", 
+              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
               "sjstats", "tidyverse", "td")
@@
 ```{r multivardis}
-mult_norm_test <- mshapiro.test(d_fs)
+mult_norm_test <- mvn(d_fs)
 print(mult_norm_test)
@@
 With Factor Scores and control variables. This is the final model we report in the paper.
+
+```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
+knitr::include_graphics("../figures/model_7.png")
+```
 

### 2019-09-19 manuscript/manuscript.RmD

@@
   - name          : "Philipp K. Masur"
-    affiliation   : "1"
+    affiliation   : "2"
   - name          : "Sabine Trepte"
@@
     institution   : "University of Hohenheim"
+  - id            : ""
+    institution   : "Johannes Gutenberg University Mainz"
 author_note: |
@@
 The data can be downloaded from http://dx.doi.org/10.7802/1937.
-
 abstract: |
@@
   Together, the results provide further evidence against the privacy paradox.
-
 keywords          : "privacy paradox, privacy concerns, information disclosure, longitudinal analysis, structural equation modeling"
@@
 
-The privacy paradox states that the information disclosure practices of Internet users are problematic: 
+The privacy paradox states that information disclosure practices of Internet users are problematic: 
 Although many people are concerned about their online privacy, they still tend to disclose plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
@@
 whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people [@masurSituationalPrivacySelfdisclosure2018].
-When it comes to concern, it is interesting that they do not seem to be established as a stand-alone theoretical concept in psychology; 
+When it comes to concerns, it is interesting that they do not seem to be established as a stand-alone theoretical concept in psychology; 
 for example, the Oxford Dictionary of Psychology does not feature a designated entry [@colmanDictionaryPsychology2015].
@@
 
-[^power]: Statistical power describes the probability statistically detecting an effect that exists empirically. 
+[^power]: Statistical power describes the probability of statistically detecting an effect that exists empirically. 
 Only with high statistical power is it possible to make valid claims about an effect's existence @cohenPowerPrimer1992.
@@
 
-Although we hypothesized that changes in people's concerns about online privacy will be directly reflected by their behavior, we were not sure about whether there would also be some long-term effects.
+Although we hypothesized that changes in people's concerns about online privacy will be directly reflected by their behavior, we were not sure about whether there would also be long-term effects.
 First, when analyzing potential long-term effects, it is important to choose an interval that is both plausible and relevant.
 For example, it makes a difference whether the effects of alcohol consumption on driving performance are tested 1 min, 1 h, or 1 day after consumption. 
-The main factor that determines an interval's optimal length is stability [@dormannOptimalTimeLags2015].
+One factor that determines an interval's optimal length is the variable's stability [@dormannOptimalTimeLags2015].
 Privacy concerns and privacy attitudes are predominantly trait-like constructs with high stabilities, therefore necessitating longer intervals.
@@
 In general, we believe that it should be possible to find long-term effects. 
-It has been argued that privacy concerns affect privacy behavior [e.g., @heirmanPredictingAdolescentsDisclosure2013]. 
-The underlying theoretical mechanism could be that the emotional part of privacy concerns causes (a) motivated information selection and (b) motivated information processing, which is likely to change actual behavior [@nabiCognitivefunctionalModelEffects1999].
+It has been argued that privacy concerns _affect_ privacy behavior [e.g., @heirmanPredictingAdolescentsDisclosure2013]. 
+The underlying theoretical mechanism could be that the emotional part of privacy concerns causes (a) motivated information selection and (b) motivated information processing, which is likely to _change_ actual behavior [@nabiCognitivefunctionalModelEffects1999].
 Specifically, when privacy concerns increase (e.g., because of experienced or witnessed privacy infringements), people might begin reading more media articles on privacy issues and might also consume these articles more carefully, which could prompt information sharing practices that are more cautious.
@@
 
-It has been argued that privacy attitudes could "bridge the gap" between concerns and information sharing [e.g., @dienlinPrivacyParadoxRelic2015]. 
+It has been argued that privacy attitudes could 'bridge the gap' between concerns and information sharing [e.g., @dienlinPrivacyParadoxRelic2015]. 
 In contrast to privacy concerns, privacy attitudes capture a more explicit, fluctuating cognitive appraisal. 
 Although both variables are related to information disclosure, attitudes are likely to be the better predictor. 
-This reasoning thus follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always, at least in part, influenced by convictions, attitudes, and cost-benefit analyses.
+This reasoning follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always, at least in part, influenced by convictions, attitudes, and cost-benefit analyses.
 Likewise, evolutionary psychology also suggests that although emotions guide behavior in the long run, it is more adaptive if behavior instead reflects a cognitive appraisal; 
@@
 
-The data were analyzed by means of a random-intercepts cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015], a method that already has been used for similar research questions [@dietvorstAdolescentPerceptionsParental2018].
-Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs allows to separate between-person variance from within-person variance. 
+The data were analyzed by means of a random-intercept cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015], a method that already has been used for similar research questions [@dietvorstAdolescentPerceptionsParental2018].
+Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs allow to separate between-person variance from within-person variance. 
 We used factor scores as observed variables to represent the variables' latent structure more closely.
@@
 Wave 1 was completed by 3,278 respondents (response rate: `r round((1 - (3278 / 5286)) * 100, 0)`%), Wave 2 by 2,448 respondents (attrition rate: `r round((1 - (2448 / 3278)) * 100, 0)`%), and Wave 3 by 2,021 respondents (attrition rate: `r round((1 - (2021 / 2448)) * 100, 0)`%).
-We filtered respondents who never used the Internet at all waves, answered fewer than 50% of the items for at least one wave, provided inconsistent birth-dates across measurements, or who did not report sociodemographic variables.
+We filtered respondents who never used the Internet at all waves, answered fewer than 50% of the items in each scale for at least one wave, provided inconsistent birth-dates across measurements, or who did not report sociodemographic variables.
 The final sample consisted of *n* = `r dollar_format(prefix = "")(n_complete)` respondents.
@@
 
-In the final sample, the average age was `r round(age_m, 0)` years (*SD* = `r round(age_sd, 0)` years), and `r (round(male_per, 2) - 1) * 100`% were male. 
+The average age was `r round(age_m, 0)` years (*SD* = `r round(age_sd, 0)` years), and `r (round(male_per, 2) - 1) * 100`% were male. 
 About `r round(edu_col_per, 0)`% reported that they had graduated from college.
@@
 ```{r Distributions, fig.cap="Results of the bivariate relations.
-above the diagonal: zero-order correlation matrix; diagonal: density plots for each variable; below the diagonal: bivariate scatter plots for zero-order correlations.
+Above the diagonal: zero-order correlation matrix; diagonal: density plots for each variable; below the diagonal: bivariate scatter plots for zero-order correlations.
 Solid regression lines represent linear regressions, dashed regression lines represent quadratic regressions.
@@
   tab_results
-  , caption = "Parameter Estimates Obtained in the Random Intercept Cross-Lagged Panel Model"
+  , caption = "Parameter Estimates Obtained in the Random-Intercept Cross-Lagged Panel Model"
   , note = paste0("The between-person correlations represent interpersonal relations.
@@
 Linking general personality traits with typical behavior, recent studies have analyzed the privacy paradox by taking an aggregate perspective.
-However, it seems important to analyze privacy behaviors from a situational perspective as well, one that accounts for temporal needs, contexts, or communication channels [@masurSituationalPrivacySelfdisclosure2018].
+However, it seems important to analyze privacy behaviors from a situational perspective as well, one that accounts for temporal needs, interpersonal perceptions, contextual cues, or characteristics of communication channels [@masurSituationalPrivacySelfdisclosure2018].
 For example, it might be the case that whereas general levels of information sharing are best explained by using privacy _concerns_, situational information sharing might be best explained using privacy _heuristics_, which are less energy consuming and more situational [cf., @sundarUnlockingPrivacyParadox2013].

### 2019-09-19 analyses/analyses.Rmd
- changed output of missing data analyses to data.frame to present results more nicely - deleted unnecessary reliability analyses; now only one for each measures reporting reliability of second order factors

@@
     toc_depth: 5
+    df_print: paged
 editor_options: 
@@
 
-```{r}
+```{r cache=F}
 d_tmp <- select(d_wide, -contains("_m"), -contains("tim"), -contains("T4"), -contains("T5"), -contains("per"), -contains("use"), -c(id, age, edu, edu_num, male))
-(test_mar <- TestMCARNormality(d_tmp))
-test_mar_p <- test_mar$pnormality
+test_mar <- TestMCARNormality(d_tmp)
+
+# print patterns
+as.data.frame(test_mar$patused)
+
+# non-parametric test
+(test_mar_p <- test_mar$pnormality)
 
@@
 summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-reliability(get(paste("fit", name, no, sep = "_")))
-```
-
-#### Longitudinal Invariance
-
-```{r}
-anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_")))
 ```
@@
 summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-reliability(get(paste("fit", name, no, sep = "_")))
 ```
@@
 summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-reliability(get(paste("fit", name, no, sep = "_")))
-```
-
-#### Longitudinal Invariance
-
-```{r}
-anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_")))
+```
+
+### Reliability
+
+```{r}
+reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t1", name, "f", sep = "_"))
+reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t2", name, "f", sep = "_"))
+reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t3", name, "f", sep = "_"))
+```
+
+### Longitudinal Invariance
+
+```{r}
+(anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_"))))
 ```
@@
 ```
+
 ### CFA

### 2019-09-19 manuscript/manuscript.RmD
- minor language edits (up to "attitudes" section)

@@
   The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
-  Using a representative sample of the German population, featuring `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves that were separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
+  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
   Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward the online  sharing of personal information than others (between-person level).
@@
 The privacy paradox states that information disclosure practices of Internet users are problematic: 
-Although many people are concerned about their online privacy, they still tend to disclose plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
-This is problematic, because sharing information online allows to accurately predict a person's future behavior [@bagrowInformationFlowReveals2019].
+Although many people are concerned about their online privacy, they still tend to share plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
 The privacy paradox and its underlying theoretical conundrum is hence of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
 If the privacy paradox really exists, it should inspire worry: 
-It would suggest that online behavior is irrational and that people are revealing too much of their personal lives to unknown third parties, fostering potentially unintended consequences such as commodification, exploitation or inappropriate recontextualization [@boydTakenOutContext2008; @sevignaniPrivacyCapitalismAge2016].
-In conclusion, understanding why people disclose information online and whether this is paradoxical or not represents an important challenge for communication scholars.
+It would suggest that online behavior is irrational and that people are revealing too much of their personal lives to unknown third parties, which can foster potentially unintended consequences such as commodification [@sevignaniPrivacyCapitalismAge2016], inappropriate recontextualization [@boydTakenOutContext2008], or increased predictability of future behavior [@bagrowInformationFlowReveals2019].
+In conclusion, understanding why people disclose information online and whether this is paradoxical or not represents an important challenge for scholars in the social sciences.
 
@@
 Granted, such a between-person perspective is interesting and represents a viable first step in analyzing the relation between these variables.
-At the same time, it is important to emphasize that the privacy paradox actually implies that the research question that should be asked is a within-person (i.e., intrapersonal) relation:
+At the same time, it is important to emphasize that the privacy paradox actually implies a within-person (i.e., intrapersonal) perspective:
 Does a person, if _he or she_ becomes more concerned about online privacy, then also share less personal information?
-This mismatch is problematic because although between-person variance is, except some specific cases, a _necessary_ condition for within-person effects, it is by no means a _sufficient_ condition.
+This mismatch is problematic because although between-person variance is, except for some special cases, a _necessary_ condition for within-person effects, it is by no means a _sufficient_ condition.
 For example, it could be that the between-person relation is determined by another stable third variable. 
-Hence, as the next step in investigating the privacy paradox and to better understand the intrapersonal relation between privacy concerns and information sharing, we now need studies with within-person designs.
+Hence, as the next step in investigating the privacy paradox and to better understand the intrapersonal relation between privacy concerns and information sharing, we need to conduct studies with within-person designs.
 
@@
 "Experiments reveal that very few individuals actually take any action to protect their personal information, even when doing so involves limited costs" (p.1). 
-Three years later, @barnesPrivacyParadoxSocial2006 discussed the behavior of young people using SNSs and coined the expression the "privacy paradox." 
+Three years later, @barnesPrivacyParadoxSocial2006 discussed the behavior of young people using SNSs and coined the expression of the _privacy paradox_. 
 Barnes listed six notions that she considered to be particularly paradoxical: (a) illusion of privacy, (b) high quantity of information sharing, (c) attitude behavior discrepancy, (d) lack of privacy concerns, (e) lack of privacy literacy, and (f) fabrication of false information.
@@
 On the one hand, some studies reported that privacy concerns were not significantly related to the disclosure of personal information [e.g., @grossInformationRevelationPrivacy2005; @taddickenPrivacyParadoxSocial2014; @tufekciCanYouSee2008], lending credence to the privacy paradox.
-On the other hand, a different set of studies showed relations that were statistically significant [@heirmanPredictingAdolescentsDisclosure2013; @walraveConnectingProtectingComparing2012; e.g., @dienlinPrivacyParadoxRelic2015], thereby refuting the privacy paradox.
+On the other hand, a different set of studies showed relations that were statistically significant [e.g., @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013; @walraveConnectingProtectingComparing2012], thereby refuting the privacy paradox.
 
-It is interesting that in a parallel line of research, other studies have also analyzed the relation between privacy concerns and subsequent information sharing; however, the term privacy paradox has often not been mentioned explicitly.
+It is interesting that in a parallel line of research other studies have also analyzed the relation between privacy concerns and information sharing; 
+however, the term privacy paradox has often not been mentioned explicitly. 
 Instead, studies have referred to the so-called _privacy calculus_. 
-The privacy calculus states that sharing personal information is affected by both the respective costs and the anticipated benefits [@culnanInformationPrivacyConcerns1999] and by now, several studies have found empirical support in various online contexts [e.g., @bolUnderstandingEffectsPersonalization2018; @dienlinExtendedPrivacyCalculus2016; @krasnovaOnlineSocialNetworks2010].
+The privacy calculus states that sharing personal information is affected by both the respective costs and the anticipated benefits [@culnanInformationPrivacyConcerns1999].
+By now, several studies have found empirical support for the privacy calculus in various online contexts [e.g., @bolUnderstandingEffectsPersonalization2018; @dienlinExtendedPrivacyCalculus2016; @krasnovaOnlineSocialNetworks2010].
 
@@
 whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people [@masurSituationalPrivacySelfdisclosure2018].
-When it comes to concerns, it is interesting that they do not seem to be established as a stand-alone theoretical concept in psychology; 
-for example, the Oxford Dictionary of Psychology does not feature a designated entry [@colmanDictionaryPsychology2015].
-In general, however, concern is defined as a "marked interest or regard usually arising through a personal tie or relationship" that also reflects an "uneasy state of blended interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
-A concern therefore partially represents a latent _motivation_ (or increased attention) to invest oneself in a specific entity and a negatively valenced _emotion_ (or affective cognition).
+When it comes to concerns, it is interesting that they do not seem to be established as a stand-alone theoretical concept in psychology: 
+For example, the Oxford Dictionary of Psychology does not feature a designated entry [@colmanDictionaryPsychology2015].
+In general, however, a concern is defined as a "marked interest or regard usually arising through a personal tie or relationship" that also reflects an "uneasy state of blended interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
+A concern therefore partially represents both a latent _motivation_ (or increased attention) to invest oneself in a specific entity and a negatively valenced _emotion_ (or affective condition).
 As such, a concern is not predominantly the result of a deliberate explicit cognition; instead, it primarily reflects an automatic implicit perception.
@@
 As a theoretical construct, privacy concerns can hence be categorized as an affective motivational disposition.
-As such, they have similarities with many other concepts such as emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (approval, dissent), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).
+As such, there are many similarities with other concepts, which includes emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (approval, dissent), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).
 
-The online sharing of personal information, on the other hand, captures how much person-related information people share when they use the Internet, including, for example, information about their age, sex, name, address, health, or finances.
+The online sharing of personal information, on the other hand, captures how much person-related information people share when they use the Internet, which includes, for example, information about their age, sex, name, address, health, or finances.
 Information sharing can be differentiated from communication and self-disclosure:
-Whereas communication is broad because it includes all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011], self-disclosure is narrow because it focuses on deliberate revelations about the true self to others [e.g., @jourardTransparentSelf1964]
+Whereas communication is broad because it comprises all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011], self-disclosure is narrow because it focuses on deliberate revelations about the true self to others [e.g., @jourardTransparentSelf1964]
 
@@
 
-It is somewhat surprising that the literature seems to lack explicit theoretical treatises on why and how human behavior should be specifically affected by concerns.
+It is somewhat surprising that the literature seems to lack explicit theoretical treatises on why and how human behavior should be affected by concerns specifically.
 More fortunately, however, there are several theoretical insights regarding how the affective motivational concepts presented above can pertain to behavior.
@@
 For example, let us consider the concept that is perhaps closest to concerns, emotions.
-By causing fight or flight reactions, emotions are potentially the most primordial trigger of behavior as they are considered an adaptive mechanism that fosters the evolution of a species [@dolanEmotionCognitionBehavior2002].
+By causing fight or flight reactions, emotions are potentially the most primordial trigger of behavior, 
+they are considered an adaptive mechanism that fosters the evolution of a species [@dolanEmotionCognitionBehavior2002].
 With their direct link to the amygdala, emotions can already trigger reactions subcortically [i.e., without activation of the more recently evolved cortical structures; @dolanEmotionCognitionBehavior2002].
@@
 and people who are more concerned about their bodies engage in more physical exercise [@reelRelationsBodyConcerns2007].
-Hence, it seems reasonable to also expect that if a person's concerns about online privacy change, this change should be reflected in a change in the extent to which this person will share personal information online.
+Hence, it seems reasonable to expect that also concerns about online privacy should be reflected in the online sharing of personal information.
 
-At the same time, there are several variables that are likely to diminish the relation.
-Most prominently, there is the so-called "attitude behavior gap", which pertains to the idea that people often act against their own attitudes [e.g., @fishbeinPredictingChangingBehavior2010]. 
-For example, despite endorsing the importance of physical health, a large part of the population does not exercise regularly.
+At the same time, there are some factors that are likely to diminish the relation.
+Most prominently, there is the so-called _attitude behavior gap_, which pertains to the idea that people often act against their own attitudes [e.g., @fishbeinPredictingChangingBehavior2010]. 
+For example, despite endorsing the importance of physical health, a large part of the population still does not exercise regularly.
 Transferred to the privacy paradox, it should not be surprising to encounter this general discrepancy also in the specific context of privacy concerns and information sharing. 
@@
 @trepteRiskyBehaviorsHow2014 listed several factors that can additionally attenuate the relation:
-if the concerns miss any actual strength,
+concerns might be missing any actual strength,
 a lack of negative personal experiences, 
-or distortions due to situational constraints such as social desirability.
+and situational constraints due to social desirability.
 
-Finally, there are also some methodological reasons that can explain why some studies did not find statistically significant relations even though they probably exist empirically.
-In general, researchers are always confronted with the so-called Duhem-Quine problem, which holds that it is impossible to test theories in isolation, because empirical tests always rely on auxiliary assumptions [e.g., @dienesUnderstandingPsychologyScience2008].
+Finally, there are also some methodological reasons that can explain why some studies did not find statistically significant relations, even when they exist empirically.
+In general, researchers are always confronted with the _Duhem-Quine problem_, which holds that it is impossible to test theories in isolation, because empirical tests always rely on auxiliary assumptions [e.g., @dienesUnderstandingPsychologyScience2008].
 In other words, if a psychological experiment fails, we do not know whether the theory is wrong or the questionnaire subpar. 
 This tenet is particularly relevant for the privacy paradox: 
-Detecting statistical significance for small effects---and in this case, we should expect to find effects that are small---is more challenging because it means that large samples are necessary to guarantee sufficient statistical power.[^power]
+Detecting statistical significance for small effects---and in this case, we should expect to find small effects---is more challenging because it means that large samples are necessary to guarantee sufficient statistical power.[^power]
 Precisely, in order to be capable of detecting a correlation between privacy concerns and information sharing in 95% of all cases, which @baruhOnlinePrivacyConcerns2017 estimated to be _r_ = -.13, we need a sample of _N_ = `r pwr.r.test(r = -.13, sig.level = .05, power = .95)$n %>%  round(0)` people.
 The reality, however, looks different: 
-In their meta-analysis, Baruh et al. reported a median sample size of _N_ = 300.
+In their meta-analysis, Baruh et al. reported a median sample size of _N_ = 300, which can explain why several studies did not find significant effects.
 
 [^power]: Statistical power describes the probability of statistically detecting an effect that exists empirically. 
-Only with high statistical power is it possible to make valid claims about an effect's existence @cohenPowerPrimer1992.
+Only with high statistical power is it possible to make valid claims about an effect's existence [@cohenPowerPrimer1992].
 
-To conclude, in line with prior research [@baruhOnlinePrivacyConcerns2017] and the within-person rationales that we have presented above, we first expected to find a significant relation between privacy concerns and information sharing both on the between-person level and the within-person level.
-Second, given the strong premise that concerns should be reflected in contiguous behaviors, alongside the existence of several diminishing factors, we expected to find a small relation between concerns about online privacy and the online sharing of personal information also on the within-person level.
+To conclude, in line with prior research [@baruhOnlinePrivacyConcerns2017] and the within-person rationales that we have presented above, we expect to find a small significant relation between privacy concerns and information sharing, both on the between-person level and the within-person level.
 
@@
 
-Although we hypothesized that changes in people's concerns about online privacy will be directly reflected by their behavior, we were not sure about whether there would also be long-term effects.
+Although we hypothesize that changes in people's concerns about online privacy will be reflected by their behavior directly, we are not sure about whether there will also be long-term effects.
 First, when analyzing potential long-term effects, it is important to choose an interval that is both plausible and relevant.
@@
 In general, we believe that it should be possible to find long-term effects. 
-It has been argued that privacy concerns _affect_ privacy behavior [e.g., @heirmanPredictingAdolescentsDisclosure2013]. 
-The underlying theoretical mechanism could be that the emotional part of privacy concerns causes (a) motivated information selection and (b) motivated information processing, which is likely to _change_ actual behavior [@nabiCognitivefunctionalModelEffects1999].
+It has been argued that privacy concerns affect privacy behavior in the long run [e.g., @heirmanPredictingAdolescentsDisclosure2013]. 
+The underlying theoretical mechanism could be that the emotional part of privacy concerns causes (a) motivated information selection and (b) motivated information processing, which is likely to change actual behavior [@nabiCognitivefunctionalModelEffects1999].
 Specifically, when privacy concerns increase (e.g., because of experienced or witnessed privacy infringements), people might begin reading more media articles on privacy issues and might also consume these articles more carefully, which could prompt information sharing practices that are more cautious.
@@
 Finally, there could also be no long-term relation after all. 
-For example, people might have already become used to sharing information online and this might stifle any further cognitive or emotional processing, a rationale central to the observation of so-called _privacy cynicism_ [e.g., @hoffmannPrivacyCynicismNew2016].
+For example, people might have already become used to sharing information online, which might stifle any further cognitive or emotional processing -- a rationale central to the observation of so-called _privacy cynicism_ [e.g., @hoffmannPrivacyCynicismNew2016].
 

### 2019-09-19 analyses/analyses.Rmd
- small language edits to manuscript - small changes to abstract - small changed to analysis file; e.g., updated order of analyses

@@
 
-### Latent correlation matrix with plots
+# Correlation matrix and distributions
 
@@
 summary(fit)
-icc_pri_con <- icc(fit)
+(icc_pri_con <- icc(fit))
 
@@
 summary(fit)
-icc_inf_sha_att <- icc(fit)
+(icc_inf_sha_att <- icc(fit))
 
@@
 summary(fit)
-icc_inf_sha_beh <- icc(fit)
+(icc_inf_sha_beh <- icc(fit))
 ```
@@
 In what follows, please find all information about our final model we present in the paper.
+
+## Visualization
+
+```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
+knitr::include_graphics("../figures/model_7.png")
+```
+
+## Results
+
+```{r}
+model <- '
+# between relations
+pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
+inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
+inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t2_inf_sha_att_fs + 1*t3_inf_sha_att_fs
+
+# within person changes
+t1_pri_con_w =~ 1*t1_pri_con_fs
+t2_pri_con_w =~ 1*t2_pri_con_fs
+t3_pri_con_w =~ 1*t3_pri_con_fs
+t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
+t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
+t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
+t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
+t2_inf_sha_att_w =~ 1*t2_inf_sha_att_fs
+t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs
+
+# within person effects
+t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
+t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
+t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
+t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
+t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
+t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
+
+# covariances
+pri_con_b ~~ cor_b_1*inf_sha_att_b + cor_b_2*inf_sha_beh_b
+inf_sha_att_b ~~ cor_b_3*inf_sha_beh_b
+t1_pri_con_w ~~ cor_w_1*t1_inf_sha_att_w + cor_w_2*t1_inf_sha_beh_w
+t1_inf_sha_att_w ~~ cor_w_3*t1_inf_sha_beh_w
+t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
+t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
+t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
+t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
+
+# setting variances of observed variables to zero
+t1_pri_con_fs ~~ 0*t1_pri_con_fs
+t2_pri_con_fs ~~ 0*t2_pri_con_fs
+t3_pri_con_fs ~~ 0*t3_pri_con_fs
+t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
+t2_inf_sha_att_fs ~~ 0*t2_inf_sha_att_fs
+t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
+t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
+t2_inf_sha_beh_fs ~~ 0*t2_inf_sha_beh_fs
+t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs
+
+# control variables
+t1_pri_con_fs ~ age + edu_num + male
+t2_pri_con_fs ~ age + edu_num + male
+t3_pri_con_fs ~ age + edu_num + male
+t1_inf_sha_beh_fs ~ age + edu_num + male
+t2_inf_sha_beh_fs ~ age + edu_num + male
+t3_inf_sha_beh_fs ~ age + edu_num + male
+t1_inf_sha_att_fs ~ age + edu_num + male
+t2_inf_sha_att_fs ~ age + edu_num + male
+t3_inf_sha_att_fs ~ age + edu_num + male
+'
+fit <- sem(model, data = d_wide, orthogonal = TRUE, missing = "ML")
+summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
+```
 

### 2019-09-19 manuscript/manuscript.RmD
- small language edits to manuscript - small changes to abstract - small changed to analysis file; e.g., updated order of analyses

@@
     institution   : "University of Hohenheim"
-  - id            : ""
+  - id            : "2"
     institution   : "Johannes Gutenberg University Mainz"
@@
   Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
-  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward the online  sharing of personal information than others (between-person level).
+  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level).
   Next, people who were more concerned than usual also shared slightly less information than usual (within-person level). 
@@
   Together, the results provide further evidence against the privacy paradox.
-keywords          : "privacy paradox, privacy concerns, information disclosure, longitudinal analysis, structural equation modeling"
+keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
 wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
@@
                       pkgs = c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
-                               "MissMech", "papaja", "psych", "pwr", "RVAideMemoire", 
+                               "MissMech", "MVN", "papaja", "psych", "pwr",  
                                "semTools", "sjstats", "tidyverse", "td"), 
@@
 
-The privacy paradox states that information disclosure practices of Internet users are problematic: 
+The privacy paradox states that the information disclosure practices of Internet users are problematic: 
 Although many people are concerned about their online privacy, they still tend to share plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
@@
 Likewise, evolutionary psychology also suggests that although emotions guide behavior in the long run, it is more adaptive if behavior instead reflects a cognitive appraisal; 
-a tenet arguably reflected best by the phylogenetic development of the neocortex or the general dominion of the human race.
+a tenet arguably reflected best by the phylogenetic development of the neocortex or, if you want, the general dominion of the human race.
 These rationales have also found some empirical support. 
-For example, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure was moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].
+For example, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure was more moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].
 
@@
 
-Concerning the potential long-term relations of privacy attitudes, the same situation exists here as mentioned above:
-Given that no prior research exists on long-term relations, several scenarios seem plausible.
-For example, attitudes could either have long-term relations or not, and information sharing could either foster or diminish privacy attitudes.
+Concerning the potential long-term relations of privacy attitudes, we are confronted with the same situation mentioned above:
+Given that we are not aware of research on long-term relations, several scenarios seem plausible.
+For example, attitudes could either have long-term relations or not, and information sharing could either foster privacy attitudes or diminish them.
 
@@
 
-We follow the recommendation by @lakensJustifyYourAlpha2017 and first justify the choice of our alpha level. 
+We follow the recommendation by @lakensJustifyYourAlpha2018 and first justify the choice of our alpha level. 
 We determined adequate error margins by considering the potential implications of both false positive and false negative findings (i.e., alpha and beta errors): 
 On the one hand, if we committed an alpha error, we would wrongfully conclude that people's concerns and behaviors are consistent. 
-Communicating such a false result to the public would unjustly reassure and placate people when they should instead be more alert.
+Communicating such a false result to the public might unjustly reassure and placate people when they should instead be more alert.
 On the other hand, if we committed a beta error, we would wrongfully conclude that individuals behave paradoxically.
@@
 Next, we set a maximum error rate of 5% for both alpha and beta. 
-As the smallest effect size of interest [SESOI; @lakensPerformingHighpoweredStudies2014], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses; significantly smaller effects were not considered able to offer support.
+As the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses;
+significantly smaller effects were not considered able to offer support.
 The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
@@
 We tested all research questions by regressing variables on all other measures obtained 6 months earlier.
-Given that we had three points of measurement, this resulted in two estimates for each Research Question.
-As we did not expect longitudinal effects to differ across time, they were constrained to be equal across all waves, thereby producing one single general measure of each effect instead of two time-specific ones.
+Given that we had three points of measurement, this resulted in two estimates for each research question.
+As we did not expect longitudinal effects to differ across time, they were constrained to be equal across all waves, which produces one single general measure of each effect instead of two time-specific ones.
 Fit was assessed according to the common criteria as described by @klinePrinciplesPracticeStructural2016. 
@@
 For the analyses, coding, and typesetting, we used `r r_citations`.
-The code, additional analyses, and a reproducible version of the manuscript can be accessed in the Online Supplementary Material (OSM) at https://osf.io/4wabh.
+The code, additional analyses, and a reproducible version of this manuscript can be accessed in the Online Supplementary Material (OSM) at https://osf.io/4wabh.
 
@@
 Other publications linked to the project can be accessed at https://osf.io/y35as/.
-The data come from a longitudinal, paper-and-pencil questionnaire study, in which a representative sample of the German population (16 years and older) was surveyed on overall five occasions.
+The data come from a longitudinal paper-and-pencil questionnaire study, in which a representative sample of the German population (16 years and older) was surveyed on overall five occasions.
 The data can be downloaded from http://dx.doi.org/10.7802/1937.
@@
 In this CATI screening, 5,286 respondents agreed to participate in all following waves. 
-
 Wave 1 was completed by 3,278 respondents (response rate: `r round((1 - (3278 / 5286)) * 100, 0)`%), Wave 2 by 2,448 respondents (attrition rate: `r round((1 - (2448 / 3278)) * 100, 0)`%), and Wave 3 by 2,021 respondents (attrition rate: `r round((1 - (2021 / 2448)) * 100, 0)`%).
@@
 Therefore, Full Information Maximum Likelihood (FIML) estimation was conducted using all available data.
-
 The average age was `r round(age_m, 0)` years (*SD* = `r round(age_sd, 0)` years), and `r (round(male_per, 2) - 1) * 100`% were male. 
@@
 Factor analyses suggested a second-order factor structure with five first-order factors. 
-The first first-order factor subsumed financial and medical information, the second covered first and last name, the third included place of residence and street (including house number), the fourth email address and phone number, and the fifth contained information about education and current job.
+The first first-order factor subsumed financial and medical information, the second first and last name, the third place of residence and street (including house number), the fourth email address and phone number, and the fifth information about education and current job.
 The means were _M_~t1~ = `r desc[["t1_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
@@
 Results revealed that the random intercepts of the two variables were significantly correlated (`r coeffs_txt(fit_riclpm, "cor_b_2", one_sided = TRUE)`). 
-Respondents who---on average across all three waves---were more concerned about their privacy than others also shared slightly less personal information online.
+Hence, respondents who---on average across all three waves---were more concerned about their privacy than others also shared slightly less personal information online.
 The effect was small.
-However, when looking at the standardized effect's confidence interval ($\beta$ = `r effect_std_ci[["est.std"]] %>% my_round("std")`, 95% CI [`r effect_std_ci[["ci.lower"]] %>% my_round("std")`, `r  effect_std_ci[["ci.upper"]] %>% my_round("std")`]), it was not significantly smaller than our SESOI of $beta$ = .10.
+However, when looking at the standardized effect's confidence interval (i.e., $\beta$ = `r effect_std_ci[["est.std"]] %>% my_round("std")`, 95% CI [`r effect_std_ci[["ci.lower"]] %>% my_round("std")`, `r  effect_std_ci[["ci.upper"]] %>% my_round("std")`]), it was not significantly smaller than our SESOI of $beta$ = .10.
 Thus, Hypothesis 1 was supported.
@@
 Hypothesis 2 proposed that if people perceived more concerns about their online privacy than they usually do, they would also share less personal information online than they usually do.
-Results revealed a small significant correlation (`r coeffs_txt(fit_riclpm, "cor_w_2", one_sided = TRUE)`), suggesting that if respondents were more concerned about their online privacy at T1 than usual, they also shared less personal information online at T1.
+Results revealed a small significant correlation (`r coeffs_txt(fit_riclpm, "cor_w_2", one_sided = TRUE)`), suggesting that if respondents were more concerned about their online privacy at T1 than usual, they also shared less personal information online at T1 than usual.
 In conclusion, the results supported Hypothesis 2.
@@
 The results revealed a medium-sized negative correlation between the two variables on the between-person level (`r coeffs_txt(fit_riclpm, "cor_b_1", one_sided = TRUE)`). 
-Thus, people who---on average across all three waves---reported being more concerned about their online privacy relative to the rest of the sample, were also moderately more likely to hold a more negative attitude toward the online sharing of personal information, thereby supporting Hypothesis 3.1.
-Hypothesis 3.2 posited that people who held more positive attitudes toward the online sharing of personal information than others would also share more personal information online than others. 
-Results showed a very strong between-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_b_3", one_sided = TRUE)`): 
-When averaged across all three waves, if people had more positive attitudes toward the online sharing of personal information than others, they were much more likely to actually share personal information online.
+Thus, people who---on average across all three waves---reported being more concerned about their online privacy relative to the rest of the sample, were also substantially more likely to hold a more negative attitude toward the online sharing of personal information, thereby supporting Hypothesis 3.1.
+Hypothesis 3.2 stated that people who held more positive attitudes toward the online sharing of personal information than others would also share more personal information online than others. 
+Results showed a very strong between-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_b_3", one_sided = TRUE)`). 
+In other words, when averaged across all three waves, if people had more positive attitudes toward the online sharing of personal information than others, they were much more likely to actually share personal information online.
 In conclusion, the results supported Hypothesis 3.2.
@@
 Hypothesis 4.2 proposed that people who held more positive attitudes toward the online sharing of personal information than usual would also share more personal information online than usual. 
-Results showed a moderate within-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_w_3", one_sided = TRUE)`), indicating that when respondents had more positive attitudes toward the online sharing of personal information at T1 than usual, they also shared more personal information online.
+Results showed a moderate within-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_w_3", one_sided = TRUE)`), indicating that when respondents had more positive attitudes toward the online sharing of personal information at T1 than usual, they also shared more personal information online than usual.
 In conclusion, the results supported Hypothesis 4.2.
@@
 With Research Question 2.1, we analyzed the longitudinal relations of concerns about online privacy and positive attitudes toward the online sharing of personal information. 
-No significant effect was found, `r coeffs_txt(fit_riclpm, "b1")`.
-Regarding Research Question 2.2, again no significant longitudinal relations emerged between privacy attitudes and privacy concerns 6 months later `r coeffs_txt(fit_riclpm, "a2")`.
+No significant effect was found (`r coeffs_txt(fit_riclpm, "b1")`).
+Regarding Research Question 2.2, again no significant longitudinal relations emerged between privacy attitudes and privacy concerns 6 months later (`r coeffs_txt(fit_riclpm, "a2")`).
 
@@
 
-Table \@ref(tab:Results1) presents an overview of all results and the OSM presents additional information and supplementary analyses (e.g., results of the RI-CLPM without socio-demographic control variables or results of alternative multilevel regression models).
+Table \@ref(tab:Results1) presents an overview of all results.
 
@@
   , note = paste0("The between-person correlations represent interpersonal relations.
-For example, results showed that people who were more concerned than others, averaged across all 3 waves, also shared less information than others.
+For example, results showed that people who were more concerned than others, averaged across all three waves, also shared less information than others.
 The within-person parameters reflect how intrapersonal changes in one variable are related to intra-personal changes in another.
@@
 
-Current research on the privacy paradox revealed that a significant relation between concerns about online privacy and the online sharing of personal information exists and that it is small [e.g., @baruhOnlinePrivacyConcerns2017].
+Current research on the privacy paradox suggests a significant and small relation between concerns about online privacy and the online sharing of personal information [e.g., @baruhOnlinePrivacyConcerns2017].
 However, whereas the theoretical premise of the privacy paradox actually addresses a within-person effect,
@@
 Taken together, the cross-sectional results are in line with the extant literature: 
-Specifically, the between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fell within the 95% confidence interval of the effect reported by Baruh et al [i.e., _r_ = -.13, 95% CI [-.07, -.18]; -@baruhOnlinePrivacyConcerns2017].
+Specifically, the between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fell within the 95% confidence interval of the effect reported by Baruh et al.
+[-@baruhOnlinePrivacyConcerns2017] (i.e., _r_ = -.13, 95% CI [-.07, -.18]).
 Note that the between-person correlations reported here represent averaged measurements across three waves, thereby rendering the findings comparatively robust. 
@@
 The within-person results showed that when a person's privacy concerns increased, the same person also shared slightly less information online than he or she usually did.
-Moreover, we found that people who developed more positive attitudes toward sharing personal information online than usual also shared substantially more personal information online.
-In conclusion, the results suggest that changes in concerns and attitudes are both partially related to changes in behavior, implying that the privacy paradox does not seem to exist also on a within-person level.
+Moreover, we found that people who developed more positive attitudes toward the online sharing of personal information than usual also shared substantially more personal information online.
+In conclusion, the results suggest that changes in concerns and attitudes are both partially related to changes in behavior, implying that also on a within-person level the privacy paradox does not seem to exist.
 
 Turning to the potential long-term effects of privacy concerns, the effects that we found were both theoretically negligible and statistically nonsignificant.
-Changes in both privacy concerns and attitudes toward the online sharing of personal information were not related to any meaningful changes in the online sharing of personal information 6 months later.
+Specifically, changes in both privacy concerns and attitudes toward the online sharing of personal information were not related to any meaningful changes in the online sharing of personal information 6 months later.
 As an explanation, it might be the case that changes in privacy concern affect information sharing more immediately. 
@@
 but only that they are very small.
-Finally, it could also be that longterm longitudinal effects simply do not exist.
+Of course, it could also be that longterm longitudinal effects simply do not exist.
 
@@
 
-As a major point of criticism, one can argue that some of the effect sizes reported in this study are only small, too small to refute the privacy paradox.
-On the one had, they could simply be a manifestation of the so-called "crud factor" [@meehlWhySummariesResearch1990, p.
+As a major point of criticism, one can argue that some of the effect sizes reported in this study are only small, too small to effectively refute the privacy paradox.
+On the one hand, they could simply be a manifestation of the so-called "crud factor" [@meehlWhySummariesResearch1990, p.
 204], which states that all psychosocial measures are related to one another to some extent.
 On the other hand, other factors such as expected benefits might play a more important role [@dienlinExtendedPrivacyCalculus2016].
-In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, one should indeed not overestimate the importance of privacy concerns; the impact on the online sharing of personal information could be larger, and other variables also play a role.
+In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, one should indeed not overestimate the importance of privacy concerns; the impact on the online sharing of personal information could be larger, and other variables surely play a role as well.
 
@@
 which we view as a strong claim.
-However, when a single study does not yield a significant result, it does not necessarily imply a theoretical problem; 
+However, when a single study does not yield a significant result it does not necessarily imply a theoretical problem; 
 instead, it could also be a statistical miss.
 Because when analyzing the privacy paradox we are likely dealing with small effects [@baruhOnlinePrivacyConcerns2017],
-and to be able to reliably detect these effect we need large samples. 
+and to be able to reliably detect small effect we need large samples. 
 In conclusion, we encourage researchers to use statistical designs that allow for sufficient statistical power.
@@
 Admittedly, there is some truth to this statement. 
-At the same time, it is not only researchers who have thought that the online sharing of personal information is paradoxical---the public media have also often suggested that people tend to use the Internet in a somewhat nonsensical or overtly risky way [e.g., @naughtonPrivacyParadoxWhy2019].
+At the same time, it is not only researchers who have thought that the online sharing of personal information is paradoxical---the public media have also often suggested that people tend to use the Internet in a somewhat nonsensical way [e.g., @naughtonPrivacyParadoxWhy2019].
 Hence, given the common interest and involvement in the privacy paradox, providing the public with a scientific answer seems relevant.
@@
 It suggests that online and offline behaviors are not ontologically different. 
-In offline contexts, as well, we find that concerns are not closely aligned with behaviors.
-For example, although most people are concerned about their health, a considerable number of people are nonetheless smokers.
+In offline contexts, we similarly find that concerns are not always closely aligned with behaviors.
+For example, although most people are concerned about their health, a considerable number of people smoke cigarettes nonetheless.
 However, despite this discrepancy public agencies are aware that they still need to foster concern about health.
@@
 Although this result is only a correlation, it suggests that addressing concerns can have societal benefits.
-Therefore, proclaiming that the online sharing of personal information is not paradoxical and that concerns about online privacy matter might leverage both people's responsibility and their agency [see also @adjeridPrivacyParadoxObjective2018].
+Therefore, proclaiming that the online sharing of personal information is not paradoxical and that concerns about online privacy indeed matter might leverage both people's responsibility and their agency [cf., @adjeridPrivacyParadoxObjective2018].
 
@@
 and if respondents considered sharing personal information not to be a sensible idea, they disclosed even less.
-Both this study and the majority of the extant literature do not support a 'privacy paradox'; 
-instead, if anything, they suggest a 'privacy orthodox'.
+Both this study and the majority of the extant literature do not support a 'privacy paradox'. 
+Instead, if anything, they suggest a 'privacy orthodox'.
 

### 2019-10-18 analyses/analyses.Rmd
- checked with newly merged data-set, exact same results

@@
 output: 
-  # pdf_document: 
   html_document:
@@
 
-```{r, echo = FALSE, include = FALSE}
+```{r, echo=F, include=F}
 # defaults
 set.seed(170819)
-options(digits = 3, width = 120, max.print = 100000)
-knitr::opts_chunk$set(echo = T, error = F, message = F, tidy = T, warning = F, cache = T)
-```
-
-```{r Packages, include = FALSE, cache=F}
+options(digits=3, width=120, max.print=100000)
+knitr::opts_chunk$set(echo=T, error=F, message=F, tidy=T, warning=F, cache=F)
+```
+
+```{r Packages, include=F, cache=F}
 # relevant packages
@@
 
-```{r include=FALSE}
+```{r include=F}
 # Extract descriptives to report in paper
@@
 
-```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
-knitr::include_graphics("../figures/model_7.png")
-```
-
 ```{r}

### 2019-10-18 data/data_wrangling.R

@@ -3,8 +3,9 @@ library(DataCombine); library(magrittr); library(tidyverse)
 
 # load data
 # note: the actual data can be obtained from http://dx.doi.org/10.7802/1937
-# please download the file "privacy-longitudinal-study_data_2019-08-27.csv" and paste into folder "data"
-d_raw <- read_csv("data/privacy-longitudinal-study_data_2019-08-27.csv")
+# please download the most current file "privacy-longitudinal-study_data_YYYY-MM-DD.csv"
+# paste this file into folder "data"
+d_raw <- read_csv("data/privacy-longitudinal-study_data_2019-10-10.csv")
 
 # select variables
 d_wide <- d_raw %>%

### 2020-04-23 analyses.Rmd
setting up github website

--- 2019-10-18 analyses/analyses.Rmd
@@
     df_print: paged
-editor_options: 
-  chunk_output_type: inline
+    code_folding: hide
 ---
@@
 options(digits=3, width=120, max.print=100000)
-knitr::opts_chunk$set(echo=T, error=F, message=F, tidy=T, warning=F, cache=F)
-```
-
-```{r Packages, include=F, cache=F}
+knitr::opts_chunk$set(echo=T, error=F, message=F, tidy=T, warning=F, cache=T)
+```
+
+```{r Packages, cache=F, results='hide'}
 # relevant packages
@@
 # export bib library
-r_refs("../bibliography/r-references.bib")
-```
-
-```{r datawrangling, include=F}
+r_refs("bibliography/r-references.bib")
+
 # first run "data_wranling.R", in order to create these objects
-d_wide <- read_csv("../data/data_wide.csv")
-d_wide_all <- read_csv("../data/data_wide_all.csv")
-d_long <- read_csv("../data/data_long.csv")
-```
-
-```{r include=F}
+d_wide <- read_csv("data/data_wide.csv")
+d_wide_all <- read_csv("data/data_wide_all.csv")
+d_long <- read_csv("data/data_long.csv")
+
 # Extract descriptives to report in paper
@@
 ```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
-knitr::include_graphics("../figures/model_7.png")
+knitr::include_graphics("figures/model_7.png")
 ```
@@
 ```{r cache=F}
-save.image("../data/workspace.RData")
-```
+save.image("data/workspace.RData")
+```

### 2020-04-23 index.Rmd
setting up github website

---
title: "Longitudinal Analysis of the Privacy Calculus"
---

On this website, you can find the companion material for the paper _A Longitudinal Analysis of the Privacy Paradox_.

You can either read the paper [online](manuscript.html) or download it as [pdf](manuscript.pdf). You can also find the detailed code and summaries of the [analyses](analyses.html) that were reported in the paper.

Please note that this OSM does not contain the actual data, which can be downloaded from http://dx.doi.org/10.7802/1937.

This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy_calc_exp). You can download the material, file an issue, or submit a pull request.

### 2020-04-23 manuscript.RmD
setting up github website

--- 2019-09-19 manuscript/manuscript.RmD
@@
 bibliography      : 
-  - [../bibliography/references.bib]
-  - [../bibliography/r-references.bib]
+  - [bibliography/references.bib]
+  - [bibliography/r-references.bib]
 lang              : "english"
@@
 mask              : no
-output            : papaja::apa6_pdf
-# output            : papaja::apa6_word
-header-includes:
-  - \setlength{\parskip}{0em}
-  - \raggedbottom
-editor_options: 
-  chunk_output_type: inline
+# to compile as pdf
+# (a) move file "_site.yml" to folder "tmp"
+# (b) uncomment the following lines; comment lines after "output: html_document ..."
+# output            : papaja::apa6_pdf
+# header-includes:
+#   - \setlength{\parskip}{0em}
+#   - \raggedbottom
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+    toc_depth: 2
 ---
-```{r knitr-set-up}
+
+```{r knitr-set-up, include=F}
 knitr::opts_chunk$set(echo=F, error=F, message=F, tidy=T, warning=F)
@@
 
-```{r load-packs, include = F}
+```{r load-packs, include=F}
 # Load and install packages
-devtools::install_github("tdienlin/td@v.0.0.2.5")
-devtools::install_github("crsh/papaja")
+# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncommen to install
 packages <- c("broman", "kableExtra", "knitr", "lavaan", "magrittr", "papaja"
@@
 # load r-bib
-r_citations <- cite_r("../bibliography/r-references.bib", 
+r_citations <- cite_r("bibliography/r-references.bib", 
                       footnote = FALSE, 
@@
 # Load Workspace
-load("../data/workspace.RData")
+load("data/workspace.RData")
 ```
+
+# Introduction
 

### 2020-04-23 analyses.Rmd
created new file "analyses additional"

@@
 devtools::install_github("tdienlin/td@v.0.0.2.5")
-required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
-              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
+required <- c("GGally", "ggplot2", "kableExtra", "knitr",
+              "lavaan", "lme4","magrittr", "MissMech", 
+              "papaja", "psych", "pwr", "MVN", "semTools", 
               "sjstats", "tidyverse", "td")
@@
 
-# Items
-## Privacy Concern
+In what follows, we report the models that were run to obtain the results reported in the manuscript. To see the underlying code, click on the button `code`.
+
+# Sociodemographics
+
+```{r}
+n_complete <- nrow(d_wide)
+age_m <- mean(d_wide$age)
+age_sd <- sd(d_wide$age)
+male_per <- 1 - mean(d_wide$male)
+edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100
+tibble(
+  "N" = n_complete,
+  "Age" = age_m,
+  "Age SD" = age_sd,
+  "Male perc." = male_per,
+  "College perc." = edu_col_per
+  ) %>% 
+  kable() %>% 
+  kable_styling("striped")
+```
+
+# Analysis of Missing Values
+
+```{r cache=F}
+d_tmp <- select(d_wide, -contains("_m"), -contains("tim"), -contains("T4"), -contains("T5"), -contains("per"), -contains("use"), -c(id, age, edu, edu_num, male))
+test_mar <- TestMCARNormality(d_tmp)
+
+# print patterns
+as.data.frame(test_mar$patused)
+
+# non-parametric test
+(test_mar_p <- test_mar$pnormality)
+
+# calculate percentage of missing data
+na_per <- mean(c(d_wide$t1_na_per, d_wide$t2_na_per, d_wide$t3_na_per)) * 100
+```
+
+Visual inspection of the missing value patterns as well as the non-parametric test suggested that all missing values could be considered to be missing at random (_p_ `r test_mar$pnormality %>% td::my_round("p_txt")`).
+
+# Measures
+
+In what follows, we report the measures we collected, including their items, factorial validity, reliability, and ICC.
+For the measures' longitudinal invariance, see [additional analyses](analyses_additional.Rmd).
+
+## Concerns about online privacy
+### Items
 
@@
 
-## Attitude Toward Online Sharing of Personal Information
-
-Now we will deal with information sharing on the Internet. Do you think that it is sensible to disclose the following pieces of information online, i.e., via the Internet?
-
-1. Financial information (bank data, account balances…)
-2. Medical information (health, medical records…)
-3. Second name
-4. First name
-5. Residence
-6. Street and house number
-7. Email address
-8. Phone number
-9. Photos (of you)
-10. Job (past and present)
-11. Education
-
-(NA = “no Internet user / no reply”, 1 = "not sensible at all", 2 = "somewhat not sensible", 3 = "in part", 4 = "somewhat sensible", 5 = "very sensible")
-
-## Online Sharing of Personal Information
-
-In the following, please indicate how often you disclose the following information on the Internet. How often do you disclose the following pieces of information online, i.e., on the Internet?
-
-1. Financial information (bank data, account balances…)
-2. Medical information (health, medical records…)
-3. Second name
-4. First name
-5. Residence
-6. Street and house number
-7. Email address
-8. Phone number
-9. Photos (of you)
-10. Job (past and present)
-11. Education
-
-(NA = “no Internet user / no reply”, 1 = "every day", 2 = "weekly", 3 = "monthly", 4 = "less than that", 5 = "never")
-
-# Power Analyses
-
-```{r power}
-n_complete <- nrow(d_wide)
-alpha <- .05
-power <- .95
-sesoi <- .1
-n <- n_complete
-n_apriori <- pwr.r.test(r = sesoi, sig.level = alpha, power = power)$n
-power_achieved_h <- pwr.r.test(r = sesoi, sig.level = alpha, n = n, alternative = "greater")$power
-alpha_balanced_h <- balance_errors(sesoi, n, one_tailed = TRUE)
-power_balanced_h <- 1 - alpha_balanced_h
-power_achieved_rq <- pwr.r.test(r = sesoi, sig.level = alpha, n = n)$power
-alpha_balanced_rq <- balance_errors(sesoi, n, one_tailed = FALSE)
-power_balanced_rq <- 1 - alpha_balanced_rq
-```
-
-A-priori power analyses revealed that N = `r n_apriori` people would be needed to find effects with a size of _r_ = `r sesoi` with a power of `r power`.
-
-Overall, the data of `r n` respondents could be used for our analyses.
-As a result, alpha and beta errors were balanced when using an alpha of `r alpha_balanced_h %>% round(3)`, resulting in an achieved power of `r power_balanced_h %>% round(3)`.
-
-# Sociodemographics
-
-```{r}
-age_m <- mean(d_wide$age)
-age_sd <- sd(d_wide$age)
-male_per <- mean(d_wide$male)
-edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100
-```
-
-# Analysis of Missing Values
-
-```{r cache=F}
-d_tmp <- select(d_wide, -contains("_m"), -contains("tim"), -contains("T4"), -contains("T5"), -contains("per"), -contains("use"), -c(id, age, edu, edu_num, male))
-test_mar <- TestMCARNormality(d_tmp)
-
-# print patterns
-as.data.frame(test_mar$patused)
-
-# non-parametric test
-(test_mar_p <- test_mar$pnormality)
-
-# calculate percentage of missing data
-na_per <- mean(c(d_wide$t1_na_per, d_wide$t2_na_per, d_wide$t3_na_per)) * 100
-```
-
-Visual inspection of the missing value patterns as well as the non-parametric test suggested that all missing values could be considered to be missing at random (_p_ `r test_mar$pnormality %>% td::my_round("p_txt")`).
-
-# Factor Analyses
-## Concerns about online privacy
-### EFA
+### CFA
 
@@
 # set-up
-no <- 0
 name <- "pri_con"
 d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
-model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
-factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
-print(factan, sort = TRUE, cut = .3)
-```
-
-### CFA
-#### First-Order Model Unconstrained
-
-```{r}
 model <- '
 # create factors
-t1_pri_con_f =~ 1*t1_pri_con_01 + t1_pri_con_02 + t1_pri_con_03 + t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06 + t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
-t2_pri_con_f =~ 1*t2_pri_con_01 + t2_pri_con_02 + t2_pri_con_03 + t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06 + t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
-t3_pri_con_f =~ 1*t3_pri_con_01 + t3_pri_con_02 + t3_pri_con_03 + t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06 + t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09
-
-# error covariances
-t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
-t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
-t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_01 ~~ t1_pri_con_01
-t2_pri_con_02 ~~ t1_pri_con_02 
-t2_pri_con_03 ~~ t1_pri_con_03
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-reliability(get(paste("fit", name, no, sep = "_")))
-```
-
-#### First-Order Model Constrained
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_01 + b2*t1_pri_con_02 + b3*t1_pri_con_03 + b4*t1_pri_con_04 + b5*t1_pri_con_05 + b6*t1_pri_con_06 + b7*t1_pri_con_07 + b8*t1_pri_con_08 + b9*t1_pri_con_09
-t2_pri_con_f =~ 1*t2_pri_con_01 + b2*t2_pri_con_02 + b3*t2_pri_con_03 + b4*t2_pri_con_04 + b5*t2_pri_con_05 + b6*t2_pri_con_06 + b7*t2_pri_con_07 + b8*t2_pri_con_08 + b9*t2_pri_con_09
-t3_pri_con_f =~ 1*t3_pri_con_01 + b2*t3_pri_con_02 + b3*t3_pri_con_03 + b4*t3_pri_con_04 + b5*t3_pri_con_05 + b6*t3_pri_con_06 + b7*t3_pri_con_07 + b8*t3_pri_con_08 + b9*t3_pri_con_09
-
-# error covariances
-t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
-t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
-t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_01 ~~ t1_pri_con_01
-t2_pri_con_02 ~~ t1_pri_con_02 
-t2_pri_con_03 ~~ t1_pri_con_03
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Unconstrained
-
-In what follows, we analyze a second-order solution of privacy concerns.
-Here, we distinguish between horizontal privacy concerns (items 4, 5, 6) and vertical privacy concerns (items 7, 8, 9).
-The resulting model fits the data better than the unidimensional one.
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_f1 + t1_pri_con_f2
-t2_pri_con_f =~ 1*t2_pri_con_f1 + t2_pri_con_f2
-t3_pri_con_f =~ 1*t3_pri_con_f1 + t3_pri_con_f2
-t1_pri_con_f1 =~ 1*t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06
-t1_pri_con_f2 =~ 1*t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
-t2_pri_con_f1 =~ 1*t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06
-t2_pri_con_f2 =~ 1*t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
-t3_pri_con_f1 =~ 1*t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06
-t3_pri_con_f2 =~ 1*t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09
+t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
+t2_pri_con_f =~ 1*t2_pri_con_f1 + a2*t2_pri_con_f2
+t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
+t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
+t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
+t2_pri_con_f1 =~ 1*t2_pri_con_04 + b2*t2_pri_con_05 + b3*t2_pri_con_06
+t2_pri_con_f2 =~ 1*t2_pri_con_07 + c2*t2_pri_con_08 + c3*t2_pri_con_09
+t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
+t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09
 
@@
 '
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Constrained
-
-```{r}
+assign(paste("fit", name, sep = "_"), cfa(model, d_wide, missing = "ML"))
+summary(get(paste("fit", name, sep = "_")), standardized = TRUE, fit.measures = TRUE)
+```
+
+### Reliability
+
+```{r}
+reliabilityL2(get(paste("fit", name, sep = "_")), paste("t1", name, "f", sep = "_"))
+reliabilityL2(get(paste("fit", name, sep = "_")), paste("t2", name, "f", sep = "_"))
+reliabilityL2(get(paste("fit", name, sep = "_")), paste("t3", name, "f", sep = "_"))
+```
+
+### ICC
+
+```{r}
+fit <- lmer(pri_con_m ~ 1 + (1 | id), filter(d_long, wave < 4))
+summary(fit)
+(icc_pri_con <- icc(fit))
+```
+
+## Attitude Toward Online Sharing of Personal Information
+### Items
+
+Now we will deal with information sharing on the Internet. Do you think that it is sensible to disclose the following pieces of information online, i.e., via the Internet?
+
+1. Financial information (bank data, account balances…)
+2. Medical information (health, medical records…)
+3. Second name
+4. First name
+5. Residence
+6. Street and house number
+7. Email address
+8. Phone number
+9. Photos (of you)
+10. Job (past and present)
+11. Education
+
+(NA = “no Internet user / no reply”, 1 = "not sensible at all", 2 = "somewhat not sensible", 3 = "in part", 4 = "somewhat sensible", 5 = "very sensible")
+
+### CFA
+
+```{r}
+name <- "inf_sha_att"
+d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
 model <- '
 # create factors
-t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
-t2_pri_con_f =~ 1*t2_pri_con_f1 + a2*t2_pri_con_f2
-t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
-t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
-t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
-t2_pri_con_f1 =~ 1*t2_pri_con_04 + b2*t2_pri_con_05 + b3*t2_pri_con_06
-t2_pri_con_f2 =~ 1*t2_pri_con_07 + c2*t2_pri_con_08 + c3*t2_pri_con_09
-t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
-t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09
-
-# error covariances
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-### Reliability
-
-```{r}
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t1", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t2", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t3", name, "f", sep = "_"))
-```
-
-### Longitudinal Invariance
-
-```{r}
-(anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_"))))
-```
-
-## Attitude Toward Online Sharing of Personal Information
-### EFA
-
-```{r}
-no <- 0
-name <- "inf_sha_att"
-d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
-model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
-factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
-print(factan, sort = TRUE, cut = .3)
-```
-
-### CFA
-#### First-Order Model Unconstrained
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_01 + t1_pri_con_02 + t1_pri_con_03 + t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06 + t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
-t2_pri_con_f =~ 1*t2_pri_con_01 + t2_pri_con_02 + t2_pri_con_03 + t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06 + t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
-t3_pri_con_f =~ 1*t3_pri_con_01 + t3_pri_con_02 + t3_pri_con_03 + t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06 + t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09
-
-# error covariances
-t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
-t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
-t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_01 ~~ t1_pri_con_01
-t2_pri_con_02 ~~ t1_pri_con_02 
-t2_pri_con_03 ~~ t1_pri_con_03
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### First-Order Model Constrained
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_01 + a2*t1_pri_con_02 + a3*t1_pri_con_03 + a4*t1_pri_con_04 + a5*t1_pri_con_05 + a6*t1_pri_con_06 + a7*t1_pri_con_07 + a8*t1_pri_con_08 + a9*t1_pri_con_09
-t2_pri_con_f =~ 1*t2_pri_con_01 + a2*t2_pri_con_02 + a3*t2_pri_con_03 + a4*t2_pri_con_04 + a5*t2_pri_con_05 + a6*t2_pri_con_06 + a7*t2_pri_con_07 + a8*t2_pri_con_08 + a9*t2_pri_con_09
-t3_pri_con_f =~ 1*t3_pri_con_01 + a2*t3_pri_con_02 + a3*t3_pri_con_03 + a4*t3_pri_con_04 + a5*t3_pri_con_05 + a6*t3_pri_con_06 + a7*t3_pri_con_07 + a8*t3_pri_con_08 + a9*t3_pri_con_09
-
-# error covariances
-t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
-t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
-t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_01 ~~ t1_pri_con_01
-t2_pri_con_02 ~~ t1_pri_con_02 
-t2_pri_con_03 ~~ t1_pri_con_03
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Unconstrained
-
-We again run models in which we build sub-dimensions referring to the empirical EFA results and theoretical considerations. Resulting model fits the data better than unidimensional one.
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + t1_inf_sha_att_f2 + t1_inf_sha_att_f3 + t1_inf_sha_att_f4 + t1_inf_sha_att_f5
-t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + t2_inf_sha_att_f2 + t2_inf_sha_att_f3 + t2_inf_sha_att_f4 + t2_inf_sha_att_f5
-t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + t3_inf_sha_att_f2 + t3_inf_sha_att_f3 + t3_inf_sha_att_f4 + t3_inf_sha_att_f5
-t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + t1_inf_sha_att_02
-t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + t1_inf_sha_att_04
-t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + t1_inf_sha_att_06
-t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + t1_inf_sha_att_08
-t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + t1_inf_sha_att_11
-t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + t2_inf_sha_att_02
-t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + t2_inf_sha_att_04
-t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + t2_inf_sha_att_06
-t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + t2_inf_sha_att_08
-t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + t2_inf_sha_att_11
-t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + t3_inf_sha_att_02
-t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + t3_inf_sha_att_04
-t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + t3_inf_sha_att_06
-t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + t3_inf_sha_att_08
-t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + t3_inf_sha_att_11
+t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + o2*t1_inf_sha_att_f2 + o3*t1_inf_sha_att_f3 + o4*t1_inf_sha_att_f4 + o5*t1_inf_sha_att_f5
+t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + o2*t2_inf_sha_att_f2 + o3*t2_inf_sha_att_f3 + o4*t2_inf_sha_att_f4 + o5*t2_inf_sha_att_f5
+t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + o2*t3_inf_sha_att_f2 + o3*t3_inf_sha_att_f3 + o4*t3_inf_sha_att_f4 + o5*t3_inf_sha_att_f5
+t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + j2*t1_inf_sha_att_02
+t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + k2*t1_inf_sha_att_04
+t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + l2*t1_inf_sha_att_06
+t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + m2*t1_inf_sha_att_08
+t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + n2*t1_inf_sha_att_11
+t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + j2*t2_inf_sha_att_02
+t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + k2*t2_inf_sha_att_04
+t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + l2*t2_inf_sha_att_06
+t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + m2*t2_inf_sha_att_08
+t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + n2*t2_inf_sha_att_11
+t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + j2*t3_inf_sha_att_02
+t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + k2*t3_inf_sha_att_04
+t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + l2*t3_inf_sha_att_06
+t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + m2*t3_inf_sha_att_08
+t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + n2*t3_inf_sha_att_11
 
@@
 '
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model at All Waves Constrained
-
-```{r}
+assign(paste("fit", name, sep = "_"), cfa(model, d_wide, missing = "ML"))
+summary(get(paste("fit", name, sep = "_")), standardized = TRUE, fit.measures = TRUE)
+```
+
+### Reliability
+
+```{r}
+reliabilityL2(get(paste("fit", name, sep = "_")), paste("t1", name, "f", sep = "_"))
+reliabilityL2(get(paste("fit", name, sep = "_")), paste("t2", name, "f", sep = "_"))
+reliabilityL2(get(paste("fit", name, sep = "_")), paste("t3", name, "f", sep = "_"))
+```
+
+### ICC
+
+```{r}
+fit <- lmer(inf_sha_att_m ~ 1 + (1 | id), filter(d_long, wave < 4))
+summary(fit)
+(icc_inf_sha_att <- icc(fit))
+```
+
+## Online Sharing of Personal Information
+### Items
+
+In the following, please indicate how often you disclose the following information on the Internet. How often do you disclose the following pieces of information online, i.e., on the Internet?
+
+1. Financial information (bank data, account balances…)
+2. Medical information (health, medical records…)
+3. Second name
+4. First name
+5. Residence
+6. Street and house number
+7. Email address
+8. Phone number
+9. Photos (of you)
+10. Job (past and present)
+11. Education
+
+(NA = “no Internet user / no reply”, 1 = "every day", 2 = "weekly", 3 = "monthly", 4 = "less than that", 5 = "never")
+
+### CFA
+
+```{r}
+name <- "inf_sha_beh"
+d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
 model <- '
 # create factors
-t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + o2*t1_inf_sha_att_f2 + o3*t1_inf_sha_att_f3 + o4*t1_inf_sha_att_f4 + o5*t1_inf_sha_att_f5
-t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + o2*t2_inf_sha_att_f2 + o3*t2_inf_sha_att_f3 + o4*t2_inf_sha_att_f4 + o5*t2_inf_sha_att_f5
-t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + o2*t3_inf_sha_att_f2 + o3*t3_inf_sha_att_f3 + o4*t3_inf_sha_att_f4 + o5*t3_inf_sha_att_f5
-t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + j2*t1_inf_sha_att_02
-t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + k2*t1_inf_sha_att_04
-t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + l2*t1_inf_sha_att_06
-t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + m2*t1_inf_sha_att_08
-t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + n2*t1_inf_sha_att_11
-t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + j2*t2_inf_sha_att_02
-t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + k2*t2_inf_sha_att_04
-t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + l2*t2_inf_sha_att_06
-t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + m2*t2_inf_sha_att_08
-t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + n2*t2_inf_sha_att_11
-t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + j2*t3_inf_sha_att_02
-t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + k2*t3_inf_sha_att_04
-t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + l2*t3_inf_sha_att_06
-t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + m2*t3_inf_sha_att_08
-t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + n2*t3_inf_sha_att_11
-
-# factor covariance
-t1_inf_sha_att_f ~~ t2_inf_sha_att_f + t3_inf_sha_att_f
-t2_inf_sha_att_f ~~ t3_inf_sha_att_f
-
-# item error covariance
-t1_inf_sha_att_01 ~~ t2_inf_sha_att_01 + t3_inf_sha_att_01
-t2_inf_sha_att_01 ~~ t3_inf_sha_att_01
-t1_inf_sha_att_02 ~~ t2_inf_sha_att_02 + t3_inf_sha_att_02
-t2_inf_sha_att_02 ~~ t3_inf_sha_att_02
-t1_inf_sha_att_03 ~~ t2_inf_sha_att_03 + t3_inf_sha_att_03
-t2_inf_sha_att_03 ~~ t3_inf_sha_att_03
-t1_inf_sha_att_04 ~~ t2_inf_sha_att_04 + t3_inf_sha_att_04
-t2_inf_sha_att_04 ~~ t3_inf_sha_att_04
-t1_inf_sha_att_05 ~~ t2_inf_sha_att_05 + t3_inf_sha_att_05
-t2_inf_sha_att_05 ~~ t3_inf_sha_att_05
-t1_inf_sha_att_06 ~~ t2_inf_sha_att_06 + t3_inf_sha_att_06
-t2_inf_sha_att_06 ~~ t3_inf_sha_att_06
-t1_inf_sha_att_07 ~~ t2_inf_sha_att_07 + t3_inf_sha_att_07
-t2_inf_sha_att_07 ~~ t3_inf_sha_att_07
-t1_inf_sha_att_08 ~~ t2_inf_sha_att_08 + t3_inf_sha_att_08
-t2_inf_sha_att_08 ~~ t3_inf_sha_att_08
-t1_inf_sha_att_10 ~~ t2_inf_sha_att_10 + t3_inf_sha_att_10
-t2_inf_sha_att_10 ~~ t3_inf_sha_att_10
-t1_inf_sha_att_11 ~~ t2_inf_sha_att_11 + t3_inf_sha_att_11
-t2_inf_sha_att_11 ~~ t3_inf_sha_att_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-### Reliability
-
-```{r}
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t1", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t2", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t3", name, "f", sep = "_"))
-```
-
-### Longitudinal Invariance
-
-```{r}
-(anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_"))))
-```
-
-## Online Sharing of Personal Information
-### EFA
-
-```{r}
-no <- 0
-name <- "inf_sha_beh"
-d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
-model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
-factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
-print(factan, sort = TRUE, cut = .3)
-```
-
-### CFA
-#### First-Order Model Unconstrained
-
-First-order model shows poor fit. Needs to be adapted (see second order model).
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_01 + t1_inf_sha_beh_02 + t1_inf_sha_beh_03 + t1_inf_sha_beh_04 + t1_inf_sha_beh_05 + t1_inf_sha_beh_06 + t1_inf_sha_beh_07 + t1_inf_sha_beh_08 + t1_inf_sha_beh_09 + t1_inf_sha_beh_10 + t1_inf_sha_beh_11
-t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_01 + t2_inf_sha_beh_02 + t2_inf_sha_beh_03 + t2_inf_sha_beh_04 + t2_inf_sha_beh_05 + t2_inf_sha_beh_06 + t2_inf_sha_beh_07 + t2_inf_sha_beh_08 + t2_inf_sha_beh_09 + t2_inf_sha_beh_10 + t2_inf_sha_beh_11
-t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_01 + t3_inf_sha_beh_02 + t3_inf_sha_beh_03 + t3_inf_sha_beh_04 + t3_inf_sha_beh_05 + t3_inf_sha_beh_06 + t3_inf_sha_beh_07 + t3_inf_sha_beh_08 + t3_inf_sha_beh_09 + t3_inf_sha_beh_10 + t3_inf_sha_beh_11
-
-# factor covariance
-t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
-t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f
-
-# item error covariance
-t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
-t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
-t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
-t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
-t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
-t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
-t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
-t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
-t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
-t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
-t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
-t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
-t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
-t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
-t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
-t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
-t1_inf_sha_beh_09 ~~ t2_inf_sha_beh_09 + t3_inf_sha_beh_09
-t2_inf_sha_beh_09 ~~ t3_inf_sha_beh_09
-t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
-t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
-t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
-t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### First-Order Model Constrained
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_01 + c2*t1_inf_sha_beh_02 + c3*t1_inf_sha_beh_03 + c4*t1_inf_sha_beh_04 + c5*t1_inf_sha_beh_05 + c6*t1_inf_sha_beh_06 + c7*t1_inf_sha_beh_07 + c8*t1_inf_sha_beh_08 + c9*t1_inf_sha_beh_09 + c10*t1_inf_sha_beh_10 + c11*t1_inf_sha_beh_11
-t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_01 + c2*t2_inf_sha_beh_02 + c3*t2_inf_sha_beh_03 + c4*t2_inf_sha_beh_04 + c5*t2_inf_sha_beh_05 + c6*t2_inf_sha_beh_06 + c7*t2_inf_sha_beh_07 + c8*t2_inf_sha_beh_08 + c9*t2_inf_sha_beh_09 + c10*t2_inf_sha_beh_10 + c11*t2_inf_sha_beh_11
-t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_01 + c2*t3_inf_sha_beh_02 + c3*t3_inf_sha_beh_03 + c4*t3_inf_sha_beh_04 + c5*t3_inf_sha_beh_05 + c6*t3_inf_sha_beh_06 + c7*t3_inf_sha_beh_07 + c8*t3_inf_sha_beh_08 + c9*t3_inf_sha_beh_09 + c10*t3_inf_sha_beh_10 + c11*t3_inf_sha_beh_11
-
-# factor covariance
-t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
-t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f
-
-# item error covariance
-t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
-t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
-t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
-t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
-t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
-t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
-t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
-t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
-t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
-t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
-t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
-t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
-t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
-t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
-t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
-t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
-t1_inf_sha_beh_09 ~~ t2_inf_sha_beh_09 + t3_inf_sha_beh_09
-t2_inf_sha_beh_09 ~~ t3_inf_sha_beh_09
-t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
-t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
-t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
-t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Unconstrained
-
-Second-order model shows much improved fit.
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + t1_inf_sha_beh_f2 + t1_inf_sha_beh_f3 + t1_inf_sha_beh_f4 + t1_inf_sha_beh_f5
-t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_f1 + t2_inf_sha_beh_f2 + t2_inf_sha_beh_f3 + t2_inf_sha_beh_f4 + t2_inf_sha_beh_f5
-t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + t3_inf_sha_beh_f2 + t3_inf_sha_beh_f3 + t3_inf_sha_beh_f4 + t3_inf_sha_beh_f5
-t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + t1_inf_sha_beh_02
-t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + t1_inf_sha_beh_04
-t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + t1_inf_sha_beh_06
-t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + t1_inf_sha_beh_08
-t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + t1_inf_sha_beh_11
-t2_inf_sha_beh_f1 =~ 1*t2_inf_sha_beh_01 + t2_inf_sha_beh_02
-t2_inf_sha_beh_f2 =~ 1*t2_inf_sha_beh_03 + t2_inf_sha_beh_04
-t2_inf_sha_beh_f3 =~ 1*t2_inf_sha_beh_05 + t2_inf_sha_beh_06
-t2_inf_sha_beh_f4 =~ 1*t2_inf_sha_beh_07 + t2_inf_sha_beh_08
-t2_inf_sha_beh_f5 =~ 1*t2_inf_sha_beh_10 + t2_inf_sha_beh_11
-t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + t3_inf_sha_beh_02
-t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + t3_inf_sha_beh_04
-t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + t3_inf_sha_beh_06
-t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + t3_inf_sha_beh_08
-t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + t3_inf_sha_beh_11
+t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + o2*t1_inf_sha_beh_f2 + o3*t1_inf_sha_beh_f3 + o4*t1_inf_sha_beh_f4 + o5*t1_inf_sha_beh_f5
+t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_f1 + o2*t2_inf_sha_beh_f2 + o3*t2_inf_sha_beh_f3 + o4*t2_inf_sha_beh_f4 + o5*t2_inf_sha_beh_f5
+t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + o2*t3_inf_sha_beh_f2 + o3*t3_inf_sha_beh_f3 + o4*t3_inf_sha_beh_f4 + o5*t3_inf_sha_beh_f5
+t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + j2*t1_inf_sha_beh_02
+t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + k2*t1_inf_sha_beh_04
+t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + l2*t1_inf_sha_beh_06
+t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + m2*t1_inf_sha_beh_08
+t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + n2*t1_inf_sha_beh_11
+t2_inf_sha_beh_f1 =~ 1*t2_inf_sha_beh_01 + j2*t2_inf_sha_beh_02
+t2_inf_sha_beh_f2 =~ 1*t2_inf_sha_beh_03 + k2*t2_inf_sha_beh_04
+t2_inf_sha_beh_f3 =~ 1*t2_inf_sha_beh_05 + l2*t2_inf_sha_beh_06
+t2_inf_sha_beh_f4 =~ 1*t2_inf_sha_beh_07 + m2*t2_inf_sha_beh_08
+t2_inf_sha_beh_f5 =~ 1*t2_inf_sha_beh_10 + n2*t2_inf_sha_beh_11
+t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + j2*t3_inf_sha_beh_02
+t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + k2*t3_inf_sha_beh_04
+t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + l2*t3_inf_sha_beh_06
+t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + m2*t3_inf_sha_beh_08
+t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + n2*t3_inf_sha_beh_11
 
@@
 '
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Constrained
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + o2*t1_inf_sha_beh_f2 + o3*t1_inf_sha_beh_f3 + o4*t1_inf_sha_beh_f4 + o5*t1_inf_sha_beh_f5
-t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_f1 + o2*t2_inf_sha_beh_f2 + o3*t2_inf_sha_beh_f3 + o4*t2_inf_sha_beh_f4 + o5*t2_inf_sha_beh_f5
-t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + o2*t3_inf_sha_beh_f2 + o3*t3_inf_sha_beh_f3 + o4*t3_inf_sha_beh_f4 + o5*t3_inf_sha_beh_f5
-t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + j2*t1_inf_sha_beh_02
-t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + k2*t1_inf_sha_beh_04
-t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + l2*t1_inf_sha_beh_06
-t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + m2*t1_inf_sha_beh_08
-t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + n2*t1_inf_sha_beh_11
-t2_inf_sha_beh_f1 =~ 1*t2_inf_sha_beh_01 + j2*t2_inf_sha_beh_02
-t2_inf_sha_beh_f2 =~ 1*t2_inf_sha_beh_03 + k2*t2_inf_sha_beh_04
-t2_inf_sha_beh_f3 =~ 1*t2_inf_sha_beh_05 + l2*t2_inf_sha_beh_06
-t2_inf_sha_beh_f4 =~ 1*t2_inf_sha_beh_07 + m2*t2_inf_sha_beh_08
-t2_inf_sha_beh_f5 =~ 1*t2_inf_sha_beh_10 + n2*t2_inf_sha_beh_11
-t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + j2*t3_inf_sha_beh_02
-t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + k2*t3_inf_sha_beh_04
-t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + l2*t3_inf_sha_beh_06
-t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + m2*t3_inf_sha_beh_08
-t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + n2*t3_inf_sha_beh_11
-
-# factor covariance
-t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
-t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f
-
-# item error covariance
-t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
-t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
-t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
-t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
-t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
-t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
-t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
-t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
-t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
-t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
-t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
-t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
-t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
-t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
-t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
-t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
-t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
-t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
-t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
-t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
+assign(paste("fit", name, sep = "_"), cfa(model, d_wide, missing = "ML"))
+summary(get(paste("fit", name, sep = "_")), standardized = TRUE, fit.measures = TRUE)
 ```
@@
 ```{r}
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t1", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t2", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t3", name, "f", sep = "_"))
-```
-
-### Longitudinal Invariance
-
-```{r}
-(anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_"))))
-```
-
-## All Measures in one Model 
-### Second Order
+reliabilityL2(get(paste("fit", name, sep = "_")), paste("t1", name, "f", sep = "_"))
+reliabilityL2(get(paste("fit", name, sep = "_")), paste("t2", name, "f", sep = "_"))
+reliabilityL2(get(paste("fit", name, sep = "_")), paste("t3", name, "f", sep = "_"))
+```
+
+### ICC
+
+```{r}
+fit <- lmer(inf_sha_beh_m ~ 1 + (1 | id), filter(d_long, wave < 4))
+summary(fit)
+(icc_inf_sha_beh <- icc(fit))
+```
+
+## Baseline Model
+
+We next estimate a model containing all measures, which is then used to extract factor scores.
 
@@
 name <- "all_vars"
-no <- 0
 model <- '
@@
 '
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-### Extract Factor Scores
-
-```{r}
-d_fs <- lavPredict(get(paste("fit", name, no, sep = "_")), type = "ov") %>% 
+assign(paste("fit", name, sep = "_"), cfa(model, d_wide, missing = "ML"))
+summary(get(paste("fit", name, sep = "_")), standardized = TRUE, fit.measures = TRUE)
+```
+
+Extract factor scores.
+
+```{r}
+d_fs <- lavPredict(get(paste("fit", name, sep = "_")), type = "ov") %>% 
   as.data.frame() %>% 
@@
 
-# Correlation matrix and distributions
+# Power Analyses
+
+```{r power}
+alpha <- .05
+power <- .95
+sesoi <- .1
+n <- n_complete
+n_apriori <- pwr.r.test(r = sesoi, sig.level = alpha, power = power)$n
+power_achieved_h <- pwr.r.test(r = sesoi, sig.level = alpha, n = n, alternative = "greater")$power
+alpha_balanced_h <- balance_errors(sesoi, n, one_tailed = TRUE)
+power_balanced_h <- 1 - alpha_balanced_h
+power_achieved_rq <- pwr.r.test(r = sesoi, sig.level = alpha, n = n)$power
+alpha_balanced_rq <- balance_errors(sesoi, n, one_tailed = FALSE)
+power_balanced_rq <- 1 - alpha_balanced_rq
+```
+
+A-priori power analyses revealed that N = `r n_apriori` people would be needed to find effects with a size of _r_ = `r sesoi` with a power of `r power`.
+
+Overall, the data of `r n` respondents could be used for our analyses.
+As a result, alpha and beta errors were balanced when using an alpha of `r alpha_balanced_h %>% round(3)`, resulting in an achieved power of `r power_balanced_h %>% round(3)`.
+
+# Results
+
+In what follows, please find all information about our final model we present in the paper.
+
+## Correlation matrix and distributions
 
@@
 corr_plot <- ggpairs(d_fs,
-                     # upper = list(continuous = wrap(td::cor_matrix, data = d_fs)),
                      lower = list(continuous = wrap(td::scat_plot, coords = c(1, 5, 1, 5)))) + 
@@
 
-# ICCs
-
-Next, we determine the Intraclass Correlation Coefficients (ICC), to determine how much variance in the measures is due to between-person differences versus within-person changes.
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + (1 | id), filter(d_long, wave < 4))
-summary(fit)
-(icc_pri_con <- icc(fit))
-
-fit <- lmer(inf_sha_att_m ~ 1 + (1 | id), filter(d_long, wave < 4))
-summary(fit)
-(icc_inf_sha_att <- icc(fit))
-
-fit <- lmer(inf_sha_beh_m ~ 1 + (1 | id), filter(d_long, wave < 4))
-summary(fit)
-(icc_inf_sha_beh <- icc(fit))
-```
-
-# Results
-
-In what follows, please find all information about our final model we present in the paper.
-
-## Visualization
+## Visualization of Model
 
@@
 
-## Results
+## Assumptions
+
+We first test the assumption of multivariate normal distribution.
+
+```{r multivardis}
+mult_norm_test <- mvn(d_fs)
+print(mult_norm_test)
+```
+
+Results show that the assumption of multivariate normal distribution was violated.
+Hence, it'd be preferable to conduct robust Maximum Likelihood Estimation.
+However, using robust estimation it is not possible to run SEM on all data using Full Information Maximum Likehoood (FIML).
+Given that we consider it more important to include as much information as possible and that estimators often produce similar results, we decided to estimate the following models using regular maximum likehood.
+
+## RI-CLPM
+
+In what follows, please find the results of the main model we report in the paper.
 
@@
 
-# Additional Analyses
-## RI-CLPM
-### Assumptions
-#### Multivariate Normal Distribution
-
-```{r multivardis}
-mult_norm_test <- mvn(d_fs)
-print(mult_norm_test)
-```
-
-Results show that the assumption of multivariate normal distribution was violated.
-Hence, it'd be preferrable to conduct robust Maximum Likelihood Estimation.
-However, using robust estimation it's not possible to run SEM on all data using Full Information Maximum Likehoood (FIML).
-Given that we consider it more important to include as much information as possible and that estimators often produce similar results, we decided to estimate the following models using regular maximum likehood.
-
-### Two Variables
-
-Here, we look at the bivariate relations of privacy concerns and information sharing.
-This is interesting, because in the paper we also address privacy attitudes, thereby potentially attentuating the effect of privacy concerns.
-However, when analyzing only these two variables we do not find larger effects sizes.
-
-#### Model 1
-
-Here, we use regular observed means.
-
-```{r }
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# intercepts
-t1_pri_con_m ~ mu1*1
-t2_pri_con_m ~ mu2*1
-t3_pri_con_m ~ mu3*1
-t1_inf_sha_beh_m ~ pi1*1
-t2_inf_sha_beh_m ~ pi2*1
-t3_inf_sha_beh_m ~ pi3*1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t2_pri_con_w =~ 1*t2_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 2
-
-Model with a (broad) single item measure of privacy concerns ("In general, how concerned are you about your privacy while using the Internet?").
-
-```{r }
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_01 + 1*t2_pri_con_01 + 1*t3_pri_con_01
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# intercepts
-t1_pri_con_01 ~ mu1*1
-t2_pri_con_01 ~ mu2*1
-t3_pri_con_01 ~ mu3*1
-t1_inf_sha_beh_m ~ pi1*1
-t2_inf_sha_beh_m ~ pi2*1
-t3_inf_sha_beh_m ~ pi3*1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_01
-t2_pri_con_w =~ 1*t2_pri_con_01
-t3_pri_con_w =~ 1*t3_pri_con_01
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 3
-
-With Factor Scores.
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-
-# intercepts
-t1_pri_con_fs ~ 1
-t2_pri_con_fs ~ 1
-t3_pri_con_fs ~ 1
-t1_inf_sha_beh_fs ~ 1
-t2_inf_sha_beh_fs ~ 1
-t3_inf_sha_beh_fs ~ 1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-'
-fit <- lavaan(model, data = d_wide)
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 4
-
-With Factor Scores and Control Variables.
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-
-# intercepts
-t1_pri_con_fs ~ 1
-t2_pri_con_fs ~ 1
-t3_pri_con_fs ~ 1
-t1_inf_sha_beh_fs ~ 1
-t2_inf_sha_beh_fs ~ 1
-t3_inf_sha_beh_fs ~ 1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-
-# control variables
-t1_pri_con_fs ~ age + edu_num + male
-t2_pri_con_fs ~ age + edu_num + male
-t3_pri_con_fs ~ age + edu_num + male
-t1_inf_sha_beh_fs ~ age + edu_num + male
-t2_inf_sha_beh_fs ~ age + edu_num + male
-t3_inf_sha_beh_fs ~ age + edu_num + male
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ml")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 5
-
-In this model, we omit all longitudinal paths in order to better estimate the concurrent relations of the variables for _all_ waves (in the regular RI-CLPM, only the relations at wave 1 can be interpreted meaningfully).
-
-```{r }
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# intercepts
-t1_pri_con_m ~ mu1*1
-t2_pri_con_m ~ mu2*1
-t3_pri_con_m ~ mu3*1
-t1_inf_sha_beh_m ~ pi1*1
-t2_inf_sha_beh_m ~ pi2*1
-t3_inf_sha_beh_m ~ pi3*1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t2_pri_con_w =~ 1*t2_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ a*t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ml")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 6
-
-The same like above, using Factor Scores and control variables.
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-
-# intercepts
-t1_pri_con_fs ~ 1
-t2_pri_con_fs ~ 1
-t3_pri_con_fs ~ 1
-t1_inf_sha_beh_fs ~ 1
-t2_inf_sha_beh_fs ~ 1
-t3_inf_sha_beh_fs ~ 1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ a*t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-
-# control variables
-t1_pri_con_fs ~ age + edu_num + male
-t2_pri_con_fs ~ age + edu_num + male
-t3_pri_con_fs ~ age + edu_num + male
-t1_inf_sha_beh_fs ~ age + edu_num + male
-t2_inf_sha_beh_fs ~ age + edu_num + male
-t3_inf_sha_beh_fs ~ age + edu_num + male
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ml")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-### Three Variables
-#### Model 1
-
-With observed means.
-
-```{r }
-model <- '
-# random intercepts (between person)
-pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
-inf_sha_att_b =~ 1*t1_inf_sha_att_m + 1*t2_inf_sha_att_m + 1*t3_inf_sha_att_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t2_pri_con_w =~ 1*t2_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_m
-t2_inf_sha_att_w =~ 1*t2_inf_sha_att_m
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_m ~~ 0*t1_pri_con_m
-t2_pri_con_m ~~ 0*t2_pri_con_m
-t3_pri_con_m ~~ 0*t3_pri_con_m
-t1_inf_sha_att_m ~~ 0*t1_inf_sha_att_m
-t2_inf_sha_att_m ~~ 0*t2_inf_sha_att_m
-t3_inf_sha_att_m ~~ 0*t3_inf_sha_att_m
-t1_inf_sha_beh_m ~~ 0*t1_inf_sha_beh_m
-t2_inf_sha_beh_m ~~ 0*t2_inf_sha_beh_m
-t3_inf_sha_beh_m ~~ 0*t3_inf_sha_beh_m
-
-# allow covariances RIs & variables measured at the same time
-pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
-inf_sha_att_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
-t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-'
-fit <- sem(model, estimator = "ML", data = d_wide, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-```
-
-#### Model 2
-
-With observed means and control variables.
-
-```{r }
-model <- '
-# random intercepts (between person)
-pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
-inf_sha_att_b =~ 1*t1_inf_sha_att_m + 1*t2_inf_sha_att_m + 1*t3_inf_sha_att_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t2_pri_con_w =~ 1*t2_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_m
-t2_inf_sha_att_w =~ 1*t2_inf_sha_att_m
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_m ~~ 0*t1_pri_con_m
-t2_pri_con_m ~~ 0*t2_pri_con_m
-t3_pri_con_m ~~ 0*t3_pri_con_m
-t1_inf_sha_att_m ~~ 0*t1_inf_sha_att_m
-t2_inf_sha_att_m ~~ 0*t2_inf_sha_att_m
-t3_inf_sha_att_m ~~ 0*t3_inf_sha_att_m
-t1_inf_sha_beh_m ~~ 0*t1_inf_sha_beh_m
-t2_inf_sha_beh_m ~~ 0*t2_inf_sha_beh_m
-t3_inf_sha_beh_m ~~ 0*t3_inf_sha_beh_m
-
-# allow covariances RIs & variables measured at the same time
-pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
-inf_sha_att_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
-t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-
-# control variables
-t1_pri_con_m ~ age + edu_num + male
-t2_pri_con_m ~ age + edu_num + male
-t3_pri_con_m ~ age + edu_num + male
-t1_inf_sha_beh_m ~ age + edu_num + male
-t2_inf_sha_beh_m ~ age + edu_num + male
-t3_inf_sha_beh_m ~ age + edu_num + male
-t1_inf_sha_att_m ~ age + edu_num + male
-t2_inf_sha_att_m ~ age + edu_num + male
-t3_inf_sha_att_m ~ age + edu_num + male
-'
-fit <- sem(model, estimator = "ML", data = d_wide, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-```
-
-#### Model 3
-
-With Factor Scores.
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t2_inf_sha_att_fs + 1*t3_inf_sha_att_fs
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
-t2_inf_sha_att_w =~ 1*t2_inf_sha_att_fs
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
-inf_sha_att_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
-t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_fs ~~ 0*t1_pri_con_fs
-t2_pri_con_fs ~~ 0*t2_pri_con_fs
-t3_pri_con_fs ~~ 0*t3_pri_con_fs
-t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
-t2_inf_sha_att_fs ~~ 0*t2_inf_sha_att_fs
-t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
-t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
-t2_inf_sha_beh_fs ~~ 0*t2_inf_sha_beh_fs
-t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs
-'
-fit <- sem(model, data = d_wide, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-```
-
-#### Model 4 (final)
-
-With Factor Scores and control variables. This is the final model we report in the paper.
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t2_inf_sha_att_fs + 1*t3_inf_sha_att_fs
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
-t2_inf_sha_att_w =~ 1*t2_inf_sha_att_fs
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ cor_b_1*inf_sha_att_b + cor_b_2*inf_sha_beh_b
-inf_sha_att_b ~~ cor_b_3*inf_sha_beh_b
-t1_pri_con_w ~~ cor_w_1*t1_inf_sha_att_w + cor_w_2*t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ cor_w_3*t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
-t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_fs ~~ 0*t1_pri_con_fs
-t2_pri_con_fs ~~ 0*t2_pri_con_fs
-t3_pri_con_fs ~~ 0*t3_pri_con_fs
-t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
-t2_inf_sha_att_fs ~~ 0*t2_inf_sha_att_fs
-t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
-t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
-t2_inf_sha_beh_fs ~~ 0*t2_inf_sha_beh_fs
-t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs
-
-# control variables
-t1_pri_con_fs ~ age + edu_num + male
-t2_pri_con_fs ~ age + edu_num + male
-t3_pri_con_fs ~ age + edu_num + male
-t1_inf_sha_beh_fs ~ age + edu_num + male
-t2_inf_sha_beh_fs ~ age + edu_num + male
-t3_inf_sha_beh_fs ~ age + edu_num + male
-t1_inf_sha_att_fs ~ age + edu_num + male
-t2_inf_sha_att_fs ~ age + edu_num + male
-t3_inf_sha_att_fs ~ age + edu_num + male
-'
-fit <- sem(model, data = d_wide, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-fit_riclpm <- fit
-effect_std_ci <- standardizedsolution(fit) %>% 
-  filter(lhs == "pri_con_b", rhs == "inf_sha_beh_b")
-```
-
-#### Model 5
-
-With Factor Scores, control variables, and 4 waves / 1 year intervals
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_m + 1*t3_pri_con_m + 1*t4_pri_con_m + 1*t5_pri_con_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t3_inf_sha_beh_m + 1*t4_inf_sha_beh_m + 1*t5_inf_sha_beh_m
-inf_sha_att_b =~ 1*t1_inf_sha_att_m + 1*t3_inf_sha_att_m + 1*t4_inf_sha_att_m + 1*t5_inf_sha_att_m
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t4_pri_con_w =~ 1*t4_pri_con_m
-t5_pri_con_w =~ 1*t5_pri_con_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-t4_inf_sha_beh_w =~ 1*t4_inf_sha_beh_m
-t5_inf_sha_beh_w =~ 1*t5_inf_sha_beh_m
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_m
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_m
-t4_inf_sha_att_w =~ 1*t4_inf_sha_att_m
-t5_inf_sha_att_w =~ 1*t5_inf_sha_att_m
-
-# within person effects
-t3_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t4_pri_con_w ~ a1*t3_pri_con_w + a2*t3_inf_sha_att_w + a3*t3_inf_sha_beh_w
-t4_inf_sha_att_w ~ b1*t3_pri_con_w + b2*t3_inf_sha_att_w + b3*t3_inf_sha_beh_w
-t4_inf_sha_beh_w ~ c1*t3_pri_con_w + c2*t3_inf_sha_att_w + c3*t3_inf_sha_beh_w
-t5_pri_con_w ~ a1*t4_pri_con_w + a2*t4_inf_sha_att_w + a3*t4_inf_sha_beh_w
-t5_inf_sha_att_w ~ b1*t4_pri_con_w + b2*t4_inf_sha_att_w + b3*t4_inf_sha_beh_w
-t5_inf_sha_beh_w ~ c1*t4_pri_con_w + c2*t4_inf_sha_att_w + c3*t4_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
-inf_sha_att_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-t4_pri_con_w ~~ a*t4_inf_sha_att_w + b*t4_inf_sha_beh_w
-t4_inf_sha_att_w ~~ c*t4_inf_sha_beh_w
-t5_pri_con_w ~~ a*t5_inf_sha_att_w + b*t5_inf_sha_beh_w
-t5_inf_sha_att_w ~~ c*t5_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_m ~~ 0*t1_pri_con_m
-t3_pri_con_m ~~ 0*t3_pri_con_m
-t4_pri_con_m ~~ 0*t4_pri_con_m
-t5_pri_con_m ~~ 0*t5_pri_con_m
-t1_inf_sha_att_m ~~ 0*t1_inf_sha_att_m
-t3_inf_sha_att_m ~~ 0*t3_inf_sha_att_m
-t4_inf_sha_att_m ~~ 0*t4_inf_sha_att_m
-t5_inf_sha_att_m ~~ 0*t5_inf_sha_att_m
-t1_inf_sha_beh_m ~~ 0*t1_inf_sha_beh_m
-t3_inf_sha_beh_m ~~ 0*t3_inf_sha_beh_m
-t4_inf_sha_beh_m ~~ 0*t4_inf_sha_beh_m
-t5_inf_sha_beh_m ~~ 0*t5_inf_sha_beh_m
-
-# control variables
-t1_pri_con_m ~ age + edu_num + male
-t3_pri_con_m ~ age + edu_num + male
-t4_pri_con_m ~ age + edu_num + male
-t5_pri_con_m ~ age + edu_num + male
-t1_inf_sha_beh_m ~ age + edu_num + male
-t3_inf_sha_beh_m ~ age + edu_num + male
-t4_inf_sha_beh_m ~ age + edu_num + male
-t5_inf_sha_beh_m ~ age + edu_num + male
-t1_inf_sha_att_m ~ age + edu_num + male
-t3_inf_sha_att_m ~ age + edu_num + male
-t4_inf_sha_att_m ~ age + edu_num + male
-t5_inf_sha_att_m ~ age + edu_num + male
-'
-fit <- sem(model, data = d_wide_all, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-```
-
-## Mixed Models
-
-In what follows, we also present the results of several mixed models.
-Using mixed models, we can include more data.
-However, one downside is that not all research questions can be answered in one single model.
-
-### Two Variables
-#### Model 1
-
-Measures overall correlation between privacy concerns and information sharing.
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + inf_sha_beh_m + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-#### Model 2
-
-Measures how current levels of information sharing are affected by generel levels of privacy concern und current levels of privacy concern.
-
-```{r}
-fit <- lmer(inf_sha_beh_m ~ pri_con_m_b + pri_con_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-Measures how current levels of privacy concern are affected by generel levels of information sharing und current levels of information sharing.
-
-```{r}
-fit <- lmer(pri_con_m ~ inf_sha_beh_m_b + inf_sha_beh_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-#### Model 3
-
-Includes control variables.
-
-```{r}
-fit <- lmer(inf_sha_beh_m ~ 1 + pri_con_m_b + pri_con_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + inf_sha_beh_m_b + inf_sha_beh_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-### Three Variables
-#### Model 1
-
-Measures how current levels of information sharing are affected by generel levels of privacy concern and current levels of privacy concern, as well as general levels of positive attitude toward information sharing and current levels of positive attitude toward information sharing.
-
-```{r}
-fit <- lmer(inf_sha_beh_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_att_m_b + inf_sha_att_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-Measures how current levels of positive attitude toward information sharing are affected by generel levels of privacy concern and current levels of privacy concern, as well as general levels of information sharing and current levels of information sharing.
-
-```{r}
-fit <- lmer(inf_sha_att_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_beh_m_b + inf_sha_beh_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-Measures how current levels of privacy concern are affected by generel levels of positive attitude toward information sharing and current levels of positive attitude toward information sharing, as well as general levels of information sharing and current levels of information sharing.
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + inf_sha_beh_m_b + inf_sha_beh_m_w + inf_sha_att_m_b + inf_sha_att_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-#### Model 2
-
-Includes control variables
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + inf_sha_att_m_b + inf_sha_att_m_w + inf_sha_beh_m_b + inf_sha_beh_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-```{r}
-fit <- lmer(inf_sha_att_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_beh_m_b + inf_sha_beh_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-```{r}
-fit <- lmer(inf_sha_beh_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_att_m_b + inf_sha_att_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
 ```{r cache=F}

### 2020-04-23 analyses_additional.Rmd
created new file "analyses additional"

--- 2019-09-19 analyses/analyses.Rmd
@@
     df_print: paged
-editor_options: 
-  chunk_output_type: inline
+    code_folding: hide
 ---
 
-```{r, echo = FALSE, include = FALSE}
+```{r, echo=F, include=F}
 # defaults
 set.seed(170819)
-options(digits = 3, width = 120, max.print = 100000)
-knitr::opts_chunk$set(echo = T, error = F, message = F, tidy = T, warning = F, cache = T)
-```
-
-```{r Packages, include = FALSE, cache=F}
+options(digits=3, width=120, max.print=100000)
+knitr::opts_chunk$set(echo=T, error=F, message=F, tidy=T, warning=F, cache=T)
+```
+
+```{r Packages, cache=F, results='hide'}
 # relevant packages
@@
 
-# export bib library
-r_refs("../bibliography/r-references.bib")
-```
-
-```{r datawrangling, include=F}
-# first run "data_wranling.R", in order to create these objects
-d_wide <- read_csv("../data/data_wide.csv")
-d_wide_all <- read_csv("../data/data_wide_all.csv")
-d_long <- read_csv("../data/data_long.csv")
-```
-
-```{r include=FALSE}
-# Extract descriptives to report in paper
-desc <- d_wide %>% 
-  summarize_at(vars(ends_with("_m")), funs(mean(., na.rm = TRUE), sd(., na.rm = TRUE)))
-```
-
-# Items
-## Privacy Concern
-
-The following deals with things that can happen on the Internet.
-
-1. In general, how concerned are you about your privacy while using the Internet?
-2. Are you concerned about online organizations not being who they claim they are?
-3. Are you concerned about online identity theft?
-4. Are you concerned about people you do not know obtaining personal information about you from your online activities?
-5. Are you concerned that if you use your credit card to buy something on the Internet your credit card number will be obtained/intercepted by someone else?
-6. Are you concerned that an email you sent may be read by someone else besides the person you sent it to?
-7. Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing on the Internet?
-8. Are you concerned that website providers are tracking your online activities?
-9. Are you concerned that you don’t know what other organizations or website providers are doing with you data?
-
-(NA = "no Internet user / no reply", 1 = "Not concerned at all" : 5 = "very concerned")
-
-## Attitude Toward Online Sharing of Personal Information
-
-Now we will deal with information sharing on the Internet. Do you think that it is sensible to disclose the following pieces of information online, i.e., via the Internet?
-
-1. Financial information (bank data, account balances…)
-2. Medical information (health, medical records…)
-3. Second name
-4. First name
-5. Residence
-6. Street and house number
-7. Email address
-8. Phone number
-9. Photos (of you)
-10. Job (past and present)
-11. Education
-
-(NA = “no Internet user / no reply”, 1 = "not sensible at all", 2 = "somewhat not sensible", 3 = "in part", 4 = "somewhat sensible", 5 = "very sensible")
-
-## Online Sharing of Personal Information
-
-In the following, please indicate how often you disclose the following information on the Internet. How often do you disclose the following pieces of information online, i.e., on the Internet?
-
-1. Financial information (bank data, account balances…)
-2. Medical information (health, medical records…)
-3. Second name
-4. First name
-5. Residence
-6. Street and house number
-7. Email address
-8. Phone number
-9. Photos (of you)
-10. Job (past and present)
-11. Education
-
-(NA = “no Internet user / no reply”, 1 = "every day", 2 = "weekly", 3 = "monthly", 4 = "less than that", 5 = "never")
-
-# Power Analyses
-
-```{r power}
-n_complete <- nrow(d_wide)
-alpha <- .05
-power <- .95
-sesoi <- .1
-n <- n_complete
-n_apriori <- pwr.r.test(r = sesoi, sig.level = alpha, power = power)$n
-power_achieved_h <- pwr.r.test(r = sesoi, sig.level = alpha, n = n, alternative = "greater")$power
-alpha_balanced_h <- balance_errors(sesoi, n, one_tailed = TRUE)
-power_balanced_h <- 1 - alpha_balanced_h
-power_achieved_rq <- pwr.r.test(r = sesoi, sig.level = alpha, n = n)$power
-alpha_balanced_rq <- balance_errors(sesoi, n, one_tailed = FALSE)
-power_balanced_rq <- 1 - alpha_balanced_rq
-```
-
-A-priori power analyses revealed that N = `r n_apriori` people would be needed to find effects with a size of _r_ = `r sesoi` with a power of `r power`.
-
-Overall, the data of `r n` respondents could be used for our analyses.
-As a result, alpha and beta errors were balanced when using an alpha of `r alpha_balanced_h %>% round(3)`, resulting in an achieved power of `r power_balanced_h %>% round(3)`.
-
-# Sociodemographics
-
-```{r}
-age_m <- mean(d_wide$age)
-age_sd <- sd(d_wide$age)
-male_per <- mean(d_wide$male)
-edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100
-```
-
-# Analysis of Missing Values
-
-```{r cache=F}
-d_tmp <- select(d_wide, -contains("_m"), -contains("tim"), -contains("T4"), -contains("T5"), -contains("per"), -contains("use"), -c(id, age, edu, edu_num, male))
-test_mar <- TestMCARNormality(d_tmp)
-
-# print patterns
-as.data.frame(test_mar$patused)
-
-# non-parametric test
-(test_mar_p <- test_mar$pnormality)
-
-# calculate percentage of missing data
-na_per <- mean(c(d_wide$t1_na_per, d_wide$t2_na_per, d_wide$t3_na_per)) * 100
-```
-
-Visual inspection of the missing value patterns as well as the non-parametric test suggested that all missing values could be considered to be missing at random (_p_ `r test_mar$pnormality %>% td::my_round("p_txt")`).
-
-# Factor Analyses
+load("data/workspace.RData") 
+```
+In what follows, we report the results of additional analyses that were also calculated.
+For example, for each measure we also report exploratory factor analyses, first order model solutions, and unconstrained solutions to estimate longitudinal  invariance.
+
+# Measures
 ## Concerns about online privacy
@@
 
-## All Measures in one Model 
+## Baseline Model
 ### Second Order
@@
 
-### Extract Factor Scores
-
-```{r}
-d_fs <- lavPredict(get(paste("fit", name, no, sep = "_")), type = "ov") %>% 
-  as.data.frame() %>% 
-  mutate(t1_pri_con_fs = rowMeans(select(., starts_with("t1_pri"))),
-         t2_pri_con_fs = rowMeans(select(., starts_with("t2_pri"))),
-         t3_pri_con_fs = rowMeans(select(., starts_with("t3_pri"))),
-         t1_inf_sha_att_fs = rowMeans(select(., starts_with("t1_inf_sha_att"))),
-         t2_inf_sha_att_fs = rowMeans(select(., starts_with("t2_inf_sha_att"))),
-         t3_inf_sha_att_fs = rowMeans(select(., starts_with("t3_inf_sha_att"))),
-         t1_inf_sha_beh_fs = rowMeans(select(., starts_with("t1_inf_sha_beh"))),
-         t2_inf_sha_beh_fs = rowMeans(select(., starts_with("t2_inf_sha_beh"))),
-         t3_inf_sha_beh_fs = rowMeans(select(., starts_with("t3_inf_sha_beh")))
-         ) %>% 
-  select(contains("_fs"))
-d_wide <- cbind(d_fs, d_wide)
-```
-
-### Latent correlation matrix with plots
-
-```{r Corrplot, fig.height = 8, fig.width = 8, size=5}
-colnames(d_fs) <- c("Concerns\nT1", "Concerns\nT2" , "Concerns\nT3",
-                    "Pos. Attitude\nT1", "Pos. Attitude\nT2" , "Pos. Attitude\nT3",
-                    "Inf. Sharing\nT1", "Inf. Sharing\nT2" , "Inf. Sharing\nT3")
-
-corr_plot <- ggpairs(d_fs,
-                     # upper = list(continuous = wrap(td::cor_matrix, data = d_fs)),
-                     lower = list(continuous = wrap(td::scat_plot, coords = c(1, 5, 1, 5)))) + 
-  theme_bw()
-print(corr_plot)
-```
-
-# ICCs
-
-Next, we determine the Intraclass Correlation Coefficients (ICC), to determine how much variance in the measures is due to between-person differences versus within-person changes.
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + (1 | id), filter(d_long, wave < 4))
-summary(fit)
-icc_pri_con <- icc(fit)
-
-fit <- lmer(inf_sha_att_m ~ 1 + (1 | id), filter(d_long, wave < 4))
-summary(fit)
-icc_inf_sha_att <- icc(fit)
-
-fit <- lmer(inf_sha_beh_m ~ 1 + (1 | id), filter(d_long, wave < 4))
-summary(fit)
-icc_inf_sha_beh <- icc(fit)
-```
-
 # Results
 
-In what follows, please find all information about our final model we present in the paper.
-
-# Additional Analyses
+In what follows, we report additional models, which are also related to our research question.
+
 ## RI-CLPM
-### Assumptions
-#### Multivariate Normal Distribution
-
-```{r multivardis}
-mult_norm_test <- mvn(d_fs)
-print(mult_norm_test)
-```
-
-Results show that the assumption of multivariate normal distribution was violated.
-Hence, it'd be preferrable to conduct robust Maximum Likelihood Estimation.
-However, using robust estimation it's not possible to run SEM on all data using Full Information Maximum Likehoood (FIML).
-Given that we consider it more important to include as much information as possible and that estimators often produce similar results, we decided to estimate the following models using regular maximum likehood.
-
 ### Two Variables
@@
 Here, we look at the bivariate relations of privacy concerns and information sharing.
-This is interesting, because in the paper we also address privacy attitudes, thereby potentially attentuating the effect of privacy concerns.
+This is interesting, because in the paper we also address privacy attitudes, thereby potentially attenuating the effect of privacy concerns.
 However, when analyzing only these two variables we do not find larger effects sizes.
@@
 With Factor Scores and control variables. This is the final model we report in the paper.
-
-```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
-knitr::include_graphics("../figures/model_7.png")
-```
 
@@
 ```
-
-```{r cache=F}
-save.image("../data/workspace.RData")
-```

### 2020-04-23 items.Rmd
created new file "analyses additional"

--- 2019-09-19 analyses/analyses.Rmd
@@
 ---
-title: "A Longitudinal Analysis of the Privacy Paradox"
-author: "Tobias Dienlin, Philipp K. Masur, Sabine Trepte"
+title: "List of Items"
 output: 
-  # pdf_document: 
   html_document:
-    toc: true
-    toc_float: true
-    toc_depth: 5
-    df_print: paged
-editor_options: 
-  chunk_output_type: inline
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+    toc_depth: 2
 ---
-
-```{r, echo = FALSE, include = FALSE}
-# defaults
-set.seed(170819)
-options(digits = 3, width = 120, max.print = 100000)
-knitr::opts_chunk$set(echo = T, error = F, message = F, tidy = T, warning = F, cache = T)
-```
-
-```{r Packages, include = FALSE, cache=F}
-# relevant packages
-devtools::install_github("tdienlin/td@v.0.0.2.5")
-required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
-              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
-              "sjstats", "tidyverse", "td")
-
-# load required libraries
-lapply(required, function(x) library(x, character.only = T))
-
-# export bib library
-r_refs("../bibliography/r-references.bib")
-```
-
-```{r datawrangling, include=F}
-# first run "data_wranling.R", in order to create these objects
-d_wide <- read_csv("../data/data_wide.csv")
-d_wide_all <- read_csv("../data/data_wide_all.csv")
-d_long <- read_csv("../data/data_long.csv")
-```
-
-```{r include=FALSE}
-# Extract descriptives to report in paper
-desc <- d_wide %>% 
-  summarize_at(vars(ends_with("_m")), funs(mean(., na.rm = TRUE), sd(., na.rm = TRUE)))
-```
 
@@
 (NA = “no Internet user / no reply”, 1 = "every day", 2 = "weekly", 3 = "monthly", 4 = "less than that", 5 = "never")
-
-# Power Analyses
-
-```{r power}
-n_complete <- nrow(d_wide)
-alpha <- .05
-power <- .95
-sesoi <- .1
-n <- n_complete
-n_apriori <- pwr.r.test(r = sesoi, sig.level = alpha, power = power)$n
-power_achieved_h <- pwr.r.test(r = sesoi, sig.level = alpha, n = n, alternative = "greater")$power
-alpha_balanced_h <- balance_errors(sesoi, n, one_tailed = TRUE)
-power_balanced_h <- 1 - alpha_balanced_h
-power_achieved_rq <- pwr.r.test(r = sesoi, sig.level = alpha, n = n)$power
-alpha_balanced_rq <- balance_errors(sesoi, n, one_tailed = FALSE)
-power_balanced_rq <- 1 - alpha_balanced_rq
-```
-
-A-priori power analyses revealed that N = `r n_apriori` people would be needed to find effects with a size of _r_ = `r sesoi` with a power of `r power`.
-
-Overall, the data of `r n` respondents could be used for our analyses.
-As a result, alpha and beta errors were balanced when using an alpha of `r alpha_balanced_h %>% round(3)`, resulting in an achieved power of `r power_balanced_h %>% round(3)`.
-
-# Sociodemographics
-
-```{r}
-age_m <- mean(d_wide$age)
-age_sd <- sd(d_wide$age)
-male_per <- mean(d_wide$male)
-edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100
-```
-
-# Analysis of Missing Values
-
-```{r cache=F}
-d_tmp <- select(d_wide, -contains("_m"), -contains("tim"), -contains("T4"), -contains("T5"), -contains("per"), -contains("use"), -c(id, age, edu, edu_num, male))
-test_mar <- TestMCARNormality(d_tmp)
-
-# print patterns
-as.data.frame(test_mar$patused)
-
-# non-parametric test
-(test_mar_p <- test_mar$pnormality)
-
-# calculate percentage of missing data
-na_per <- mean(c(d_wide$t1_na_per, d_wide$t2_na_per, d_wide$t3_na_per)) * 100
-```
-
-Visual inspection of the missing value patterns as well as the non-parametric test suggested that all missing values could be considered to be missing at random (_p_ `r test_mar$pnormality %>% td::my_round("p_txt")`).
-
-# Factor Analyses
-## Concerns about online privacy
-### EFA
-
-```{r}
-# set-up
-no <- 0
-name <- "pri_con"
-d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
-model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
-factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
-print(factan, sort = TRUE, cut = .3)
-```
-
-### CFA
-#### First-Order Model Unconstrained
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_01 + t1_pri_con_02 + t1_pri_con_03 + t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06 + t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
-t2_pri_con_f =~ 1*t2_pri_con_01 + t2_pri_con_02 + t2_pri_con_03 + t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06 + t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
-t3_pri_con_f =~ 1*t3_pri_con_01 + t3_pri_con_02 + t3_pri_con_03 + t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06 + t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09
-
-# error covariances
-t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
-t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
-t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_01 ~~ t1_pri_con_01
-t2_pri_con_02 ~~ t1_pri_con_02 
-t2_pri_con_03 ~~ t1_pri_con_03
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-reliability(get(paste("fit", name, no, sep = "_")))
-```
-
-#### First-Order Model Constrained
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_01 + b2*t1_pri_con_02 + b3*t1_pri_con_03 + b4*t1_pri_con_04 + b5*t1_pri_con_05 + b6*t1_pri_con_06 + b7*t1_pri_con_07 + b8*t1_pri_con_08 + b9*t1_pri_con_09
-t2_pri_con_f =~ 1*t2_pri_con_01 + b2*t2_pri_con_02 + b3*t2_pri_con_03 + b4*t2_pri_con_04 + b5*t2_pri_con_05 + b6*t2_pri_con_06 + b7*t2_pri_con_07 + b8*t2_pri_con_08 + b9*t2_pri_con_09
-t3_pri_con_f =~ 1*t3_pri_con_01 + b2*t3_pri_con_02 + b3*t3_pri_con_03 + b4*t3_pri_con_04 + b5*t3_pri_con_05 + b6*t3_pri_con_06 + b7*t3_pri_con_07 + b8*t3_pri_con_08 + b9*t3_pri_con_09
-
-# error covariances
-t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
-t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
-t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_01 ~~ t1_pri_con_01
-t2_pri_con_02 ~~ t1_pri_con_02 
-t2_pri_con_03 ~~ t1_pri_con_03
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Unconstrained
-
-In what follows, we analyze a second-order solution of privacy concerns.
-Here, we distinguish between horizontal privacy concerns (items 4, 5, 6) and vertical privacy concerns (items 7, 8, 9).
-The resulting model fits the data better than the unidimensional one.
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_f1 + t1_pri_con_f2
-t2_pri_con_f =~ 1*t2_pri_con_f1 + t2_pri_con_f2
-t3_pri_con_f =~ 1*t3_pri_con_f1 + t3_pri_con_f2
-t1_pri_con_f1 =~ 1*t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06
-t1_pri_con_f2 =~ 1*t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
-t2_pri_con_f1 =~ 1*t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06
-t2_pri_con_f2 =~ 1*t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
-t3_pri_con_f1 =~ 1*t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06
-t3_pri_con_f2 =~ 1*t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09
-
-# error covariances
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Constrained
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
-t2_pri_con_f =~ 1*t2_pri_con_f1 + a2*t2_pri_con_f2
-t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
-t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
-t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
-t2_pri_con_f1 =~ 1*t2_pri_con_04 + b2*t2_pri_con_05 + b3*t2_pri_con_06
-t2_pri_con_f2 =~ 1*t2_pri_con_07 + c2*t2_pri_con_08 + c3*t2_pri_con_09
-t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
-t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09
-
-# error covariances
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-### Reliability
-
-```{r}
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t1", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t2", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t3", name, "f", sep = "_"))
-```
-
-### Longitudinal Invariance
-
-```{r}
-(anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_"))))
-```
-
-## Attitude Toward Online Sharing of Personal Information
-### EFA
-
-```{r}
-no <- 0
-name <- "inf_sha_att"
-d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
-model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
-factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
-print(factan, sort = TRUE, cut = .3)
-```
-
-### CFA
-#### First-Order Model Unconstrained
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_01 + t1_pri_con_02 + t1_pri_con_03 + t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06 + t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
-t2_pri_con_f =~ 1*t2_pri_con_01 + t2_pri_con_02 + t2_pri_con_03 + t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06 + t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
-t3_pri_con_f =~ 1*t3_pri_con_01 + t3_pri_con_02 + t3_pri_con_03 + t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06 + t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09
-
-# error covariances
-t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
-t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
-t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_01 ~~ t1_pri_con_01
-t2_pri_con_02 ~~ t1_pri_con_02 
-t2_pri_con_03 ~~ t1_pri_con_03
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### First-Order Model Constrained
-
-```{r}
-model <- '
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_01 + a2*t1_pri_con_02 + a3*t1_pri_con_03 + a4*t1_pri_con_04 + a5*t1_pri_con_05 + a6*t1_pri_con_06 + a7*t1_pri_con_07 + a8*t1_pri_con_08 + a9*t1_pri_con_09
-t2_pri_con_f =~ 1*t2_pri_con_01 + a2*t2_pri_con_02 + a3*t2_pri_con_03 + a4*t2_pri_con_04 + a5*t2_pri_con_05 + a6*t2_pri_con_06 + a7*t2_pri_con_07 + a8*t2_pri_con_08 + a9*t2_pri_con_09
-t3_pri_con_f =~ 1*t3_pri_con_01 + a2*t3_pri_con_02 + a3*t3_pri_con_03 + a4*t3_pri_con_04 + a5*t3_pri_con_05 + a6*t3_pri_con_06 + a7*t3_pri_con_07 + a8*t3_pri_con_08 + a9*t3_pri_con_09
-
-# error covariances
-t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
-t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
-t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_01 ~~ t1_pri_con_01
-t2_pri_con_02 ~~ t1_pri_con_02 
-t2_pri_con_03 ~~ t1_pri_con_03
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Unconstrained
-
-We again run models in which we build sub-dimensions referring to the empirical EFA results and theoretical considerations. Resulting model fits the data better than unidimensional one.
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + t1_inf_sha_att_f2 + t1_inf_sha_att_f3 + t1_inf_sha_att_f4 + t1_inf_sha_att_f5
-t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + t2_inf_sha_att_f2 + t2_inf_sha_att_f3 + t2_inf_sha_att_f4 + t2_inf_sha_att_f5
-t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + t3_inf_sha_att_f2 + t3_inf_sha_att_f3 + t3_inf_sha_att_f4 + t3_inf_sha_att_f5
-t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + t1_inf_sha_att_02
-t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + t1_inf_sha_att_04
-t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + t1_inf_sha_att_06
-t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + t1_inf_sha_att_08
-t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + t1_inf_sha_att_11
-t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + t2_inf_sha_att_02
-t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + t2_inf_sha_att_04
-t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + t2_inf_sha_att_06
-t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + t2_inf_sha_att_08
-t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + t2_inf_sha_att_11
-t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + t3_inf_sha_att_02
-t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + t3_inf_sha_att_04
-t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + t3_inf_sha_att_06
-t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + t3_inf_sha_att_08
-t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + t3_inf_sha_att_11
-
-# factor covariance
-t1_inf_sha_att_f ~~ t2_inf_sha_att_f + t3_inf_sha_att_f
-t2_inf_sha_att_f ~~ t3_inf_sha_att_f
-
-# item error covariance
-t1_inf_sha_att_01 ~~ t2_inf_sha_att_01 + t3_inf_sha_att_01
-t2_inf_sha_att_01 ~~ t3_inf_sha_att_01
-t1_inf_sha_att_02 ~~ t2_inf_sha_att_02 + t3_inf_sha_att_02
-t2_inf_sha_att_02 ~~ t3_inf_sha_att_02
-t1_inf_sha_att_03 ~~ t2_inf_sha_att_03 + t3_inf_sha_att_03
-t2_inf_sha_att_03 ~~ t3_inf_sha_att_03
-t1_inf_sha_att_04 ~~ t2_inf_sha_att_04 + t3_inf_sha_att_04
-t2_inf_sha_att_04 ~~ t3_inf_sha_att_04
-t1_inf_sha_att_05 ~~ t2_inf_sha_att_05 + t3_inf_sha_att_05
-t2_inf_sha_att_05 ~~ t3_inf_sha_att_05
-t1_inf_sha_att_06 ~~ t2_inf_sha_att_06 + t3_inf_sha_att_06
-t2_inf_sha_att_06 ~~ t3_inf_sha_att_06
-t1_inf_sha_att_07 ~~ t2_inf_sha_att_07 + t3_inf_sha_att_07
-t2_inf_sha_att_07 ~~ t3_inf_sha_att_07
-t1_inf_sha_att_08 ~~ t2_inf_sha_att_08 + t3_inf_sha_att_08
-t2_inf_sha_att_08 ~~ t3_inf_sha_att_08
-t1_inf_sha_att_10 ~~ t2_inf_sha_att_10 + t3_inf_sha_att_10
-t2_inf_sha_att_10 ~~ t3_inf_sha_att_10
-t1_inf_sha_att_11 ~~ t2_inf_sha_att_11 + t3_inf_sha_att_11
-t2_inf_sha_att_11 ~~ t3_inf_sha_att_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model at All Waves Constrained
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + o2*t1_inf_sha_att_f2 + o3*t1_inf_sha_att_f3 + o4*t1_inf_sha_att_f4 + o5*t1_inf_sha_att_f5
-t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + o2*t2_inf_sha_att_f2 + o3*t2_inf_sha_att_f3 + o4*t2_inf_sha_att_f4 + o5*t2_inf_sha_att_f5
-t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + o2*t3_inf_sha_att_f2 + o3*t3_inf_sha_att_f3 + o4*t3_inf_sha_att_f4 + o5*t3_inf_sha_att_f5
-t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + j2*t1_inf_sha_att_02
-t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + k2*t1_inf_sha_att_04
-t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + l2*t1_inf_sha_att_06
-t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + m2*t1_inf_sha_att_08
-t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + n2*t1_inf_sha_att_11
-t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + j2*t2_inf_sha_att_02
-t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + k2*t2_inf_sha_att_04
-t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + l2*t2_inf_sha_att_06
-t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + m2*t2_inf_sha_att_08
-t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + n2*t2_inf_sha_att_11
-t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + j2*t3_inf_sha_att_02
-t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + k2*t3_inf_sha_att_04
-t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + l2*t3_inf_sha_att_06
-t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + m2*t3_inf_sha_att_08
-t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + n2*t3_inf_sha_att_11
-
-# factor covariance
-t1_inf_sha_att_f ~~ t2_inf_sha_att_f + t3_inf_sha_att_f
-t2_inf_sha_att_f ~~ t3_inf_sha_att_f
-
-# item error covariance
-t1_inf_sha_att_01 ~~ t2_inf_sha_att_01 + t3_inf_sha_att_01
-t2_inf_sha_att_01 ~~ t3_inf_sha_att_01
-t1_inf_sha_att_02 ~~ t2_inf_sha_att_02 + t3_inf_sha_att_02
-t2_inf_sha_att_02 ~~ t3_inf_sha_att_02
-t1_inf_sha_att_03 ~~ t2_inf_sha_att_03 + t3_inf_sha_att_03
-t2_inf_sha_att_03 ~~ t3_inf_sha_att_03
-t1_inf_sha_att_04 ~~ t2_inf_sha_att_04 + t3_inf_sha_att_04
-t2_inf_sha_att_04 ~~ t3_inf_sha_att_04
-t1_inf_sha_att_05 ~~ t2_inf_sha_att_05 + t3_inf_sha_att_05
-t2_inf_sha_att_05 ~~ t3_inf_sha_att_05
-t1_inf_sha_att_06 ~~ t2_inf_sha_att_06 + t3_inf_sha_att_06
-t2_inf_sha_att_06 ~~ t3_inf_sha_att_06
-t1_inf_sha_att_07 ~~ t2_inf_sha_att_07 + t3_inf_sha_att_07
-t2_inf_sha_att_07 ~~ t3_inf_sha_att_07
-t1_inf_sha_att_08 ~~ t2_inf_sha_att_08 + t3_inf_sha_att_08
-t2_inf_sha_att_08 ~~ t3_inf_sha_att_08
-t1_inf_sha_att_10 ~~ t2_inf_sha_att_10 + t3_inf_sha_att_10
-t2_inf_sha_att_10 ~~ t3_inf_sha_att_10
-t1_inf_sha_att_11 ~~ t2_inf_sha_att_11 + t3_inf_sha_att_11
-t2_inf_sha_att_11 ~~ t3_inf_sha_att_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-### Reliability
-
-```{r}
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t1", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t2", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t3", name, "f", sep = "_"))
-```
-
-### Longitudinal Invariance
-
-```{r}
-(anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_"))))
-```
-
-## Online Sharing of Personal Information
-### EFA
-
-```{r}
-no <- 0
-name <- "inf_sha_beh"
-d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
-model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
-factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
-print(factan, sort = TRUE, cut = .3)
-```
-
-### CFA
-#### First-Order Model Unconstrained
-
-First-order model shows poor fit. Needs to be adapted (see second order model).
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_01 + t1_inf_sha_beh_02 + t1_inf_sha_beh_03 + t1_inf_sha_beh_04 + t1_inf_sha_beh_05 + t1_inf_sha_beh_06 + t1_inf_sha_beh_07 + t1_inf_sha_beh_08 + t1_inf_sha_beh_09 + t1_inf_sha_beh_10 + t1_inf_sha_beh_11
-t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_01 + t2_inf_sha_beh_02 + t2_inf_sha_beh_03 + t2_inf_sha_beh_04 + t2_inf_sha_beh_05 + t2_inf_sha_beh_06 + t2_inf_sha_beh_07 + t2_inf_sha_beh_08 + t2_inf_sha_beh_09 + t2_inf_sha_beh_10 + t2_inf_sha_beh_11
-t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_01 + t3_inf_sha_beh_02 + t3_inf_sha_beh_03 + t3_inf_sha_beh_04 + t3_inf_sha_beh_05 + t3_inf_sha_beh_06 + t3_inf_sha_beh_07 + t3_inf_sha_beh_08 + t3_inf_sha_beh_09 + t3_inf_sha_beh_10 + t3_inf_sha_beh_11
-
-# factor covariance
-t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
-t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f
-
-# item error covariance
-t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
-t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
-t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
-t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
-t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
-t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
-t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
-t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
-t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
-t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
-t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
-t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
-t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
-t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
-t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
-t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
-t1_inf_sha_beh_09 ~~ t2_inf_sha_beh_09 + t3_inf_sha_beh_09
-t2_inf_sha_beh_09 ~~ t3_inf_sha_beh_09
-t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
-t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
-t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
-t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### First-Order Model Constrained
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_01 + c2*t1_inf_sha_beh_02 + c3*t1_inf_sha_beh_03 + c4*t1_inf_sha_beh_04 + c5*t1_inf_sha_beh_05 + c6*t1_inf_sha_beh_06 + c7*t1_inf_sha_beh_07 + c8*t1_inf_sha_beh_08 + c9*t1_inf_sha_beh_09 + c10*t1_inf_sha_beh_10 + c11*t1_inf_sha_beh_11
-t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_01 + c2*t2_inf_sha_beh_02 + c3*t2_inf_sha_beh_03 + c4*t2_inf_sha_beh_04 + c5*t2_inf_sha_beh_05 + c6*t2_inf_sha_beh_06 + c7*t2_inf_sha_beh_07 + c8*t2_inf_sha_beh_08 + c9*t2_inf_sha_beh_09 + c10*t2_inf_sha_beh_10 + c11*t2_inf_sha_beh_11
-t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_01 + c2*t3_inf_sha_beh_02 + c3*t3_inf_sha_beh_03 + c4*t3_inf_sha_beh_04 + c5*t3_inf_sha_beh_05 + c6*t3_inf_sha_beh_06 + c7*t3_inf_sha_beh_07 + c8*t3_inf_sha_beh_08 + c9*t3_inf_sha_beh_09 + c10*t3_inf_sha_beh_10 + c11*t3_inf_sha_beh_11
-
-# factor covariance
-t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
-t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f
-
-# item error covariance
-t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
-t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
-t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
-t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
-t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
-t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
-t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
-t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
-t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
-t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
-t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
-t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
-t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
-t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
-t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
-t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
-t1_inf_sha_beh_09 ~~ t2_inf_sha_beh_09 + t3_inf_sha_beh_09
-t2_inf_sha_beh_09 ~~ t3_inf_sha_beh_09
-t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
-t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
-t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
-t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Unconstrained
-
-Second-order model shows much improved fit.
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + t1_inf_sha_beh_f2 + t1_inf_sha_beh_f3 + t1_inf_sha_beh_f4 + t1_inf_sha_beh_f5
-t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_f1 + t2_inf_sha_beh_f2 + t2_inf_sha_beh_f3 + t2_inf_sha_beh_f4 + t2_inf_sha_beh_f5
-t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + t3_inf_sha_beh_f2 + t3_inf_sha_beh_f3 + t3_inf_sha_beh_f4 + t3_inf_sha_beh_f5
-t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + t1_inf_sha_beh_02
-t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + t1_inf_sha_beh_04
-t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + t1_inf_sha_beh_06
-t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + t1_inf_sha_beh_08
-t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + t1_inf_sha_beh_11
-t2_inf_sha_beh_f1 =~ 1*t2_inf_sha_beh_01 + t2_inf_sha_beh_02
-t2_inf_sha_beh_f2 =~ 1*t2_inf_sha_beh_03 + t2_inf_sha_beh_04
-t2_inf_sha_beh_f3 =~ 1*t2_inf_sha_beh_05 + t2_inf_sha_beh_06
-t2_inf_sha_beh_f4 =~ 1*t2_inf_sha_beh_07 + t2_inf_sha_beh_08
-t2_inf_sha_beh_f5 =~ 1*t2_inf_sha_beh_10 + t2_inf_sha_beh_11
-t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + t3_inf_sha_beh_02
-t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + t3_inf_sha_beh_04
-t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + t3_inf_sha_beh_06
-t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + t3_inf_sha_beh_08
-t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + t3_inf_sha_beh_11
-
-# factor covariance
-t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
-t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f
-
-# item error covariance
-t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
-t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
-t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
-t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
-t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
-t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
-t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
-t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
-t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
-t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
-t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
-t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
-t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
-t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
-t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
-t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
-t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
-t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
-t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
-t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Second-Order Model Constrained
-
-```{r}
-model <- '
-# create factors
-t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + o2*t1_inf_sha_beh_f2 + o3*t1_inf_sha_beh_f3 + o4*t1_inf_sha_beh_f4 + o5*t1_inf_sha_beh_f5
-t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_f1 + o2*t2_inf_sha_beh_f2 + o3*t2_inf_sha_beh_f3 + o4*t2_inf_sha_beh_f4 + o5*t2_inf_sha_beh_f5
-t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + o2*t3_inf_sha_beh_f2 + o3*t3_inf_sha_beh_f3 + o4*t3_inf_sha_beh_f4 + o5*t3_inf_sha_beh_f5
-t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + j2*t1_inf_sha_beh_02
-t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + k2*t1_inf_sha_beh_04
-t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + l2*t1_inf_sha_beh_06
-t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + m2*t1_inf_sha_beh_08
-t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + n2*t1_inf_sha_beh_11
-t2_inf_sha_beh_f1 =~ 1*t2_inf_sha_beh_01 + j2*t2_inf_sha_beh_02
-t2_inf_sha_beh_f2 =~ 1*t2_inf_sha_beh_03 + k2*t2_inf_sha_beh_04
-t2_inf_sha_beh_f3 =~ 1*t2_inf_sha_beh_05 + l2*t2_inf_sha_beh_06
-t2_inf_sha_beh_f4 =~ 1*t2_inf_sha_beh_07 + m2*t2_inf_sha_beh_08
-t2_inf_sha_beh_f5 =~ 1*t2_inf_sha_beh_10 + n2*t2_inf_sha_beh_11
-t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + j2*t3_inf_sha_beh_02
-t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + k2*t3_inf_sha_beh_04
-t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + l2*t3_inf_sha_beh_06
-t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + m2*t3_inf_sha_beh_08
-t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + n2*t3_inf_sha_beh_11
-
-# factor covariance
-t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
-t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f
-
-# item error covariance
-t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
-t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
-t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
-t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
-t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
-t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
-t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
-t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
-t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
-t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
-t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
-t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
-t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
-t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
-t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
-t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
-t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
-t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
-t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
-t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-### Reliability
-
-```{r}
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t1", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t2", name, "f", sep = "_"))
-reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t3", name, "f", sep = "_"))
-```
-
-### Longitudinal Invariance
-
-```{r}
-(anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_"))))
-```
-
-## All Measures in one Model 
-### Second Order
-
-```{r CFA_All}
-name <- "all_vars"
-no <- 0
-model <- '
-# Privacy Concerns
-# create factors
-t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
-t2_pri_con_f =~ 1*t2_pri_con_f1 + a2*t2_pri_con_f2
-t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
-t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
-t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
-t2_pri_con_f1 =~ 1*t2_pri_con_04 + b2*t2_pri_con_05 + b3*t2_pri_con_06
-t2_pri_con_f2 =~ 1*t2_pri_con_07 + c2*t2_pri_con_08 + c3*t2_pri_con_09
-t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
-t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09
-
-# error covariances
-t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
-t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
-t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
-t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
-t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
-t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
-t2_pri_con_04 ~~ t1_pri_con_04
-t2_pri_con_05 ~~ t1_pri_con_05 
-t2_pri_con_06 ~~ t1_pri_con_06
-t2_pri_con_07 ~~ t1_pri_con_07
-t2_pri_con_08 ~~ t1_pri_con_08
-t2_pri_con_09 ~~ t1_pri_con_09
-
-# factor covariances
-t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
-t2_pri_con_f ~~ t3_pri_con_f
-
-# Information Sharing Attitude
-# create factors
-t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + d2*t1_inf_sha_att_f2 + d3*t1_inf_sha_att_f3 + d4*t1_inf_sha_att_f4 + d5*t1_inf_sha_att_f5
-t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + d2*t2_inf_sha_att_f2 + d3*t2_inf_sha_att_f3 + d4*t2_inf_sha_att_f4 + d5*t2_inf_sha_att_f5
-t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + d2*t3_inf_sha_att_f2 + d3*t3_inf_sha_att_f3 + d4*t3_inf_sha_att_f4 + d5*t3_inf_sha_att_f5
-t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + e*t1_inf_sha_att_02
-t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + f*t1_inf_sha_att_04
-t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + g*t1_inf_sha_att_06
-t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + h*t1_inf_sha_att_08
-t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + i*t1_inf_sha_att_11
-t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + e*t2_inf_sha_att_02
-t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + f*t2_inf_sha_att_04
-t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + g*t2_inf_sha_att_06
-t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + h*t2_inf_sha_att_08
-t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + i*t2_inf_sha_att_11
-t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + e*t3_inf_sha_att_02
-t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + f*t3_inf_sha_att_04
-t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + g*t3_inf_sha_att_06
-t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + h*t3_inf_sha_att_08
-t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + i*t3_inf_sha_att_11
-
-# factor covariance
-t1_inf_sha_att_f ~~ t2_inf_sha_att_f + t3_inf_sha_att_f
-t2_inf_sha_att_f ~~ t3_inf_sha_att_f
-
-# item error covariance
-t1_inf_sha_att_01 ~~ t2_inf_sha_att_01 + t3_inf_sha_att_01
-t2_inf_sha_att_01 ~~ t3_inf_sha_att_01
-t1_inf_sha_att_02 ~~ t2_inf_sha_att_02 + t3_inf_sha_att_02
-t2_inf_sha_att_02 ~~ t3_inf_sha_att_02
-t1_inf_sha_att_03 ~~ t2_inf_sha_att_03 + t3_inf_sha_att_03
-t2_inf_sha_att_03 ~~ t3_inf_sha_att_03
-t1_inf_sha_att_04 ~~ t2_inf_sha_att_04 + t3_inf_sha_att_04
-t2_inf_sha_att_04 ~~ t3_inf_sha_att_04
-t1_inf_sha_att_05 ~~ t2_inf_sha_att_05 + t3_inf_sha_att_05
-t2_inf_sha_att_05 ~~ t3_inf_sha_att_05
-t1_inf_sha_att_06 ~~ t2_inf_sha_att_06 + t3_inf_sha_att_06
-t2_inf_sha_att_06 ~~ t3_inf_sha_att_06
-t1_inf_sha_att_07 ~~ t2_inf_sha_att_07 + t3_inf_sha_att_07
-t2_inf_sha_att_07 ~~ t3_inf_sha_att_07
-t1_inf_sha_att_08 ~~ t2_inf_sha_att_08 + t3_inf_sha_att_08
-t2_inf_sha_att_08 ~~ t3_inf_sha_att_08
-t1_inf_sha_att_10 ~~ t2_inf_sha_att_10 + t3_inf_sha_att_10
-t2_inf_sha_att_10 ~~ t3_inf_sha_att_10
-t1_inf_sha_att_11 ~~ t2_inf_sha_att_11 + t3_inf_sha_att_11
-t2_inf_sha_att_11 ~~ t3_inf_sha_att_11
-
-# information sharing behavior
-# create factors
-t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + o2*t1_inf_sha_beh_f2 + o3*t1_inf_sha_beh_f3 + o4*t1_inf_sha_beh_f4 + o5*t1_inf_sha_beh_f5
-t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_f1 + o2*t2_inf_sha_beh_f2 + o3*t2_inf_sha_beh_f3 + o4*t2_inf_sha_beh_f4 + o5*t2_inf_sha_beh_f5
-t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + o2*t3_inf_sha_beh_f2 + o3*t3_inf_sha_beh_f3 + o4*t3_inf_sha_beh_f4 + o5*t3_inf_sha_beh_f5
-t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + j2*t1_inf_sha_beh_02
-t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + k2*t1_inf_sha_beh_04
-t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + l2*t1_inf_sha_beh_06
-t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + m2*t1_inf_sha_beh_08
-t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + n2*t1_inf_sha_beh_11
-t2_inf_sha_beh_f1 =~ 1*t2_inf_sha_beh_01 + j2*t2_inf_sha_beh_02
-t2_inf_sha_beh_f2 =~ 1*t2_inf_sha_beh_03 + k2*t2_inf_sha_beh_04
-t2_inf_sha_beh_f3 =~ 1*t2_inf_sha_beh_05 + l2*t2_inf_sha_beh_06
-t2_inf_sha_beh_f4 =~ 1*t2_inf_sha_beh_07 + m2*t2_inf_sha_beh_08
-t2_inf_sha_beh_f5 =~ 1*t2_inf_sha_beh_10 + n2*t2_inf_sha_beh_11
-t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + j2*t3_inf_sha_beh_02
-t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + k2*t3_inf_sha_beh_04
-t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + l2*t3_inf_sha_beh_06
-t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + m2*t3_inf_sha_beh_08
-t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + n2*t3_inf_sha_beh_11
-
-# factor covariance
-t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
-t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f
-
-# item error covariance
-t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
-t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
-t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
-t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
-t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
-t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
-t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
-t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
-t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
-t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
-t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
-t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
-t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
-t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
-t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
-t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
-t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
-t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
-t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
-t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
-
-## Correlations Attitude and Behavior-Items
-t1_inf_sha_beh_01 ~~ t1_inf_sha_att_01
-t1_inf_sha_beh_02 ~~ t1_inf_sha_att_02
-t1_inf_sha_beh_03 ~~ t1_inf_sha_att_03
-t1_inf_sha_beh_04 ~~ t1_inf_sha_att_04
-t1_inf_sha_beh_05 ~~ t1_inf_sha_att_05
-t1_inf_sha_beh_06 ~~ t1_inf_sha_att_06
-t1_inf_sha_beh_07 ~~ t1_inf_sha_att_07
-t1_inf_sha_beh_08 ~~ t1_inf_sha_att_08
-t1_inf_sha_beh_10 ~~ t1_inf_sha_att_10
-t1_inf_sha_beh_11 ~~ t1_inf_sha_att_11
-t2_inf_sha_beh_01 ~~ t2_inf_sha_att_01
-t2_inf_sha_beh_02 ~~ t2_inf_sha_att_02
-t2_inf_sha_beh_03 ~~ t2_inf_sha_att_03
-t2_inf_sha_beh_04 ~~ t2_inf_sha_att_04
-t2_inf_sha_beh_05 ~~ t2_inf_sha_att_05
-t2_inf_sha_beh_06 ~~ t2_inf_sha_att_06
-t2_inf_sha_beh_07 ~~ t2_inf_sha_att_07
-t2_inf_sha_beh_08 ~~ t2_inf_sha_att_08
-t2_inf_sha_beh_10 ~~ t2_inf_sha_att_10
-t2_inf_sha_beh_11 ~~ t2_inf_sha_att_11
-t3_inf_sha_beh_01 ~~ t3_inf_sha_att_01
-t3_inf_sha_beh_02 ~~ t3_inf_sha_att_02
-t3_inf_sha_beh_03 ~~ t3_inf_sha_att_03
-t3_inf_sha_beh_04 ~~ t3_inf_sha_att_04
-t3_inf_sha_beh_05 ~~ t3_inf_sha_att_05
-t3_inf_sha_beh_06 ~~ t3_inf_sha_att_06
-t3_inf_sha_beh_07 ~~ t3_inf_sha_att_07
-t3_inf_sha_beh_08 ~~ t3_inf_sha_att_08
-t3_inf_sha_beh_10 ~~ t3_inf_sha_att_10
-t3_inf_sha_beh_11 ~~ t3_inf_sha_att_11
-'
-no <- no + 1
-assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
-summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
-```
-
-### Extract Factor Scores
-
-```{r}
-d_fs <- lavPredict(get(paste("fit", name, no, sep = "_")), type = "ov") %>% 
-  as.data.frame() %>% 
-  mutate(t1_pri_con_fs = rowMeans(select(., starts_with("t1_pri"))),
-         t2_pri_con_fs = rowMeans(select(., starts_with("t2_pri"))),
-         t3_pri_con_fs = rowMeans(select(., starts_with("t3_pri"))),
-         t1_inf_sha_att_fs = rowMeans(select(., starts_with("t1_inf_sha_att"))),
-         t2_inf_sha_att_fs = rowMeans(select(., starts_with("t2_inf_sha_att"))),
-         t3_inf_sha_att_fs = rowMeans(select(., starts_with("t3_inf_sha_att"))),
-         t1_inf_sha_beh_fs = rowMeans(select(., starts_with("t1_inf_sha_beh"))),
-         t2_inf_sha_beh_fs = rowMeans(select(., starts_with("t2_inf_sha_beh"))),
-         t3_inf_sha_beh_fs = rowMeans(select(., starts_with("t3_inf_sha_beh")))
-         ) %>% 
-  select(contains("_fs"))
-d_wide <- cbind(d_fs, d_wide)
-```
-
-### Latent correlation matrix with plots
-
-```{r Corrplot, fig.height = 8, fig.width = 8, size=5}
-colnames(d_fs) <- c("Concerns\nT1", "Concerns\nT2" , "Concerns\nT3",
-                    "Pos. Attitude\nT1", "Pos. Attitude\nT2" , "Pos. Attitude\nT3",
-                    "Inf. Sharing\nT1", "Inf. Sharing\nT2" , "Inf. Sharing\nT3")
-
-corr_plot <- ggpairs(d_fs,
-                     # upper = list(continuous = wrap(td::cor_matrix, data = d_fs)),
-                     lower = list(continuous = wrap(td::scat_plot, coords = c(1, 5, 1, 5)))) + 
-  theme_bw()
-print(corr_plot)
-```
-
-# ICCs
-
-Next, we determine the Intraclass Correlation Coefficients (ICC), to determine how much variance in the measures is due to between-person differences versus within-person changes.
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + (1 | id), filter(d_long, wave < 4))
-summary(fit)
-icc_pri_con <- icc(fit)
-
-fit <- lmer(inf_sha_att_m ~ 1 + (1 | id), filter(d_long, wave < 4))
-summary(fit)
-icc_inf_sha_att <- icc(fit)
-
-fit <- lmer(inf_sha_beh_m ~ 1 + (1 | id), filter(d_long, wave < 4))
-summary(fit)
-icc_inf_sha_beh <- icc(fit)
-```
-
-# Results
-
-In what follows, please find all information about our final model we present in the paper.
-
-# Additional Analyses
-## RI-CLPM
-### Assumptions
-#### Multivariate Normal Distribution
-
-```{r multivardis}
-mult_norm_test <- mvn(d_fs)
-print(mult_norm_test)
-```
-
-Results show that the assumption of multivariate normal distribution was violated.
-Hence, it'd be preferrable to conduct robust Maximum Likelihood Estimation.
-However, using robust estimation it's not possible to run SEM on all data using Full Information Maximum Likehoood (FIML).
-Given that we consider it more important to include as much information as possible and that estimators often produce similar results, we decided to estimate the following models using regular maximum likehood.
-
-### Two Variables
-
-Here, we look at the bivariate relations of privacy concerns and information sharing.
-This is interesting, because in the paper we also address privacy attitudes, thereby potentially attentuating the effect of privacy concerns.
-However, when analyzing only these two variables we do not find larger effects sizes.
-
-#### Model 1
-
-Here, we use regular observed means.
-
-```{r }
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# intercepts
-t1_pri_con_m ~ mu1*1
-t2_pri_con_m ~ mu2*1
-t3_pri_con_m ~ mu3*1
-t1_inf_sha_beh_m ~ pi1*1
-t2_inf_sha_beh_m ~ pi2*1
-t3_inf_sha_beh_m ~ pi3*1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t2_pri_con_w =~ 1*t2_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 2
-
-Model with a (broad) single item measure of privacy concerns ("In general, how concerned are you about your privacy while using the Internet?").
-
-```{r }
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_01 + 1*t2_pri_con_01 + 1*t3_pri_con_01
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# intercepts
-t1_pri_con_01 ~ mu1*1
-t2_pri_con_01 ~ mu2*1
-t3_pri_con_01 ~ mu3*1
-t1_inf_sha_beh_m ~ pi1*1
-t2_inf_sha_beh_m ~ pi2*1
-t3_inf_sha_beh_m ~ pi3*1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_01
-t2_pri_con_w =~ 1*t2_pri_con_01
-t3_pri_con_w =~ 1*t3_pri_con_01
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 3
-
-With Factor Scores.
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-
-# intercepts
-t1_pri_con_fs ~ 1
-t2_pri_con_fs ~ 1
-t3_pri_con_fs ~ 1
-t1_inf_sha_beh_fs ~ 1
-t2_inf_sha_beh_fs ~ 1
-t3_inf_sha_beh_fs ~ 1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-'
-fit <- lavaan(model, data = d_wide)
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 4
-
-With Factor Scores and Control Variables.
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-
-# intercepts
-t1_pri_con_fs ~ 1
-t2_pri_con_fs ~ 1
-t3_pri_con_fs ~ 1
-t1_inf_sha_beh_fs ~ 1
-t2_inf_sha_beh_fs ~ 1
-t3_inf_sha_beh_fs ~ 1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-
-# control variables
-t1_pri_con_fs ~ age + edu_num + male
-t2_pri_con_fs ~ age + edu_num + male
-t3_pri_con_fs ~ age + edu_num + male
-t1_inf_sha_beh_fs ~ age + edu_num + male
-t2_inf_sha_beh_fs ~ age + edu_num + male
-t3_inf_sha_beh_fs ~ age + edu_num + male
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ml")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 5
-
-In this model, we omit all longitudinal paths in order to better estimate the concurrent relations of the variables for _all_ waves (in the regular RI-CLPM, only the relations at wave 1 can be interpreted meaningfully).
-
-```{r }
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# intercepts
-t1_pri_con_m ~ mu1*1
-t2_pri_con_m ~ mu2*1
-t3_pri_con_m ~ mu3*1
-t1_inf_sha_beh_m ~ pi1*1
-t2_inf_sha_beh_m ~ pi2*1
-t3_inf_sha_beh_m ~ pi3*1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t2_pri_con_w =~ 1*t2_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ a*t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ml")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-#### Model 6
-
-The same like above, using Factor Scores and control variables.
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-
-# intercepts
-t1_pri_con_fs ~ 1
-t2_pri_con_fs ~ 1
-t3_pri_con_fs ~ 1
-t1_inf_sha_beh_fs ~ 1
-t2_inf_sha_beh_fs ~ 1
-t3_inf_sha_beh_fs ~ 1
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-
-# estimate variances
-pri_con_b ~~ pri_con_b
-inf_sha_beh_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_pri_con_w
-t2_pri_con_w ~~ t2_pri_con_w
-t3_pri_con_w ~~ t3_pri_con_w
-t1_inf_sha_beh_w ~~ t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~~ t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~~ t3_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ a*t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_beh_w
-
-# control variables
-t1_pri_con_fs ~ age + edu_num + male
-t2_pri_con_fs ~ age + edu_num + male
-t3_pri_con_fs ~ age + edu_num + male
-t1_inf_sha_beh_fs ~ age + edu_num + male
-t2_inf_sha_beh_fs ~ age + edu_num + male
-t3_inf_sha_beh_fs ~ age + edu_num + male
-'
-
-fit <- lavaan(model, data = d_wide, missing = "ml")
-summary(fit, standardized = TRUE, fit.measures = TRUE)
-```
-
-### Three Variables
-#### Model 1
-
-With observed means.
-
-```{r }
-model <- '
-# random intercepts (between person)
-pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
-inf_sha_att_b =~ 1*t1_inf_sha_att_m + 1*t2_inf_sha_att_m + 1*t3_inf_sha_att_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t2_pri_con_w =~ 1*t2_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_m
-t2_inf_sha_att_w =~ 1*t2_inf_sha_att_m
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_m ~~ 0*t1_pri_con_m
-t2_pri_con_m ~~ 0*t2_pri_con_m
-t3_pri_con_m ~~ 0*t3_pri_con_m
-t1_inf_sha_att_m ~~ 0*t1_inf_sha_att_m
-t2_inf_sha_att_m ~~ 0*t2_inf_sha_att_m
-t3_inf_sha_att_m ~~ 0*t3_inf_sha_att_m
-t1_inf_sha_beh_m ~~ 0*t1_inf_sha_beh_m
-t2_inf_sha_beh_m ~~ 0*t2_inf_sha_beh_m
-t3_inf_sha_beh_m ~~ 0*t3_inf_sha_beh_m
-
-# allow covariances RIs & variables measured at the same time
-pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
-inf_sha_att_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
-t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-'
-fit <- sem(model, estimator = "ML", data = d_wide, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-```
-
-#### Model 2
-
-With observed means and control variables.
-
-```{r }
-model <- '
-# random intercepts (between person)
-pri_con_b =~ 1*t1_pri_con_m + 1*t2_pri_con_m + 1*t3_pri_con_m
-inf_sha_att_b =~ 1*t1_inf_sha_att_m + 1*t2_inf_sha_att_m + 1*t3_inf_sha_att_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t2_inf_sha_beh_m + 1*t3_inf_sha_beh_m
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t2_pri_con_w =~ 1*t2_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_m
-t2_inf_sha_att_w =~ 1*t2_inf_sha_att_m
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_m ~~ 0*t1_pri_con_m
-t2_pri_con_m ~~ 0*t2_pri_con_m
-t3_pri_con_m ~~ 0*t3_pri_con_m
-t1_inf_sha_att_m ~~ 0*t1_inf_sha_att_m
-t2_inf_sha_att_m ~~ 0*t2_inf_sha_att_m
-t3_inf_sha_att_m ~~ 0*t3_inf_sha_att_m
-t1_inf_sha_beh_m ~~ 0*t1_inf_sha_beh_m
-t2_inf_sha_beh_m ~~ 0*t2_inf_sha_beh_m
-t3_inf_sha_beh_m ~~ 0*t3_inf_sha_beh_m
-
-# allow covariances RIs & variables measured at the same time
-pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
-inf_sha_att_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
-t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-
-# control variables
-t1_pri_con_m ~ age + edu_num + male
-t2_pri_con_m ~ age + edu_num + male
-t3_pri_con_m ~ age + edu_num + male
-t1_inf_sha_beh_m ~ age + edu_num + male
-t2_inf_sha_beh_m ~ age + edu_num + male
-t3_inf_sha_beh_m ~ age + edu_num + male
-t1_inf_sha_att_m ~ age + edu_num + male
-t2_inf_sha_att_m ~ age + edu_num + male
-t3_inf_sha_att_m ~ age + edu_num + male
-'
-fit <- sem(model, estimator = "ML", data = d_wide, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-```
-
-#### Model 3
-
-With Factor Scores.
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t2_inf_sha_att_fs + 1*t3_inf_sha_att_fs
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
-t2_inf_sha_att_w =~ 1*t2_inf_sha_att_fs
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
-inf_sha_att_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
-t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_fs ~~ 0*t1_pri_con_fs
-t2_pri_con_fs ~~ 0*t2_pri_con_fs
-t3_pri_con_fs ~~ 0*t3_pri_con_fs
-t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
-t2_inf_sha_att_fs ~~ 0*t2_inf_sha_att_fs
-t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
-t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
-t2_inf_sha_beh_fs ~~ 0*t2_inf_sha_beh_fs
-t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs
-'
-fit <- sem(model, data = d_wide, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-```
-
-#### Model 4 (final)
-
-With Factor Scores and control variables. This is the final model we report in the paper.
-
-```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
-knitr::include_graphics("../figures/model_7.png")
-```
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
-inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t2_inf_sha_att_fs + 1*t3_inf_sha_att_fs
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_fs
-t2_pri_con_w =~ 1*t2_pri_con_fs
-t3_pri_con_w =~ 1*t3_pri_con_fs
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
-t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
-t2_inf_sha_att_w =~ 1*t2_inf_sha_att_fs
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs
-
-# within person effects
-t2_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t2_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t2_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t3_pri_con_w ~ a1*t2_pri_con_w + a2*t2_inf_sha_att_w + a3*t2_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t2_pri_con_w + b2*t2_inf_sha_att_w + b3*t2_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t2_pri_con_w + c2*t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ cor_b_1*inf_sha_att_b + cor_b_2*inf_sha_beh_b
-inf_sha_att_b ~~ cor_b_3*inf_sha_beh_b
-t1_pri_con_w ~~ cor_w_1*t1_inf_sha_att_w + cor_w_2*t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ cor_w_3*t1_inf_sha_beh_w
-t2_pri_con_w ~~ a*t2_inf_sha_att_w + b*t2_inf_sha_beh_w
-t2_inf_sha_att_w ~~ c*t2_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_fs ~~ 0*t1_pri_con_fs
-t2_pri_con_fs ~~ 0*t2_pri_con_fs
-t3_pri_con_fs ~~ 0*t3_pri_con_fs
-t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
-t2_inf_sha_att_fs ~~ 0*t2_inf_sha_att_fs
-t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
-t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
-t2_inf_sha_beh_fs ~~ 0*t2_inf_sha_beh_fs
-t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs
-
-# control variables
-t1_pri_con_fs ~ age + edu_num + male
-t2_pri_con_fs ~ age + edu_num + male
-t3_pri_con_fs ~ age + edu_num + male
-t1_inf_sha_beh_fs ~ age + edu_num + male
-t2_inf_sha_beh_fs ~ age + edu_num + male
-t3_inf_sha_beh_fs ~ age + edu_num + male
-t1_inf_sha_att_fs ~ age + edu_num + male
-t2_inf_sha_att_fs ~ age + edu_num + male
-t3_inf_sha_att_fs ~ age + edu_num + male
-'
-fit <- sem(model, data = d_wide, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-fit_riclpm <- fit
-effect_std_ci <- standardizedsolution(fit) %>% 
-  filter(lhs == "pri_con_b", rhs == "inf_sha_beh_b")
-```
-
-#### Model 5
-
-With Factor Scores, control variables, and 4 waves / 1 year intervals
-
-```{r}
-model <- '
-# between relations
-pri_con_b =~ 1*t1_pri_con_m + 1*t3_pri_con_m + 1*t4_pri_con_m + 1*t5_pri_con_m
-inf_sha_beh_b =~ 1*t1_inf_sha_beh_m + 1*t3_inf_sha_beh_m + 1*t4_inf_sha_beh_m + 1*t5_inf_sha_beh_m
-inf_sha_att_b =~ 1*t1_inf_sha_att_m + 1*t3_inf_sha_att_m + 1*t4_inf_sha_att_m + 1*t5_inf_sha_att_m
-
-# within person changes
-t1_pri_con_w =~ 1*t1_pri_con_m
-t3_pri_con_w =~ 1*t3_pri_con_m
-t4_pri_con_w =~ 1*t4_pri_con_m
-t5_pri_con_w =~ 1*t5_pri_con_m
-t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_m
-t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_m
-t4_inf_sha_beh_w =~ 1*t4_inf_sha_beh_m
-t5_inf_sha_beh_w =~ 1*t5_inf_sha_beh_m
-t1_inf_sha_att_w =~ 1*t1_inf_sha_att_m
-t3_inf_sha_att_w =~ 1*t3_inf_sha_att_m
-t4_inf_sha_att_w =~ 1*t4_inf_sha_att_m
-t5_inf_sha_att_w =~ 1*t5_inf_sha_att_m
-
-# within person effects
-t3_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
-t3_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
-t3_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
-t4_pri_con_w ~ a1*t3_pri_con_w + a2*t3_inf_sha_att_w + a3*t3_inf_sha_beh_w
-t4_inf_sha_att_w ~ b1*t3_pri_con_w + b2*t3_inf_sha_att_w + b3*t3_inf_sha_beh_w
-t4_inf_sha_beh_w ~ c1*t3_pri_con_w + c2*t3_inf_sha_att_w + c3*t3_inf_sha_beh_w
-t5_pri_con_w ~ a1*t4_pri_con_w + a2*t4_inf_sha_att_w + a3*t4_inf_sha_beh_w
-t5_inf_sha_att_w ~ b1*t4_pri_con_w + b2*t4_inf_sha_att_w + b3*t4_inf_sha_beh_w
-t5_inf_sha_beh_w ~ c1*t4_pri_con_w + c2*t4_inf_sha_att_w + c3*t4_inf_sha_beh_w
-
-# covariances
-pri_con_b ~~ inf_sha_att_b + inf_sha_beh_b
-inf_sha_att_b ~~ inf_sha_beh_b
-t1_pri_con_w ~~ t1_inf_sha_att_w + t1_inf_sha_beh_w
-t1_inf_sha_att_w ~~ t1_inf_sha_beh_w
-t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
-t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
-t4_pri_con_w ~~ a*t4_inf_sha_att_w + b*t4_inf_sha_beh_w
-t4_inf_sha_att_w ~~ c*t4_inf_sha_beh_w
-t5_pri_con_w ~~ a*t5_inf_sha_att_w + b*t5_inf_sha_beh_w
-t5_inf_sha_att_w ~~ c*t5_inf_sha_beh_w
-
-# setting variances of observed variables to zero
-t1_pri_con_m ~~ 0*t1_pri_con_m
-t3_pri_con_m ~~ 0*t3_pri_con_m
-t4_pri_con_m ~~ 0*t4_pri_con_m
-t5_pri_con_m ~~ 0*t5_pri_con_m
-t1_inf_sha_att_m ~~ 0*t1_inf_sha_att_m
-t3_inf_sha_att_m ~~ 0*t3_inf_sha_att_m
-t4_inf_sha_att_m ~~ 0*t4_inf_sha_att_m
-t5_inf_sha_att_m ~~ 0*t5_inf_sha_att_m
-t1_inf_sha_beh_m ~~ 0*t1_inf_sha_beh_m
-t3_inf_sha_beh_m ~~ 0*t3_inf_sha_beh_m
-t4_inf_sha_beh_m ~~ 0*t4_inf_sha_beh_m
-t5_inf_sha_beh_m ~~ 0*t5_inf_sha_beh_m
-
-# control variables
-t1_pri_con_m ~ age + edu_num + male
-t3_pri_con_m ~ age + edu_num + male
-t4_pri_con_m ~ age + edu_num + male
-t5_pri_con_m ~ age + edu_num + male
-t1_inf_sha_beh_m ~ age + edu_num + male
-t3_inf_sha_beh_m ~ age + edu_num + male
-t4_inf_sha_beh_m ~ age + edu_num + male
-t5_inf_sha_beh_m ~ age + edu_num + male
-t1_inf_sha_att_m ~ age + edu_num + male
-t3_inf_sha_att_m ~ age + edu_num + male
-t4_inf_sha_att_m ~ age + edu_num + male
-t5_inf_sha_att_m ~ age + edu_num + male
-'
-fit <- sem(model, data = d_wide_all, orthogonal = TRUE, missing = "ML")
-summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
-```
-
-## Mixed Models
-
-In what follows, we also present the results of several mixed models.
-Using mixed models, we can include more data.
-However, one downside is that not all research questions can be answered in one single model.
-
-### Two Variables
-#### Model 1
-
-Measures overall correlation between privacy concerns and information sharing.
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + inf_sha_beh_m + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-#### Model 2
-
-Measures how current levels of information sharing are affected by generel levels of privacy concern und current levels of privacy concern.
-
-```{r}
-fit <- lmer(inf_sha_beh_m ~ pri_con_m_b + pri_con_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-Measures how current levels of privacy concern are affected by generel levels of information sharing und current levels of information sharing.
-
-```{r}
-fit <- lmer(pri_con_m ~ inf_sha_beh_m_b + inf_sha_beh_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-#### Model 3
-
-Includes control variables.
-
-```{r}
-fit <- lmer(inf_sha_beh_m ~ 1 + pri_con_m_b + pri_con_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + inf_sha_beh_m_b + inf_sha_beh_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-### Three Variables
-#### Model 1
-
-Measures how current levels of information sharing are affected by generel levels of privacy concern and current levels of privacy concern, as well as general levels of positive attitude toward information sharing and current levels of positive attitude toward information sharing.
-
-```{r}
-fit <- lmer(inf_sha_beh_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_att_m_b + inf_sha_att_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-Measures how current levels of positive attitude toward information sharing are affected by generel levels of privacy concern and current levels of privacy concern, as well as general levels of information sharing and current levels of information sharing.
-
-```{r}
-fit <- lmer(inf_sha_att_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_beh_m_b + inf_sha_beh_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-Measures how current levels of privacy concern are affected by generel levels of positive attitude toward information sharing and current levels of positive attitude toward information sharing, as well as general levels of information sharing and current levels of information sharing.
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + inf_sha_beh_m_b + inf_sha_beh_m_w + inf_sha_att_m_b + inf_sha_att_m_w + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-#### Model 2
-
-Includes control variables
-
-```{r}
-fit <- lmer(pri_con_m ~ 1 + inf_sha_att_m_b + inf_sha_att_m_w + inf_sha_beh_m_b + inf_sha_beh_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-```{r}
-fit <- lmer(inf_sha_att_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_beh_m_b + inf_sha_beh_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-```{r}
-fit <- lmer(inf_sha_beh_m ~ 1 + pri_con_m_b + pri_con_m_w + inf_sha_att_m_b + inf_sha_att_m_w + male + age + edu_num + (1 | id) + (1 | wave), d_long)
-summary(fit)
-std_beta(fit)
-```
-
-```{r cache=F}
-save.image("../data/workspace.RData")
-```

### 2020-04-23 manuscript.RmD
- update website

@@
 
-  This manuscript features online supplementary material that includes the code, additional analyses, and a reproducible version of the manuscript (https://osf.io/4wabh).
+  This manuscript features a companion website that includes detailed summaries of the statistical results, the code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy-paradox-longitudinal).
 The data can be downloaded from http://dx.doi.org/10.7802/1937.
@@
 For the analyses, coding, and typesetting, we used `r r_citations`.
-The code, additional analyses, and a reproducible version of this manuscript can be accessed in the Online Supplementary Material (OSM) at https://osf.io/4wabh.
+The code, additional analyses, and a reproducible version of this manuscript can be found on the manuscript's companion website at https://tdienlin.github.io/privacy-paradox-longitudinal.
 

### 2020-05-07 analyses.Rmd
- Implemented feedback from reviews - Toned down implications - First language edits

@@
 ```{r Corrplot, fig.height = 8, fig.width = 8, size=5}
-colnames(d_fs) <- c("Concerns\nT1", "Concerns\nT2" , "Concerns\nT3",
-                    "Pos. Attitude\nT1", "Pos. Attitude\nT2" , "Pos. Attitude\nT3",
-                    "Inf. Sharing\nT1", "Inf. Sharing\nT2" , "Inf. Sharing\nT3")
+colnames(d_fs) <- c("Privacy\nconcerns\nT1", "Privacy\nconcerns\nT2" , "Privacy\nconcerns\nT3",
+                    "Positive\nattitude\nT1", "Positive\nattitude\nT2" , "Positive\nattitude\nT3",
+                    "Information\nsharing\nT1", "Information\nsharing\nT2" , "Information\nsharing\nT3")
 

### 2020-05-07 analyses_additional.Rmd
- Implemented feedback from reviews - Toned down implications - First language edits

@@
 
+Same model, but with unconstrained effects. That way, we can empirically test the assumption whether effects have changed over time.
 With Factor Scores, control variables, and 4 waves / 1 year intervals
+
+```{r}
+model_free <- '
+# between relations
+pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
+inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
+inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t2_inf_sha_att_fs + 1*t3_inf_sha_att_fs
+
+# within person changes
+t1_pri_con_w =~ 1*t1_pri_con_fs
+t2_pri_con_w =~ 1*t2_pri_con_fs
+t3_pri_con_w =~ 1*t3_pri_con_fs
+t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
+t2_inf_sha_beh_w =~ 1*t2_inf_sha_beh_fs
+t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
+t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
+t2_inf_sha_att_w =~ 1*t2_inf_sha_att_fs
+t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs
+
+# within person effects
+t2_pri_con_w ~ a1*t1_pri_con_w + t1_inf_sha_att_w + t1_inf_sha_beh_w
+t2_inf_sha_att_w ~ t1_pri_con_w + b2*t1_inf_sha_att_w + t1_inf_sha_beh_w
+t2_inf_sha_beh_w ~ t1_pri_con_w + t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
+t3_pri_con_w ~ a1*t2_pri_con_w + t2_inf_sha_att_w + t2_inf_sha_beh_w
+t3_inf_sha_att_w ~ t2_pri_con_w + b2*t2_inf_sha_att_w + t2_inf_sha_beh_w
+t3_inf_sha_beh_w ~ t2_pri_con_w + t2_inf_sha_att_w + c3*t2_inf_sha_beh_w
+
+# covariances
+pri_con_b ~~ cor_b_1*inf_sha_att_b + cor_b_2*inf_sha_beh_b
+inf_sha_att_b ~~ cor_b_3*inf_sha_beh_b
+t1_pri_con_w ~~ cor_w_1*t1_inf_sha_att_w + cor_w_2*t1_inf_sha_beh_w
+t1_inf_sha_att_w ~~ cor_w_3*t1_inf_sha_beh_w
+t2_pri_con_w ~~ t2_inf_sha_att_w + t2_inf_sha_beh_w
+t2_inf_sha_att_w ~~ t2_inf_sha_beh_w
+t3_pri_con_w ~~ t3_inf_sha_att_w + t3_inf_sha_beh_w
+t3_inf_sha_att_w ~~ t3_inf_sha_beh_w
+
+# setting variances of observed variables to zero
+t1_pri_con_fs ~~ 0*t1_pri_con_fs
+t2_pri_con_fs ~~ 0*t2_pri_con_fs
+t3_pri_con_fs ~~ 0*t3_pri_con_fs
+t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
+t2_inf_sha_att_fs ~~ 0*t2_inf_sha_att_fs
+t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
+t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
+t2_inf_sha_beh_fs ~~ 0*t2_inf_sha_beh_fs
+t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs
+
+# control variables
+t1_pri_con_fs ~ age + edu_num + male
+t2_pri_con_fs ~ age + edu_num + male
+t3_pri_con_fs ~ age + edu_num + male
+t1_inf_sha_beh_fs ~ age + edu_num + male
+t2_inf_sha_beh_fs ~ age + edu_num + male
+t3_inf_sha_beh_fs ~ age + edu_num + male
+t1_inf_sha_att_fs ~ age + edu_num + male
+t2_inf_sha_att_fs ~ age + edu_num + male
+t3_inf_sha_att_fs ~ age + edu_num + male
+'
+fit_free <- sem(model_free, data = d_wide, orthogonal = TRUE, missing = "ML")
+summary(fit_free, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
+effect_std_ci_free <- standardizedsolution(fit) %>% 
+  filter(lhs == "pri_con_b", rhs == "inf_sha_beh_b")
+
+# model comparison
+(model_comp <- anova(fit_riclpm, fit_free))
+```
+Shows that model with freely estimated parameters does not show significantly improved fit.
+
+#### Model 6
 
@@
 ```
+
+```{r include=F}
+save.image("data/workspace.RData")
+```

### 2020-05-07 manuscript.RmD
- Implemented feedback from reviews - Toned down implications - First language edits

@@
 To the best of our knowledge, all empirical studies conducted so far have investigated the privacy paradox from a between-person (i.e., interpersonal) perspective.
-By employing empirical tests of between-person variance (e.g., cross-sectional questionnaires analyzed with multiple regression or Pearson correlations), studies have analyzed whether people who are more concerned than _others_ also share less personal information than _others_.
-Granted, such a between-person perspective is interesting and represents a viable first step in analyzing the relation between these variables.
-At the same time, it is important to emphasize that the privacy paradox actually implies a within-person (i.e., intrapersonal) perspective:
+By employing empirical tests relations between people (e.g., cross-sectional questionnaires analyzed with multiple regression or Pearson correlations), studies have analyzed whether people who are more concerned than _others_ also share less personal information than _others_.
+Although such a between-person perspective is interesting and represents a viable first step, it cannot make informed claims regarding causality.
+The privacy paradox, however, actually implies a within-person (i.e., intrapersonal) causal perspective:
 Does a person, if _he or she_ becomes more concerned about online privacy, then also share less personal information?
-This mismatch is problematic because although between-person variance is, except for some special cases, a _necessary_ condition for within-person effects, it is by no means a _sufficient_ condition.
-For example, it could be that the between-person relation is determined by another stable third variable. 
-Hence, as the next step in investigating the privacy paradox and to better understand the intrapersonal relation between privacy concerns and information sharing, we need to conduct studies with within-person designs.
+This mismatch is problematic because although between-person relations are, except for some special cases, a _necessary_ condition for causal within-person effects, they are by no means a _sufficient_ one.
+For example, it could be that the between-person relation is determined by another third variable. 
+Hence, as the next step in investigating the privacy paradox and to better understand the intrapersonal causal relation between privacy concerns and information sharing, it is necessary to conduct studies with within-person designs.
 
-As a result, with this study we aim to answer four major questions. 
+With this study we therefore aim to answer four major questions. 
 First, on a between-person level, how are concerns about online privacy related to the online sharing of personal information? 
@@
 "Experiments reveal that very few individuals actually take any action to protect their personal information, even when doing so involves limited costs" (p.1). 
-Three years later, @barnesPrivacyParadoxSocial2006 discussed the behavior of young people using SNSs and coined the expression of the _privacy paradox_. 
-Barnes listed six notions that she considered to be particularly paradoxical: (a) illusion of privacy, (b) high quantity of information sharing, (c) attitude behavior discrepancy, (d) lack of privacy concerns, (e) lack of privacy literacy, and (f) fabrication of false information.
+Three years later, @barnesPrivacyParadoxSocial2006 discussed the behavior of young people using SNSs, popularizing the term _privacy paradox_. 
+Barnes listed six aspects of online behavior that she considered to be particularly paradoxical: (a) illusion of privacy, (b) high quantity of information sharing, (c) attitude behavior discrepancy, (d) lack of privacy concerns, (e) lack of privacy literacy, and (f) fabrication of false information.
+@norbergPrivacyParadoxPersonal2007 was one of the first to explicitly analyze the privacy paradox empirically.
+The study finds a mismatch between concerns and behavior, which is aligned with several other experimental studies conducted at the time [beresfordUnwillingnessPayPrivacy2012; hannOvercomingOnlineInformation2007; hubermanValuatingPrivacy2005].
 
-Subsequent research analyzed the privacy paradox more explicitly, focusing on Barnes's third tenet, the attitude-behavior discrepancy. 
-On the one hand, some studies reported that privacy concerns were not significantly related to the disclosure of personal information [e.g., @grossInformationRevelationPrivacy2005; @taddickenPrivacyParadoxSocial2014; @tufekciCanYouSee2008], lending credence to the privacy paradox.
-On the other hand, a different set of studies showed relations that were statistically significant [e.g., @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013; @walraveConnectingProtectingComparing2012], thereby refuting the privacy paradox.
+While there are various understandings and operationalizations of the privacy paradox [@kokolakisPrivacyAttitudesPrivacy2017], subsequent research on the privacy paradox arguably focused on Barnes's third tenet, the attitude-behavior discrepancy.
+Whereas some studies reported that privacy concerns were not significantly related to the disclosure of personal information [e.g., @grossInformationRevelationPrivacy2005; @taddickenPrivacyParadoxSocial2014; @tufekciCanYouSee2008], which lends credence to the privacy paradox,
+a different set of studies showed relations that were statistically significant [e.g., @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013; @walraveConnectingProtectingComparing2012], which refutes the privacy paradox.
 
-It is interesting that in a parallel line of research other studies have also analyzed the relation between privacy concerns and information sharing; 
+Notably, in a parallel line of research other studies have also analyzed the relation between privacy concerns and information sharing; 
 however, the term privacy paradox has often not been mentioned explicitly. 
@@
 @baruhOnlinePrivacyConcerns2017 published the first empirical meta-analysis on the relations between privacy concerns and various forms of social media use (e.g., information sharing or SNS usage). 
-On the basis of 37 studies, @baruhOnlinePrivacyConcerns2017 found a small and significant statistical relation between concerns about online privacy and online information sharing (_r_ = -.13). 
-For other systematic literature reviews, see @barthPrivacyParadoxInvestigating2017, @gerberExplainingPrivacyParadox2018, and @kokolakisPrivacyAttitudesPrivacy2017.
-In conclusion, the current literature suggests that a significant relation between concerns about online privacy and the online sharing of personal information exists and that it is small---which speaks against the privacy paradox.
+On the basis of 37 studies, @baruhOnlinePrivacyConcerns2017 found a small and significant statistical relation between concerns about online privacy and online information sharing (_r_ = -.13, 95% CI [-.07, -.18]).
+Another more recent meta analysis by @yuMetaanalysisExplorePrivacy2020 also finds a significant bivariate relation between privacy concerns and information sharing, although smaller (_r_ = -.06, 95% CI [-.01, -.12]]).
+There also exist several systematic literature reviews on the privacy paradox [@barthPrivacyParadoxInvestigating2017; @gerberExplainingPrivacyParadox2018; @kokolakisPrivacyAttitudesPrivacy2017]
+@kokolakisPrivacyAttitudesPrivacy2017 conclude that "the dichotomy between privacy attitude and behaviour should not be considered a paradox anymore." (p. 130)
+However, the authors also note that the privacy paradox is a "complex phenomenon that has not been fully explained yet".
+@barthPrivacyParadoxInvestigating2017 are more skeptical, and argue that "attempts to theoretically explain and practically solve the problem of the privacy paradox are still scarce and we feel the subject deserves far more research attention" (p.
+1052).
+
+In conclusion, large parts of the current literature suggests that a significant relation between concerns about online privacy and the online sharing of personal information exists and that it is small---which speaks against the privacy paradox.
 
@@
 whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people [@masurSituationalPrivacySelfdisclosure2018].
-When it comes to concerns, it is interesting that they do not seem to be established as a stand-alone theoretical concept in psychology: 
-For example, the Oxford Dictionary of Psychology does not feature a designated entry [@colmanDictionaryPsychology2015].
-In general, however, a concern is defined as a "marked interest or regard usually arising through a personal tie or relationship" that also reflects an "uneasy state of blended interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
-A concern therefore partially represents both a latent _motivation_ (or increased attention) to invest oneself in a specific entity and a negatively valenced _emotion_ (or affective condition).
-As such, a concern is not predominantly the result of a deliberate explicit cognition; instead, it primarily reflects an automatic implicit perception.
+When it comes to concerns specifically, interestingly they do not seem to be established as a stand-alone theoretical concept in psychology [@colmanDictionaryPsychology2015].
+Lexically, concerns are defined as a "marked interest or regard usually arising through a personal tie or relationship" that also reflect an "uneasy state of blended interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
+Concerns therefore represent both a latent _motivation_ (or increased attention) and a negatively valenced _emotion_ (or affective condition).
+As such, concerns are not the result of a deliberate explicit cognition.
+Instead, they stem from an automatic implicit perception.
 Taken together, concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened.
 As a theoretical construct, privacy concerns can hence be categorized as an affective motivational disposition.
-As such, there are many similarities with other concepts, which includes emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (approval, dissent), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).
+As such, there are many similarities with other concepts, which includes emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (risk perception, approval), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).
 
@@
 Information sharing can be differentiated from communication and self-disclosure:
-Whereas communication is broad because it comprises all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011], self-disclosure is narrow because it focuses on deliberate revelations about the true self to others [e.g., @jourardTransparentSelf1964]
+Communication is broad, because it comprises all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011].
+Self-disclosure is narrow, because it focuses on deliberate revelations about the true self to others [e.g., @jourardTransparentSelf1964].
+Information sharing is even more specific, because it addresses only person-related information but ignores other types of self-disclosure such as personal fears, values, or plans.
 
@@
 
-It is somewhat surprising that the literature seems to lack explicit theoretical treatises on why and how human behavior should be affected by concerns specifically.
-More fortunately, however, there are several theoretical insights regarding how the affective motivational concepts presented above can pertain to behavior.
-The results are unanimous: They can all affect behavior profoundly.
-For example, let us consider the concept that is perhaps closest to concerns, emotions.
-By causing fight or flight reactions, emotions are potentially the most primordial trigger of behavior, 
-they are considered an adaptive mechanism that fosters the evolution of a species [@dolanEmotionCognitionBehavior2002].
-With their direct link to the amygdala, emotions can already trigger reactions subcortically [i.e., without activation of the more recently evolved cortical structures; @dolanEmotionCognitionBehavior2002].
-It hence seems plausible to suggest that privacy concerns, with their emotional dependency, also share this function at least partially.
-Moreover, changes in concerns might be correlated with changes in behavior because people usually aim to reduce discrepancies between cognitions and behavior [@festingerTheoryCognitiveDissonance1957].
-There are also several empirical accounts of how concerns affect behavior:
-People who are more concerned about the environment show more environment-related behaviors [@bambergHowDoesEnvironmental2003], 
-people who are more concerned about their appearance consume fewer calories [@hayesConcernAppearanceHealth1987], 
-and people who are more concerned about their bodies engage in more physical exercise [@reelRelationsBodyConcerns2007].
-Hence, it seems reasonable to expect that also concerns about online privacy should be reflected in the online sharing of personal information.
+Currently, there seems to be a lack of studies that explicitly analyze how behavior is affected by _concerns_.
+Fortunately, however, we know much about the behavioral effects of related concepts such as attitudes or fears, which all can affect behavior profoundly [@fishbeinPredictingChangingBehavior2010; @rogersCognitivePhysiologicalProcesses1983].
+Emotions, perhaps the concept most closely related to concerns, have a particularly strong effect on behavior. 
+By causing fight, flight, or freeze reactions, they are a primordial trigger of behavior and an adaptive mechanism fostering the evolution of a species [@dolanEmotionCognitionBehavior2002].
+With their direct link to the amygdala, emotions can trigger reactions already subcortically [i.e., without activation of the more recently evolved cortical structures; @dolanEmotionCognitionBehavior2002].
+
+Also empirically, concerns have been shown to affect behavior: 
+People more concerned about the environment show more environment-related behaviors [@bambergHowDoesEnvironmental2003]; people more concerned about their appearance consume fewer calories [@hayesConcernAppearanceHealth1987];
+People more concerned about their bodies engage in more physical exercise [@reelRelationsBodyConcerns2007].
+Taken together, it is reasonable to expect that also concerns about online privacy should reflect in the online sharing of personal information.
 
 At the same time, there are some factors that are likely to diminish the relation.
-Most prominently, there is the so-called _attitude behavior gap_, which pertains to the idea that people often act against their own attitudes [e.g., @fishbeinPredictingChangingBehavior2010]. 
-For example, despite endorsing the importance of physical health, a large part of the population still does not exercise regularly.
-Transferred to the privacy paradox, it should not be surprising to encounter this general discrepancy also in the specific context of privacy concerns and information sharing. 
-The explanation is simple: Other factors such as subjective norms and perceived behavioral control can also determine behavior [@ajzenIntentionsActionsTheory1985], and this automatically limits the predictive capacity of attitudes or concerns.
-Specifically, two of the most influential factors that affect online information sharing are (a) the strong subjective norms to participate online [@heirmanPredictingAdolescentsDisclosure2013] and (b) the manifold benefits that accrue from participation [@krasnovaOnlineSocialNetworks2010].
-In other words, instead of considering privacy concerns it is often more important to attain social support, special offers, or tailored services.
+Most prominently, there is the so-called _attitude behavior gap_ [@fishbeinPredictingChangingBehavior2010], which states that people sometimes act against their own attitudes. 
+Not everyone concerned about his or her physical health exercises regularly.
+The explanation is simple.
+Other factors such as subjective norms and perceived behavioral control also determine behavior [@ajzenIntentionsActionsTheory1985], which automatically reduces the impact of attitudes or concerns. 
+Specifically, two of the most influential factors that affect online information sharing are (a) strong subjective norms to participate online [@heirmanPredictingAdolescentsDisclosure2013] and (b) the manifold benefits that accrue from participation [@krasnovaOnlineSocialNetworks2010].
+In other words, users often prioritize social support, special offers, or improved services.
 @trepteRiskyBehaviorsHow2014 listed several factors that can additionally attenuate the relation:
-concerns might be missing any actual strength,
-a lack of negative personal experiences, 
+lack of strength of concerns,
+absence of negative personal experiences, 
 and situational constraints due to social desirability.
+In conclusion, also in the context of the privacy paradox we should not expect to find a perfect relation between attitudes and behaviors, but rather a small to moderate relation.
 
-Finally, there are also some methodological reasons that can explain why some studies did not find statistically significant relations, even when they exist empirically.
-In general, researchers are always confronted with the _Duhem-Quine problem_, which holds that it is impossible to test theories in isolation, because empirical tests always rely on auxiliary assumptions [e.g., @dienesUnderstandingPsychologyScience2008].
+Finally, there are also some methodological reasons that explain why some studies did not detect statistically significant relations.
+In general, researchers are confronted with the _Duhem-Quine problem_, which holds that it is impossible to test theories in isolation, because empirical tests always rely on auxiliary assumptions [@dienesUnderstandingPsychologyScience2008].
 In other words, if a psychological experiment fails, we do not know whether the theory is wrong or the questionnaire subpar. 
@@
 The reality, however, looks different: 
-In their meta-analysis, Baruh et al. reported a median sample size of _N_ = 300, which can explain why several studies did not find significant effects.
+In their meta-analysis, @baruhOnlinePrivacyConcerns2017 reported a median sample size of _N_ = 300, which can explain why several studies did not find significant effects.
 
@@
 
-To conclude, in line with prior research [@baruhOnlinePrivacyConcerns2017] and the within-person rationales that we have presented above, we expect to find a small significant relation between privacy concerns and information sharing, both on the between-person level and the within-person level.
+In conclusion, in line with prior research [@baruhOnlinePrivacyConcerns2017] and the within-person rationales that we have presented above, we expect to find a small significant relation between privacy concerns and information sharing, both on the between-person level and the within-person level.
 
@@
 
-Although we hypothesize that changes in people's concerns about online privacy will be reflected by their behavior directly, we are not sure about whether there will also be long-term effects.
+Although short-term effects are likely, it is unclear whether there will be any long-term effects.
 First, when analyzing potential long-term effects, it is important to choose an interval that is both plausible and relevant.
-For example, it makes a difference whether the effects of alcohol consumption on driving performance are tested 1 min, 1 h, or 1 day after consumption. 
+For example, it makes a difference whether the effects of alcohol consumption on driving performance are tested 1 minute, 1 hour, or 1 day after consumption. 
 One factor that determines an interval's optimal length is the variable's stability [@dormannOptimalTimeLags2015].
-Privacy concerns and privacy attitudes are predominantly trait-like constructs with high stabilities, therefore necessitating longer intervals.
+Privacy concerns and privacy attitudes are predominantly trait-like constructs with high stabilities, which is why they necessitate longer intervals.
 Other studies with comparable research questions have used an interval of 6 months [e.g., @valkenburgEffectsInstantMessaging2009], which we consider to be plausible also in this case.
@@
 In contrast to privacy concerns, privacy attitudes capture a more explicit, fluctuating cognitive appraisal. 
-Although both variables are related to information disclosure, attitudes are likely to be the better predictor. 
+Although both variables are related to information disclosure, attitudes are likely the better predictor. 
 This reasoning follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always, at least in part, influenced by convictions, attitudes, and cost-benefit analyses.
-Likewise, evolutionary psychology also suggests that although emotions guide behavior in the long run, it is more adaptive if behavior instead reflects a cognitive appraisal; 
-a tenet arguably reflected best by the phylogenetic development of the neocortex or, if you want, the general dominion of the human race.
-These rationales have also found some empirical support. 
-For example, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure was more moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].
+<!-- Likewise, also evolutionary psychology suggests that although emotions guide behavior in the long run, it is more adaptive if behavior instead reflects a cognitive appraisal;  -->
+<!-- a tenet arguably reflected best by the phylogenetic development of the neocortex or, if you want, the general dominion of the human race. -->
+Also empirically, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure was only moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].
 
@@
 
-The data were analyzed by means of a random-intercept cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015], a method that already has been used for similar research questions [@dietvorstAdolescentPerceptionsParental2018].
+```{r RICLPM, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM).", fig.align="center"}
+knitr::include_graphics("figures/model_7.png")
+```
+
+The data were analyzed by means of a random-intercept cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015].
+For a visualization, see Figure \@ref(fig:RICLPM).
+RI-ClPMs have already been used for similar research questions [@dietvorstAdolescentPerceptionsParental2018].
 Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs allow to separate between-person variance from within-person variance. 
@@
 Given that we had three points of measurement, this resulted in two estimates for each research question.
-As we did not expect longitudinal effects to differ across time, they were constrained to be equal across all waves, which produces one single general measure of each effect instead of two time-specific ones.
+As we did not assume longitudinal effects to differ across time, they were constrained to be equal across all waves, which produces one single general measure of each effect instead of two time-specific ones.
+(We later tested this assumption also empirically.
+Indeed, the model with constrained effects did not show significantly reduced model fit, $\chi$^{2}(`r model_comp[2, 6]`) = `r model_comp[2, 7] %>% my_round("p")`, _p_ = `r model_comp[2, 5] %>% my_round("est")`, which supports the assumption that effects did not change significantly across time.)
 Fit was assessed according to the common criteria as described by @klinePrinciplesPracticeStructural2016. 
@@
 Each item was answered on a 5-point scale ranging from 1 (*never*) to 5 (*daily*). 
-Factor analyses suggested a second-order factor structure with five first-order factors. 
+Factor analyses suggested a second-order factor structure with five first-order factors of two items each.
 The first first-order factor subsumed financial and medical information, the second first and last name, the third place of residence and street (including house number), the fourth email address and phone number, and the fifth information about education and current job.
@@
 
-Current research on the privacy paradox suggests a significant and small relation between concerns about online privacy and the online sharing of personal information [e.g., @baruhOnlinePrivacyConcerns2017].
+Most research on the privacy paradox suggests that there is a significant and small relation between concerns and the online sharing of personal information [e.g., @baruhOnlinePrivacyConcerns2017]. 
 However, whereas the theoretical premise of the privacy paradox actually addresses a within-person effect,
-empirical studies have analyzed between-person relations.
-On the basis of a representative sample of the German population, from which three waves of data separated by 6 months were collected, we have hence analyzed the privacy paradox by differentiating general between-person relations, short-term within-person relations, as well as long-term within-person effects.
+most empirical studies have analyzed between-person relations.
+On the basis of a representative sample of the German population, from which three waves of data separated by 6 months were collected, we hence analyzed the privacy paradox by differentiating general between-person relations, short-term within-person relations, as well as long-term within-person effects.
+Together, this approach allows for informed inferences about the variables' causal relationship.
 
@@
 In addition, people who were more concerned about their privacy than others also held substantially more negative attitudes toward disclosing personal information online.
-Notably, we found a very strong between-person correlation between attitudes toward information sharing and actual information sharing, implying that typical online disclosure can be precisely predicted by a person's attitude.
+Notably, we found a very strong between-person correlation between attitudes toward information sharing and actual information sharing, which shows that typical online disclosure can be predicted precisely by a person's attitude.
 Taken together, the cross-sectional results are in line with the extant literature:
-Specifically, the between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fell within the 95% confidence interval of the effect reported by Baruh et al.
-[-@baruhOnlinePrivacyConcerns2017] (i.e., _r_ = -.13, 95% CI [-.07, -.18]).
-Note that the between-person correlations reported here represent averaged measurements across three waves, thereby rendering the findings comparatively robust. 
-In conclusion, this study replicates the finding that the privacy paradox does not seem to exist on a between-person level:
+The between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fell within the 95% confidence interval of the effect reported by @baruhOnlinePrivacyConcerns2017 (i.e., _r_ = -.13, 95% CI [-.07, -.18]).
+Note that the between-person correlations reported here represent averaged measurements across three waves, which should make the findings more robust than typical one-shot measures.
+
+In conclusion, this study suggests that the privacy paradox does not exist on a between-person level.
 The differences between people with regard to their online information sharing behavior can be explained by differences in privacy concerns to a small extent, and by differences in privacy attitudes to a large extent.
+The more specific we become, the better we can explain online behavior. 
+Whereas privacy concerns are related only weakly to online information sharing [e.g., @baruhOnlinePrivacyConcerns2017], more specific risks perceptions are more closely related to behavior [e.g., @bolUnderstandingEffectsPersonalization2018; @yuMetaanalysisExplorePrivacy2020], while behavioral attitudes are the best predictors [@dienlinPrivacyParadoxRelic2015].
 
-The within-person results showed that when a person's privacy concerns increased, the same person also shared slightly less information online than he or she usually did.
-Moreover, we found that people who developed more positive attitudes toward the online sharing of personal information than usual also shared substantially more personal information online.
-In conclusion, the results suggest that changes in concerns and attitudes are both partially related to changes in behavior, implying that also on a within-person level the privacy paradox does not seem to exist.
+The within-person results showed that when a person's privacy concerns increased, the same person also shared slightly less information online than usual.
+Moreover, people who developed more positive attitudes toward the online sharing of personal information than usual, also shared substantially more personal information online.
+Together, changes in concerns and attitudes are both related to changes in behavior, which suggests that the privacy paradox does not exist also on the within-person level.
 
-Turning to the potential long-term effects of privacy concerns, the effects that we found were both theoretically negligible and statistically nonsignificant.
-Specifically, changes in both privacy concerns and attitudes toward the online sharing of personal information were not related to any meaningful changes in the online sharing of personal information 6 months later.
+We did not find any long-term effects, however.
+Specifically, changes in both privacy concerns and attitudes toward the online sharing of personal information were not related to any meaningful changes in the online sharing of personal information 6 months later, and vice versa.
 As an explanation, it might be the case that changes in privacy concern affect information sharing more immediately. 
-To test this assumption, we would need study designs with shorter intervals [cf., @keijsersParentalMonitoringAdolescent2016].
+To test this assumption, we would need study designs with shorter intervals [@keijsersParentalMonitoringAdolescent2016].
 Moreover, given that the directions of most longitudinal relations were in line with the between-person and within-person relations, 
-it might be the case that longitudinal effects do indeed take place, 
+longitudinal effects might indeed take place, 
 but only that they are very small.
@@
 
-As a major point of criticism, one can argue that some of the effect sizes reported in this study are only small, too small to effectively refute the privacy paradox.
+Some of the effect sizes reported in this study are potentially not large enough to refute the privacy paradox. 
 On the one hand, they could simply be a manifestation of the so-called "crud factor" [@meehlWhySummariesResearch1990, p.
@@
 On the other hand, other factors such as expected benefits might play a more important role [@dienlinExtendedPrivacyCalculus2016].
-In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, one should indeed not overestimate the importance of privacy concerns; the impact on the online sharing of personal information could be larger, and other variables surely play a role as well.
+In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, one should indeed not overestimate the importance of privacy concerns.
+The effect could be larger, and other variables surely play a role as well.
 
-The study relied on estimations of information sharing that were based on self-reports. 
-As has been shown before, people are not particularly good at estimating the frequency of behaviors that are part of their daily routines [@scharkowAccuracySelfreportedInternet2016].
-Whenever possible, future studies should aim to combine self-reports of cognitions with objective observations of behavior.
+In this study we measured information sharing using self-reports. 
+However, self-reports of frequent and routine behaviors are often imprecise and unreliable [@scharkowAccuracySelfreportedInternet2016]. 
+This represents a profound limitation of our study. 
+Whenever possible, future studies should aim to collect objective observations of behavior.
 
 Finally, please note that the hypotheses presented in this study were not formally preregistered.
-At the time when the study was conceived in 2014, we unfortunately were not yet aware of the importance of this practice.
+At the time when the study was conceived in 2014, we were not yet aware of the importance of preregistration.
 
@@
 
-Although this is arguably the first study to demonstrate a within-person relation between concerns about online privacy and the online sharing of personal information, what is still missing is evidence of within-person longitudinal effects.
-The fact that we found significant within-person correlations at T1 but not across the 6-month intervals suggests that longitudinal effects do take place, but that a different time interval might be needed to uncover them.
-For theoretical reasons (e.g., due to availability heuristics), it would be plausible to use intervals that are shorter;
-for statistical reasons (e.g., because of the high stability of privacy concerns), however, it would even make sense to probe intervals that are longer [@dormannOptimalTimeLags2015].
+Evidence of within-person longitudinal effects is still missing. 
+Although we found significant within-person correlations at T1, they were absent across the 6-month intervals.
+Together, this suggests that longitudinal effects exist, but that they take place on a different time interval.
+Future research might hence probe different intervals.
+For theoretical reasons (e.g., due to availability heuristics), it is plausible to use intervals that are shorter;
+for statistical reasons (e.g., because of the high stability of privacy concerns), however, it also makes sense to test longer intervals  [@dormannOptimalTimeLags2015].
 
-Linking general personality traits with typical behavior, recent studies have analyzed the privacy paradox by taking an aggregate perspective.
-However, it seems important to analyze privacy behaviors from a situational perspective as well, one that accounts for temporal needs, interpersonal perceptions, contextual cues, or characteristics of communication channels [@masurSituationalPrivacySelfdisclosure2018].
-For example, it might be the case that whereas general levels of information sharing are best explained by using privacy _concerns_, situational information sharing might be best explained using privacy _heuristics_, which are less energy consuming and more situational [cf., @sundarUnlockingPrivacyParadox2013].
+Although we argue that in most circumstances privacy concerns and behavior should correlate modestly, the exact extent to which they relate depends on a plethora of boundary conditions.
+Future research should hence explicitly focus on analyzing different contexts and situations. 
+Building on @kokolakisPrivacyAttitudesPrivacy2017, we suggest the following boundary conditions:
 
-As a final note, the privacy paradox argues that privacy concerns do not reflect whatsoever on the sharing of personal information online, 
-which we view as a strong claim.
-However, when a single study does not yield a significant result it does not necessarily imply a theoretical problem; 
-instead, it could also be a statistical miss.
-Because when analyzing the privacy paradox we are likely dealing with small effects [@baruhOnlinePrivacyConcerns2017],
-and to be able to reliably detect small effect we need large samples. 
-In conclusion, we encourage researchers to use statistical designs that allow for sufficient statistical power.
+ - Context (professional, social, commercial, health-related, etc.);
+ - Situation (new, habitualized, unexpected, etc.);
+ - Mood (positive vs. negative, etc.);
+ - Extent of control (high vs. low);
+ - Type of information processing applied (implicit, heuristic, or peripheral vs. explicit, analytic, or central);
+ - Existence of bias (e.g., overconfidence, optimism, comparative optimism, hyperbolic discounting);
+ - Type of information (sensitive vs. superficial, biographic, person-related, etc.);
+ - Benefit immediacy and risk diffusion (high vs. low).
+
+Specifically, we encourage analyzing privacy behaviors also from a situational perspective, accounting for temporal needs, interpersonal perceptions, contextual cues, or characteristics of communication channels [@masurSituationalPrivacySelfdisclosure2018].
+For example, whereas general levels of information sharing are likely best explained by using privacy _concerns_, situational information sharing might be best explained using privacy _heuristics_ [@sundarUnlockingPrivacyParadox2013].
+
+Next to these theory-related boundary conditions there are methodological ones:
+
+ - Analysis design (theoretical, experimental, questionnaire-based, interview-based, anecdotal);
+ - Quality of measurement (high vs. low; low quality less likely to detect statistical significance);
+ - Sample size (small vs. large; small samples less likely to detect statistical significance);
+ - Statistical analysis (SEM vs. Regression; analyses without error control less likely to find statistical significance);
+ - Operationalization (concerns vs. risk perceptions vs. behavioral attitudes; the more specific, the stronger the relation).
+
+When analyzing the privacy paradox we are likely dealing with small effects [@baruhOnlinePrivacyConcerns2017].
+Hence, to detect these small effects reliably we need large samples. 
+This is often not the case [@baruhOnlinePrivacyConcerns2017].
+In conclusion, we emphasize to use statistical designs that allow for sufficient statistical power.
 
@@
 
-Taken together, one might ask: What's the big deal? 
-Researchers have now come closer to solving the privacy paradox, which is a problem that by producing studies with non-significant results they have created themselves.
-Admittedly, there is some truth to this statement. 
-At the same time, it is not only researchers who have thought that the online sharing of personal information is paradoxical---the public media have also often suggested that people tend to use the Internet in a somewhat nonsensical way [e.g., @naughtonPrivacyParadoxWhy2019].
-Hence, given the common interest and involvement in the privacy paradox, providing the public with a scientific answer seems relevant.
+Being able to show that online behaviors are not paradoxical can be socially relevant.
+Consider the similar case of fear appeals and protective behavior, where there is also only a small correlation [@witteMetaanalysisFearAppeals2000].
+However, fear appeals are used in public campaigns nonetheless, oftentimes to much success [@wakefieldUseMassMedia2010].
+Likewise, proclaiming that the online sharing of personal information is not paradoxical and that concerns about online privacy matter, could lead to more cautious and reflective behavior.
+It is probably no coincidence that the General Data Protection Regulation, which strengthens the privacy rights of consumers, was passed in Europe, where privacy concerns are particularly pronounced [@europeancommissionDataProtectionSpecial2015].
 
-Second, being able to show that online behaviors are not paradoxical has another benefit: 
-It suggests that online and offline behaviors are not ontologically different. 
-In offline contexts, we similarly find that concerns are not always closely aligned with behaviors.
-For example, although most people are concerned about their health, a considerable number of people smoke cigarettes nonetheless.
-However, despite this discrepancy public agencies are aware that they still need to foster concern about health.
-For example, in May 2016, the European Union mandated that cigarette packages must display graphic warning labels;
-while stable in the years before, sales of cigarettes in Germany in 2016 dropped by 6.3 billion units, equaling 7.7% [@statistischesbundesamt201675Billion2017]. 
-Although this result is only a correlation, it suggests that addressing concerns can have societal benefits.
-Therefore, proclaiming that the online sharing of personal information is not paradoxical and that concerns about online privacy indeed matter might leverage both people's responsibility and their agency [cf., @adjeridPrivacyParadoxObjective2018].
-
-In sum, this study showed that when people were more concerned about their privacy, they also shared a little less personal information about themselves online, 
-and if respondents considered sharing personal information not to be a sensible idea, they disclosed even less.
-Both this study and the majority of the extant literature do not support a 'privacy paradox'. 
-Instead, if anything, they suggest a 'privacy orthodox'.
+In sum, this study showed that when people were more concerned about their privacy, they also shared a little less personal information about themselves online.
+If respondents considered sharing personal information to be insensible, they disclosed substantially less information.
+Together, these findings do not support the existence of a privacy paradox, at least in this particular context and operationalization.
+No evidence of long-term effects was found, however.
+Further research is needed to understand the potential causal interplay of concerns, attitudes, and behavior.
 

### 2020-05-07 manuscript.RmD
- language updates - shortened manuscript

@@
   All authors contributed extensively to the work presented in this paper.
-TD, PM, & ST designed the study; PM supervised the data collection; PM administered the data importation; TD & PM wrote the code, ran the models, and analyzed the output data; TD wrote major parts of manuscript, and PM & ST contributed individual sections and comments; ST supervised the project and wrote the grant application (in 2012).
+TD, PM, & ST designed the study; PM supervised the data collection; PM administered the data importation; TD & PM wrote the code, ran the models, and analyzed the output data; TD wrote most parts of manuscript, and PM & ST contributed individual sections and comments; ST supervised the project and wrote the grant application (in 2012).
   The authors declare no competing interests.
@@
   The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
-  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
+  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective.
+We differentiate between-person relations from within-person effects.
   Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level).
-  Next, people who were more concerned than usual also shared slightly less information than usual (within-person level). 
-  At the same time, we found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
-  Together, the results provide further evidence against the privacy paradox.
+  People who were more concerned than usual also shared slightly less information than usual (within-person level). 
+  We found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
+  The results provide further evidence against the privacy paradox, but more research is needed to better understand the variables' potential causal relation.
 keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
@@
                       footnote = FALSE, 
-                      pkgs = c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
-                               "MissMech", "MVN", "papaja", "psych", "pwr",  
-                               "semTools", "sjstats", "tidyverse", "td"), 
+                      pkgs = c("GGally", "ggplot2", "lavaan", 
+                               "MissMech", "MVN", "psych", "pwr",  
+                               "semTools", "sjstats"), 
                       withhold = FALSE)
@@
 
-The privacy paradox states that the information disclosure practices of Internet users are problematic: 
-Although many people are concerned about their online privacy, they still tend to share plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
-The privacy paradox and its underlying theoretical conundrum is hence of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
+The privacy paradox states that the information disclosure of Internet users is problematic: 
+Although many people are concerned about their online privacy, they still share plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
+The privacy paradox and its underlying theoretical conundrum is hence of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia entries  [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
 If the privacy paradox really exists, it should inspire worry: 
-It would suggest that online behavior is irrational and that people are revealing too much of their personal lives to unknown third parties, which can foster potentially unintended consequences such as commodification [@sevignaniPrivacyCapitalismAge2016], inappropriate recontextualization [@boydTakenOutContext2008], or increased predictability of future behavior [@bagrowInformationFlowReveals2019].
-In conclusion, understanding why people disclose information online and whether this is paradoxical or not represents an important challenge for scholars in the social sciences.
+It would suggest that online behavior is irrational and that people are revealing too much of their personal lives to unknown third parties, which can cause various problems [e.g., @sevignaniPrivacyCapitalismAge2016].
+Understanding why people disclose information online and whether or not this is paradoxical therefore represents an important challenge.
 
 However, current research on the privacy paradox has one major limitation: 
-To the best of our knowledge, all empirical studies conducted so far have investigated the privacy paradox from a between-person (i.e., interpersonal) perspective.
-By employing empirical tests relations between people (e.g., cross-sectional questionnaires analyzed with multiple regression or Pearson correlations), studies have analyzed whether people who are more concerned than _others_ also share less personal information than _others_.
+To the best of our knowledge, most empirical studies conducted so far have investigated the privacy paradox from a between-person (i.e., interpersonal) perspective.
+By employing empirical tests of relations between people (e.g., cross-sectional questionnaires analyzed with multiple regression or Pearson correlations), studies have analyzed whether people who are more concerned than _others_ also share less personal information than _others_.
 Although such a between-person perspective is interesting and represents a viable first step, it cannot make informed claims regarding causality.
-The privacy paradox, however, actually implies a within-person (i.e., intrapersonal) causal perspective:
+The privacy paradox, however, implies a causal perspective:
 Does a person, if _he or she_ becomes more concerned about online privacy, then also share less personal information?
 This mismatch is problematic because although between-person relations are, except for some special cases, a _necessary_ condition for causal within-person effects, they are by no means a _sufficient_ one.
-For example, it could be that the between-person relation is determined by another third variable. 
-Hence, as the next step in investigating the privacy paradox and to better understand the intrapersonal causal relation between privacy concerns and information sharing, it is necessary to conduct studies with within-person designs.
+For example, it could be that the between-person relation is determined other third variables. 
+Hence, as the next step in investigating the privacy paradox and to better understand the causal relation between privacy concerns and information sharing, it is necessary to conduct studies with within-person designs.
 
-With this study we therefore aim to answer four major questions. 
+With this study we aim to answer four major questions. 
 First, on a between-person level, how are concerns about online privacy related to the online sharing of personal information? 
@@
 "Experiments reveal that very few individuals actually take any action to protect their personal information, even when doing so involves limited costs" (p.1). 
-Three years later, @barnesPrivacyParadoxSocial2006 discussed the behavior of young people using SNSs, popularizing the term _privacy paradox_. 
+Three years later, @barnesPrivacyParadoxSocial2006 discussed the behavior of young people on SNSs, popularizing the term _privacy paradox_. 
 Barnes listed six aspects of online behavior that she considered to be particularly paradoxical: (a) illusion of privacy, (b) high quantity of information sharing, (c) attitude behavior discrepancy, (d) lack of privacy concerns, (e) lack of privacy literacy, and (f) fabrication of false information.
-@norbergPrivacyParadoxPersonal2007 was one of the first to explicitly analyze the privacy paradox empirically.
-The study finds a mismatch between concerns and behavior, which is aligned with several other experimental studies conducted at the time [beresfordUnwillingnessPayPrivacy2012; hannOvercomingOnlineInformation2007; hubermanValuatingPrivacy2005].
+@norbergPrivacyParadoxPersonal2007 were one of the first to empirically analyze the privacy paradox explicitly.
+The study found a mismatch between concerns and behavior, which is aligned with several other experimental studies conducted at the time [@beresfordUnwillingnessPayPrivacy2012; @hannOvercomingOnlineInformation2007; @hubermanValuatingPrivacy2005].
 
-While there are various understandings and operationalizations of the privacy paradox [@kokolakisPrivacyAttitudesPrivacy2017], subsequent research on the privacy paradox arguably focused on Barnes's third tenet, the attitude-behavior discrepancy.
+While there are various understandings and operationalizations of the privacy paradox [@kokolakisPrivacyAttitudesPrivacy2017], subsequent research focused on Barnes's third tenet, the attitude-behavior discrepancy.
 Whereas some studies reported that privacy concerns were not significantly related to the disclosure of personal information [e.g., @grossInformationRevelationPrivacy2005; @taddickenPrivacyParadoxSocial2014; @tufekciCanYouSee2008], which lends credence to the privacy paradox,
-a different set of studies showed relations that were statistically significant [e.g., @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013; @walraveConnectingProtectingComparing2012], which refutes the privacy paradox.
+a different set of studies showed significant relations [e.g., @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013; @walraveConnectingProtectingComparing2012], which refutes the privacy paradox.
 
-Notably, in a parallel line of research other studies have also analyzed the relation between privacy concerns and information sharing; 
-however, the term privacy paradox has often not been mentioned explicitly. 
-Instead, studies have referred to the so-called _privacy calculus_. 
-The privacy calculus states that sharing personal information is affected by both the respective costs and the anticipated benefits [@culnanInformationPrivacyConcerns1999].
+Notably, in a parallel line of research other studies have also analyzed the relation between privacy concerns and information sharing.
+However, the term privacy paradox was often not mentioned explicitly. 
+Instead, studies have referred to the so-called _privacy calculus_, 
+which states that sharing personal information is affected by both the respective costs and the anticipated benefits [@culnanInformationPrivacyConcerns1999].
 By now, several studies have found empirical support for the privacy calculus in various online contexts [e.g., @bolUnderstandingEffectsPersonalization2018; @dienlinExtendedPrivacyCalculus2016; @krasnovaOnlineSocialNetworks2010].
@@
 On the basis of 37 studies, @baruhOnlinePrivacyConcerns2017 found a small and significant statistical relation between concerns about online privacy and online information sharing (_r_ = -.13, 95% CI [-.07, -.18]).
-Another more recent meta analysis by @yuMetaanalysisExplorePrivacy2020 also finds a significant bivariate relation between privacy concerns and information sharing, although smaller (_r_ = -.06, 95% CI [-.01, -.12]]).
-There also exist several systematic literature reviews on the privacy paradox [@barthPrivacyParadoxInvestigating2017; @gerberExplainingPrivacyParadox2018; @kokolakisPrivacyAttitudesPrivacy2017]
-@kokolakisPrivacyAttitudesPrivacy2017 conclude that "the dichotomy between privacy attitude and behaviour should not be considered a paradox anymore." (p. 130)
+Another more recent meta analysis by @yuMetaanalysisExplorePrivacy2020 also finds a significant bivariate relation between privacy concerns and information sharing, albeit smaller (_r_ = -.06, 95% CI [-.01, -.12]]).
+There also exist several systematic literature reviews on the privacy paradox [@barthPrivacyParadoxInvestigating2017; @gerberExplainingPrivacyParadox2018; @kokolakisPrivacyAttitudesPrivacy2017].
+@kokolakisPrivacyAttitudesPrivacy2017 come to the conclusion that "the dichotomy between privacy attitude and behaviour should not be considered a paradox anymore." (p. 130)
 However, the authors also note that the privacy paradox is a "complex phenomenon that has not been fully explained yet".
@@
 
-In conclusion, large parts of the current literature suggests that a significant relation between concerns about online privacy and the online sharing of personal information exists and that it is small---which speaks against the privacy paradox.
+<!-- In conclusion, large parts of the current literature suggests that a significant relation between concerns about online privacy and the online sharing of personal information exists and that it is small---which speaks against the privacy paradox.
+-->
 
@@
 Hence, privacy captures aspects of both volitional _control_ and social _separateness_.
-Several dimensions of privacy have been proposed:
-For example, it is possible to distinguish a vertical and a horizontal level;
-whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people [@masurSituationalPrivacySelfdisclosure2018].
-When it comes to concerns specifically, interestingly they do not seem to be established as a stand-alone theoretical concept in psychology [@colmanDictionaryPsychology2015].
+Several dimensions of privacy have been proposed.
+For example, it is possible to distinguish a vertical and a horizontal level.
+Whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people [@masurSituationalPrivacySelfdisclosure2018].
+When it comes to concerns in general, interestingly they do not seem to be established as a stand-alone theoretical concept in psychology [@colmanDictionaryPsychology2015].
 Lexically, concerns are defined as a "marked interest or regard usually arising through a personal tie or relationship" that also reflect an "uneasy state of blended interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
-Concerns therefore represent both a latent _motivation_ (or increased attention) and a negatively valenced _emotion_ (or affective condition).
-As such, concerns are not the result of a deliberate explicit cognition.
-Instead, they stem from an automatic implicit perception.
+Concerns therefore represent both a latent _motivation_ (or increased attention), a negatively valenced _emotion_ (or affective condition), and are mostly implicit.
+As a theoretical construct, privacy concerns can hence be categorized as an affective motivational disposition.
+As such, there are many similarities with other concepts, including emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (risk perception, approval), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).
 Taken together, concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened.
-As a theoretical construct, privacy concerns can hence be categorized as an affective motivational disposition.
-As such, there are many similarities with other concepts, which includes emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (risk perception, approval), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).
 
-The online sharing of personal information, on the other hand, captures how much person-related information people share when they use the Internet, which includes, for example, information about their age, sex, name, address, health, or finances.
-Information sharing can be differentiated from communication and self-disclosure:
+The online sharing of personal information, on the other hand, captures how much person-related information people share when they use the Internet, including information about their age, sex, name, address, health, and finances.
+Information sharing can be differentiated from communication and self-disclosure.
 Communication is broad, because it comprises all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011].
@@
 
-Currently, there seems to be a lack of studies that explicitly analyze how behavior is affected by _concerns_.
+Currently, there is a lack of studies that explicitly analyze how behavior is affected by _concerns_ in general.
 Fortunately, however, we know much about the behavioral effects of related concepts such as attitudes or fears, which all can affect behavior profoundly [@fishbeinPredictingChangingBehavior2010; @rogersCognitivePhysiologicalProcesses1983].
 Emotions, perhaps the concept most closely related to concerns, have a particularly strong effect on behavior. 
-By causing fight, flight, or freeze reactions, they are a primordial trigger of behavior and an adaptive mechanism fostering the evolution of a species [@dolanEmotionCognitionBehavior2002].
-With their direct link to the amygdala, emotions can trigger reactions already subcortically [i.e., without activation of the more recently evolved cortical structures; @dolanEmotionCognitionBehavior2002].
+By causing fight, flight, or freeze reactions, they are a primordial trigger of behavior and are considered to be an adaptive mechanism of evolved species [@dolanEmotionCognitionBehavior2002].
+<!-- With their direct link to the amygdala, emotions can trigger reactions already subcortically [i.e., without activation of the more recently evolved cortical structures; @dolanEmotionCognitionBehavior2002].
+-->
 
-Also empirically, concerns have been shown to affect behavior: 
-People more concerned about the environment show more environment-related behaviors [@bambergHowDoesEnvironmental2003]; people more concerned about their appearance consume fewer calories [@hayesConcernAppearanceHealth1987];
+Also empirically, concerns have been shown to affect behavior. 
+People more concerned about the environment show more environment-related behaviors [@bambergHowDoesEnvironmental2003].
+People more concerned about their appearance consume fewer calories [@hayesConcernAppearanceHealth1987].
 People more concerned about their bodies engage in more physical exercise [@reelRelationsBodyConcerns2007].
@@
 Not everyone concerned about his or her physical health exercises regularly.
-The explanation is simple.
+The explanation is simple:
 Other factors such as subjective norms and perceived behavioral control also determine behavior [@ajzenIntentionsActionsTheory1985], which automatically reduces the impact of attitudes or concerns. 
-Specifically, two of the most influential factors that affect online information sharing are (a) strong subjective norms to participate online [@heirmanPredictingAdolescentsDisclosure2013] and (b) the manifold benefits that accrue from participation [@krasnovaOnlineSocialNetworks2010].
+Specifically, two of the most influential factors that affect online information sharing are (a) strong subjective norms [@heirmanPredictingAdolescentsDisclosure2013] and (b) expected benefits[@krasnovaOnlineSocialNetworks2010].
 In other words, users often prioritize social support, special offers, or improved services.
@@
 absence of negative personal experiences, 
-and situational constraints due to social desirability.
-In conclusion, also in the context of the privacy paradox we should not expect to find a perfect relation between attitudes and behaviors, but rather a small to moderate relation.
+or situational constraints due to social desirability.
+In conclusion, also in the context of the privacy paradox we should not expect to find a perfect relation between attitudes and behaviors.
+Expecting a small to moderate relation is more reasonable.
 
-Finally, there are also some methodological reasons that explain why some studies did not detect statistically significant relations.
-In general, researchers are confronted with the _Duhem-Quine problem_, which holds that it is impossible to test theories in isolation, because empirical tests always rely on auxiliary assumptions [@dienesUnderstandingPsychologyScience2008].
+Finally, there are also some methodological explanations why some studies did not detect statistically significant relations.
+Researchers are always confronted with the so-called _Duhem-Quine problem_, which holds that it is impossible to test theories in isolation, because empirical tests always rely on auxiliary assumptions [@dienesUnderstandingPsychologyScience2008].
 In other words, if a psychological experiment fails, we do not know whether the theory is wrong or the questionnaire subpar. 
@@
 
-In conclusion, in line with prior research [@baruhOnlinePrivacyConcerns2017] and the within-person rationales that we have presented above, we expect to find a small significant relation between privacy concerns and information sharing, both on the between-person level and the within-person level.
+In conclusion, in line with prior research and the within-person rationales presented above, we expect to find a small significant relation between privacy concerns and information sharing, both on the between-person level and the within-person level.
 
@@
 
-Although short-term effects are likely, it is unclear whether there will be any long-term effects.
+Although short-term effects are likely, it is still unclear whether long-term effects exist as well.
 First, when analyzing potential long-term effects, it is important to choose an interval that is both plausible and relevant.
-For example, it makes a difference whether the effects of alcohol consumption on driving performance are tested 1 minute, 1 hour, or 1 day after consumption. 
-One factor that determines an interval's optimal length is the variable's stability [@dormannOptimalTimeLags2015].
+(It makes a large difference whether the effects of alcohol consumption on driving performance are tested after 1 minute, 1 hour, or 1 day.) 
+One factor that determines an interval's optimal length is the stability of the variables [@dormannOptimalTimeLags2015].
 Privacy concerns and privacy attitudes are predominantly trait-like constructs with high stabilities, which is why they necessitate longer intervals.
@@
 
-At the same time, the adverse effect of information sharing on privacy concerns seems also plausible, with two potential outcomes. 
+At the same time, the adverse effect of information sharing on privacy concerns seems plausible as well, with two potential outcomes. 
 On the one hand, the long-term relation could be negative: 
-If people start to share more information online, they might become increasingly aware that their privacy is at risk, which might stir concern.
-On the other hand, the long-term relation might also be positive, because when people share more personal information online, they might become accustomed to doing so, which might reduce concern [for example, due to the mere exposure effect; @zajoncAttitudinalEffectsMere1968].
-Finally, there could also be no long-term relation after all. 
-For example, people might have already become used to sharing information online, which might stifle any further cognitive or emotional processing -- a rationale central to the observation of so-called _privacy cynicism_ [e.g., @hoffmannPrivacyCynicismNew2016].
+If people start to share more information online, they might become increasingly aware that their privacy is at risk, thereby stirring concern.
+On the other hand, the long-term relation might also be positive:
+When people share more personal information online they might become accustomed to doing so, which potentially reduces concern [for example, due to the mere exposure effect; @zajoncAttitudinalEffectsMere1968].
+Finally, there could also be no long-term relation at all: 
+People might have already become used to sharing information online, which stifles further cognitive or emotional processing.
+This rationale is central to so-called _privacy cynicism_ [e.g., @hoffmannPrivacyCynicismNew2016].
 
@@
 
-It has been argued that privacy attitudes could 'bridge the gap' between concerns and information sharing [e.g., @dienlinPrivacyParadoxRelic2015]. 
+It has been argued that privacy attitudes could bridge the gap between concerns and information sharing [e.g., @dienlinPrivacyParadoxRelic2015]. 
 In contrast to privacy concerns, privacy attitudes capture a more explicit, fluctuating cognitive appraisal. 
 Although both variables are related to information disclosure, attitudes are likely the better predictor. 
-This reasoning follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always, at least in part, influenced by convictions, attitudes, and cost-benefit analyses.
+This reasoning follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always at least partially influenced by convictions, attitudes, and cost-benefit analyses.
 <!-- Likewise, also evolutionary psychology suggests that although emotions guide behavior in the long run, it is more adaptive if behavior instead reflects a cognitive appraisal;  -->
@@
 
-Concerning the potential long-term relations of privacy attitudes, we are confronted with the same situation mentioned above:
-Given that we are not aware of research on long-term relations, several scenarios seem plausible.
-For example, attitudes could either have long-term relations or not, and information sharing could either foster privacy attitudes or diminish them.
+Concerning the potential long-term relations of privacy attitudes, we are confronted with the same situation mentioned above.
+Because we are not aware of research on long-term relations, several scenarios seem plausible.
+Attitudes could either have long-term relations or not, and information sharing could either foster privacy attitudes or diminish them.
 
@@
 On the one hand, if we committed an alpha error, we would wrongfully conclude that people's concerns and behaviors are consistent. 
-Communicating such a false result to the public might unjustly reassure and placate people when they should instead be more alert.
+Communicating such a false result to the public might unjustly reassure people when they should be more alert.
 On the other hand, if we committed a beta error, we would wrongfully conclude that individuals behave paradoxically.
@@
 We consider both errors to be equally detrimental. 
-Hence, we chose to use error rates that are balanced.
-Next, we set a maximum error rate of 5% for both alpha and beta. 
+Hence, we chose balanced error rates, setting a maximum error rate of 5% for both alpha and beta. 
 As the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses;
@@
 The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
-On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi`, we calculated that we needed a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents.
+On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi`, we calculated a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents.
 Given the final sample size of `r dollar_format(prefix = "")(n)` respondents (see below), alpha and beta errors were balanced for our hypotheses (research questions) when we used a critical alpha of `r alpha_balanced_h  %>% round(3) * 100`% (`r alpha_balanced_rq  %>% round(3) * 100`%), resulting in a power of `r power_balanced_h %>% round(3) * 100`%  (`r power_balanced_rq %>% round(3) * 100`%) to detect small effects.
@@
 
-The data were analyzed by means of a random-intercept cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015].
+The data were analyzed using of a random-intercept cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015].
 For a visualization, see Figure \@ref(fig:RICLPM).
-RI-ClPMs have already been used for similar research questions [@dietvorstAdolescentPerceptionsParental2018].
-Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs allow to separate between-person variance from within-person variance. 
+Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs can separate between-person variance from within-person variance. 
 We used factor scores as observed variables to represent the variables' latent structure more closely.
@@
 As we did not assume longitudinal effects to differ across time, they were constrained to be equal across all waves, which produces one single general measure of each effect instead of two time-specific ones.
-(We later tested this assumption also empirically.
-Indeed, the model with constrained effects did not show significantly reduced model fit, $\chi$^{2}(`r model_comp[2, 6]`) = `r model_comp[2, 7] %>% my_round("p")`, _p_ = `r model_comp[2, 5] %>% my_round("est")`, which supports the assumption that effects did not change significantly across time.)
+(We later tested this assumption empirically.
+As expected, the model with constrained effects did not show significantly reduced model fit, $\chi$^2^(`r model_comp[2, 6]`) = `r model_comp[2, 7] %>% my_round("p")`, _p_ = `r model_comp[2, 5] %>% my_round("est")`, which supports that effects did not change over time.)
 Fit was assessed according to the common criteria as described by @klinePrinciplesPracticeStructural2016. 
@@
 
-This study is part of a large-scale project which investigates the development of privacy and self-disclosure, including several other variables. 
+This study is part of a large-scale project which investigates the development of privacy and self-disclosure, including severaldother variables. 
 Other publications linked to the project can be accessed at https://osf.io/y35as/.
@@
 The first three waves were collected from May 2014 to May 2015, with intervals of 6 months each.
-The last two waves, collected on May 2016 and May 2017, had an interval of one year.
+The last two waves were collected on May 2016 and May 2017, and had an interval of one year.
 Because we hypothesized the effects to take place across half a year, the last two waves were not included in the analyses presented here.
@@
 Wave 1 was completed by 3,278 respondents (response rate: `r round((1 - (3278 / 5286)) * 100, 0)`%), Wave 2 by 2,448 respondents (attrition rate: `r round((1 - (2448 / 3278)) * 100, 0)`%), and Wave 3 by 2,021 respondents (attrition rate: `r round((1 - (2021 / 2448)) * 100, 0)`%).
-We filtered respondents who never used the Internet at all waves, answered fewer than 50% of the items in each scale for at least one wave, provided inconsistent birth-dates across measurements, or who did not report sociodemographic variables.
+We filtered respondents who never used the Internet at all waves, answered fewer than 50% of the items in each scale for at least one wave, provided inconsistent birth-dates across measurements, or did not report sociodemographic variables.
 The final sample consisted of *n* = `r dollar_format(prefix = "")(n_complete)` respondents.
@@
 Therefore, Full Information Maximum Likelihood (FIML) estimation was conducted using all available data.
-The average age was `r round(age_m, 0)` years (*SD* = `r round(age_sd, 0)` years), and `r (round(male_per, 2) - 1) * 100`% were male. 
+The average age was `r round(age_m, 0)` years (*SD* = `r round(age_sd, 0)` years), and `r round(male_per, 2) * 100`% were male. 
 About `r round(edu_col_per, 0)`% reported that they had graduated from college.
@@
 For each item, factor loadings were constrained to be equal across waves.
-Constrained and unconstrained models were compared using $\chi^2$ differences tests; all results were nonsignificant, suggesting longitudinal factorial invariance.
+Constrained and unconstrained models were compared using $\chi^2$ differences tests.
+All results were nonsignificant, suggesting longitudinal factorial invariance.
 The measures showed good composite reliability in all three waves. 
 Graphical displays of the variables' distributions showed that privacy concerns were skewed to the left, privacy attitudes were normally distributed, and information sharing was skewed to the right (Figure \@ref(fig:Distributions), diagonal).
-Finally, we also calculated the intra-class correlation coefficient, quantifying how much variance in the variables' factor scores could be attributed to between-person differences.
+We calculated intra-class correlation coefficients to quantify how much variance in the variables' factor scores could be attributed to between-person differences.
 An English translation of the original German items can be found in the OSM.
@@
 
-Privacy concerns were measured as a second-order factor: 
+Privacy concerns were measured as a second-order factor. 
 Three items captured the vertical dimension (e.g., "How concerned are you that institutions or intelligence services collect and analyze data that you disclosed on the Internet?"), and three items captured the horizontal dimension (e.g., "How concerned are you that people that you do not know might obtain information about you because of you online activities?").
@@
 
-To measure respondent's level of information disclosure, they were asked to indicate how often they disclosed 10 different pieces of information on the Internet. 
+To measure respondent's level of information disclosure, they were asked how often they disclosed 10 different pieces of information on the Internet. 
 The exact question was: "How often do you disclose the following pieces of information online (i.e., on the Internet)?" 
@@
 
-Respondents' attitudes toward disclosing personal information online were similarly captured with 10 items that measured the general appraisal of disclosing the same 10 pieces of information. 
+Respondents' attitudes toward disclosing personal information online were captured with 10 items that measured the general appraisal of disclosing the same 10 pieces of information. 
 Adhering to the principle of compatibility [@fishbeinPredictingChangingBehavior2010], the items were parallel to those of the actual disclosure scale. 
@@
 The effect was small.
-However, when looking at the standardized effect's confidence interval (i.e., $\beta$ = `r effect_std_ci[["est.std"]] %>% my_round("std")`, 95% CI [`r effect_std_ci[["ci.lower"]] %>% my_round("std")`, `r  effect_std_ci[["ci.upper"]] %>% my_round("std")`]), it was not significantly smaller than our SESOI of $beta$ = .10.
+When looking at the standardized effect's confidence interval (i.e., $\beta$ = `r effect_std_ci[["est.std"]] %>% my_round("std")`, 95% CI [`r effect_std_ci[["ci.lower"]] %>% my_round("std")`, `r  effect_std_ci[["ci.upper"]] %>% my_round("std")`]), it was not significantly smaller than our SESOI of $beta$ = .10.
 Thus, Hypothesis 1 was supported.
@@
 The results revealed a medium-sized negative correlation between the two variables on the between-person level (`r coeffs_txt(fit_riclpm, "cor_b_1", one_sided = TRUE)`). 
-Thus, people who---on average across all three waves---reported being more concerned about their online privacy relative to the rest of the sample, were also substantially more likely to hold a more negative attitude toward the online sharing of personal information, thereby supporting Hypothesis 3.1.
+Thus, people who---on average across all three waves---reported being more concerned about their online privacy relative to the rest of the sample, were also substantially more likely to hold a more negative attitude toward the online sharing of personal information.
+The results therefore supported Hypothesis 3.1.
 Hypothesis 3.2 stated that people who held more positive attitudes toward the online sharing of personal information than others would also share more personal information online than others. 
@@
 Hypothesis 4.2 proposed that people who held more positive attitudes toward the online sharing of personal information than usual would also share more personal information online than usual. 
-Results showed a moderate within-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_w_3", one_sided = TRUE)`), indicating that when respondents had more positive attitudes toward the online sharing of personal information at T1 than usual, they also shared more personal information online than usual.
+Results showed a moderate within-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_w_3", one_sided = TRUE)`), which indicates that when respondents had more positive attitudes at T1 than usual, they also shared more personal information than usual.
 In conclusion, the results supported Hypothesis 4.2.
@@
 The within-person parameters reflect how intrapersonal changes in one variable are related to intra-personal changes in another.
-For example, results showed that if a person was more concerned at T1 than he or she usually is, he or she also shared less information than usual.")
+For example, results showed that if a person was more concerned at T1 than usual, they also shared less information than usual.")
   , font_size = "small"
@@
 
-Most research on the privacy paradox suggests that there is a significant and small relation between concerns and the online sharing of personal information [e.g., @baruhOnlinePrivacyConcerns2017]. 
-However, whereas the theoretical premise of the privacy paradox actually addresses a within-person effect,
-most empirical studies have analyzed between-person relations.
+Most research on the privacy paradox suggests a significant small effect of privacy concerns on the online sharing of personal information [e.g., @baruhOnlinePrivacyConcerns2017]. 
+However, whereas the theoretical premise of the privacy paradox addresses a within-person _effect_,
+most empirical studies have analyzed between-person _relations_.
 On the basis of a representative sample of the German population, from which three waves of data separated by 6 months were collected, we hence analyzed the privacy paradox by differentiating general between-person relations, short-term within-person relations, as well as long-term within-person effects.
@@
 In addition, people who were more concerned about their privacy than others also held substantially more negative attitudes toward disclosing personal information online.
-Notably, we found a very strong between-person correlation between attitudes toward information sharing and actual information sharing, which shows that typical online disclosure can be predicted precisely by a person's attitude.
+Notably, we found a very strong between-person correlation between attitudes toward information sharing and actual information sharing.
+This finding shows that typical online disclosure can be predicted precisely by a person's attitude.
 Taken together, the cross-sectional results are in line with the extant literature:
-The between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fell within the 95% confidence interval of the effect reported by @baruhOnlinePrivacyConcerns2017 (i.e., _r_ = -.13, 95% CI [-.07, -.18]).
+The between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fall within the 95% confidence interval of the effect reported by @baruhOnlinePrivacyConcerns2017 (i.e., _r_ = -.13, 95% CI [-.07, -.18]).
 Note that the between-person correlations reported here represent averaged measurements across three waves, which should make the findings more robust than typical one-shot measures.
@@
 The differences between people with regard to their online information sharing behavior can be explained by differences in privacy concerns to a small extent, and by differences in privacy attitudes to a large extent.
-The more specific we become, the better we can explain online behavior. 
-Whereas privacy concerns are related only weakly to online information sharing [e.g., @baruhOnlinePrivacyConcerns2017], more specific risks perceptions are more closely related to behavior [e.g., @bolUnderstandingEffectsPersonalization2018; @yuMetaanalysisExplorePrivacy2020], while behavioral attitudes are the best predictors [@dienlinPrivacyParadoxRelic2015].
+The more specific we become, the better we can explain online behavior: 
+Whereas privacy concerns are related only weakly to online information sharing [e.g., @baruhOnlinePrivacyConcerns2017], more specific risks perceptions are related to behavior more closely [e.g., @bolUnderstandingEffectsPersonalization2018; @yuMetaanalysisExplorePrivacy2020], whereas behavioral attitudes are the best predictors [@dienlinPrivacyParadoxRelic2015].
 
@@
 Moreover, people who developed more positive attitudes toward the online sharing of personal information than usual, also shared substantially more personal information online.
-Together, changes in concerns and attitudes are both related to changes in behavior, which suggests that the privacy paradox does not exist also on the within-person level.
+Together, changes in concerns and attitudes are both related to changes in behavior, which speaks against the privacy paradox also on the within-person level.
 
 We did not find any long-term effects, however.
-Specifically, changes in both privacy concerns and attitudes toward the online sharing of personal information were not related to any meaningful changes in the online sharing of personal information 6 months later, and vice versa.
+Changes in both privacy concerns and attitudes toward the online sharing of personal information were not related to any meaningful changes in the online sharing of personal information 6 months later, and vice versa.
 As an explanation, it might be the case that changes in privacy concern affect information sharing more immediately. 
@@
 but only that they are very small.
-Of course, it could also be that longterm longitudinal effects simply do not exist.
+Of course, it could also be that longterm longitudinal effects do not exist.
 
@@
 
-Some of the effect sizes reported in this study are potentially not large enough to refute the privacy paradox. 
-On the one hand, they could simply be a manifestation of the so-called "crud factor" [@meehlWhySummariesResearch1990, p.
+Some of the effect sizes reported in this study are potentially not large enough to refute the privacy paradox completely. 
+On the one hand, they could be a manifestation of the so-called "crud factor" [@meehlWhySummariesResearch1990, p.
 204], which states that all psychosocial measures are related to one another to some extent.
 On the other hand, other factors such as expected benefits might play a more important role [@dienlinExtendedPrivacyCalculus2016].
-In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, one should indeed not overestimate the importance of privacy concerns.
-The effect could be larger, and other variables surely play a role as well.
+In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, the importance of privacy concerns should not be exaggerated.
+The effects could be larger, and other variables surely play a role as well.
 
@@
 Although we found significant within-person correlations at T1, they were absent across the 6-month intervals.
-Together, this suggests that longitudinal effects exist, but that they take place on a different time interval.
-Future research might hence probe different intervals.
-For theoretical reasons (e.g., due to availability heuristics), it is plausible to use intervals that are shorter;
+Together, this suggests that longitudinal effects might exist, but that they take place on a different time interval.
+Future research could hence probe different intervals.
+For theoretical reasons (e.g., due to availability heuristics), it is plausible to use short intervals;
 for statistical reasons (e.g., because of the high stability of privacy concerns), however, it also makes sense to test longer intervals  [@dormannOptimalTimeLags2015].
 
-Although we argue that in most circumstances privacy concerns and behavior should correlate modestly, the exact extent to which they relate depends on a plethora of boundary conditions.
-Future research should hence explicitly focus on analyzing different contexts and situations. 
+Although we argue that in most circumstances privacy concerns and behavior should correlate modestly, the exact extent depends on a many boundary conditions.
+Future research should hence explicitly analyze different contexts and situations. 
 Building on @kokolakisPrivacyAttitudesPrivacy2017, we suggest the following boundary conditions:
 
- - Context (professional, social, commercial, health-related, etc.);
- - Situation (new, habitualized, unexpected, etc.);
- - Mood (positive vs. negative, etc.);
+ - Context (e.g., professional, social, commercial, or health-related);
+ - Situation (e.g., new, habitualized, or unexpected);
+ - Mood (e.g., positive vs. negative);
  - Extent of control (high vs. low);
  - Type of information processing applied (implicit, heuristic, or peripheral vs. explicit, analytic, or central);
- - Existence of bias (e.g., overconfidence, optimism, comparative optimism, hyperbolic discounting);
- - Type of information (sensitive vs. superficial, biographic, person-related, etc.);
+ - Existence of bias (e.g., overconfidence, optimism, comparative optimism, or hyperbolic discounting);
+ - Type of information (e.g., sensitive vs. superficial, biographic, or person-related);
  - Benefit immediacy and risk diffusion (high vs. low).
@@
 
-Next to these theory-related boundary conditions there are methodological ones:
+Next to these theory-related boundary conditions there are also methodological ones:
 
- - Analysis design (theoretical, experimental, questionnaire-based, interview-based, anecdotal);
+ - Analysis design (e.g., theoretical, experimental, questionnaire-based, interview-based, or anecdotal);
  - Quality of measurement (high vs. low; low quality less likely to detect statistical significance);
  - Sample size (small vs. large; small samples less likely to detect statistical significance);
- - Statistical analysis (SEM vs. Regression; analyses without error control less likely to find statistical significance);
- - Operationalization (concerns vs. risk perceptions vs. behavioral attitudes; the more specific, the stronger the relation).
+ - Statistical analysis (e.g., SEM vs. Regression; analyses without error control less likely to find statistical significance);
+ - Operationalization (e.g., concerns vs. risk perceptions vs. behavioral attitudes; the more specific, the stronger the relation).
 

### 2020-05-07 manuscript.RmD
- added e-mail addresses
- updated pdf

@@
   - name          : "Philipp K. Masur"
+    email         : "philipp.masur@uni-mainz.de"
     affiliation   : "2"
   - name          : "Sabine Trepte"
+    email         : "sabine.trepte@uni-hohenheim.de"
     affiliation   : "1"
@@
 # (b) uncomment the following lines; comment lines after "output: html_document ..."
-# output            : papaja::apa6_pdf
-# header-includes:
-#   - \setlength{\parskip}{0em}
-#   - \raggedbottom
-output:
-  html_document:
-    toc: TRUE
-    toc_float:
-      collapsed: FALSE
-    toc_depth: 2
+output            : papaja::apa6_pdf
+header-includes:
+  - \setlength{\parskip}{0em}
+  - \raggedbottom
+# output:
+#   html_document:
+#     toc: TRUE
+#     toc_float:
+#       collapsed: FALSE
+#     toc_depth: 2
 ---

### 2020-05-08 analyses.Rmd
- language updates

@@
 age_sd <- sd(d_wide$age)
-male_per <- 1 - mean(d_wide$male)
+male_per <- mean(d_wide$male) - 1
 edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100

### 2020-05-08 analyses_additional.Rmd
- language updates

@@
 ```
+
 In what follows, we report the results of additional analyses that were also calculated.
@@
 
-```{r include=F}
+```{r include=F, cache=F}
 save.image("data/workspace.RData")

### 2020-05-08 manuscript.RmD
- language updates

--- 2020-05-07 manuscript.RmD
@@
   The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
-  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective.
-We differentiate between-person relations from within-person effects.
-  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level).
+  On the basis of a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective.
+Using a cross-lagged panel model with random intercepts, we differentiate between-person relations from within-person effects.
+  Results revealed that people who were more concerned about their online privacy than others also shared slightly less personal information and had substantially more negative attitudes toward information sharing (between-person level).
   People who were more concerned than usual also shared slightly less information than usual (within-person level). 
   We found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
-  The results provide further evidence against the privacy paradox, but more research is needed to better understand the variables' potential causal relation.
+  The results provide further evidence against the privacy paradox, but more research is needed to better understand the variables' potential causal relations.
 keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
@@
 The privacy paradox states that the information disclosure of Internet users is problematic: 
-Although many people are concerned about their online privacy, they still share plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
-The privacy paradox and its underlying theoretical conundrum is hence of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia entries  [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
+Although many people are concerned about their privacy online, they still share plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
+The privacy paradox and its underlying theoretical conundrum is of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia entries  [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
 If the privacy paradox really exists, it should inspire worry: 
@@
 
-However, current research on the privacy paradox has one major limitation: 
-To the best of our knowledge, most empirical studies conducted so far have investigated the privacy paradox from a between-person (i.e., interpersonal) perspective.
+However, current research on the privacy paradox has one major limitation. 
+To the best of our knowledge, most empirical studies conducted so far have investigated the privacy paradox from a between-person perspective.
 By employing empirical tests of relations between people (e.g., cross-sectional questionnaires analyzed with multiple regression or Pearson correlations), studies have analyzed whether people who are more concerned than _others_ also share less personal information than _others_.
-Although such a between-person perspective is interesting and represents a viable first step, it cannot make informed claims regarding causality.
+Although such a perspective is interesting and represents a viable first step, it cannot make informed claims regarding causality.
 The privacy paradox, however, implies a causal perspective:
@@
 Second, on a within-person level, does information sharing decrease when concerns increase?
-Third, what are the potential long-term effects, are changes in concerns related to changes in information sharing 6 months later and/or vice versa? 
+Third, what are the potential long-term effects?
+Are changes in concerns related to changes in information sharing 6 months later and/or vice versa? 
 Fourth, what is the role of privacy attitudes, do they mediate the relation between privacy concerns and information sharing?
-To best answer and contextualize these questions, we first provide an in-depth theoretical analysis of the privacy paradox, after which we present the empirical results of a longitudinal panel study.
+To best answer and contextualize these questions, we first provide an in-depth theoretical analysis of the privacy paradox, after which we present the empirical results of a longitudinal panel study, which is representative of the German population.
 
@@
 Notably, in a parallel line of research other studies have also analyzed the relation between privacy concerns and information sharing.
-However, the term privacy paradox was often not mentioned explicitly. 
+However, the term privacy paradox was often not used explicitly. 
 Instead, studies have referred to the so-called _privacy calculus_, 
-which states that sharing personal information is affected by both the respective costs and the anticipated benefits [@culnanInformationPrivacyConcerns1999].
+which states that the sharing of personal information online is affected by both the respective costs and the anticipated benefits [@culnanInformationPrivacyConcerns1999].
 By now, several studies have found empirical support for the privacy calculus in various online contexts [e.g., @bolUnderstandingEffectsPersonalization2018; @dienlinExtendedPrivacyCalculus2016; @krasnovaOnlineSocialNetworks2010].
@@
 Currently, there is a lack of studies that explicitly analyze how behavior is affected by _concerns_ in general.
-Fortunately, however, we know much about the behavioral effects of related concepts such as attitudes or fears, which all can affect behavior profoundly [@fishbeinPredictingChangingBehavior2010; @rogersCognitivePhysiologicalProcesses1983].
+Fortunately, however, we know much about the behavioral effects of related concepts such as attitudes or fears, which all can affect behavior, sometimes profoundly [@fishbeinPredictingChangingBehavior2010; @rogersCognitivePhysiologicalProcesses1983].
 Emotions, perhaps the concept most closely related to concerns, have a particularly strong effect on behavior. 
@@
 People more concerned about their bodies engage in more physical exercise [@reelRelationsBodyConcerns2007].
-Taken together, it is reasonable to expect that also concerns about online privacy should reflect in the online sharing of personal information.
+Taken together, it is reasonable to expect that also concerns about online privacy should somehow reflect in the online sharing of personal information.
 
-At the same time, there are some factors that are likely to diminish the relation.
+At the same time, there are some factors that likely diminish the relation.
 Most prominently, there is the so-called _attitude behavior gap_ [@fishbeinPredictingChangingBehavior2010], which states that people sometimes act against their own attitudes. 
-Not everyone concerned about his or her physical health exercises regularly.
+Evidently, not everyone concerned about their physical health exercises regularly.
 The explanation is simple:
 Other factors such as subjective norms and perceived behavioral control also determine behavior [@ajzenIntentionsActionsTheory1985], which automatically reduces the impact of attitudes or concerns. 
-Specifically, two of the most influential factors that affect online information sharing are (a) strong subjective norms [@heirmanPredictingAdolescentsDisclosure2013] and (b) expected benefits[@krasnovaOnlineSocialNetworks2010].
-In other words, users often prioritize social support, special offers, or improved services.
+Specifically, two of the most influential factors that affect online information sharing are (a) strong subjective norms [@heirmanPredictingAdolescentsDisclosure2013] and (b) expected benefits [@krasnovaOnlineSocialNetworks2010].
+In other words, users often prioritize social support, special offers, or improved services, accepting that their privacy will be diminished.
 @trepteRiskyBehaviorsHow2014 listed several factors that can additionally attenuate the relation:
@@
 or situational constraints due to social desirability.
-In conclusion, also in the context of the privacy paradox we should not expect to find a perfect relation between attitudes and behaviors.
-Expecting a small to moderate relation is more reasonable.
+In conclusion, also in the context of the privacy paradox it _not_ reasonable to expect a _perfect_ relation between attitudes and behaviors.
+However, we should still expect to find a relation that is _small_ or _moderate_.
 
-Finally, there are also some methodological explanations why some studies did not detect statistically significant relations.
-Researchers are always confronted with the so-called _Duhem-Quine problem_, which holds that it is impossible to test theories in isolation, because empirical tests always rely on auxiliary assumptions [@dienesUnderstandingPsychologyScience2008].
+There are also some methodological explanations as to why some studies did not detect statistically significant relations.
+Researchers are always confronted with the so-called _Duhem-Quine problem_, according to which it is impossible to test theories in isolation, because empirical tests always rely on auxiliary assumptions [@dienesUnderstandingPsychologyScience2008].
 In other words, if a psychological experiment fails, we do not know whether the theory is wrong or the questionnaire subpar. 
 This tenet is particularly relevant for the privacy paradox: 
-Detecting statistical significance for small effects---and in this case, we should expect to find small effects---is more challenging because it means that large samples are necessary to guarantee sufficient statistical power.[^power]
+Detecting statistical significance for small effects---and, again, we should expect to find small effects---is more challenging because it means that large samples are necessary to guarantee sufficient statistical power.[^power]
 Precisely, in order to be capable of detecting a correlation between privacy concerns and information sharing in 95% of all cases, which @baruhOnlinePrivacyConcerns2017 estimated to be _r_ = -.13, we need a sample of _N_ = `r pwr.r.test(r = -.13, sig.level = .05, power = .95)$n %>%  round(0)` people.
@@
 First, when analyzing potential long-term effects, it is important to choose an interval that is both plausible and relevant.
-(It makes a large difference whether the effects of alcohol consumption on driving performance are tested after 1 minute, 1 hour, or 1 day.) 
+(It makes a large difference whether the effects of alcohol consumption on driving performance are tested after say 1 minute, 1 hour, or 1 day.) 
 One factor that determines an interval's optimal length is the stability of the variables [@dormannOptimalTimeLags2015].
 Privacy concerns and privacy attitudes are predominantly trait-like constructs with high stabilities, which is why they necessitate longer intervals.
-Other studies with comparable research questions have used an interval of 6 months [e.g., @valkenburgEffectsInstantMessaging2009], which we consider to be plausible also in this case.
+Other studies with comparable research questions have therefore used an interval of 6 months [e.g., @valkenburgEffectsInstantMessaging2009], which we adopt also in this study.
 
@@
 
-At the same time, the adverse effect of information sharing on privacy concerns seems plausible as well, with two potential outcomes. 
+At the same time, the adverse effect seems plausible as well, with two potential outcomes. 
 On the one hand, the long-term relation could be negative: 
@@
 Hence, we chose balanced error rates, setting a maximum error rate of 5% for both alpha and beta. 
-As the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses;
-significantly smaller effects were not considered able to offer support.
+As the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses.
+Significantly smaller effects were not considered able to offer support.
 The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
-On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi`, we calculated a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents.
+On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi %>% my_round("beta")`, we calculated a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents.
 Given the final sample size of `r dollar_format(prefix = "")(n)` respondents (see below), alpha and beta errors were balanced for our hypotheses (research questions) when we used a critical alpha of `r alpha_balanced_h  %>% round(3) * 100`% (`r alpha_balanced_rq  %>% round(3) * 100`%), resulting in a power of `r power_balanced_h %>% round(3) * 100`%  (`r power_balanced_rq %>% round(3) * 100`%) to detect small effects.
@@
 
-The data were analyzed using of a random-intercept cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015].
+The data were analyzed using of a random-intercept cross-lagged panel model [RI-CLPM, @hamakerCritiqueCrosslaggedPanel2015].
 For a visualization, see Figure \@ref(fig:RICLPM).
@@
 
-For the analyses, coding, and typesetting, we used `r r_citations`.
+For the analyses, we used `r r_citations`.
 The code, additional analyses, and a reproducible version of this manuscript can be found on the manuscript's companion website at https://tdienlin.github.io/privacy-paradox-longitudinal.
@@
 
-This study is part of a large-scale project which investigates the development of privacy and self-disclosure, including severaldother variables. 
+This study is part of a large-scale project which investigates the development of privacy and self-disclosure, including several other variables. 
 Other publications linked to the project can be accessed at https://osf.io/y35as/.
@@
 Because we hypothesized the effects to take place across half a year, the last two waves were not included in the analyses presented here.
-First, a sample of 14,714 potential respondents was drawn from a representative omnibus survey in Germany (ADM master sample), employing a random last-two-digit dialing procedure. 
+First, a sample of 14,714 potential respondents was drawn from a representative omnibus survey in Germany (ADM master sample), using a random last-two-digit dialing procedure. 
 In this CATI screening, 5,286 respondents agreed to participate in all following waves. 
@@
 Visual inspection of the missing value patterns as well as the non-parametric test by @R-MissMech suggested that all missing values could be considered missing at random (*p* `r test_mar_p %>% my_round("p_txt")`).
-Therefore, Full Information Maximum Likelihood (FIML) estimation was conducted using all available data.
+Therefore, Full Information Maximum Likelihood estimation was conducted using all available data.
 The average age was `r round(age_m, 0)` years (*SD* = `r round(age_sd, 0)` years), and `r round(male_per, 2) * 100`% were male. 
@@
 However, whereas the theoretical premise of the privacy paradox addresses a within-person _effect_,
-most empirical studies have analyzed between-person _relations_.
+most empirical studies have analyzed only between-person _relations_.
 On the basis of a representative sample of the German population, from which three waves of data separated by 6 months were collected, we hence analyzed the privacy paradox by differentiating general between-person relations, short-term within-person relations, as well as long-term within-person effects.
@@
 
-The results of the between-person analyses showed that people who were more concerned about their privacy than others also shared personal information slightly less frequently.
+The results of the between-person analyses showed that people who were more concerned about their privacy than others were slightly less likely to share personal information.
 In addition, people who were more concerned about their privacy than others also held substantially more negative attitudes toward disclosing personal information online.
-Notably, we found a very strong between-person correlation between attitudes toward information sharing and actual information sharing.
-This finding shows that typical online disclosure can be predicted precisely by a person's attitude.
+Notably, we found a very strong between-person correlation between attitudes toward information sharing and actual information sharing, which shows that typical online disclosure can be predicted precisely by a person's attitude.
 Taken together, the cross-sectional results are in line with the extant literature:
 The between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fall within the 95% confidence interval of the effect reported by @baruhOnlinePrivacyConcerns2017 (i.e., _r_ = -.13, 95% CI [-.07, -.18]).
-Note that the between-person correlations reported here represent averaged measurements across three waves, which should make the findings more robust than typical one-shot measures.
+Note that the between-person correlations reported here represent averaged measurements across three waves, which makes the findings more robust than typical one-shot measures.
 
 In conclusion, this study suggests that the privacy paradox does not exist on a between-person level.
-The differences between people with regard to their online information sharing behavior can be explained by differences in privacy concerns to a small extent, and by differences in privacy attitudes to a large extent.
+The differences between people with regard to their online information sharing behavior can be explained by differences in their privacy concerns to a small extent, and by differences in their privacy attitudes to a large extent.
 The more specific we become, the better we can explain online behavior: 
@@
 Moreover, people who developed more positive attitudes toward the online sharing of personal information than usual, also shared substantially more personal information online.
-Together, changes in concerns and attitudes are both related to changes in behavior, which speaks against the privacy paradox also on the within-person level.
+Together, changes in concerns and attitudes are therefore related to changes in behavior, which speaks against the privacy paradox also on the within-person level.
 
 We did not find any long-term effects, however.
-Changes in both privacy concerns and attitudes toward the online sharing of personal information were not related to any meaningful changes in the online sharing of personal information 6 months later, and vice versa.
+Changes in both privacy concerns and attitudes toward the online sharing of personal information were not related to any meaningful changes in the online sharing of personal information 6 months later (and vice versa).
 As an explanation, it might be the case that changes in privacy concern affect information sharing more immediately. 
-To test this assumption, we would need study designs with shorter intervals [@keijsersParentalMonitoringAdolescent2016].
+To test this assumption, we would need studies with shorter intervals [@keijsersParentalMonitoringAdolescent2016].
 Moreover, given that the directions of most longitudinal relations were in line with the between-person and within-person relations, 
@@
 In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, the importance of privacy concerns should not be exaggerated.
-The effects could be larger, and other variables surely play a role as well.
+The effects could be larger, and other variables play a role as well.
 
@@
 For theoretical reasons (e.g., due to availability heuristics), it is plausible to use short intervals;
-for statistical reasons (e.g., because of the high stability of privacy concerns), however, it also makes sense to test longer intervals  [@dormannOptimalTimeLags2015].
+for statistical reasons (e.g., because of the high stability of privacy concerns), it would also make sense to test longer intervals  [@dormannOptimalTimeLags2015].
 
@@
 Future research should hence explicitly analyze different contexts and situations. 
-Building on @kokolakisPrivacyAttitudesPrivacy2017, we suggest the following boundary conditions:
+Building on @kokolakisPrivacyAttitudesPrivacy2017, we suggest to analyze the following boundary conditions:
 
@@
 Specifically, we encourage analyzing privacy behaviors also from a situational perspective, accounting for temporal needs, interpersonal perceptions, contextual cues, or characteristics of communication channels [@masurSituationalPrivacySelfdisclosure2018].
-For example, whereas general levels of information sharing are likely best explained by using privacy _concerns_, situational information sharing might be best explained using privacy _heuristics_ [@sundarUnlockingPrivacyParadox2013].
+For example, whereas general levels of information sharing are likely best explained by using privacy _concerns_, situational information sharing might be best explained by using privacy _heuristics_ [@sundarUnlockingPrivacyParadox2013].
 
@@
 
-When analyzing the privacy paradox we are likely dealing with small effects [@baruhOnlinePrivacyConcerns2017].
+We emphasize that when analyzing the privacy paradox we are likely dealing with small effects [@baruhOnlinePrivacyConcerns2017].
 Hence, to detect these small effects reliably we need large samples. 
 This is often not the case [@baruhOnlinePrivacyConcerns2017].
-In conclusion, we emphasize to use statistical designs that allow for sufficient statistical power.
+In conclusion, it is crucial to use statistical designs that allow for sufficient statistical power.
 

### 2020-05-08 manuscript.RmD
- updated language

@@
 # (a) move file "_site.yml" to folder "tmp"
-# (b) uncomment the following lines; comment lines after "output: html_document ..."
+# (b) uncomment the following lines until incl. "\raggedbottom"
+# (c) comment lines after "output: html_document ..."
 # output            : papaja::apa6_pdf
@@
 Although many people are concerned about their privacy online, they still share plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
-The privacy paradox and its underlying theoretical conundrum is of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia entries  [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
+The privacy paradox is of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia entries  [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
 If the privacy paradox really exists, it should inspire worry: 
-It would suggest that online behavior is irrational and that people are revealing too much of their personal lives to unknown third parties, which can cause various problems [e.g., @sevignaniPrivacyCapitalismAge2016].
+It would suggest that online behavior is irrational and that people are revealing too much of their personal information, which can cause various problems [e.g., @sevignaniPrivacyCapitalismAge2016].
 Understanding why people disclose information online and whether or not this is paradoxical therefore represents an important challenge.

### 2020-05-11 manuscript.RmD
- added literature

@@
 Privacy is defined as the "[...] voluntary and temporary withdrawal of a person from the general society through physical or psychological means [...]" [@westinPrivacyFreedom1967, 7]. 
-Hence, privacy captures aspects of both volitional _control_ and social _separateness_.
+Privacy captures aspects of both volitional _control_ and social _separateness_ [@braunlichLinkingLooseEnds2020; @marwickNetworkedPrivacyHow2014].
 Several dimensions of privacy have been proposed.
-For example, it is possible to distinguish a vertical and a horizontal level.
-Whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people [@masurSituationalPrivacySelfdisclosure2018].
+For example, it is possible to distinguish a vertical and a horizontal level [@masurSituationalPrivacySelfdisclosure2018].
+Whereas the vertical level captures privacy from authorities, institutions, or companies, horizontal privacy addresses privacy from peers, colleagues, or other people.
 When it comes to concerns in general, interestingly they do not seem to be established as a stand-alone theoretical concept in psychology [@colmanDictionaryPsychology2015].
@@
 At the same time, the adverse effect seems plausible as well, with two potential outcomes. 
-On the one hand, the long-term relation could be negative: 
-If people start to share more information online, they might become increasingly aware that their privacy is at risk, thereby stirring concern.
-On the other hand, the long-term relation might also be positive:
+On the one hand, the long-term relation could be positive: 
+If people start to share more information online, they might become increasingly aware that their privacy is at risk, thereby stirring concern [@tsay-vogelSocialMediaCultivating2018].
+On the other hand, the long-term relation might also be negative:
 When people share more personal information online they might become accustomed to doing so, which potentially reduces concern [for example, due to the mere exposure effect; @zajoncAttitudinalEffectsMere1968].
@@
 It has been argued that privacy attitudes could bridge the gap between concerns and information sharing [e.g., @dienlinPrivacyParadoxRelic2015]. 
-In contrast to privacy concerns, privacy attitudes capture a more explicit, fluctuating cognitive appraisal. 
+In contrast to privacy concerns, privacy attitudes capture a more explicit, fluctuating cognitive appraisal [@tsay-vogelSocialMediaCultivating2018].
 Although both variables are related to information disclosure, attitudes are likely the better predictor. 
 This reasoning follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always at least partially influenced by convictions, attitudes, and cost-benefit analyses.
-<!-- Likewise, also evolutionary psychology suggests that although emotions guide behavior in the long run, it is more adaptive if behavior instead reflects a cognitive appraisal;  -->
-<!-- a tenet arguably reflected best by the phylogenetic development of the neocortex or, if you want, the general dominion of the human race. -->
 Also empirically, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure was only moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].

### 2021-03-16 analyses.Rmd
- update for NM&S submission

@@
 ---
-title: "A Longitudinal Analysis of the Privacy Paradox"
-author: "Tobias Dienlin, Philipp K. Masur, Sabine Trepte"
+title: "A longitudinal analysis of the privacy paradox"
 output: 
@@
 # relevant packages
-devtools::install_github("tdienlin/td@v.0.0.2.5")
+devtools::install_github("tdienlin/td@v0.0.2.6")
 required <- c("GGally", "ggplot2", "kableExtra", "knitr",
@@
 
-In what follows, we report the measures we collected, including their items, factorial validity, reliability, and ICC.
+In what follows, we report the measures we used for our analyses, including their items, factorial validity, reliability, and ICC.
+
+We conducted confirmatory factor analyses to determine the underlying factor structure and to remove items that showed poor measurement properties (see [additional analyses](analyses_additional.Rmd)).
+
 For the measures' longitudinal invariance, see [additional analyses](analyses_additional.Rmd).
@@
 
-1. In general, how concerned are you about your privacy while using the Internet?
-2. Are you concerned about online organizations not being who they claim they are?
-3. Are you concerned about online identity theft?
 4. Are you concerned about people you do not know obtaining personal information about you from your online activities?
@@
 
-1. Financial information (bank data, account balances…)
-2. Medical information (health, medical records…)
-3. Second name
-4. First name
-5. Residence
-6. Street and house number
-7. Email address
-8. Phone number
-9. Photos (of you)
-10. Job (past and present)
-11. Education
+&nbsp; 1. Financial information (bank data, account balances…)  
+&nbsp; 2. Medical information (health, medical records…)  
+&nbsp; 3. Second name  
+&nbsp; 4. First name  
+&nbsp; 5. Residence  
+&nbsp; 6. Street and house number  
+&nbsp; 7. Email address  
+&nbsp; 8. Phone number  
+&nbsp; 10. Job (past and present)  
+&nbsp; 11. Education
 
@@
 corr_plot <- ggpairs(d_fs,
+                     upper = list(continuous = cor_plot),
                      lower = list(continuous = wrap(td::scat_plot, coords = c(1, 5, 1, 5)))) + 

### 2021-03-16 analyses_additional.Rmd
- update for NM&S submission

@@
     code_folding: hide
+    number_sections: true
 ---
@@
 # relevant packages
-devtools::install_github("tdienlin/td@v.0.0.2.5")
+devtools::install_github("tdienlin/td@v0.0.2.6")
 required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
-              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
+              "MissMech", # attention: pkg is obsolete, needs to be installed manually
+              "papaja", "psych", "pwr", "MVN", "semTools", 
               "sjstats", "tidyverse", "td")
@@
 name <- "pri_con"
-d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
+d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"), -contains("_fs"))
 model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
@@
 
-```{r CFA_All}
+```{r CFA_All_ALL}
 name <- "all_vars"
@@
 
+#### Model 7 (longer intervals)
+
+This is like the final model reported in the paper, but with other, that is longer, intervals. Now, waves are separated by 1 year and span until 2018.
+
+We first need to redo the factor scores, because we now have a different sample.
+
+Specifically, we first estimate a model containing all measures, which is then used to extract factor scores.
+
+```{r CFA_All}
+name <- "all_vars"
+model <- '
+# Privacy Concerns
+# create factors
+t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
+t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
+t4_pri_con_f =~ 1*t4_pri_con_f1 + a2*t4_pri_con_f2
+t5_pri_con_f =~ 1*t5_pri_con_f1 + a2*t5_pri_con_f2
+t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
+t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
+t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
+t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09
+t4_pri_con_f1 =~ 1*t4_pri_con_04 + b2*t4_pri_con_05 + b3*t4_pri_con_06
+t4_pri_con_f2 =~ 1*t4_pri_con_07 + c2*t4_pri_con_08 + c3*t4_pri_con_09
+t5_pri_con_f1 =~ 1*t5_pri_con_04 + b2*t5_pri_con_05 + b3*t5_pri_con_06
+t5_pri_con_f2 =~ 1*t5_pri_con_07 + c2*t5_pri_con_08 + c3*t5_pri_con_09
+
+# error covariances
+t5_pri_con_04 ~~ t4_pri_con_04 + t3_pri_con_04 + t1_pri_con_04
+t5_pri_con_05 ~~ t4_pri_con_05 + t3_pri_con_05 + t1_pri_con_05
+t5_pri_con_06 ~~ t4_pri_con_06 + t3_pri_con_06 + t1_pri_con_06
+t5_pri_con_07 ~~ t4_pri_con_07 + t3_pri_con_07 + t1_pri_con_07
+t5_pri_con_08 ~~ t4_pri_con_08 + t3_pri_con_08 + t1_pri_con_08
+t5_pri_con_09 ~~ t4_pri_con_09 + t3_pri_con_09 + t1_pri_con_09
+t4_pri_con_04 ~~ t3_pri_con_04 + t1_pri_con_04
+t4_pri_con_05 ~~ t3_pri_con_05 + t1_pri_con_05
+t4_pri_con_06 ~~ t3_pri_con_06 + t1_pri_con_06
+t4_pri_con_07 ~~ t3_pri_con_07 + t1_pri_con_07
+t4_pri_con_08 ~~ t3_pri_con_08 + t1_pri_con_08
+t4_pri_con_09 ~~ t3_pri_con_09 + t1_pri_con_09
+t3_pri_con_04 ~~ t1_pri_con_04
+t3_pri_con_05 ~~ t1_pri_con_05 
+t3_pri_con_06 ~~ t1_pri_con_06
+t3_pri_con_07 ~~ t1_pri_con_07
+t3_pri_con_08 ~~ t1_pri_con_08
+t3_pri_con_09 ~~ t1_pri_con_09
+
+# factor covariances
+t5_pri_con_f ~~ t1_pri_con_f + t3_pri_con_f + t4_pri_con_f
+t1_pri_con_f ~~ t3_pri_con_f + t4_pri_con_f
+t3_pri_con_f ~~ t4_pri_con_f
+
+# Information Sharing Attitude
+# create factors
+t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + d2*t1_inf_sha_att_f2 + d3*t1_inf_sha_att_f3 + d4*t1_inf_sha_att_f4 + d5*t1_inf_sha_att_f5
+t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + d2*t3_inf_sha_att_f2 + d3*t3_inf_sha_att_f3 + d4*t3_inf_sha_att_f4 + d5*t3_inf_sha_att_f5
+t4_inf_sha_att_f =~ 1*t4_inf_sha_att_f1 + d2*t4_inf_sha_att_f2 + d3*t4_inf_sha_att_f3 + d4*t4_inf_sha_att_f4 + d5*t4_inf_sha_att_f5
+t5_inf_sha_att_f =~ 1*t5_inf_sha_att_f1 + d2*t5_inf_sha_att_f2 + d3*t5_inf_sha_att_f3 + d4*t5_inf_sha_att_f4 + d5*t5_inf_sha_att_f5
+
+t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + e*t1_inf_sha_att_02
+t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + f*t1_inf_sha_att_04
+t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + g*t1_inf_sha_att_06
+t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + h*t1_inf_sha_att_08
+t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + i*t1_inf_sha_att_11
+t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + e*t3_inf_sha_att_02
+t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + f*t3_inf_sha_att_04
+t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + g*t3_inf_sha_att_06
+t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + h*t3_inf_sha_att_08
+t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + i*t3_inf_sha_att_11
+t4_inf_sha_att_f1 =~ 1*t4_inf_sha_att_01 + e*t4_inf_sha_att_02
+t4_inf_sha_att_f2 =~ 1*t4_inf_sha_att_03 + f*t4_inf_sha_att_04
+t4_inf_sha_att_f3 =~ 1*t4_inf_sha_att_05 + g*t4_inf_sha_att_06
+t4_inf_sha_att_f4 =~ 1*t4_inf_sha_att_07 + h*t4_inf_sha_att_08
+t4_inf_sha_att_f5 =~ 1*t4_inf_sha_att_10 + i*t4_inf_sha_att_11
+t5_inf_sha_att_f1 =~ 1*t5_inf_sha_att_01 + e*t5_inf_sha_att_02
+t5_inf_sha_att_f2 =~ 1*t5_inf_sha_att_03 + f*t5_inf_sha_att_04
+t5_inf_sha_att_f3 =~ 1*t5_inf_sha_att_05 + g*t5_inf_sha_att_06
+t5_inf_sha_att_f4 =~ 1*t5_inf_sha_att_07 + h*t5_inf_sha_att_08
+t5_inf_sha_att_f5 =~ 1*t5_inf_sha_att_10 + i*t5_inf_sha_att_11
+
+# factor covariance
+t5_inf_sha_att_f ~~ t1_inf_sha_att_f + t3_inf_sha_att_f + t4_inf_sha_att_f
+t1_inf_sha_att_f ~~ t3_inf_sha_att_f + t4_inf_sha_att_f
+t3_inf_sha_att_f ~~ t4_inf_sha_att_f
+
+# item error covariance
+t5_inf_sha_att_01 ~~ t1_inf_sha_att_01 + t3_inf_sha_att_01 + t4_inf_sha_att_01
+t1_inf_sha_att_01 ~~ t3_inf_sha_att_01 + t4_inf_sha_att_01
+t3_inf_sha_att_01 ~~ t4_inf_sha_att_01
+t5_inf_sha_att_02 ~~ t1_inf_sha_att_02 + t3_inf_sha_att_02 + t4_inf_sha_att_02
+t1_inf_sha_att_02 ~~ t3_inf_sha_att_02 + t4_inf_sha_att_02
+t3_inf_sha_att_02 ~~ t4_inf_sha_att_02
+t5_inf_sha_att_03 ~~ t1_inf_sha_att_03 + t3_inf_sha_att_03 + t4_inf_sha_att_03
+t1_inf_sha_att_03 ~~ t3_inf_sha_att_03 + t4_inf_sha_att_03
+t3_inf_sha_att_03 ~~ t4_inf_sha_att_03
+t5_inf_sha_att_04 ~~ t1_inf_sha_att_04 + t3_inf_sha_att_04 + t4_inf_sha_att_04
+t1_inf_sha_att_04 ~~ t3_inf_sha_att_04 + t4_inf_sha_att_04
+t3_inf_sha_att_04 ~~ t4_inf_sha_att_04
+t5_inf_sha_att_05 ~~ t1_inf_sha_att_05 + t3_inf_sha_att_05 + t4_inf_sha_att_05
+t1_inf_sha_att_05 ~~ t3_inf_sha_att_05 + t4_inf_sha_att_05
+t3_inf_sha_att_05 ~~ t4_inf_sha_att_05
+t5_inf_sha_att_06 ~~ t1_inf_sha_att_06 + t3_inf_sha_att_06 + t4_inf_sha_att_06
+t1_inf_sha_att_06 ~~ t3_inf_sha_att_06 + t4_inf_sha_att_06
+t3_inf_sha_att_06 ~~ t4_inf_sha_att_06
+t5_inf_sha_att_07 ~~ t1_inf_sha_att_07 + t3_inf_sha_att_07 + t4_inf_sha_att_07
+t1_inf_sha_att_07 ~~ t3_inf_sha_att_07 + t4_inf_sha_att_07
+t3_inf_sha_att_07 ~~ t4_inf_sha_att_07
+t5_inf_sha_att_08 ~~ t1_inf_sha_att_08 + t3_inf_sha_att_08 + t4_inf_sha_att_08
+t1_inf_sha_att_08 ~~ t3_inf_sha_att_08 + t4_inf_sha_att_08
+t3_inf_sha_att_08 ~~ t4_inf_sha_att_08
+t5_inf_sha_att_10 ~~ t1_inf_sha_att_10 + t3_inf_sha_att_10 + t4_inf_sha_att_10
+t1_inf_sha_att_10 ~~ t3_inf_sha_att_10 + t4_inf_sha_att_10
+t3_inf_sha_att_10 ~~ t4_inf_sha_att_10
+t5_inf_sha_att_11 ~~ t1_inf_sha_att_11 + t3_inf_sha_att_11 + t4_inf_sha_att_11
+t1_inf_sha_att_11 ~~ t3_inf_sha_att_11 + t4_inf_sha_att_11
+t3_inf_sha_att_11 ~~ t4_inf_sha_att_11
+
+# information sharing behavior
+# create factors
+t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + o2*t1_inf_sha_beh_f2 + o3*t1_inf_sha_beh_f3 + o4*t1_inf_sha_beh_f4 + o5*t1_inf_sha_beh_f5
+t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + o2*t3_inf_sha_beh_f2 + o3*t3_inf_sha_beh_f3 + o4*t3_inf_sha_beh_f4 + o5*t3_inf_sha_beh_f5
+t4_inf_sha_beh_f =~ 1*t4_inf_sha_beh_f1 + o2*t4_inf_sha_beh_f2 + o3*t4_inf_sha_beh_f3 + o4*t4_inf_sha_beh_f4 + o5*t4_inf_sha_beh_f5
+t5_inf_sha_beh_f =~ 1*t5_inf_sha_beh_f1 + o2*t5_inf_sha_beh_f2 + o3*t5_inf_sha_beh_f3 + o4*t5_inf_sha_beh_f4 + o5*t5_inf_sha_beh_f5
+t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + j2*t1_inf_sha_beh_02
+t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + k2*t1_inf_sha_beh_04
+t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + l2*t1_inf_sha_beh_06
+t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + m2*t1_inf_sha_beh_08
+t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + n2*t1_inf_sha_beh_11
+t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + j2*t3_inf_sha_beh_02
+t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + k2*t3_inf_sha_beh_04
+t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + l2*t3_inf_sha_beh_06
+t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + m2*t3_inf_sha_beh_08
+t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + n2*t3_inf_sha_beh_11
+t4_inf_sha_beh_f1 =~ 1*t4_inf_sha_beh_01 + j2*t4_inf_sha_beh_02
+t4_inf_sha_beh_f2 =~ 1*t4_inf_sha_beh_03 + k2*t4_inf_sha_beh_04
+t4_inf_sha_beh_f3 =~ 1*t4_inf_sha_beh_05 + l2*t4_inf_sha_beh_06
+t4_inf_sha_beh_f4 =~ 1*t4_inf_sha_beh_07 + m2*t4_inf_sha_beh_08
+t4_inf_sha_beh_f5 =~ 1*t4_inf_sha_beh_10 + n2*t4_inf_sha_beh_11
+t5_inf_sha_beh_f1 =~ 1*t5_inf_sha_beh_01 + j2*t5_inf_sha_beh_02
+t5_inf_sha_beh_f2 =~ 1*t5_inf_sha_beh_03 + k2*t5_inf_sha_beh_04
+t5_inf_sha_beh_f3 =~ 1*t5_inf_sha_beh_05 + l2*t5_inf_sha_beh_06
+t5_inf_sha_beh_f4 =~ 1*t5_inf_sha_beh_07 + m2*t5_inf_sha_beh_08
+t5_inf_sha_beh_f5 =~ 1*t5_inf_sha_beh_10 + n2*t5_inf_sha_beh_11
+
+# factor covariance
+t5_inf_sha_beh_f ~~ t1_inf_sha_beh_f + t3_inf_sha_beh_f + t4_inf_sha_beh_f
+t1_inf_sha_beh_f ~~ t3_inf_sha_beh_f + t4_inf_sha_beh_f
+t3_inf_sha_beh_f ~~ t4_inf_sha_beh_f
+
+# item error covariance
+t5_inf_sha_beh_01 ~~ t1_inf_sha_beh_01 + t3_inf_sha_beh_01 + t4_inf_sha_beh_01
+t1_inf_sha_beh_01 ~~ t3_inf_sha_beh_01 + t4_inf_sha_beh_01
+t3_inf_sha_beh_01 ~~ t4_inf_sha_beh_01
+t5_inf_sha_beh_02 ~~ t1_inf_sha_beh_02 + t3_inf_sha_beh_02 + t4_inf_sha_beh_02
+t1_inf_sha_beh_02 ~~ t3_inf_sha_beh_02 + t4_inf_sha_beh_02
+t3_inf_sha_beh_02 ~~ t4_inf_sha_beh_02
+t5_inf_sha_beh_03 ~~ t1_inf_sha_beh_03 + t3_inf_sha_beh_03 + t4_inf_sha_beh_03
+t1_inf_sha_beh_03 ~~ t3_inf_sha_beh_03 + t4_inf_sha_beh_03
+t3_inf_sha_beh_03 ~~ t4_inf_sha_beh_03
+t5_inf_sha_beh_04 ~~ t1_inf_sha_beh_04 + t3_inf_sha_beh_04 + t4_inf_sha_beh_04
+t1_inf_sha_beh_04 ~~ t3_inf_sha_beh_04 + t4_inf_sha_beh_04
+t3_inf_sha_beh_04 ~~ t4_inf_sha_beh_04
+t5_inf_sha_beh_05 ~~ t1_inf_sha_beh_05 + t3_inf_sha_beh_05 + t4_inf_sha_beh_05
+t1_inf_sha_beh_05 ~~ t3_inf_sha_beh_05 + t4_inf_sha_beh_05
+t3_inf_sha_beh_05 ~~ t4_inf_sha_beh_05
+t5_inf_sha_beh_06 ~~ t1_inf_sha_beh_06 + t3_inf_sha_beh_06 + t4_inf_sha_beh_06
+t1_inf_sha_beh_06 ~~ t3_inf_sha_beh_06 + t4_inf_sha_beh_06
+t3_inf_sha_beh_06 ~~ t4_inf_sha_beh_06
+t5_inf_sha_beh_07 ~~ t1_inf_sha_beh_07 + t3_inf_sha_beh_07 + t4_inf_sha_beh_07
+t1_inf_sha_beh_07 ~~ t3_inf_sha_beh_07 + t4_inf_sha_beh_07
+t3_inf_sha_beh_07 ~~ t4_inf_sha_beh_07
+t5_inf_sha_beh_08 ~~ t1_inf_sha_beh_08 + t3_inf_sha_beh_08 + t4_inf_sha_beh_08
+t1_inf_sha_beh_08 ~~ t3_inf_sha_beh_08 + t4_inf_sha_beh_08
+t3_inf_sha_beh_08 ~~ t4_inf_sha_beh_08
+t5_inf_sha_beh_10 ~~ t1_inf_sha_beh_10 + t3_inf_sha_beh_10 + t4_inf_sha_beh_10
+t1_inf_sha_beh_10 ~~ t3_inf_sha_beh_10 + t4_inf_sha_beh_10
+t3_inf_sha_beh_10 ~~ t4_inf_sha_beh_10
+t5_inf_sha_beh_11 ~~ t1_inf_sha_beh_11 + t3_inf_sha_beh_11 + t4_inf_sha_beh_11
+t1_inf_sha_beh_11 ~~ t3_inf_sha_beh_11 + t4_inf_sha_beh_11
+t3_inf_sha_beh_11 ~~ t4_inf_sha_beh_11
+
+## Correlations Attitude and Behavior-Items
+t1_inf_sha_beh_01 ~~ t1_inf_sha_att_01
+t1_inf_sha_beh_02 ~~ t1_inf_sha_att_02
+t1_inf_sha_beh_03 ~~ t1_inf_sha_att_03
+t1_inf_sha_beh_04 ~~ t1_inf_sha_att_04
+t1_inf_sha_beh_05 ~~ t1_inf_sha_att_05
+t1_inf_sha_beh_06 ~~ t1_inf_sha_att_06
+t1_inf_sha_beh_07 ~~ t1_inf_sha_att_07
+t1_inf_sha_beh_08 ~~ t1_inf_sha_att_08
+t1_inf_sha_beh_10 ~~ t1_inf_sha_att_10
+t1_inf_sha_beh_11 ~~ t1_inf_sha_att_11
+t3_inf_sha_beh_01 ~~ t3_inf_sha_att_01
+t3_inf_sha_beh_02 ~~ t3_inf_sha_att_02
+t3_inf_sha_beh_03 ~~ t3_inf_sha_att_03
+t3_inf_sha_beh_04 ~~ t3_inf_sha_att_04
+t3_inf_sha_beh_05 ~~ t3_inf_sha_att_05
+t3_inf_sha_beh_06 ~~ t3_inf_sha_att_06
+t3_inf_sha_beh_07 ~~ t3_inf_sha_att_07
+t3_inf_sha_beh_08 ~~ t3_inf_sha_att_08
+t3_inf_sha_beh_10 ~~ t3_inf_sha_att_10
+t3_inf_sha_beh_11 ~~ t3_inf_sha_att_11
+t4_inf_sha_beh_01 ~~ t4_inf_sha_att_01
+t4_inf_sha_beh_02 ~~ t4_inf_sha_att_02
+t4_inf_sha_beh_03 ~~ t4_inf_sha_att_03
+t4_inf_sha_beh_04 ~~ t4_inf_sha_att_04
+t4_inf_sha_beh_05 ~~ t4_inf_sha_att_05
+t4_inf_sha_beh_06 ~~ t4_inf_sha_att_06
+t4_inf_sha_beh_07 ~~ t4_inf_sha_att_07
+t4_inf_sha_beh_08 ~~ t4_inf_sha_att_08
+t4_inf_sha_beh_10 ~~ t4_inf_sha_att_10
+t4_inf_sha_beh_11 ~~ t4_inf_sha_att_11
+t5_inf_sha_beh_01 ~~ t5_inf_sha_att_01
+t5_inf_sha_beh_02 ~~ t5_inf_sha_att_02
+t5_inf_sha_beh_03 ~~ t5_inf_sha_att_03
+t5_inf_sha_beh_04 ~~ t5_inf_sha_att_04
+t5_inf_sha_beh_05 ~~ t5_inf_sha_att_05
+t5_inf_sha_beh_06 ~~ t5_inf_sha_att_06
+t5_inf_sha_beh_07 ~~ t5_inf_sha_att_07
+t5_inf_sha_beh_08 ~~ t5_inf_sha_att_08
+t5_inf_sha_beh_10 ~~ t5_inf_sha_att_10
+t5_inf_sha_beh_11 ~~ t5_inf_sha_att_11
+'
+assign(paste("fit", name, sep = "_"), cfa(model, d_wide_all, missing = "ML"))
+summary(get(paste("fit", name, sep = "_")), standardized = TRUE, fit.measures = TRUE)
+```
+
+Extract factor scores.
+
+```{r}
+d_fs_all <- lavPredict(get(paste("fit", name, sep = "_")), type = "ov") %>% 
+  as.data.frame() %>% 
+  mutate(t1_pri_con_fs = rowMeans(select(., starts_with("t1_pri"))),
+         t3_pri_con_fs = rowMeans(select(., starts_with("t3_pri"))),
+         t4_pri_con_fs = rowMeans(select(., starts_with("t4_pri"))),
+         t5_pri_con_fs = rowMeans(select(., starts_with("t5_pri"))),
+         t1_inf_sha_att_fs = rowMeans(select(., starts_with("t1_inf_sha_att"))),
+         t3_inf_sha_att_fs = rowMeans(select(., starts_with("t3_inf_sha_att"))),
+         t4_inf_sha_att_fs = rowMeans(select(., starts_with("t4_inf_sha_att"))),
+         t5_inf_sha_att_fs = rowMeans(select(., starts_with("t5_inf_sha_att"))),
+         t1_inf_sha_beh_fs = rowMeans(select(., starts_with("t1_inf_sha_beh"))),
+         t3_inf_sha_beh_fs = rowMeans(select(., starts_with("t3_inf_sha_beh"))),
+         t4_inf_sha_beh_fs = rowMeans(select(., starts_with("t4_inf_sha_beh"))),
+         t5_inf_sha_beh_fs = rowMeans(select(., starts_with("t5_inf_sha_beh")))
+         ) %>% 
+  select(contains("_fs"))
+d_wide_all <- cbind(d_fs_all, d_wide_all)
+```
+
+Run new model.
+
+```{r}
+model <- '
+# between relations
+pri_con_b =~ 1*t1_pri_con_fs + 1*t3_pri_con_fs + 1*t4_pri_con_fs + 1*t5_pri_con_fs
+inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs + 1*t4_inf_sha_beh_fs  + 1*t5_inf_sha_beh_fs
+inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t3_inf_sha_att_fs + 1*t4_inf_sha_att_fs + 1*t5_inf_sha_att_fs
+
+# within person changes
+t1_pri_con_w =~ 1*t1_pri_con_fs
+t3_pri_con_w =~ 1*t3_pri_con_fs
+t4_pri_con_w =~ 1*t4_pri_con_fs
+t5_pri_con_w =~ 1*t5_pri_con_fs
+t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
+t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
+t4_inf_sha_beh_w =~ 1*t4_inf_sha_beh_fs
+t5_inf_sha_beh_w =~ 1*t5_inf_sha_beh_fs
+t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
+t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs
+t4_inf_sha_att_w =~ 1*t4_inf_sha_att_fs
+t5_inf_sha_att_w =~ 1*t5_inf_sha_att_fs
+
+# within person effects
+t3_pri_con_w ~ a1*t1_pri_con_w + a2*t1_inf_sha_att_w + a3*t1_inf_sha_beh_w
+t3_inf_sha_att_w ~ b1*t1_pri_con_w + b2*t1_inf_sha_att_w + b3*t1_inf_sha_beh_w
+t3_inf_sha_beh_w ~ c1*t1_pri_con_w + c2*t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
+t4_pri_con_w ~ a1*t3_pri_con_w + a2*t3_inf_sha_att_w + a3*t3_inf_sha_beh_w
+t4_inf_sha_att_w ~ b1*t3_pri_con_w + b2*t3_inf_sha_att_w + b3*t3_inf_sha_beh_w
+t4_inf_sha_beh_w ~ c1*t3_pri_con_w + c2*t3_inf_sha_att_w + c3*t3_inf_sha_beh_w
+t5_pri_con_w ~ a1*t4_pri_con_w + a2*t4_inf_sha_att_w + a3*t4_inf_sha_beh_w
+t5_inf_sha_att_w ~ b1*t4_pri_con_w + b2*t4_inf_sha_att_w + b3*t4_inf_sha_beh_w
+t5_inf_sha_beh_w ~ c1*t4_pri_con_w + c2*t4_inf_sha_att_w + c3*t4_inf_sha_beh_w
+
+# covariances
+pri_con_b ~~ cor_b_1*inf_sha_att_b + cor_b_2*inf_sha_beh_b
+inf_sha_att_b ~~ cor_b_3*inf_sha_beh_b
+t1_pri_con_w ~~ cor_w_1*t1_inf_sha_att_w + cor_w_2*t1_inf_sha_beh_w
+t1_inf_sha_att_w ~~ cor_w_3*t1_inf_sha_beh_w
+t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
+t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
+t4_pri_con_w ~~ a*t4_inf_sha_att_w + b*t4_inf_sha_beh_w
+t4_inf_sha_att_w ~~ c*t4_inf_sha_beh_w
+t5_pri_con_w ~~ a*t5_inf_sha_att_w + b*t5_inf_sha_beh_w
+t5_inf_sha_att_w ~~ c*t5_inf_sha_beh_w
+
+# setting variances of observed variables to zero
+t1_pri_con_fs ~~ 0*t1_pri_con_fs
+t3_pri_con_fs ~~ 0*t3_pri_con_fs
+t4_pri_con_fs ~~ 0*t4_pri_con_fs
+t5_pri_con_fs ~~ 0*t5_pri_con_fs
+t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
+t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
+t4_inf_sha_att_fs ~~ 0*t4_inf_sha_att_fs
+t5_inf_sha_att_fs ~~ 0*t5_inf_sha_att_fs
+t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
+t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs
+t4_inf_sha_beh_fs ~~ 0*t4_inf_sha_beh_fs
+t5_inf_sha_beh_fs ~~ 0*t5_inf_sha_beh_fs
+
+# control variables
+t1_pri_con_fs ~ age + edu_num + male
+t3_pri_con_fs ~ age + edu_num + male
+t4_pri_con_fs ~ age + edu_num + male
+t5_pri_con_fs ~ age + edu_num + male
+t1_inf_sha_beh_fs ~ age + edu_num + male
+t3_inf_sha_beh_fs ~ age + edu_num + male
+t4_inf_sha_beh_fs ~ age + edu_num + male
+t5_inf_sha_beh_fs ~ age + edu_num + male
+t1_inf_sha_att_fs ~ age + edu_num + male
+t3_inf_sha_att_fs ~ age + edu_num + male
+t4_inf_sha_att_fs ~ age + edu_num + male
+t5_inf_sha_att_fs ~ age + edu_num + male
+'
+fit <- sem(model, data = d_wide_all, orthogonal = TRUE, missing = "ML")
+summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
+fit_riclpm_5w <- fit
+```
+
+The results show the same between person effects.
+Within-person effects disappear, which is understandable given the longer interval.
+Effects hence remain stable also across longer time intervals and until 2018.
+
 ## Mixed Models

### 2021-03-16 index.Rmd
- update for NM&S submission

@@
 ---
-title: "Longitudinal Analysis of the Privacy Calculus"
+title: "A longitudinal analysis of the privacy paradox"
 ---
 
-On this website, you can find the companion material for the paper _A Longitudinal Analysis of the Privacy Paradox_.
+On this website, you can find the companion material for the paper _A longitudinal analysis of the privacy paradox_.
 
@@
 
-Please note that this OSM does not contain the actual data, which can be downloaded from http://dx.doi.org/10.7802/1937.
+Please note that this OSM does not contain the actual data, which can be downloaded [here](http://dx.doi.org/10.7802/1937).
 
-This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy_calc_exp). You can download the material, file an issue, or submit a pull request.
+This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy-paradox-longitudinal).
+You can download the material, file an issue, or submit a pull request.

### 2021-03-16 items.Rmd
- update for NM&S submission

@@
 
-1. In general, how concerned are you about your privacy while using the Internet?
-2. Are you concerned about online organizations not being who they claim they are?
-3. Are you concerned about online identity theft?
-4. Are you concerned about people you do not know obtaining personal information about you from your online activities?
-5. Are you concerned that if you use your credit card to buy something on the Internet your credit card number will be obtained/intercepted by someone else?
-6. Are you concerned that an email you sent may be read by someone else besides the person you sent it to?
-7. Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing on the Internet?
-8. Are you concerned that website providers are tracking your online activities?
-9. Are you concerned that you don’t know what other organizations or website providers are doing with you data?
+ - Are you concerned about people you do not know obtaining personal information about you from your online activities?
+ - Are you concerned that if you use your credit card to buy something on the Internet your credit card number will be obtained/intercepted by someone else?
+ - Are you concerned that an email you sent may be read by someone else besides the person you sent it to?
+ - Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing on the Internet?
+ - Are you concerned that website providers are tracking your online activities?
+ - Are you concerned that you don’t know what other organizations or website providers are doing with you data?
 
@@
 
-1. Financial information (bank data, account balances…)
-2. Medical information (health, medical records…)
-3. Second name
-4. First name
-5. Residence
-6. Street and house number
-7. Email address
-8. Phone number
-9. Photos (of you)
-10. Job (past and present)
-11. Education
+ - Financial information (bank data, account balances…)
+ - Medical information (health, medical records…)
+ - Second name
+ - First name
+ - Residence
+ - Street and house number
+ - Email address
+ - Phone number
+ - Job (past and present)
+ - Education
 
@@
 
-1. Financial information (bank data, account balances…)
-2. Medical information (health, medical records…)
-3. Second name
-4. First name
-5. Residence
-6. Street and house number
-7. Email address
-8. Phone number
-9. Photos (of you)
-10. Job (past and present)
-11. Education
+ -  Financial information (bank data, account balances…)
+ -  Medical information (health, medical records…)
+ -  Second name
+ -  First name
+ -  Residence
+ -  Street and house number
+ -  Email address
+ -  Phone number
+ -  Job (past and present)
+ -  Education
 

### 2021-03-16 manuscript.RmD
- update for NM&S submission

@@
 ---
-title             : "A Longitudinal Analysis of the Privacy Paradox" 
-shorttitle        : "Longitudinal Analysis of the Privacy Paradox"
+title             : "A longitudinal analysis of the privacy paradox" 
+shorttitle        : "A longitudinal analysis of the privacy paradox"
 author:            
   - name          : "Tobias Dienlin"
-    email         : "tobias.dienlin@uni-hohenheim.de"
+    email         : "tobias.dienlin@univie.ac.at"
     affiliation   : "1"
-    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
+    address       : "University of Vienna, Department of Communication, 1090 Vienna, Austria"
+  - name          : "Philipp K. Masur"
+    email         : "p.k.masur@vu.nl"
+    affiliation   : "2"
     corresponding : yes
-  - name          : "Philipp K. Masur"
-    email         : "philipp.masur@uni-mainz.de"
-    affiliation   : "2"
   - name          : "Sabine Trepte"
     email         : "sabine.trepte@uni-hohenheim.de"
-    affiliation   : "1"
+    affiliation   : "3"
 affiliation:
-
   - id            : "1"
+    institution   : "University of Vienna"
+  - id            : "2"
+    institution   : "VU Amsterdam"
+  - id            : "3"
     institution   : "University of Hohenheim"
-  - id            : "2"
-    institution   : "Johannes Gutenberg University Mainz"
-author_note: |
+authornote: |
   All authors contributed extensively to the work presented in this paper.
@@
   This manuscript features a companion website that includes detailed summaries of the statistical results, the code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy-paradox-longitudinal).
-The data can be downloaded from http://dx.doi.org/10.7802/1937.
+The data can be downloaded from http://dx.doi.org/10.7802/1937
+
 abstract: |
-  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
-  On the basis of a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective.
+  The privacy paradox states that people’s concerns about online privacy are unrelated to their online sharing of personal information.
+On the basis of a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective.
 Using a cross-lagged panel model with random intercepts, we differentiate between-person relations from within-person effects.
@@
 We found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
-  The results provide further evidence against the privacy paradox, but more research is needed to better understand the variables' potential causal relations.
+The results provide further evidence against the privacy paradox, but more research is needed to better understand potential causal relations.
 keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
@@
 lineno            : yes
-bibliography      : 
-  - [bibliography/references.bib]
-  - [bibliography/r-references.bib]
-lang              : "english"
 class             : "man"
@@
 # (c) comment lines after "output: html_document ..."
-# output            : papaja::apa6_pdf
-# header-includes:
-#   - \setlength{\parskip}{0em}
-#   - \raggedbottom
-output:
-  html_document:
-    toc: TRUE
-    toc_float:
-      collapsed: FALSE
-    toc_depth: 2
+output            : papaja::apa6_pdf
+header-includes:
+  - \setlength{\parskip}{0em}
+  - \raggedbottom
+# output:
+#   html_document:
+#     toc: TRUE
+#     toc_float:
+#       collapsed: FALSE
+#     toc_depth: 2
+bibliography      : 
+  - [bibliography/references.bib]
+  - [bibliography/r-references.bib]
+csl               : "sage-harvard.csl"
 ---
@@
 # Load and install packages
-# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncommen to install
-packages <- c("broman", "kableExtra", "knitr", "lavaan", "magrittr", "papaja"
+# devtools::install_github("tdienlin/td@v.0.0.2.4")  # uncomment to install
+# devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE) # uncomment to install
+# devtools::install_github("crsh/papaja")  # uncomment to install
+# devtools::install_github("cran/MissMech")
+packages <- c("broman", "GGally", "kableExtra", "knitr", "lavaan", "magrittr", "papaja"
              , "psych", "pwr", "td", "tidyverse", "semTools", "scales")
@@
 
-# Introduction
+<!-- # Introduction -->
 
@@
 This mismatch is problematic because although between-person relations are, except for some special cases, a _necessary_ condition for causal within-person effects, they are by no means a _sufficient_ one.
-For example, it could be that the between-person relation is determined other third variables. 
+For example, it could be that the between-person relation is determined by other third variables. 
 Hence, as the next step in investigating the privacy paradox and to better understand the causal relation between privacy concerns and information sharing, it is necessary to conduct studies with within-person designs.
@@
 First, on a between-person level, how are concerns about online privacy related to the online sharing of personal information? 
-Second, on a within-person level, does information sharing decrease when concerns increase?
+Second, on a within-person level, is information sharing lower than usual when concerns are higher than usual?
 Third, what are the potential long-term effects?
@@
 On the basis of 37 studies, @baruhOnlinePrivacyConcerns2017 found a small and significant statistical relation between concerns about online privacy and online information sharing (_r_ = -.13, 95% CI [-.07, -.18]).
-Another more recent meta analysis by @yuMetaanalysisExplorePrivacy2020 also finds a significant bivariate relation between privacy concerns and information sharing, albeit smaller (_r_ = -.06, 95% CI [-.01, -.12]]).
+Another more recent meta analysis by @yuMetaanalysisExplorePrivacy2020 also finds a significant bivariate relation between privacy concerns and information sharing, albeit smaller (_r_ = -.06, 95% CI [-.01, -.12]).
 There also exist several systematic literature reviews on the privacy paradox [@barthPrivacyParadoxInvestigating2017; @gerberExplainingPrivacyParadox2018; @kokolakisPrivacyAttitudesPrivacy2017].
@@
 
-<!-- In conclusion, large parts of the current literature suggests that a significant relation between concerns about online privacy and the online sharing of personal information exists and that it is small---which speaks against the privacy paradox.
--->
-
 ## Defining Privacy Concerns and Information Sharing
@@
 Privacy captures aspects of both volitional _control_ and social _separateness_ [@braunlichLinkingLooseEnds2020; @marwickNetworkedPrivacyHow2014].
+People from all cultural backgrounds require privacy to fulfill fundamental needs including personal care, protected communication, intimacy, or sexuality [@altmanPrivacyRegulationCulturally1977; @westinPrivacyFreedom1967].
+Being a universal human right [@assembly1948universal, Art. 12], privacy is essential for safety, psychosocial flourishing, and dignity.
+It is driven by both individual needs and interpersonal negotiations thereof [@trepteSocialMediaPrivacy2020].
+
 Several dimensions of privacy have been proposed.
@@
 When it comes to concerns in general, interestingly they do not seem to be established as a stand-alone theoretical concept in psychology [@colmanDictionaryPsychology2015].
-Lexically, concerns are defined as a "marked interest or regard usually arising through a personal tie or relationship" that also reflect an "uneasy state of blended interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
-Concerns therefore represent both a latent _motivation_ (or increased attention), a negatively valenced _emotion_ (or affective condition), and are mostly implicit.
+Concerns are usually understood as an uneasy mix of "interest, uncertainty, and apprehension" [@merriam-websterDefinitionConcern2018].
 As a theoretical construct, privacy concerns can hence be categorized as an affective motivational disposition.
-As such, there are many similarities with other concepts, including emotions (e.g., fear, anxiety), moods (e.g., dismay, fatigue), attitudes (risk perception, approval), values (e.g., autonomy, freedom), personality traits (e.g., introversion, risk avoidance), and even physiological activation (e.g., attention, arousal).
 Taken together, concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened.
 
-The online sharing of personal information, on the other hand, captures how much person-related information people share when they use the Internet, including information about their age, sex, name, address, health, and finances.
+The online sharing of personal information, on the other hand, captures how much person-related information people share when they use the Internet.
 Information sharing can be differentiated from communication and self-disclosure.
 Communication is broad, because it comprises all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011].
-Self-disclosure is narrow, because it focuses on deliberate revelations about the true self to others [e.g., @jourardTransparentSelf1964].
-Information sharing is even more specific, because it addresses only person-related information but ignores other types of self-disclosure such as personal fears, values, or plans.
+Self-disclosure is more narrow, because it focuses on deliberate revelations about the true self to others, which including aspects such as personal fears, values, or plans [e.g., @jourardTransparentSelf1964].
+Information sharing is even more specific, because it addresses only person-related information,  including information about their age, sex, name, address, health, and finances.
+
+In what follows we hence investigate the two concepts of (a) concerns about online privacy and (b) online information sharing, aiming to investigate how they relate conceptually.
+In doing so, we adopt and focus on the perspective of individual people.
 
@@
 By causing fight, flight, or freeze reactions, they are a primordial trigger of behavior and are considered to be an adaptive mechanism of evolved species [@dolanEmotionCognitionBehavior2002].
-<!-- With their direct link to the amygdala, emotions can trigger reactions already subcortically [i.e., without activation of the more recently evolved cortical structures; @dolanEmotionCognitionBehavior2002].
--->
 
-Also empirically, concerns have been shown to affect behavior. 
-People more concerned about the environment show more environment-related behaviors [@bambergHowDoesEnvironmental2003].
-People more concerned about their appearance consume fewer calories [@hayesConcernAppearanceHealth1987].
-People more concerned about their bodies engage in more physical exercise [@reelRelationsBodyConcerns2007].
+Also empirically, concerns have been shown to affect behavior [@hayesConcernAppearanceHealth1987; @reelRelationsBodyConcerns2007]. 
+For example, people more concerned about the environment show more environment-related behaviors [@bambergHowDoesEnvironmental2003].
 Taken together, it is reasonable to expect that also concerns about online privacy should somehow reflect in the online sharing of personal information.
@@
 Other factors such as subjective norms and perceived behavioral control also determine behavior [@ajzenIntentionsActionsTheory1985], which automatically reduces the impact of attitudes or concerns.
+
 Specifically, two of the most influential factors that affect online information sharing are (a) strong subjective norms [@heirmanPredictingAdolescentsDisclosure2013] and (b) expected benefits [@krasnovaOnlineSocialNetworks2010].
 In other words, users often prioritize social support, special offers, or improved services, accepting that their privacy will be diminished.
+Sometimes, privacy concerns do not relate information sharing, because users lack the skills, knowledge, or literacy to change their online behavior, creating feelings of apathy or cynicism [@hargittaiWhatCanReally2016; @hoffmannPrivacyCynicismNew2016].
+Likewise, personal information is also often shared by others, a phenomenon described as "networked privacy" [@marwickNetworkedPrivacyHow2014], which further reduces the power of individuals to determine how much personal information can be found online.
 @trepteRiskyBehaviorsHow2014 listed several factors that can additionally attenuate the relation:
@@
 or situational constraints due to social desirability.
-In conclusion, also in the context of the privacy paradox it _not_ reasonable to expect a _perfect_ relation between attitudes and behaviors.
+In conclusion, also in the context of the privacy paradox it is _not_ reasonable to expect a _perfect_ relation between attitudes and behaviors.
 However, we should still expect to find a relation that is _small_ or _moderate_.
@@
 
-In conclusion, in line with prior research and the within-person rationales presented above, we expect to find a small significant relation between privacy concerns and information sharing, both on the between-person level and the within-person level.
+In conclusion, we expect to find a small significant relation between privacy concerns and information sharing, both on the between-person level (Hypothesis 1) and the within-person level (Hypothesis 2).[^1]
 
@@
 Hypothesis 2: People who are more concerned about their online privacy than they usually are will also share less personal information online than they usually do.
+
+[^1]: To explain, with Hypothesis 1, we compare _different_ people with one another by analyzing their _average_ values across all measurements.
+In other words, does a person, who is generally more concerned than others, also generally share less information than others?
+With Hypothesis 2, we compare _specific_ measurements within the _same_ person.
+In other words, does a person, if he/she is more concerned on T1 than on average, share more or less information on T1 than on average?
 
@@
 The underlying theoretical mechanism could be that the emotional part of privacy concerns causes (a) motivated information selection and (b) motivated information processing, which is likely to change actual behavior [@nabiCognitivefunctionalModelEffects1999].
-Specifically, when privacy concerns increase (e.g., because of experienced or witnessed privacy infringements), people might begin reading more media articles on privacy issues and might also consume these articles more carefully, which could prompt information sharing practices that are more cautious.
+Specifically, when privacy concerns are higher than usual (e.g., because of experienced or witnessed privacy infringements), people might begin reading more media articles on privacy issues and might also consume these articles more carefully, which could prompt information sharing practices that are more cautious.
 Also empirically, a study with 290 participants found small negative longitudinal (between-person) relations between privacy concerns and self-disclosure [@koohikamaliInvestigationDynamicModel2019].
@@
 People might have already become used to sharing information online, which stifles further cognitive or emotional processing.
-This rationale is central to so-called _privacy cynicism_ [e.g., @hoffmannPrivacyCynicismNew2016].
+This rationale is central to _privacy cynicism_ [e.g., @hoffmannPrivacyCynicismNew2016].
 
@@
 It has been argued that privacy attitudes could bridge the gap between concerns and information sharing [e.g., @dienlinPrivacyParadoxRelic2015]. 
-In contrast to privacy concerns, privacy attitudes capture a more explicit, fluctuating cognitive appraisal [@tsay-vogelSocialMediaCultivating2018].
-Although both variables are related to information disclosure, attitudes are likely the better predictor. 
-This reasoning follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always at least partially influenced by convictions, attitudes, and cost-benefit analyses.
-Also empirically, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure was only moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].
+In contrast to general and implicit privacy concerns, privacy attitudes capture a more explicit, specific cognitive appraisal [@tsay-vogelSocialMediaCultivating2018]. 
+Because general dispositions oftentimes affect more specific appraisals [@fishbeinPredictingChangingBehavior2010], general concerns about privacy may similarly affect more specific privacy attitudes [@dienlinPrivacyParadoxRelic2015].
+This reasoning follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always at least partially influenced by specific convictions, attitudes, and cost-benefit analyses.
+Therefore, although both variables are related to information disclosure, attitudes are likely the better predictor. 
+Also empirically, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure intentions of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure intentions was only moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].
 
@@
 # Method
-## Statistics
-
-We follow the recommendation by @lakensJustifyYourAlpha2018 and first justify the choice of our alpha level. 
-We determined adequate error margins by considering the potential implications of both false positive and false negative findings (i.e., alpha and beta errors): 
-On the one hand, if we committed an alpha error, we would wrongfully conclude that people's concerns and behaviors are consistent. 
-Communicating such a false result to the public might unjustly reassure people when they should be more alert.
-On the other hand, if we committed a beta error, we would wrongfully conclude that individuals behave paradoxically.
-Communicating such a false result would unjustly accuse people of implausible behavior, potentially causing unnecessary distress or reactance.
-We consider both errors to be equally detrimental. 
-Hence, we chose balanced error rates, setting a maximum error rate of 5% for both alpha and beta. 
-As the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses.
-Significantly smaller effects were not considered able to offer support.
-The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
-On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi %>% my_round("beta")`, we calculated a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents.
-Given the final sample size of `r dollar_format(prefix = "")(n)` respondents (see below), alpha and beta errors were balanced for our hypotheses (research questions) when we used a critical alpha of `r alpha_balanced_h  %>% round(3) * 100`% (`r alpha_balanced_rq  %>% round(3) * 100`%), resulting in a power of `r power_balanced_h %>% round(3) * 100`%  (`r power_balanced_rq %>% round(3) * 100`%) to detect small effects.
-
-```{r RICLPM, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM).", fig.align="center"}
-knitr::include_graphics("figures/model_7.png")
-```
-
-The data were analyzed using of a random-intercept cross-lagged panel model [RI-CLPM, @hamakerCritiqueCrosslaggedPanel2015].
-For a visualization, see Figure \@ref(fig:RICLPM).
-Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs can separate between-person variance from within-person variance. 
-We used factor scores as observed variables to represent the variables' latent structure more closely.
-We tested H1, H3.1, and H3.2 by correlating the random intercepts, which represent the respondents' individual mean scores across all three waves.
-We tested H2, H4.1, and H4.2 by correlating the respondents' within-person variance at T1, which captures their specific deviation at T1 from their overall score.
-We tested all research questions by regressing variables on all other measures obtained 6 months earlier.
-Given that we had three points of measurement, this resulted in two estimates for each research question.
-As we did not assume longitudinal effects to differ across time, they were constrained to be equal across all waves, which produces one single general measure of each effect instead of two time-specific ones.
-(We later tested this assumption empirically.
-As expected, the model with constrained effects did not show significantly reduced model fit, $\chi$^2^(`r model_comp[2, 6]`) = `r model_comp[2, 7] %>% my_round("p")`, _p_ = `r model_comp[2, 5] %>% my_round("est")`, which supports that effects did not change over time.)
-Fit was assessed according to the common criteria as described by @klinePrinciplesPracticeStructural2016. 
-The final model fit the data well, `r fit_txt(fit_riclpm)`.
-
-For the analyses, we used `r r_citations`.
-The code, additional analyses, and a reproducible version of this manuscript can be found on the manuscript's companion website at https://tdienlin.github.io/privacy-paradox-longitudinal.
-
 ## Procedure and Respondents
@@
 This study is part of a large-scale project which investigates the development of privacy and self-disclosure, including several other variables. 
-Other publications linked to the project can be accessed at https://osf.io/y35as/.
+Other publications linked to the project can be accessed at [link blinded during review].
 The data come from a longitudinal paper-and-pencil questionnaire study, in which a representative sample of the German population (16 years and older) was surveyed on overall five occasions.
-The data can be downloaded from http://dx.doi.org/10.7802/1937.
+The data can be downloaded from [link blinded during review].
 
@@
 Privacy concerns were measured as a second-order factor. 
-Three items captured the vertical dimension (e.g., "How concerned are you that institutions or intelligence services collect and analyze data that you disclosed on the Internet?"), and three items captured the horizontal dimension (e.g., "How concerned are you that people that you do not know might obtain information about you because of you online activities?").
+Three self-developed items captured the vertical dimension (e.g., "How concerned are you that institutions or intelligence services collect and analyze data that you disclosed on the Internet?"), and three items by @buchananDevelopmentMeasuresOnline2007 captured the horizontal dimension (e.g., "How concerned are you that people that you do not know might obtain information about you because of you online activities?").
 Respondents rated all items on a 5-point scale ranging from 1 (*not at all concerned*) to 5 (*very concerned*). 
@@
 
-To measure respondent's level of information disclosure, they were asked how often they disclosed 10 different pieces of information on the Internet. 
+To measure respondent's level of information disclosure, they were asked how often they disclosed 10 different pieces of information on the Internet [@europeancommissionAttitudesDataProtection2011]. 
 The exact question was: "How often do you disclose the following pieces of information online (i.e., on the Internet)?" 
@@
 
-Respondents' attitudes toward disclosing personal information online were captured with 10 items that measured the general appraisal of disclosing the same 10 pieces of information. 
+Respondents' attitudes toward disclosing personal information online were captured with 10 items that measured the general appraisal of disclosing the same 10 pieces of information [@europeancommissionAttitudesDataProtection2011].
 Adhering to the principle of compatibility [@fishbeinPredictingChangingBehavior2010], the items were parallel to those of the actual disclosure scale. 
@@
 Overall, `r icc_inf_sha_att$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.
+
+## Data Analysis
+
+We follow the recommendation by @lakensJustifyYourAlpha2018 and first justify the choice of our alpha level. 
+We determined adequate error margins by considering the potential implications of both false positive and false negative findings (i.e., alpha and beta errors): 
+On the one hand, if we committed an alpha error, we would wrongfully conclude that people's concerns and behaviors are consistent. 
+Communicating such a false result to the public might unjustly reassure people when they should be more alert.
+On the other hand, if we committed a beta error, we would wrongfully conclude that individuals behave paradoxically.
+Communicating such a false result would unjustly accuse people of implausible behavior, potentially causing unnecessary distress or reactance.
+We consider both errors to be equally detrimental. 
+Hence, we chose balanced error rates, setting a maximum error rate of 5% for both alpha and beta. 
+As the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses.
+Significantly smaller effects were not considered able to offer support.
+The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
+On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi %>% my_round("beta")`, we calculated a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents.
+Given the final sample size of `r dollar_format(prefix = "")(n)` respondents, alpha and beta errors were balanced for our hypotheses (research questions) when we used a critical alpha of `r alpha_balanced_h  %>% round(3) * 100`% (`r alpha_balanced_rq  %>% round(3) * 100`%), resulting in a power of `r power_balanced_h %>% round(3) * 100`%  (`r power_balanced_rq %>% round(3) * 100`%) to detect small effects.
+
+```{r RICLPM, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM).", fig.align="center"}
+knitr::include_graphics("figures/model_7.png")
+```
+
+The data were analyzed using of a random-intercept cross-lagged panel model [RI-CLPM, @hamakerCritiqueCrosslaggedPanel2015].
+For a visualization, see Figure \@ref(fig:RICLPM).
+Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs can separate between-person variance from within-person variance. 
+We used factor scores as observed variables to represent the variables' latent structure more closely.
+We tested H1, H3.1, and H3.2 by correlating the random intercepts, which represent the respondents' individual mean scores across all three waves.
+We tested H2, H4.1, and H4.2 by correlating the respondents' within-person variance at T1, which captures their specific deviation at T1 from their overall score.
+We tested all research questions by regressing variables on all other measures obtained 6 months earlier.
+Given that we had three points of measurement, this resulted in two estimates for each research question.
+As we did not assume longitudinal effects to differ across time, they were constrained to be equal across all waves, which produces one single general measure of each effect instead of two time-specific ones.
+(We later tested this assumption empirically.
+As expected, the model with constrained effects did not show significantly reduced model fit, $\chi$^2^(`r model_comp[2, 6]`) = `r model_comp[2, 7] %>% my_round("p")`, _p_ = `r model_comp[2, 5] %>% my_round("est")`, which supports that effects did not change over time.)
+Fit was assessed according to the common criteria as described by @klinePrinciplesPracticeStructural2016. 
+The final model fit the data well, `r fit_txt(fit_riclpm)`.
+
+For the analyses, we used `r r_citations`.
+The code, additional analyses (e.g., ICCs or analyses of invariance), and a reproducible version of this manuscript can be found on the manuscript's companion website at https://xmtra.github.io/privacy-paradox.
 
@@
 
+In an additional analysis, we also tested the same model with a 1 year interval, which allowed to include data spanning until winter 2016 and 2017.
+Most effects remained the same.
+For example, we again found that people more concerned than others were less positive regarding information sharing (_r_ = -.36, _p_ < .001 ) and shared less information (_r_ = -.15, _p_ = .002). 
+Likewise, people more positive toward data sharing than others also shared substantially more data (_r_ = .66, _p_ < .001).
+Because including these two additional waves significantly reduces sample size, and because we consider it more likely that effects take place more immediately, these results should be considered exploratory.
+For an overview of the results, see the additional analyses on our companion website (Section 2.1.2.7).
+
 # Discussion
@@
 Taken together, the cross-sectional results are in line with the extant literature:
-The between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fall within the 95% confidence interval of the effect reported by @baruhOnlinePrivacyConcerns2017 (i.e., _r_ = -.13, 95% CI [-.07, -.18]).
-Note that the between-person correlations reported here represent averaged measurements across three waves, which makes the findings more robust than typical one-shot measures.
+The between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.09) fall within the 95% confidence interval of the effect reported by @baruhOnlinePrivacyConcerns2017 (i.e., _r_ = -.13, 95% CI [-.07, -.18]).
+Notably, the between-person correlations reported here represent averaged measurements across three waves, which makes the findings more robust than typical one-shot measures.
 
@@
 
-The within-person results showed that when a person's privacy concerns increased, the same person also shared slightly less information online than usual.
+The within-person results showed that when a person's privacy concerns are higher than usual, the same person also shared slightly less information online than usual.
 Moreover, people who developed more positive attitudes toward the online sharing of personal information than usual, also shared substantially more personal information online.
@@
 
+The data were collected between May 2014 and May 2015---hence, after the Snowden revelations in 2013, but before the Equifax data breach in 2017, the Cambridge Analytica data breach in 2018, or the implementation of the General Data Protection Regulation in 2018.
+Such sweeping events, however, could affect privacy concerns, online behavior, or their mutual relation, which would limit the generalizability of our results. 
+Although this is an important caveat, we have reason to believe that our findings are largely robust. 
+First, additional analyses showed that the within-person relationships were stable across waves (a period of 1 year). 
+Second, another set of additional analyses showed that most effects remained stable until winter 2017.
+Third, records of online search terms revealed that although interest in privacy-related topics and privacy-enhancing technologies increased after the Snowden revelations, it returned to prior levels after only two weeks [@preibuschPrivacyBehaviorsSnowden2015].
+It thus seems that levels of privacy concerns and information sharing, as well as their mutual relationship, are largely robust.
+
+In asking how much information respondents share when using the Internet in general, we automatically aggregated different platforms, contexts, and situations.
+However, privacy mechanisms can differ largely across contexts [@nissenbaumPrivacyContextTechnology2010] and situations [@masurSituationalPrivacySelfdisclosure2018].
+Our broad perspective, therefore, is somewhat problematic and limits our capacity to understand and predict the behavior of individual people in specific situations.
+At the same time, aiming to maximize generalizability, we were able to extract some general underlying patterns, which can serve as a starting point for more contextualized analyses (see below).
+
 Some of the effect sizes reported in this study are potentially not large enough to refute the privacy paradox completely. 
@@
 204], which states that all psychosocial measures are related to one another to some extent.
-On the other hand, other factors such as expected benefits might play a more important role [@dienlinExtendedPrivacyCalculus2016].
+On the other hand, additional factors such as expected benefits might play a more important role [@dienlinExtendedPrivacyCalculus2016].
 In conclusion, although our results suggest that privacy concerns and privacy attitudes are correlated with information sharing, the importance of privacy concerns should not be exaggerated.
@@
 However, self-reports of frequent and routine behaviors are often imprecise and unreliable [@scharkowAccuracySelfreportedInternet2016]. 
-This represents a profound limitation of our study. 
-Whenever possible, future studies should aim to collect objective observations of behavior.
+This represents a profound limitation of our study; whenever possible, future studies should aim to collect objective observations of specific types of behavior.
 
@@
 
-Evidence of within-person longitudinal effects is still missing. 
+We emphasize that when analyzing the privacy paradox we are likely dealing with small effects [@baruhOnlinePrivacyConcerns2017].
+Hence, to detect these small effects reliably we need large samples. 
+This is often not the case [@baruhOnlinePrivacyConcerns2017].
+In conclusion, it is crucial to use statistical designs that allow for sufficient statistical power.
+
+Next, evidence of within-person longitudinal effects is still missing. 
 Although we found significant within-person correlations at T1, they were absent across the 6-month intervals.
@@
 
+In general, we emphasize that our findings should not be overgeneralized. 
+They are conditional on the data we collected, the methods we applied, and the theoretical perspectives we adopted. 
+We stress that analyzing the privacy paradox in other contexts using alternative approaches will likely lead to different results.
 Although we argue that in most circumstances privacy concerns and behavior should correlate modestly, the exact extent depends on a many boundary conditions.
-Future research should hence explicitly analyze different contexts and situations. 
+Future research should hence explicitly analyze different contexts [@nissenbaumPrivacyContextTechnology2010] and situations [@masurSituationalPrivacySelfdisclosure2018]. 
 Building on @kokolakisPrivacyAttitudesPrivacy2017, we suggest to analyze the following boundary conditions:
@@
  - Type of information (e.g., sensitive vs. superficial, biographic, or person-related);
- - Benefit immediacy and risk diffusion (high vs. low).
+ - Benefit immediacy and risk diffusion (high vs. low);
+ - Object of investigation (e.g., individual people, interactions between people, developmental perspectives, critical incidents, societal structures, or historical developments).
 
 Specifically, we encourage analyzing privacy behaviors also from a situational perspective, accounting for temporal needs, interpersonal perceptions, contextual cues, or characteristics of communication channels [@masurSituationalPrivacySelfdisclosure2018].
-For example, whereas general levels of information sharing are likely best explained by using privacy _concerns_, situational information sharing might be best explained by using privacy _heuristics_ [@sundarUnlockingPrivacyParadox2013].
+For example, whereas general levels of information sharing are likely best explained using privacy _concerns_, situational information sharing might be best explained using privacy _heuristics_ [@sundarUnlockingPrivacyParadox2013].
 
@@
 
- - Analysis design (e.g., theoretical, experimental, questionnaire-based, interview-based, or anecdotal);
+ - Analysis design and perspective (e.g., theoretical, experimental, questionnaire-based, interview-based, ethnographic, or computational);
  - Quality of measurement (high vs. low; low quality less likely to detect statistical significance);
@@
  - Operationalization (e.g., concerns vs. risk perceptions vs. behavioral attitudes; the more specific, the stronger the relation).
-
-We emphasize that when analyzing the privacy paradox we are likely dealing with small effects [@baruhOnlinePrivacyConcerns2017].
-Hence, to detect these small effects reliably we need large samples. 
-This is often not the case [@baruhOnlinePrivacyConcerns2017].
-In conclusion, it is crucial to use statistical designs that allow for sufficient statistical power.
 
@@
 
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
 <div id="refs"></div>

### 2021-03-16 title_page.RmD
- update for NM&S submission

---
title             : "Analyzing the Privacy Paradox Using a Nationally Representative Three-Wave Panel Study" 
shorttitle        : "Analyzing the Privacy Paradox"
author:            
  - name          : "Tobias Dienlin"
    email         : "tobias.dienlin@univie.ac.at"
    affiliation   : "1"
    address       : "University of Vienna, Department of Communication, 1090 Vienna, Austria"
    corresponding : yes
  - name          : "Philipp K. Masur"
    affiliation   : "2"
  - name          : "Sabine Trepte"
    affiliation   : "3"
affiliation:
  - id            : "1"
    institution   : "University of Vienna"
  - id            : "2"
    institution   : "VU Amsterdam"
  - id            : "3"
    institution   : "University of Hohenheim"
authornote: |
  All authors contributed extensively to the work presented in this paper. TD, PM, & ST designed the study; PM supervised the data collection; PM administered the data importation; TD & PM wrote the code, ran the models, and analyzed the output data; TD wrote most parts of manuscript, and PM & ST contributed individual sections and comments; ST supervised the project and wrote the grant application (in 2012). 
  The authors declare no competing interests.
  This research was funded by the German Federal Ministry of Education and Research (BMBF) Grant 16KIS0094, awarded to Sabine Trepte.

  This manuscript features a companion website that includes detailed summaries of the statistical results, the code, additional analyses, and a reproducible version of the manuscript (https://xmtra.github.io/privacy-paradox/). The data can be downloaded from http://dx.doi.org/10.7802/1937. 
keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
lang              : "english"
class             : "man"
mask              : no
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
editor_options: 
  chunk_output_type: inline
---
```{r knitr-set-up, include=F}
knitr::opts_chunk$set(echo=F, error=F, message=F, tidy=T, warning=F)
```

```{r load-data, include=F, cache=T}
# Load Workspace
load("data/workspace.RData")
```

### 2021-03-16 manuscript.RmD
- updated URL

@@
 # to compile as pdf
-# (a) move file "_site.yml" to folder "tmp"
+# (a) move file "_site.yml" to folder "archive"
 # (b) uncomment the following lines until incl. "\raggedbottom"
@@
 For the analyses, we used `r r_citations`.
-The code, additional analyses (e.g., ICCs or analyses of invariance), and a reproducible version of this manuscript can be found on the manuscript's companion website at https://xmtra.github.io/privacy-paradox.
+The code, additional analyses (e.g., ICCs or analyses of invariance), and a reproducible version of this manuscript can be found on the manuscript's companion website at https://tdienlin.github.io/privacy-paradox-longitudinal/.
 

### 2021-05-26 manuscript.RmD
- last minor edits after checking proofs

@@
 # (c) comment lines after "output: html_document ..."
-output            : papaja::apa6_pdf
-header-includes:
-  - \setlength{\parskip}{0em}
-  - \raggedbottom
-# output:
-#   html_document:
-#     toc: TRUE
-#     toc_float:
-#       collapsed: FALSE
-#     toc_depth: 2
+# output            : papaja::apa6_pdf
+# header-includes:
+#   - \setlength{\parskip}{0em}
+#   - \raggedbottom
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+    toc_depth: 2
 bibliography      : 
@@
 The privacy paradox, however, implies a causal perspective:
-Does a person, if _he or she_ becomes more concerned about online privacy, then also share less personal information?
+Does a person, if _they_ become more concerned about online privacy, then also share less personal information?
 This mismatch is problematic because although between-person relations are, except for some special cases, a _necessary_ condition for causal within-person effects, they are by no means a _sufficient_ one.
@@
 Three years later, @barnesPrivacyParadoxSocial2006 discussed the behavior of young people on SNSs, popularizing the term _privacy paradox_. 
-Barnes listed six aspects of online behavior that she considered to be particularly paradoxical: (a) illusion of privacy, (b) high quantity of information sharing, (c) attitude behavior discrepancy, (d) lack of privacy concerns, (e) lack of privacy literacy, and (f) fabrication of false information.
+Barnes considered the following six aspects of online behavior particularly paradoxical: (a) illusion of privacy, (b) high quantity of information sharing, (c) attitude behavior discrepancy, (d) lack of privacy concerns, (e) lack of privacy literacy, and (f) fabrication of false information.
 @norbergPrivacyParadoxPersonal2007 were one of the first to empirically analyze the privacy paradox explicitly.
@@
 As a theoretical construct, privacy concerns can hence be categorized as an affective motivational disposition.
-Taken together, concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened.
+Taken together, concerns about online privacy represent how much an individual is motivated to focus on their control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that their privacy might be threatened.
 
@@
 Communication is broad, because it comprises all verbal and nonverbal information that is emitted [e.g., @watzlawickPragmaticsHumanCommunication2011].
-Self-disclosure is more narrow, because it focuses on deliberate revelations about the true self to others, which including aspects such as personal fears, values, or plans [e.g., @jourardTransparentSelf1964].
+Self-disclosure is more narrow, because it focuses on deliberate revelations about the true self to others, including aspects such as personal fears, values, or plans [e.g., @jourardTransparentSelf1964].
 Information sharing is even more specific, because it addresses only person-related information,  including information about their age, sex, name, address, health, and finances.
@@
 In other words, users often prioritize social support, special offers, or improved services, accepting that their privacy will be diminished.
-Sometimes, privacy concerns do not relate information sharing, because users lack the skills, knowledge, or literacy to change their online behavior, creating feelings of apathy or cynicism [@hargittaiWhatCanReally2016; @hoffmannPrivacyCynicismNew2016].
+Sometimes, privacy concerns do not relate to information sharing, because users lack the skills, knowledge, or literacy to change their online behavior, creating feelings of apathy or cynicism [@hargittaiWhatCanReally2016; @hoffmannPrivacyCynicismNew2016].
 Likewise, personal information is also often shared by others, a phenomenon described as "networked privacy" [@marwickNetworkedPrivacyHow2014], which further reduces the power of individuals to determine how much personal information can be found online.
@@
 This tenet is particularly relevant for the privacy paradox: 
-Detecting statistical significance for small effects---and, again, we should expect to find small effects---is more challenging because it means that large samples are necessary to guarantee sufficient statistical power.[^power]
+Detecting statistical significance for small effects---and, again, we should expect to find small or moderate effects---is more challenging because it means that large samples are necessary to guarantee sufficient statistical power.[^power]
 Precisely, in order to be capable of detecting a correlation between privacy concerns and information sharing in 95% of all cases, which @baruhOnlinePrivacyConcerns2017 estimated to be _r_ = -.13, we need a sample of _N_ = `r pwr.r.test(r = -.13, sig.level = .05, power = .95)$n %>%  round(0)` people.
@@
 With Hypothesis 2, we compare _specific_ measurements within the _same_ person.
-In other words, does a person, if he/she is more concerned on T1 than on average, share more or less information on T1 than on average?
+In other words, does a person, if they are more concerned on T1 than on average, share more or less information on T1 than on average?
 
@@
 First, when analyzing potential long-term effects, it is important to choose an interval that is both plausible and relevant.
-(It makes a large difference whether the effects of alcohol consumption on driving performance are tested after say 1 minute, 1 hour, or 1 day.) 
+It makes a large difference whether the effects of alcohol consumption on driving performance are tested after say 1 minute, 1 hour, or 1 day. 
 One factor that determines an interval's optimal length is the stability of the variables [@dormannOptimalTimeLags2015].
@@
 This study is part of a large-scale project which investigates the development of privacy and self-disclosure, including several other variables. 
-Other publications linked to the project can be accessed at [link blinded during review].
+Other publications linked to the project can be accessed at https://osf.io/y35as/.
 The data come from a longitudinal paper-and-pencil questionnaire study, in which a representative sample of the German population (16 years and older) was surveyed on overall five occasions.
-The data can be downloaded from [link blinded during review].
+The data can be downloaded from https://doi.org/10.7802/1937.
 
@@
 Graphical displays of the variables' distributions showed that privacy concerns were skewed to the left, privacy attitudes were normally distributed, and information sharing was skewed to the right (Figure \@ref(fig:Distributions), diagonal).
-We calculated intra-class correlation coefficients to quantify how much variance in the variables' factor scores could be attributed to between-person differences.
-An English translation of the original German items can be found in the OSM.
+We calculated intraclass correlation coefficients (ICCs) to quantify how much variance in the variables' factor scores could be attributed to between-person differences.
+An English translation of the original German items can be found in the online supplementary material.
 
@@
 
-```{r RICLPM, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM).", fig.align="center"}
+```{r RICLPM, fig.cap="The estimated random-intercept cross-lagged panel model (RI-CLPM).", fig.align="center"}
 knitr::include_graphics("figures/model_7.png")
@@
 
- - Context (e.g., professional, social, commercial, or health-related);
- - Situation (e.g., new, habitualized, or unexpected);
- - Mood (e.g., positive vs. negative);
- - Extent of control (high vs. low);
- - Type of information processing applied (implicit, heuristic, or peripheral vs. explicit, analytic, or central);
- - Existence of bias (e.g., overconfidence, optimism, comparative optimism, or hyperbolic discounting);
- - Type of information (e.g., sensitive vs. superficial, biographic, or person-related);
- - Benefit immediacy and risk diffusion (high vs. low);
- - Object of investigation (e.g., individual people, interactions between people, developmental perspectives, critical incidents, societal structures, or historical developments).
+ - context (e.g., professional, social, commercial, or health-related);
+ - situation (e.g., new, habitualized, or unexpected);
+ - mood (e.g., positive vs. negative);
+ - extent of control (high vs. low);
+ - type of information processing applied (implicit, heuristic, or peripheral vs. explicit, analytic, or central);
+ - existence of bias (e.g., overconfidence, optimism, comparative optimism, or hyperbolic discounting);
+ - type of information (e.g., sensitive vs. superficial, biographic, or person-related);
+ - benefit immediacy and risk diffusion (high vs. low);
+ - object of investigation (e.g., individual people, interactions between people, developmental perspectives, critical incidents, societal structures, or historical developments).
 
@@
 
- - Analysis design and perspective (e.g., theoretical, experimental, questionnaire-based, interview-based, ethnographic, or computational);
- - Quality of measurement (high vs. low; low quality less likely to detect statistical significance);
- - Sample size (small vs. large; small samples less likely to detect statistical significance);
- - Statistical analysis (e.g., SEM vs. Regression; analyses without error control less likely to find statistical significance);
- - Operationalization (e.g., concerns vs. risk perceptions vs. behavioral attitudes; the more specific, the stronger the relation).
+ - analysis design and perspective (e.g., theoretical, experimental, questionnaire-based, interview-based, ethnographic, or computational);
+ - quality of measurement (high vs. low; low quality less likely to detect statistical significance);
+ - sample size (small vs. large; small samples less likely to detect statistical significance);
+ - statistical analysis (e.g., SEM vs. Regression; analyses without error control less likely to find statistical significance);
+ - operationalization (e.g., concerns vs. risk perceptions vs. behavioral attitudes; the more specific, the stronger the relation).
 

### 2021-05-26 data/data_wrangling.R

@@ -3,9 +3,14 @@ library(DataCombine); library(magrittr); library(tidyverse)
 
 # load data
 # note: the actual data can be obtained from http://dx.doi.org/10.7802/1937
-# please download the most current file "privacy-longitudinal-study_data_YYYY-MM-DD.csv"
 # paste this file into folder "data"
 d_raw <- read_csv("data/privacy-longitudinal-study_data_2019-10-10.csv")
+
+# Please note that during the submission process of this article, 
+# a newer version of the data set was published (https://doi.org/10.7802/2117). 
+# The new dataset contains additional data of participants that initially 
+# were lost because of a transmission error. Using this newer version yields to 
+# the same inferences and comparable results, with changes only in decimals
 
 # select variables
 d_wide <- d_raw %>%

### 2023-11-15 manuscript.RmD
- removed table of contents

@@
 #   - \raggedbottom
-output:
-  html_document:
-    toc: TRUE
-    toc_float:
-      collapsed: FALSE
-    toc_depth: 2
+output: html_document
+#  output:
+#  html_document:
+    # toc: TRUE
+    # toc_float:
+    #   collapsed: FALSE
+    # toc_depth: 2
 bibliography      : 
